### 2023-10-14 NovelLBM.tex
Squash large files
initial commit
some PTT
alginate data
Data rename
alginate done
methyl cellulose
Literature and Method
validation theory
PTT derivation
malaspinas comparison
malaspinas
validation wip
shuffle fraction dependency
Wi Dependency
2D poiseuille
Create fig:ptt_N.py
3D poiseuille
fix PTT
RT-DC
Update .gitignore

\documentclass[a4paper,12pt]{scrartcl}
\usepackage[american]{babel} % default is american but allow for cyrillic text via \textcyrillic{...}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage[toc, page]{appendix}
\usepackage{float} %better image positions
\DeclareUnicodeCharacter{2212}{-} %Mathplotlib uses 2212 instead of -
\usepackage{adjustbox} %Adjust boxed content
\usepackage{graphicx} %graphics support
% \usepackage{svg} % only works with inkscape shell scirpt as dependency (convert to eps instead) move to pdf
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{sidecap}

\usepackage{hyperref} %link support
\usepackage{pdflscape} %pages can be landscape
\usepackage{colortbl} %colored table rows and columns

\usepackage[
backend=bibtex,
citestyle=numeric-comp,
maxbibnames=10,
sorting=none
]{biblatex}
\addbibresource{assets/bib/bib.bib}

\usepackage{todonotes}

\usepackage[locale=US]{siunitx}
\sisetup{per-mode=fraction}
\sisetup{separate-uncertainty=true}

\usepackage{pythonhighlightRK} % provides python environment

\setlength\parindent{0pt}

%\newcommand{\mover}[2]{\pdfmarkupcomment[color=yellow, markup=Highlight]{#1}{#2}}
\newcommand{\parab}[1]{\paragraph{#1}\mbox{}\newline}
\newcommand{\n}{\newline}
\newcommand{\abs}[1]{\lvert#1\rvert}
\newcommand{\vecColumn}[1]{\begin{pmatrix}#1\end{pmatrix}}

\usepackage{bbm} % provides unit tensor via \mathbbm{1}
\newcommand{\ma}[1]{\underline{#1}}
\newcommand{\uT}{\mathbbm{1}}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\dif}{d}
\DeclareMathOperator{\Dif}{D}

\definecolor{background}{RGB}{51,51,51} % Because i can lol
\definecolor{secondaryBackground}{RGB}{60,60,60} % Because i can lol
\usepackage[enable=true]{darkmode}
\pagecolor{background}

\title{Novel lattice Boltzmann method for simulation of strongly shear thinning viscoelastic fluids}
\author{Richard Kellnberger$^1$}
\date{October, 2023}
\begin{document}
	\maketitle

	\begin{center}
		$^1$ Biofluid Simulation and Modeling – Theoretische Physik VI, University of Bayreuth, Bayreuth, Germany
	\end{center}
	\vspace{\fill}
	\begin{center}
		%TODO abstact
	\end{center}
	%TODO keywords

	\newpage
	\null
	\newpage

	\tableofcontents

	\newpage

	\section{Introduction}
	\todo{do}

	\section{Rheology of viscoelastic fluids}
	Viscoelastic behavior in fluids was first discovered during the second world war when mixing flamethrower liquid\cite{franck2017}. Since then many models have been derived to describe the different effects exhibited by this class of material. In general the stress exhibited by these fluids is not only dependent on the current shear, but is also time-dependent. This complex behavior can often be decoupled into a shear dependent viscosity and a normal stress. These can be for the most part understood separately. The viscosity usually exhibits shear thinning behavior. This behavior is well understood because it has many technical applications and is a common side effect of increasing the viscosity of fluids which is also often desired. Therefore, there exist many phenomenological descriptions of shear thinning. A particularly general one is the Carreau-Yasuda model. It will be discussed in the following to illustrate qualitatively how such fluids behave. The elastic components will be discussed afterward.
	\subsection{Carreau-Yasuda - phenomenological description for shear thinning viscosity}
	In Yasudas 1979 PhD-Thesis\cite{yasuda1979} the earlier Carreau model\cite{carreau1972} was extended to describe the shear thinning behavior of polymers and polymer solutions for many parameters. The viscosity $\eta$ decreases with the shear rate $\dot{\gamma}$ as follows.
	\begin{equation}
		\eta\left(\dot{\gamma}\right) = \eta_\infty + \frac{\eta_0 - \eta_\infty}{\left[1+\left(\lambda\dot{\gamma}\right)^{a_1}\right]^\frac{a_2}{a_1}}
	\end{equation}
	Here $\eta_0$ is the zero shear viscosity, $\eta_\infty$ is the infinite shear viscosity, $\lambda$ is the relaxation time and $a_1$ and $a_2$ are parameters in regard to the slope. As can be seen in figure \ref{fig:CY}, the Carreau-Yasuda model describes two plateaus of constant viscosity ($\eta_0$ and $\eta_\infty$) connected by a $Wi^{-a_2}$ power law. $a_1$ governs how gradual the connection between the initial plateau and the power law is. Here the Weissenberg number $Wi = \lambda\dot{\gamma}$ has been introduced. The start of the actual thinning is around $Wi = 1$. Values below are often considered \glqq small\grqq{ } Weissenber numbers, while the ones above are considered \glqq large\grqq. The onset of the second plateau depends on a material parameter, which we term the viscosity ratio and define as follows.
	\begin{equation}\label{eq:R_eta_CY}
		R_\eta = \frac{\eta_0 - \eta_\infty}{\eta_\infty}
	\end{equation}
	As will be shown later, this is actually a crucial stability parameter for the simulations. This means, that the widely available parameters obtained by fitting this phenomenological model are sufficient to predict the stability of simulations. However, to actually simulate viscoelastic fluids, a model es required, that predicts a viscosity similar to the one shown here, and the normal stress exhibited by such fluids. This will be discussed in the following section.
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/CY.eps}
		\caption{Double logarithmic plot of the Carreau-Yasuda model for different $a_1$.}
		\label{fig:CY}
	\end{figure}
	\subsection{Constitutive equations for the polymer stress}
	Both the viscosity and the normal stress can be viewed as components of a stress tensor. For some linear viscoelastic liquids simulations without modeling the constitutive equation of this tensor are possible using a slightly modified lattice Boltzmann method\cite{giraud1998,lallemand2003}. More general cases have used elastic dumbbells to model the polymers typically contained in viscoelastic fluids. The first of which was the Oldroyd-B model introduced in 1958\cite{oldroyd1958}. Also, it does not reproduce all effects shown by viscoelastic fluids (critically it is not shear thinning), it is still the most popular model today due to its simplicity. In elongational flow, the dumbbells modeled by Oldroyd-B can be stretched infinitely, leading to unphysical behavior. To avoid this the finite extensible FENE-P model was developed by Bird et al.\cite{bird1980,bird1987}. This model is also particularly popular, but we found it to be problematic, as fitting it to rheological data for some of the materials we work with results in unphysical parameters. Furthermore, using it is detrimental for stability, especially for high Weissenberg numbers (for details see appendix \ref{app:FENE-P}). There also exist many other derived or extended FENE type models one could choose from. Oliveira showed, that many of them follow a common formalism\cite{oliveira2009} and can be brought to a common form despite looking quite different in their original formulation. Among this group of models is also the Phan-Thien Tanner (PTT) model\cite{phan-thien1977,phan-thien1978}. It was originally derived for polymer networks in solution, but also fits well with the fluids we use. As these models all have similar mathematical forms and produce similar shapes, the physical background likely does not matter much. There exists an exponential version and a more general form of the PTT model using the gamma function\cite{ferras2019}. As our simulations algorithm is GPU based, using the more general form would necessitate the implementation of the gamma function incurring segnificant computational cost for limited gain. Therefore, we opted for the exponential version. For this the constitutive equation for the stress reads as follows.
	\begin{equation}
		\overset{\nabla}{\ma{\tau}} = -\xi\left(\ma{\tau}\cdot\ma{D} + \ma{D}\cdot\ma{\tau}\right) - e^{\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}}\frac{\ma{\tau}}{\lambda} + 2\frac{\eta_\text{p}}{\lambda}\ma{D}
	\end{equation}
	Here, $\ma{\tau}$ is the polymer stress tensor and $\ma{D}$ is the strain rate tensor. $\eta_\text{p}$ is the polymer viscosity and $\lambda$ is the relaxation time. $\epsilon$ is the extensibility parameter and $\xi$ describes the slip in the polymer network. This model uses the upper convected derivative, which is defined as follows.\todo{clarify nabla u and fix Ts}
	\begin{equation}
		\overset{\nabla}{\ma{A}} = \frac{\Dif\ma{A}}{\Dif t} - \left(\left(\nabla\vec{u}\right)^\text{T}\cdot\ma{A} + \ma{A}\cdot\left(\nabla\vec{u}\right)\right)
	\end{equation}
	Where $\vec{u}$ is the fluid velocity. This equation contains the material derivative defined as follows.
	\begin{equation}
		\frac{\Dif\ma{A}}{\Dif t} = \frac{\partial\ma{A}}{\partial t} + \vec{u}\cdot\nabla\ma{A}
	\end{equation}
	The semi analytical solution reads as follows\cite{ferras2019}.
	\begin{equation}
		\exp\left[\frac{\epsilon\lambda}{\eta_\text{p}}\left(\frac{2-2\xi}{2-\xi}\right)\tau_{xx}\right]^2\tau_{xx}=\left(2-\xi\right)\left(\lambda\dot{\gamma}\right)^2\left(\frac{\eta_\text{p}}{\lambda} - \tau_{xx}\xi\right)
	\end{equation}
	\begin{equation}
		\tau_{xy}\left(\dot{\gamma}\right) = \frac{\eta_\text{p}\dot{\gamma}-\tau_{xx}Wi\xi}{\exp\left[\frac{\epsilon\lambda}{\eta_\text{p}}\left(\frac{2-2\xi}{2-\xi}\right)\tau_{xx}\right]}
	\end{equation}
	\begin{equation}
		\eta\left(\dot{\gamma}\right) = \frac{\tau_{xy}\left(\dot{\gamma}\right)}{\dot{\gamma}}
	\end{equation}
	\begin{equation}
		N_1 = \frac{2\tau_{xx}}{2-\xi}
	\end{equation}
	Where $N_1$ is the first normal stress difference.

	The shear dependent viscosity in this model can be seen in figure \ref{fig:ptt_eta}. One can see a Newtonian plateau and a $Wi{-1}$ power law. Other constitutive equations lead to other power laws. Therefore, one can pick a model, that fits the data best. The parameter $\epsilon$ controls the $Wi$ at which thinning takes place. Compared to the phenomenological CY model, PTT does not have a minimum viscosity and keeps trending towards zero. This is unphysical and current lattice Boltzmann methods require a viscosity to be present. This is remedied by adding an offset $\eta_\text{s}$ to the viscosity. The resulting curve can be seen in figure \ref{fig:ptt_eta_s}. The resulting curve is very similar to the CY model and thus is also suited to describe many different viscoelastic liquids. Furthermore, this allows to see some similarities. The $\eta_\text{s}$ parameter is equivalent to $\eta_\infty$ and $\eta_\text{p} + \eta_\text{s} = \eta_0$. With this the viscosity ratio defined in equation \ref{eq:R_eta_CY} can be rewritten with these parameters as follows.
	\begin{equation}\label{eq:R_eta_ptt}
		R_\eta = \frac{\eta_\text{p}}{\eta_\text{s}}
	\end{equation}
	The index p expresses the viscosity from polymers, while the s means viscosity from solvent. This alleges, that the viscosity for infinite shear becomes the solvent viscosity. This however is not entirely accurate in general. That being said, the exact value of $\eta_\text{s}$ is not relevant given $Wi$ is low enough, which it often is. Given, that data is rarely available at shear rates high enough to determine $\eta_\text{s}$ reliably, due to technical difficulties, it can usually not be determined from data. Therefore, it is common to just use the solvent viscosity.
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/ptt_eta.eps}
		\caption{Double logarithmic plot of the PTT model for $\xi=0$ and different $\epsilon$.}
		\label{fig:ptt_eta}
	\end{figure}
		\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/ptt_eta_s.eps}
		\caption{Double logarithmic plot of the PTT model for $\xi=0$ and different $\epsilon$ with an offset.}
		\label{fig:ptt_eta_s}
	\end{figure}
	For the polymers solutions we work with, $\xi$ is effectively zero, as can be suspected from its physical interpretation. Therefore, we set it to zero for the rest of this work. This also simplifies the model significantly and allows it to be solved analytically using the Lambert $W$ function. In the following we show fits for several viscoelastic fluids, to show, that PTT does fit and to establish an expected range for the parameters.
	\subsection{Fitting PTT to experimental data}
	For $\xi = 0$ and using the Lambert $W$ function, the solutions for PTT are as follows.
	\begin{equation}
		\eta\left(\dot{\gamma}\right) = \frac{\eta_\text{p}}{\exp\left[0.5W_0\left(4\epsilon Wi^2\right)\right]}
	\end{equation}
	\begin{equation}
		N_1 = \frac{\eta_\text{p}}{2\epsilon\lambda}W_0\left(4\epsilon Wi^2\right)
	\end{equation}
	From this, one can see, that it is not sufficient to fit the viscosity as it could be formulated using two parameters ($\eta_\text{p}$ and $\epsilon\lambda^2$). Therefore, it has to many parameters and the fit has a one dimensional solution space.
	The same holds for $N_1$ using $\eta_\text{p}\lambda$ and $\epsilon\lambda^2$. Therefore, it is necessary to fit both curves at the same time. This is not a unique feature of PTT, it is also the case for e.g. FENE-P (see appendix \ref{app:FENE-P}). In the following we show the fit results for an Alginate solution, for several concentrations of methyl cellulose solution and for a few other fluids.
	\subsubsection{Alginate}
	Alginate solutions are very important as bioinks or as scaffolding in the field of biofabrication. Alginate is also a common food additive. The solutions used here are \SI{4}{\percent} by weight of DuPont VIVAPHARM Alginate PH176 in PBS (essentially water)\todo{cite email from Tomasz Jüngst from 23.03.2023?}. The solution were prepared and measured by the Group of Tomasz Jüngst\todo{cite properly}. The measurements were done using a plate-plate rheometer. The first normal stress difference $N_1$ was calculated from the measured normal force using the following equation\cite{kulicke1977}.\todo{data so far does not include second correction term; needed info: was this plate plate? where is shear rate in PP rheometer? we claim $N_2$ is 0, therefore PP is fine, but we would really prefer CP}\todo{confirm diameter}
	\begin{equation}
		N_1 = \frac{2F}{\pi R^2} + \frac{3}{20}\rho\omega^2R^2
	\end{equation}
	Where $F$ is the measured normal force, $R$ is the radius of the rheometer, $\rho$ is the density of the fluid and $\omega$ is the angular velocity of the rheometer.

	The data for viscosity and first normal stress difference was fitted simultaneously for all 21 individual measurements in the dataset. The results can be seen in figures \ref{fig:fit_alginate_eta} and \ref{fig:fit_alginate_N}. The steps that can be seen in the plot of the first normal stress difference are due to the limited resolution of the rheometer used. It can be seen, that the data varies significantly, due to variations on preparation and/or measurement. The fit does not reproduce the shape perfectly but does always stay within the variation of the data. This is sufficient. While setting $\eta_\text{s} = \SI{1}{\milli\pascal\second}$, the parameters obtained are as follows.\todo{subject to change; different than before!!}
	\begin{align}
		\eta_\text{p} &= \SI{48.2\pm0.4}{\pascal\second}\\
		\lambda &= \SI{0.343 \pm 0.004}{\second}\\
		\epsilon &= \num{0.545 \pm 0.010}
	\end{align}
	With this the viscosity ratio becomes $R_\eta = \num{48.2\pm0.4e3}$. However, this carries the assumption of $\eta_\text{s}$. Strictly from the data, we can only specify $R_\eta > 70$, using $\eta_\text{s} < \min\left(\eta\right)$. Given, the data shows no sign of flattening the actual value of $R_\eta$ is significantly higher than $70$.

	These parameters (predominately $\eta_\text{p}$) are dependent on concentration. This will be shown in the next section with the example of methyl cellulose.
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/fit_alginate_eta.eps}
		\caption{Double logarithmic plot of 21 measurements of the viscosity of an alginate solution and a PTT fit.}
		\label{fig:fit_alginate_eta}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/fit_alginate_N.eps}
		\caption{Double logarithmic plot of 21 measurements of the normal force (converted to stress) of an alginate solution and a PTT fit.}
		\label{fig:fit_alginate_N}
	\end{figure}
	\subsubsection{Methyl cellulose}
	Methyl cellulose is also used in research involving cells as a nontoxic thickening agent. It is also widely used in the food industry. The data used here\cite{buyukurganci2023}, was measured using plate-plate and cone-plate rheometer geometry. The three solutions measured are \SI{0.49}{\percent}, \SI{0.59}{\percent} and \SI{0.83}{\percent} methyl cellulose in PBS. The measured data as well as the fit results can be seen in figures \ref{fig:fit_mc_eta} and \ref{fig:fit_mc_N}. One can see, that while PTT is not the optimal model for this solution, the agreement is still acceptable. The fit gives the following parameters.
	\begin{center}
		\begin{tabular}{c|c|c|c}
			Concentration/\unit{\percent} & $\eta_\text{p}/\unit{\milli\pascal\second}$ & $\lambda/\unit{\milli\second}$ & $\epsilon$ \\
			\hline
			\num{0.49} & \num{18.7\pm0.4} & \num{0.344\pm0.003} & \num{0.270\pm0.003} \\
			\num{0.59} & \num{32.5\pm0.7} & \num{0.433\pm0.004} & \num{0.365\pm0.004} \\
			\num{0.83} & \num{81\pm2} & \num{0.714\pm0.009} & \num{0.496\pm0.006}
		\end{tabular}
	\end{center}
	From the derivation of the model it would be expected, that only $\eta_\text{p}$ scales with the concentration. However, all the parameter show a significant dependency on concentration. $R_\eta$ can be approximated from the data as $R_\eta > 3$, $R_\eta > 4$ and $R_\eta > 9$ for \SI{0.49}{\percent}, \SI{0.59}{\percent} and \SI{0.83}{\percent} receptively. They again are likely much higher. The expected values based on the assumed $\eta_\text{s}$ are $R_\eta = \num{18.7\pm0.4}$, $R_\eta = \num{32.5\pm0.7}$ and $R_\eta = \num{81\pm2}$ respectively.
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/fit_mc_eta.eps}
		\caption{Double logarithmic plot of measurements of the viscosity of three methyl cellulose solutions and a PTT fit.}
		\label{fig:fit_mc_eta}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/fit_mc_N.eps}
		\caption{Double logarithmic plot of measurements of the normal force (converted to stress) of three methyl cellulose solutions and a PTT fit.}
		\label{fig:fit_mc_N}
	\end{figure}
	\subsubsection{Other fluids}
	\todo{mostly mention $R_\eta$ for different fluids}
	\todo{do}
	With the usual range of the parameters and $R_\eta$ established, we provide a quick overview about the current literature and capabilities in the following section.

	\section{Existing LBM methods}
	There are many existing LBM methods to simulate viscoelastic materials in three dimensions. Some simple linear viscoelastic effects can be described through multi-relaxation-time models \cite{lallemand2003}, but in general more complicated methods are required. For more general cases the solving of a second equation is required. There are several options for the equation describing the polymer. Among these are the constitutive equation\cite{gupta2015} and a Fokker-Planck equation\cite{onishi2005}. Solving these equations can be done through multiple ways. These include a finite volume solver, a finite difference solver\cite{gupta2015}, another LBM like solver\cite{ma2020} and an advection-diffusion scheme\cite{onishi2005}. These secondary solvers need to be coupled to the primary LBM solver. Options to do that include introducing an additional forcing term to the LBM and altering the LBM stress directly\cite{dzanic2022}.

	Among the publications implementing a constitutive equation most use Oldroyd-B or older models. Many also use FENE-P despite its shortcomings. The PTT model, which is currently the model used by us is rarely employed, though many authors do mention it.

	While these options lead to wide range of different coupled solvers, the results are similar. Some authors note, that the Weissenberg number could be extremely high using their scheme\cite{malaspinas2010}, the simulations actually presented in the publications usually only go up to $Wi = 10$\cite{malaspinas2010,su2013_2} or $Wi = 100$\cite{gupta2015,ma2020,gupta2016}. As can be seen in figure \ref{fig:ptt_eta_s} above, $Wi \leq 100$ covers most of the range already, and it seems plausible, that current capabilities cover most of not all experiments in this regard.

	However, another stability criterion, which only some others mention is the viscosity ratio. Its definition in literature varies significantly. We use equation \ref{eq:R_eta_ptt} whenever possible. For some publications we have to estimate it using data extracted from plots and equation \ref{eq:R_eta_CY}. Publications often stay at or below $R_\eta = 1$\cite{gupta2015,onishi2006,wang2020,su2013_2,gupta2015_2}, while the ones trying higher ratios report being limited below $R_\eta = 10$\cite{malaspinas2010,ma2020,kuron2021} due to stability issues. There are several options being explored in the literature to increase stability. The most prominent among them is the inclusion of an artificial diffusivity, which introduces a small error compared to the analytical solution of th constitutive equation. All of these ultimately fail to extend the range of stable viscosity ratios significantly. This means, that for the existing simulation approaches, the zero shear viscosity and the infinite shear viscosity are similar, which is only sufficient for very dilute solutions. The methods currently available do not allow the simulation of the real fluids mentioned before. Therefore, we developed a new method capable of much higher viscosity ratios. This novel approach will be discussed in the following section.

	\section{Numerical method}
	Our numerical consists of several well known methods and our novel viscosity shuffling. In the following we provide a brief overview about the well known basics and an in depth explanation of our novel method.
	\subsection{Basics}
	To solve the fluid we use a lattice Boltzmann algorithm with a single relaxation time. One could also use multi relaxation time, but we found the benefit to be negligible. For the velocity set we use D3Q19 as D3Q27 did not provide significant benefit for us but increases computational cost significantly. We solve the constitutive equation with a finite volume solver. This simplifies the boundary conditions significantly as we set the stress flux through the walls to zero. The advection term in the constitutive equation is handled with the corner transport upwind scheme. The source terms are integrated using the Euler method. The exact implemented and its derivation can be found in appendix \ref{app:implementation}. The coupling to the main lattice Boltzmann solver happens using the stress directly according to Dzanic et al.\cite{dzanic2022_2}. However, we modify the coupled stress as is explained in the following.
	\subsection{Novel viscosity shuffling}
	Performing Chapman-Enskog analysis on the LBM reveals the total stress experienced by the fluid ($\ma{\sigma}$) to be as follows\cite{onishi2006}.
	\begin{align}
		\ma{\sigma} &= 2\eta_\text{s}\ma{D} + \ma{\tau}
		\intertext{We now add a zero.}
		&= 2\eta_\text{s}\ma{D} + \ma{\tau}_\text{shuffle} + \ma{\tau} - \ma{\tau}_\text{shuffle}
		\intertext{With $\ma{\tau}_\text{shuffle} = 2\alpha_\text{s}\eta_\text{p}\ma{D}$}
		&= 2\left(\eta_\text{s} + \alpha_\text{s}\eta_\text{p}\right)\ma{D} + \left(\ma{\tau} - 2\alpha_\text{s}\eta_\text{p}\ma{D}\right)
	\end{align}
	With this new parameter $\alpha_\text{s}$ we can shuffle an arbitrary amount of viscosity around, as we use $\eta_\text{s} + \alpha_\text{s}\eta_\text{p}$ as the viscosity in the LBM algorithm, and the stress calculated via the constitutive equation gets a relatively simple offset applied to it before being included in the LBM. This allows for the first time to our knowledge to pick $\eta_\text{s} = 0$. This allows for accurate comparisons to the analytical solutions of the constitutive equation, as these usually do not include $\eta_\text{s}$. Furthermore, instead of using artificial diffusivity to stabilize the simulation or employing any other artificial remedy, this scheme allows to not modify the parameters and to simulate the exact physical system that is desired. The reason for the instability is, simply speaking, that the polymer contribution overpowers the LBM stress. This can be compared to the inclusion of very large forces, which cause some equilibrium populations to become negative resulting in the LBM become unstable. The viscosity shuffling allows us to increase the LBM stress while decreasing the polymer contribution. This shifts the balance towards stability. Crucially, this happens without altering the physical system simulated. In terms of stability, we could define an effective $R_\eta$, calculated from the stress contributions as follows.
	\begin{equation}
		R_{\eta\text{, eff}} = \frac{\eta_\text{p}-\alpha_\text{s}\eta_\text{p}}{\eta_\text{s} + \alpha_\text{s}\eta_\text{p}} = \frac{1-\alpha_\text{s}}{\frac{\eta_\text{s}}{\eta_\text{p}} + \alpha_\text{s}} = \frac{1-\alpha_\text{s}}{1 + \alpha_\text{s}R_{\eta}}R_{\eta} \overset{\alpha_\text{s}R_{\eta}\gg1}{=} \frac{1-\alpha_\text{s}}{\alpha_\text{s}}
	\end{equation}
	Given $\alpha_\text{s}$ is large enough, arbitrary $R_{\eta\text{, eff}}$ can be reached, bringing the simulation within the range, that is stable with current methods, and thus arbitrary $R_{\eta}$ become stable. A trade-off is, that $\alpha_\text{s}$ decreases the time-step. In the following section we validate this novel approach against analytical solutions for realistic parameters. Furthermore, we compare the accuracy of this scheme with literature.

	\section{Validation and comparison}
	To validate the simulations we compare the simulated velocity field of analytically solvable geometries to theory. For pressure gradient driven channel and pipe geometries, the analytical solution is as follows\cite{oliveira1999}.
	\begin{equation}
		u\left(r\right) = \frac{Gl^2}{2^{j+1}\eta_\text{p}}\left(e^\frac{R^2}{l^2}-e^\frac{r^2}{l^2}\right)
	\end{equation}
	Where $u\left(r\right)$ is the radius dependent velocity, $G = -\partial_xp$ is the pressure gradient in the direction of the pipe and $l$ is a constant defined as follows.
	\begin{equation}
	l^2 = \frac{2^{2j-1}\eta_\text{p}^2}{\epsilon\lambda^2G^2}
	\end{equation}
	The index $j$ gives the solution for the channel for $j=0$ and the pipe for $j=1$.

	We need this solution to compare to literature. However, this solution does not include $\eta_\text{s}$, which is required in general. With the inclusion of the solvent viscosity (for details see appendix \ref{app:PTT}), the solution reads as follows.\todo{also wrong}
	\begin{equation}
		u\left(r\right) = \frac{Gl^2}{2^{j+1}\eta_\text{s}}\left[\ln\left(1+\frac{\eta_\text{s}}{\eta_\text{p}}e^\frac{R^2}{l^2}\right)-\ln\left(1+\frac{\eta_\text{s}}{\eta_\text{p}}e^\frac{r^2}{l^2}\right)\right]
	\end{equation}
	In the following we compare results for channel and pipe flow to these equations for realistic parameters. Afterward we compare the accuracy of our simulation algorithm against literature.
	%We use richard/master fe0fc04115b9b6ea6628bcc6cb6593d3f72ac0ea (2023-11-05)
	\subsection{2D Poiseuille vs theory}\todo{rename to channel flow?}\todo{include cylindrical nozzle from conical nozzle sim}

	\subsection{3D Poiseuille vs theory}\todo{rename to pipe flow?}

	\subsection{Comparison with literature}
	Malaspinas et al.\cite{ma2020} provide a detailed validation and claim very high accuracy. Therefore, we pick this as a comparison. We aim at the reproduction of figures 17 and 18 from said paper. We calculate this 2D flow in 3D as the viscoelastic algorithm has not been validated for 2D velocity sets. Otherwise the geometry is identical. It is not entirely clear to us, how they define typical scales. We define the typical velocity as the maximum velocity, as is likely done in the paper. The typical length, we set as half of the channel width. We define the typical shear rate as typical velocity divided by typical length. We set $\eta_\text{s} = \SI{1}{\milli\pascal\second}$ as the paper only gives ratios, and it probably does not matter here. Nevertheless, our lattice units do not line up exactly with those from Malaspinas, as our viscosity is different due to the shuffling.
	%Beware equation 61 in the paper is wrong. It should have an 8 instead of the 4.
	The parameters from the paper ($R_\nu$, $Wi$ and $N$) are varied as in the paper. The error is calculated as follows.
	\begin{equation}\label{eq:l2error}
		E_\text{u} = \frac{1}{u_\text{max}}\sqrt{\frac{1}{N}\sum\abs{u_\text{simulation}-u_\text{theory}}^2}
	\end{equation}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/malaspinas2010.eps}
		\caption{Double logarithmic plot of the L2 error as defined in equation \ref{eq:l2error} from Malaspinas et al.\cite{malaspinas2010} (dots) compared to our algorithm (x) as a function of grid resolution.}
		\label{fig:malaspinas2010}
	\end{figure}
	As can be seen in figure \ref{fig:malaspinas2010}, our results notably do not depend on the Weissenberg Number. While our error decreases with N with a constant power, Malaspinas et al. see diminishing returns. While these results are excellent, the error in our implementation is still dependent on the viscosity ratio. When going to significantly higher ratios, this needs to be checked to ensure it does not get too large.\todo{link to appendix where we validate this}
	With this, one can see, that we are not only capable to simulate parameters not yet accessible, but our implementation is also better for the parameters used in literature. Knowing our simulations to be good we in the following show results for interesting systems, that are not analytically solvable.
	\section{Results for non analytically solvable systems}\todo{do all of these with MC}
	\subsection{Conical nozzle}
	\todo{do}
	\subsection{Cell in shear flow}
	\todo{do}
	\subsection{RT-DC}
	\todo{do}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_v.eps}
		\caption{Plot of the velocity in the RT-DC channel.}
		\label{fig:RT-DC_v}
	\end{figure}
	\begin{figure}[H]
	\centering
	\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_tau.eps}
	\caption{Plot of the polymer stress in the RT-DC channel.}
	\label{fig:RT-DC_tau}
	\end{figure}

	\section{Conclusion}
	\todo{do}

	\newpage
	\printbibliography[heading=bibintoc]

	\appendix
	\appendixpage
	\section{Implementation of constitutive equations}\label{app:implementation}\todo{Note available analytical solutions}
	There is a large amount of viscoelastic models. It is also common to extend these to create new models. As Oliveira shows\cite{oliveira2009} many of these can be expressed to a common form and thus actually are variants of a common idea. This allows both to easily find new models and implement them. In the following polymer contributions $\ma{\tau}$ of the models we have currently implemented are described. For notation, we mostly follow close to Oliveira\cite{oliveira2009}.
	\parab{Implementation}
	The actual implementation uses tensors related to $\tau$ to unify the calculations as much as possible. We denote these tensors as $\ma{A}$ and give the relation for each model. Whenever we explicitly need $\ma{\tau}$, we convert it. For Oldroyd-B this does not seem necessary and might even be slightly detrimental to performance. However, such a replacement simplifies the constitutive equation for FENE-P significantly and doing it for the other models as well allows a unified code with little adaptation for each model. It also makes the equations easier to understand and analyze. We stick with $\ma{A}$ as the Tensor containing the stress information, although its meaning is different for the different models listed here. This way, it can be seen, that all the models listed here can be brought to the common form listed below.\todo{claryfy nabla u and fix Ts}
	\begin{equation}
		\frac{\partial\ma{A}}{\partial t} + \vec{u}\cdot\nabla\ma{A} = \left(\left(\nabla\vec{u}\right)^\text{T}\cdot\ma{A} + \ma{A}\cdot\left(\nabla\vec{u}\right)\right)+\ma{S}_\text{R} + 2\ma{D}
	\end{equation}
	Where $\ma{S}_\text{R}$ is a model-dependent term. In the following only this will be specified as all other terms are the same for all models. The second term on the left-hand side is handled via CTU, the rest is Euler-integrated.

	\subsection{Oldroyd-B}
	This model was originally developed by Oldroyd\cite{oldroyd1958}. The constitutive equation reads as follows.
	\begin{equation}
		\overset{\nabla}{\ma{\tau}} = -\frac{\ma{\tau}}{\lambda} + 2\frac{\eta}{\lambda}\ma{D}
	\end{equation}
	$\lambda$ is the polymer relaxation time and $\eta$ is the polymer viscosity. This viscosity also defines the magnitude of the elastic forces. Both these parameters also appear in the other models. We usually do not use this model, as it is not shear thinning.
	\parab{Implementation}
	\begin{equation}
		\ma{S}_\text{R} = -\frac{\ma{A}}{\lambda}
	\end{equation}
	\begin{equation}
		\ma{\tau} = \frac{\eta}{\lambda}\ma{A}
	\end{equation}

	\subsection{FENE-P}\todo{cite oliveira for theory}\todo{a lot more detail can be found in my dedicated FENE-P repo -> include derivation?}
	This model was originally developed by Bird\cite{bird1980}\cite{bird1987}. It can be viewed as an Extension of the Oldroyd-B by limiting the polymers to finite extensibility. It has particularly many derivatives. Its constitutive equation reads as follows.
	\begin{equation}
		\overset{\nabla}{\ma{\tau}} = -Z\frac{\ma{\tau}}{\lambda} + \left(\ma{\tau}+(1-e b)\frac{\eta}{\lambda}\uT\right)\frac{\Dif\ln Z}{\Dif t} + 2(1-eb)\frac{\eta}{\lambda}\ma{D}
	\end{equation}
	With the extensibility parameter b, $e = \frac{2}{b\left(b + 2\right)}$ and
	\begin{equation}
		Z = 1 + \frac{3}{b}\left(\frac{b}{b + 2}+\frac{\Tr\ma{\tau}}{3\frac{\eta}{\lambda}}\right)
	\end{equation}
	Note, that the sign of $\ma{\tau}$ differs from Birds formulation. Also, the relation $nk_\text{B}\theta = \frac{\eta}{\lambda}$ has already been used to avoid introducing additional parameters. Particularly for large shear rates, it is numerically possible, that the polymer exceeds its maximal extensibility. If it is extended beyond the maximum the equations cause it to extend further, making this model unstable for high shear rates. Even with the decomposition proposed by Dzanic\cite{dzanic2022}, we were not yet able to get it stable. Thus, it is currently unused.
	\parab{Implementation}
	\begin{equation}
		\ma{S}_\text{R} = \frac{\Tr\ma{A}\uT + \left(b + 2\right)\ma{A}}{\lambda\frac{b+2}{b+5}\left(\Tr\ma{A}-b-2\right)}
	\end{equation}
	\begin{equation}
		\ma{\tau} = \frac{\eta}{\lambda}\frac{b}{b+2-\Tr\ma{A}}\left(\ma{A}+\frac{\Tr\ma{A}}{b+2}\uT\right)
	\end{equation}
	This seems complicated, but removes the highly problematic $\frac{\Dif\ln Z}{\Dif t}$ term, which causes issues in implementation details.

	\subsection{PTT}
	Originating from Phan-Thien and Tanner\cite{phan-thien1977} it was soon after slightly extended by Phan-Thien\cite{phan-thien1978} to the exponential form we use. There is also an even more general form from Ferrás\cite{ferras2019}, which due to its use of the Gamma function is hard to implement on GPUs. The constitutive equation reads as follows.
	\begin{equation}
		\overset{\nabla}{\ma{\tau}} = -\xi\left(\ma{\tau}\cdot\ma{D} + \ma{D}\cdot\ma{\tau}\right) - e^{\frac{\epsilon\lambda}{\eta}\Tr\ma{\tau}}\frac{\ma{\tau}}{\lambda} + 2\frac{\eta}{\lambda}\ma{D}
	\end{equation}
	Where $\epsilon$ and $\xi$ are additional parameters related to the network this model is supposed to model. For our polymer solutions $\xi$ is always (effectively) zero.
	\parab{Implementation}
	\begin{equation}
		\ma{S}_\text{R} = -\xi\left(\ma{A}\cdot\ma{D} + \ma{D}\cdot\ma{A}\right) - e^{\epsilon\Tr\ma{A}}\frac{\ma{A}}{\lambda}
	\end{equation}
	\begin{equation}
		\ma{\tau} = \frac{\eta}{\lambda}\ma{A}
	\end{equation}

	\section{FENE-P}\label{app:FENE-P}
	\todo{stability issue, fitting parameter, see fenep repo}
	\section{Analytical solution for PTT}\label{app:PTT}\todo{This is wrong (to the best of my knoledge) not analytically solveable -> semi analytic solution}
	Our derivation is analogous to Oliveira\cite{oliveira1999}. To account for the added viscous stress due to $\eta_\text{s}$, equilibrium is reached at lower polymer stresses. Therefore, Oliveiras equation (7) needs to be modified as follows.
	\begin{equation}
		\tau_{xy} = \partial_xp\frac{r}{2^j} - \eta_\text{s}\dot{\gamma}
	\end{equation}
	Where the second term is added due to the presence of the solvent viscosity. This term also propagates to Oliveiras equation (9) as follows.
	\begin{align}
		\dot{\gamma} &= f\left(\frac{2\lambda}{\eta_\text{p}}\left[\partial_xp\right]^2\frac{r^2}{2^{2j}}\right)\frac{1}{\eta_\text{p}}\left(\partial_xp\frac{r}{2^j}-\eta_\text{s}\dot{\gamma}\right)
		\intertext{This cannot be integrated as easily as without $\eta_\text{s}$, but is still solvable.}
		\dot{\gamma}\left\{1+\frac{\eta_\text{s}}{\eta_\text{p}}f\left(\frac{2\lambda}{\eta_\text{p}}\left[\partial_xp\right]^2\frac{r^2}{2^{2j}}\right)\right\} &= f\left(\frac{2\lambda}{\eta_\text{p}}\left[\partial_xp\right]^2\frac{r^2}{2^{2j}}\right)\partial_xp\frac{r}{\eta_\text{p}2^j} \\
		\dot{\gamma} &= \frac{f\left(...\right)}{1+\frac{\eta_\text{s}}{\eta_\text{p}}f\left(...\right)}\partial_xp\frac{r}{\eta_\text{p}2^j}
	\end{align}
	For the exponential version of PTT the following $f$ is defined as follows.
	\begin{equation}
		f\left(\Tr\ma{\tau}\right) = \exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)
	\end{equation}
	The equation can be solved by integration as $\dot{\gamma} = \partial_ru$. We start with the following substitution.
	\begin{equation}
		v = \frac{\epsilon\lambda^2}{\eta_\text{p}^2}\left(\partial_xp\right)^2\frac{r^2}{2^{2j-1}}
	\end{equation}
	With this $u$ is as follows.
	\begin{align}
		u\left(r\right) &= \frac{\eta_\text{p}2^{j-2}}{\epsilon\lambda^2\partial_xp}\int\frac{e^v}{1+\frac{\eta_\text{s}}{\eta_\text{p}}e^v}dv
		\intertext{Substitute $v^\prime = 1+\frac{\eta_\text{s}}{\eta_\text{p}}e^v$}
		&= \frac{\eta_\text{p}2^{j-2}}{\epsilon\lambda^2\partial_xp}\frac{\eta_\text{p}}{\eta_\text{s}}\int\frac{1}{v^\prime}dv^\prime \\
		&= \frac{\eta_\text{p}2^{j-2}}{\epsilon\lambda^2\partial_xp}\frac{\eta_\text{p}}{\eta_\text{s}}\left(\ln v^\prime + C\right) \\
		&= \frac{\eta_\text{p}2^{j-2}}{\epsilon\lambda^2\partial_xp}\frac{\eta_\text{p}}{\eta_\text{s}}\left[\ln\left(1+\frac{\eta_\text{s}}{\eta_\text{p}}e^v\right) + C\right]
		\intertext{Using $l^2:= \frac{r^2}{v^2}$}
		&= \frac{\eta_\text{p}2^{j-2}}{\epsilon\lambda^2\partial_xp}\frac{\eta_\text{p}}{\eta_\text{s}}\left[\ln\left(1+\frac{\eta_\text{s}}{\eta_\text{p}}e^\frac{r^2}{l^2}\right) + C\right]
	\end{align}
	Using $u\left(R\right)\overset{!}{=}0$ and $G = -\partial_xp$ the following is recovered.
	\begin{equation}
		u\left(r\right) = \frac{Gl^2}{2^{j+1}\eta_\text{s}}\left[\ln\left(1+\frac{\eta_\text{s}}{\eta_\text{p}}e^\frac{R^2}{l^2}\right)-\ln\left(1+\frac{\eta_\text{s}}{\eta_\text{p}}e^\frac{r^2}{l^2}\right)\right]
	\end{equation}
	\section{Parameter studies}
	\todo{do}
	\subsection{Viscosity shuffle fraction dependency}\label{app:viscSuffleDependency}
	We use PTT with the methyl cellulose parameters. In a shear flow with the very small shearrate of $\dot{\gamma} = \SI{1}{\per\second}$, the viscosity shuffle fraction is varied. As can be seen in figure \ref{fig:suffleParameterStudy}, the observed viscosity does not depend on $\alpha_\text{s}$. The simulation gives $\eta = \SI{19.6999988048\pm0.0000000002}{\milli\pascal}$, while theory gives $\eta = \SI{19.699998805}{\milli\pascal}$. Therefore, the simulation is incredibly accurate.\todo{maybe add alphas < 1}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/suffleParameterStudy.eps}
		\caption{Plot of the simulated viscosity as a dependency of the viscosity shuffle fraction. The axis label does not have enough digits to reflect the precision archived.}
		\label{fig:suffleParameterStudy}
	\end{figure}
	\subsection{Weissenberg number dependency}
	We use the same setup as in section \ref{app:viscSuffleDependency}, but vary the shear rate instead of $\alpha_\text{s}$, which is equal to unity here. As can be seen in figure \ref{fig:wiParameterStudy}, the agreement is very good. The maximum relative error is \num{2e-11}. The simulation becomes asymptotic. For higher shear, it equilibrates faster. Those data points have significantly smaller errors (\num{7e-16}) suggesting, that the simulation was not fully equilibrated for the smaller shear rates. Also, this suggests, that when the simulation has fully equilibrated the error is smaller than can be captured in a 32-bit float.
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/wiParameterStudy.eps}
		\caption{Plot of the simulated viscosity as a dependency of the Weissenber number.}
		\label{fig:wiParameterStudy}
	\end{figure}
	\subsection{2D Poiseuille vs theory}\todo{not finished}
	setup above R = 10µm; shear rate approximation to px\n
	Worst $G$.
	\iffalse
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU0.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyU0}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU1.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyU1}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU2.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyU2}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU3.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyU3}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU4.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyU4}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU5.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyU5}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU6.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyU6}
	\end{figure}
	\fi
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU7.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyU7}
	\end{figure}
	\iffalse
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU8.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyU8}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU9.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyU9}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU10.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyU10}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU11.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyU11}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU12.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyU12}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU13.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyU13}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU14.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyU14}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr0.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyErr0}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr1.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyErr1}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr2.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyErr2}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr3.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyErr3}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr4.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyErr4}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr5.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyErr5}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr6.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyErr6}
	\end{figure}
	\fi
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr7.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyErr7}
	\end{figure}
	\iffalse
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr8.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyErr8}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr9.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyErr9}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr10.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyErr10}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr11.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyErr11}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr12.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyErr12}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr13.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyErr13}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr14.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyErr14}
	\end{figure}
	\fi
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:2DParameterStudyErr}
	\end{figure}
	Interestingly, the last one work besides Ma being approx 10.\n
	This error is not influenced by shuffling fraction or lattice resolution\n
	The shape the sim returns can be obtained by the theory by modifying px and or etap\n
	The resulting error is (approx) centered around Wi of max viscosity gradient.

	\subsection{3D Poiseuille vs theory}\todo{not finished}
	Like above but 3D\n
	Worst $G$.
	\iffalse
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU0.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyU0}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU1.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyU1}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU2.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyU2}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU3.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyU3}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU4.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyU4}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU5.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyU5}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU6.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyU6}
	\end{figure}
	\fi
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU7.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyU7}
	\end{figure}
	\iffalse
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU8.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyU8}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU9.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyU9}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU10.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyU10}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU11.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyU11}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr0.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyErr0}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr1.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyErr1}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr2.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyErr2}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr3.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyErr3}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr4.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyErr4}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr5.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyErr5}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr6.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyErr6}
	\end{figure}
	\fi
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr7.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyErr7}
	\end{figure}
	\iffalse
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr8.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyErr8}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr9.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyErr9}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr10.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyErr10}
	\end{figure}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr11.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyErr11}
	\end{figure}
	\fi
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr.eps}
		\caption{Plot of the simulated velocity as a dependency of the radius.}
		\label{fig:3DParameterStudyErr}
	\end{figure}
	Worse due to wall approx.\n
	Failed for high Ma.

\end{document}

### 2023-10-14 assets/python/CY.py

@@ -1,0 +1,37 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the   class.
+
+Created on Sat Oct 14 19:57:01 2023
+
+@author: Richard Kellnberger
+"""
+
+from pathlib import Path
+
+import matplotlib.pyplot as plt
+import numpy as np
+from style import *
+
+
+def CY(eta0, etaInf, Wi, a1, a2):
+    return etaInf + (eta0 - etaInf) / (1 + Wi**a1) ** (a2 / a1)
+
+
+def plot():
+    wi = np.logspace(-4, 7, num=1000)
+    plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+    plt.plot(wi, CY(100, 1, wi, 1, 1), label=r"$a_1 = 1$")
+    plt.plot(wi, CY(100, 1, wi, 2, 1), label=r"$a_1 = 2$")
+    plt.plot(wi, CY(100, 1, wi, 3, 1), label=r"$a_1 = 3$")
+    plt.xscale("log")
+    plt.yscale("log")
+    plt.xlabel(r"$Wi$")
+    plt.ylabel(r"$\eta/\unit{\pascal\second}$")
+    plt.yticks([1, 100], [r"$\eta_\infty$", r"$\eta_0$"])
+    plt.legend()
+    plt.savefig("../plots/CY.eps")
+
+
+if __name__ == "__main__":
+    plot()

### 2023-10-14 assets/python/fig:2DParameterStudy.py

@@ -1,0 +1,216 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the  class.
+
+Created on Tue Sep  5 10:51:20 2023
+
+@author: Richard Kellnberger
+"""
+
+import json
+import sys
+from pathlib import Path
+from time import time
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pyvista as pv
+import scipy
+from scipy.special import lambertw
+from multiprocessing import Pool
+from style import *
+
+eta_s = 1e-3
+j = 0
+R = 10e-6
+
+
+def ptt_eta(gd, eta_p, lam, epsilon):
+    return eta_p / np.exp(0.5 * lambertw(4 * epsilon * (gd * lam) ** 2)) + eta_s
+
+
+def getl2(G, eta_p, lam, epsilon):
+    return np.float128(2 ** (2 * j - 1) * eta_p**2 / (epsilon * lam**2 * G**2))
+
+
+# According to Oliveira 1999
+def uS(r, G, eta_p, lam, epsilon):  # eta_s = 0
+    l2 = getl2(G, eta_p, lam, epsilon)
+    return G * l2 / (2 ** (j + 1) * (eta_p + eta_s)) * (np.exp(R**2 / l2) - np.exp(r**2 / l2))
+
+
+def uHP(r, G, eta_p):
+    return G / (2 * (eta_p + eta_s)) * (R**2 - r**2)
+
+
+def getFun(r, G, lam, eta_p, epsilon):
+    def fun(x):
+        return (
+            2 * epsilon * lam**2 / eta_p**2 * (-G * r / 2**j - eta_s * x) ** 2
+            - np.log(eta_p)
+            + np.log(-G * r / 2**j / x - eta_s)
+        )
+
+    return fun
+
+
+def calc(r, G, lam, eta_p, epsilon):
+    guess = -G * r / 2**j / eta_s / 10
+    fun = getFun(r, G, lam, eta_p, epsilon)
+    answ = scipy.optimize.root(fun, guess)
+    return answ.x[0]
+
+
+def findRoot(G, lam, eta_p, epsilon):
+    dr = R * 1e-5
+    r = np.arange(0, R, dr)
+    ru = np.arange(dr, R + dr, dr)
+
+    param = [(re, G, lam, eta_p, epsilon) for re in r[1:]]
+
+    with Pool(32) as p:
+        res = p.starmap(calc, param)
+
[…]

### 2023-10-14 assets/python/fig:3DParameterStudy.py

@@ -1,0 +1,214 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the  class.
+
+Created on Tue Sep  5 10:51:20 2023
+
+@author: Richard Kellnberger
+"""
+
+import json
+import sys
+from pathlib import Path
+from time import time
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pyvista as pv
+import scipy
+from scipy.special import lambertw
+from multiprocessing import Pool
+from style import *
+
+eta_s = 1e-3
+j = 1
+R = 10e-6
+
+
+def ptt_eta(gd, eta_p, lam, epsilon):
+    return eta_p / np.exp(0.5 * lambertw(4 * epsilon * (gd * lam) ** 2)) + eta_s
+
+
+def getl2(G, eta_p, lam, epsilon):
+    return np.float128(2 ** (2 * j - 1) * eta_p**2 / (epsilon * lam**2 * G**2))
+
+
+# According to Oliveira 1999
+def uS(r, G, eta_p, lam, epsilon):  # eta_s = 0
+    l2 = getl2(G, eta_p, lam, epsilon)
+    return G * l2 / (2 ** (j + 1) * (eta_p + eta_s)) * (np.exp(R**2 / l2) - np.exp(r**2 / l2))
+
+
+def uHP(r, G, eta_p):
+    return G / (4 * (eta_p + eta_s)) * (R**2 - r**2)
+
+
+def getFun(r, G, lam, eta_p, epsilon):
+    def fun(x):
+        return (
+            2 * epsilon * lam**2 / eta_p**2 * (-G * r / 2**j - eta_s * x) ** 2
+            - np.log(eta_p)
+            + np.log(-G * r / 2**j / x - eta_s)
+        )
+
+    return fun
+
+
+def calc(r, G, lam, eta_p, epsilon):
+    guess = -G * r / 2**j / eta_s / 10
+    fun = getFun(r, G, lam, eta_p, epsilon)
+    answ = scipy.optimize.root(fun, guess)
+    return answ.x[0]
+
+
+def findRoot(G, lam, eta_p, epsilon):
+    dr = R * 1e-5
+    r = np.arange(0, R, dr)
+    ru = np.arange(dr, R + dr, dr)
+
+    param = [(re, G, lam, eta_p, epsilon) for re in r[1:]]
+
+    with Pool(32) as p:
+        res = p.starmap(calc, param)
+
[…]

### 2023-10-14 assets/python/fig:RT-DC.py

@@ -1,0 +1,115 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the  class.
+
+Created on Tue Sep  5 10:51:20 2023
+
+@author: Richard Kellnberger
+"""
+
+import json
+import sys
+from multiprocessing import Pool
+from pathlib import Path
+from time import time
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pyvista as pv
+import scipy
+from scipy.special import lambertw
+from style import *
+
+eta_s = 1e-3
+
+
+def process():
+    baseDir = Path("../data/RT-DC/0/")
+    cDir = baseDir / "vtkfiles/polymerConformationTensor/"
+    sDir = baseDir / "vtkfiles/strainRateTensor/"
+    vDir = baseDir / "vtkfiles/velocity/"
+    jsonFile = baseDir / "parameters.json"
+    f = open(jsonFile)
+    parameters = json.load(f)
+    f.close()
+
+    V0 = parameters["info"]["conversions"]["V0"]
+    L0 = parameters["info"]["conversions"]["L0"]
+    T0 = parameters["info"]["conversions"]["T0"]
+    rho0 = 1e3
+    p0 = rho0 * V0**2
+    G = parameters["info"]["px"] * p0 / L0
+    # print("###")
+    # print(parameters["info"]["px"])
+    # print(p0 / L0)
+    # print(G)
+
+    cFile = cDir / "C_500000.vtk"
+    sFile = sDir / "S_500000.vtk"
+    vFile = vDir / "u_500000.vtk"
+    eta_p_SI = 18.7e-3
+    lambda_SI = 0.344e-3
+    epsilon = 0.27
+    # print(uHP(0, G, eta_p_SI))
+    # print("---")
+    data = pv.read(cFile)
+    dataS = pv.read(sFile)
+    dataV = pv.read(vFile)
+    Lx, Ly, Lz = data.dimensions
+    tauField = data.get_array("data") * eta_p_SI / lambda_SI
+    tauField = np.reshape(tauField, (Lx, Ly, Lz, 6), "F")
+    sField = dataS.get_array("data") / T0
+    sField = np.reshape(sField, (Lx, Ly, Lz, 6), "F")
[…]

### 2023-10-14 assets/python/fig:fit_alginate.py

@@ -1,0 +1,162 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the   class.
+
+Created on Sat Oct 14 19:57:01 2023
+
+@author: Richard Kellnberger
+"""
+
+import codecs
+from pathlib import Path
+
+import matplotlib.pyplot as plt
+import numpy as np
+import scipy
+from scipy.special import lambertw
+from style import *
+
+
+def CY(eta0, etaInf, Wi, a1, a2):
+    return etaInf + (eta0 - etaInf) / (1 + Wi**a1) ** (a2 / a1)
+
+
+def readFile(index):
+    f = codecs.open(
+        f"../data/Daten_SOP_BioPrint_Alginat_PH176/SOP_Bioprint_Probe_{index}.csv", "r", "utf-16"
+    )
+    lines = f.readlines()
+    gdEs = []
+    etas = []
+    gdNs = []
+    Ns = []
+    upper = False  # weahter to read the upper intervall (mostly bad)
+    if upper:
+        for l in lines[402:423]:
+            _, _, _, _, _, _, _, _, _, _, eta, gd, _, _, F, _ = l.split("\t")
+            gdEs.append(float(gd))
+            etas.append(float(eta))
+            if float(F) > 0:
+                gdNs.append(float(gd))
+                Ns.append(float(F))
+
+    for l in lines[428:578]:
+        _, _, _, _, _, _, _, _, _, _, eta, gd, _, _, F, _ = l.split("\t")
+        gdEs.append(float(gd))
+        etas.append(float(eta))
+        if float(F) > 0:
+            gdNs.append(float(gd))
+            Ns.append(float(F))
+    idxE = np.argsort(gdEs)
+    gdEs = np.asarray(gdEs)[idxE]
+    etas = np.asarray(etas)[idxE] / 1e3
+    idxN = np.argsort(gdNs)
+    gdNs = np.asarray(gdNs)[idxN]
+    r = 25 / 2 * 1e-3  # Source: dude trust me bro
+    Ns = np.asarray(Ns)[idxN] * 2 / (r**2 * np.pi)
+    # plt.plot(gdNs, Ns, "rx")
+    d = 0
+    # d = 2e-3  # Plate distance; I don't know; This is PP right?
[…]

### 2023-10-14 assets/python/fig:fit_mc.py

@@ -1,0 +1,143 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the   class.
+
+Created on Sat Oct 14 19:57:01 2023
+
+@author: Richard Kellnberger
+"""
+
+import codecs
+from pathlib import Path
+
+import matplotlib.pyplot as plt
+import numpy as np
+import scipy
+from scipy.special import lambertw
+from style import *
+
+
+def CY(eta0, etaInf, Wi, a1, a2):
+    return etaInf + (eta0 - etaInf) / (1 + Wi**a1) ** (a2 / a1)
+
+
+def readFile(index):
+    gdEs, etas = np.genfromtxt(
+        f"../data/methylcellulose/cc_cp_visc_0_{index}.txt", delimiter=";", unpack=True
+    )
+    gdNs, Ns = np.genfromtxt(
+        f"../data/methylcellulose/cp_normal_0_{index}.txt", delimiter=";", unpack=True
+    )
+    etas /= 1e3
+
+    # plt.plot(gdNs, Ns, "bx")
+    # plt.xscale("log")
+    # plt.yscale("log")
+    # plt.ylim(1e-2, 1e3)
+    # plt.show()
+    # plt.plot(gdEs, etas)
+    # plt.xscale("log")
+    # plt.yscale("log")
+    # plt.show()
+    return gdEs, etas, gdNs, Ns
+
+
+eta_s = 1e-3
+
+
+def ptt_eta(gd, eta_p, lam, epsilon):
+    return eta_p / np.exp(0.5 * lambertw(4 * epsilon * (gd * lam) ** 2)) + eta_s
+
+
+def ptt_N(gd, eta_p, lam, epsilon):
+    return eta_p / (2 * epsilon * lam) * lambertw(4 * epsilon * (lam * gd) ** 2)
+
+
+def merge(fun1, x1, y1, fun2, x2, y2):
+    log = True
+    x = np.concatenate((x1, x2))
+    y = np.concatenate((y1, y2))
+    if log:
+        y = np.log(y)
+
+    def fun(x, *param):
+        res = np.concatenate((fun1(x1, *param), fun2(x2, *param)))
+        if log:
+            return np.log(res)
+        else:
+            return res
+
+    return x, y, fun
+
+
+if __name__ == "__main__":
+    for i in [49, 59, 83]:
+        gde, e, gdn, n = readFile(i)
+        plt.plot(gde, e, "x", label=f"{i}")
[…]

### 2023-10-14 assets/python/fig:malaspinas2010.py

@@ -1,0 +1,105 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the  class.
+
+Created on Tue Sep  5 10:51:20 2023
+
+@author: Richard Kellnberger
+"""
+
+import json
+import sys
+from pathlib import Path
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pyvista as pv
+
+from style import *
+
+R = 10e-6
+
+
+# https://doi.org/10.1016/j.jnnfm.2010.09.001 eq. 57 and 61 corrected
+def u(r, vmax):
+    return (1 - r**2 / R**2) * vmax
+
+
+def process(index):
+    VmaxSI = 1
+    if index >= 8:
+        VmaxSI = 0.14285714285714285
+    baseDir = Path(f"../data/malaspinas2010/fluidx3d/{index}/")
+    velocityDir = baseDir / "vtkfiles/velocity/"
+    jsonFile = baseDir / "parameters.json"
+    f = open(jsonFile)
+    parameters = json.load(f)
+    f.close()
+
+    V0 = parameters["info"]["conversions"]["V0"]
+    L0 = parameters["info"]["conversions"]["L0"]
+
+    velFile = velocityDir / "u_4000000.vtk"
+    data = pv.read(velFile)
+    Lx, Ly, Lz = data.dimensions
+    velocityField = data.get_array("data") * V0
+    velocityField = np.reshape(velocityField, (Lx, Ly, Lz, 3), "F")
+
+    rlattice = (np.arange(0, Ly, 1) - Ly / 2 + 0.5) * L0
+    rlattice[0] += L0 / 2
+    rlattice[-1] -= L0 / 2
+
+    l2error = np.sqrt(
+        np.sum((velocityField[1, 1:-1, 1, 0] - u(rlattice[1:-1], VmaxSI)) ** 2)
+        / np.sum(u(rlattice[1:-1], VmaxSI) ** 2)
+    )
+    otherError = np.sqrt(
+        np.sum((velocityField[1, 1:-1, 1, 0] - u(rlattice[1:-1], VmaxSI)) ** 2) / (Ly - 2)
+    )
+    return l2error, otherError / VmaxSI
+
+
+N = [25, 50, 100, 200]  # It is clear, that these are the exact values
+plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+i = 0
+for fig, R_nu in zip([17, 18], [0.1, 0.7]):
+    for Wi in [0.1, 1]:
[…]

### 2023-10-14 assets/python/fig:ptt_N.py

@@ -1,0 +1,53 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the   class.
+
+Created on Sat Oct 14 19:57:01 2023
+
+@author: Richard Kellnberger
+"""
+
+from pathlib import Path
+
+import matplotlib.pyplot as plt
+import numpy as np
+from scipy.special import lambertw
+from style import *
+
+
+def CY(eta0, etaInf, Wi, a1, a2):
+    return etaInf + (eta0 - etaInf) / (1 + Wi**a1) ** (a2 / a1)
+
+
+def ppt_eta(eta_p, Wi, epsilon):
+    # tau_xxbygd = eta_p / (2 * epsilon * Wi) * lambertw(4 * epsilon * Wi**2)
+    # return eta_p / np.exp(epsilon * Wi / eta_p * tau_xxbygd)
+    return eta_p / np.exp(0.5 * lambertw(4 * epsilon * Wi**2))
+
+
+def ppt_N(eta_p, gd, lam, epsilon):
+    return eta_p / (2 * epsilon * lam) * lambertw(4 * epsilon * (lam * gd) ** 2)
+
+
+def plot():
+    wi = np.logspace(-4, 7, num=1000)
+    plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+    plt.plot(wi, ppt_N(100, wi, 1, 1), label=r"$\epsilon = 1$")
+    plt.plot(wi, ppt_N(100, wi, 1, 0.1), label=r"$\epsilon = 0.1$")
+    plt.plot(wi, ppt_N(100, wi, 1, 0.01), label=r"$\epsilon = 0.01$")
+    plt.plot(wi, ppt_N(100, wi, 0.1, 1), label=r"$\epsilon = 1$")
+    plt.plot(wi, ppt_N(100, wi, 0.1, 0.1), label=r"$\epsilon = 0.1$")
+    plt.plot(wi, ppt_N(100, wi, 0.1, 0.01), label=r"$\epsilon = 0.01$")
+    plt.plot(wi, ppt_N(1000, wi, 0.1, 1), label=r"$\epsilon = 1$")
+    plt.xscale("log")
+    plt.yscale("log")
+    plt.xlabel(r"$Wi$")
+    plt.ylabel(r"$\eta/\unit{\pascal\second}$")
+    plt.yticks([1, 100], [r"$\eta_\infty$", r"$\eta_\text{p}$"])
[…]

### 2023-10-14 assets/python/fig:ptt_eta.py

@@ -1,0 +1,58 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the   class.
+
+Created on Sat Oct 14 19:57:01 2023
+
+@author: Richard Kellnberger
+"""
+
+from pathlib import Path
+
+import matplotlib.pyplot as plt
+import numpy as np
+from scipy.special import lambertw
+from style import *
+
+
+def CY(eta0, etaInf, Wi, a1, a2):
+    return etaInf + (eta0 - etaInf) / (1 + Wi**a1) ** (a2 / a1)
+
+
+def ptt_eta(eta_p, Wi, epsilon):
+    # tau_xxbygd = eta_p / (2 * epsilon * Wi) * lambertw(4 * epsilon * Wi**2)
+    # return eta_p / np.exp(epsilon * Wi / eta_p * tau_xxbygd)
+    return eta_p / np.exp(0.5 * lambertw(4 * epsilon * Wi**2))
+
+
+def plot():
+    wi = np.logspace(-4, 7, num=1000)
+    plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+    plt.plot(wi, ptt_eta(100, wi, 1), label=r"$\epsilon = 1$")
+    plt.plot(wi, ptt_eta(100, wi, 0.1), label=r"$\epsilon = 0.1$")
+    plt.plot(wi, ptt_eta(100, wi, 0.01), label=r"$\epsilon = 0.01$")
+    plt.xscale("log")
+    plt.yscale("log")
+    plt.xlabel(r"$Wi$")
+    plt.ylabel(r"$\eta/\unit{\pascal\second}$")
+    plt.yticks([1, 100], [r"$\eta_\infty$", r"$\eta_\text{p}$"])
+    plt.ylim(0.8, 125)
+    plt.legend()
+    plt.savefig("../plots/ptt_eta.eps")
+
+    plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+    plt.plot(wi, ptt_eta(99, wi, 1) + 1, label=r"$\epsilon = 1$")
+    plt.plot(wi, ptt_eta(99, wi, 0.1) + 1, label=r"$\epsilon = 0.1$")
+    plt.plot(wi, ptt_eta(99, wi, 0.01) + 1, label=r"$\epsilon = 0.01$")
+    plt.xscale("log")
+    plt.yscale("log")
+    plt.xlabel(r"$Wi$")
[…]

### 2023-10-14 assets/python/fig:shuffleParameterStudy.py

@@ -1,0 +1,78 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the  class.
+
+Created on Tue Sep  5 10:51:20 2023
+
+@author: Richard Kellnberger
+"""
+
+import json
+import sys
+from pathlib import Path
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pyvista as pv
+from scipy.special import lambertw
+from style import *
+
+eta_s = 1e-3
+
+
+def ptt_eta(gd, eta_p, lam, epsilon):
+    return eta_p / np.exp(0.5 * lambertw(4 * epsilon * (gd * lam) ** 2)) + eta_s
+
+
+def process(index):
+    baseDir = Path(f"../data/SuffleParameterStudy/{index}/")
+    cDir = baseDir / "vtkfiles/polymerConformationTensor/"
+    sDir = baseDir / "vtkfiles/strainRateTensor/"
+    jsonFile = baseDir / "parameters.json"
+    f = open(jsonFile)
+    parameters = json.load(f)
+    f.close()
+
+    V0 = parameters["info"]["conversions"]["V0"]
+    L0 = parameters["info"]["conversions"]["L0"]
+    T0 = parameters["info"]["conversions"]["T0"]
+    rho0 = 1e3
+
+    cFile = cDir / "C_10000000.vtk"
+    sFile = sDir / "S_10000000.vtk"
+    eta_p_SI = 18.7e-3
+    lambda_SI = 0.344e-3
+    data = pv.read(cFile)
+    dataS = pv.read(sFile)
+    Lx, Ly, Lz = data.dimensions
+    tauField = data.get_array("data") * eta_p_SI / lambda_SI
+    tauField = np.reshape(tauField, (Lx, Ly, Lz, 6), "F")
+    sField = dataS.get_array("data") / T0
+    sField = np.reshape(sField, (Lx, Ly, Lz, 6), "F")
+
+    tau12 = tauField[Lx // 2, Ly // 2, Lz // 2, 3]
+    D12 = sField[Lx // 2, Ly // 2, Lz // 2, 3]
+    shearRateSI = parameters["shearRateSI"]
+    eta = tau12 / shearRateSI + 1e-3
+    return eta, D12
+
+
+etas = []
+ds = []
+for i in range(11):
+    eta, D12 = process(i)
[…]

### 2023-10-14 assets/python/fig:wiParameterStudy.py

@@ -1,0 +1,90 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the  class.
+
+Created on Tue Sep  5 10:51:20 2023
+
+@author: Richard Kellnberger
+"""
+
+import json
+import sys
+from pathlib import Path
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pyvista as pv
+from scipy.special import lambertw
+from style import *
+
+eta_s = 1e-3
+
+
+def ptt_eta(gd, eta_p, lam, epsilon):
+    return eta_p / np.exp(0.5 * lambertw(4 * epsilon * (gd * lam) ** 2)) + eta_s
+
+
+def process(index):
+    baseDir = Path(f"../data/wiParameterStudy/{index}/")
+    cDir = baseDir / "vtkfiles/polymerConformationTensor/"
+    sDir = baseDir / "vtkfiles/strainRateTensor/"
+    jsonFile = baseDir / "parameters.json"
+    f = open(jsonFile)
+    parameters = json.load(f)
+    f.close()
+
+    V0 = parameters["info"]["conversions"]["V0"]
+    L0 = parameters["info"]["conversions"]["L0"]
+    T0 = parameters["info"]["conversions"]["T0"]
+    rho0 = 1e3
+
+    cFile = cDir / "C_5000000.vtk"
+    sFile = sDir / "S_5000000.vtk"
+    eta_p_SI = 18.7e-3
+    lambda_SI = 0.344e-3
+    data = pv.read(cFile)
+    dataS = pv.read(sFile)
+    Lx, Ly, Lz = data.dimensions
+    tauField = data.get_array("data") * eta_p_SI / lambda_SI
+    tauField = np.reshape(tauField, (Lx, Ly, Lz, 6), "F")
+    sField = dataS.get_array("data") / T0
+    sField = np.reshape(sField, (Lx, Ly, Lz, 6), "F")
+
+    tau12 = tauField[Lx // 2, Ly // 2, Lz // 2, 3]
+    D12 = sField[Lx // 2, Ly // 2, Lz // 2, 3]
+    shearRateSI = parameters["shearRateSI"]
+    eta = tau12 / shearRateSI + 1e-3
+    return eta, D12
+
+
+etas = []
+ds = []
+for i in range(15):
[…]

### 2023-10-14 assets/python/flowRate.py

@@ -1,0 +1,129 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the  class.
+
+Created on Tue Sep  5 10:51:20 2023
+
+@author: Richard Kellnberger
+"""
+
+import json
+import sys
+from multiprocessing import Pool
+from pathlib import Path
+from time import time
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pyvista as pv
+import scipy
+from scipy.special import lambertw
+from style import *
+
+eta_s = 1e-3
+j = 1
+# R = 200e-6  # G = 77891.69129767214
+R = 1.8e-3  # G = 11.947169068625888
+
+
+def ptt_eta(gd, eta_p, lam, epsilon):
+    return eta_p / np.exp(0.5 * lambertw(4 * epsilon * (gd * lam) ** 2)) + eta_s
+
+
+def getl2(G, eta_p, lam, epsilon):
+    return np.float128(2 ** (2 * j - 1) * eta_p**2 / (epsilon * lam**2 * G**2))
+
+
+# According to Oliveira 1999
+def uS(r, G, eta_p, lam, epsilon):  # eta_s = 0
+    l2 = getl2(G, eta_p, lam, epsilon)
+    return G * l2 / (2 ** (j + 1) * (eta_p + eta_s)) * (np.exp(R**2 / l2) - np.exp(r**2 / l2))
+
+
+def uHP(r, G, eta_p):
+    return G / (4 * (eta_p + eta_s)) * (R**2 - r**2)
+
+
+def getFun(r, G, lam, eta_p, epsilon):
+    def fun(x):
+        return (
+            2 * epsilon * lam**2 / eta_p**2 * (-G * r / 2**j - eta_s * x) ** 2
+            - np.log(eta_p)
+            + np.log(-G * r / 2**j / x - eta_s)
+        )
+
+    return fun
+
+
+def calc(r, G, lam, eta_p, epsilon):
+    guess = -G * r / 2**j / eta_s / 10
+    fun = getFun(r, G, lam, eta_p, epsilon)
+    answ = scipy.optimize.root(fun, guess)
+    return answ.x[0]
+
+
+def findRoot(G, lam, eta_p, epsilon):
+    dr = R * 1e-5
+    r = np.arange(0, R, dr)
+    ru = np.arange(dr, R + dr, dr)
+
+    param = [(re, G, lam, eta_p, epsilon) for re in r[1:]]
+
+    with Pool(32) as p:
[…]

### 2023-10-14 assets/python/inputForNozzle.py

@@ -1,0 +1,103 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the  class.
+
+Created on Tue Sep  5 10:51:20 2023
+
+@author: Richard Kellnberger
+"""
+
+import json
+import sys
+from multiprocessing import Pool
+from pathlib import Path
+from time import time
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pyvista as pv
+import scipy
+from scipy.special import lambertw
+from style import *
+
+
+def process():
+    baseDir = Path(f"../data/Nozzle/{0}/")
+    cDir = baseDir / "vtkfiles/polymerConformationTensor/"
+    vDir = baseDir / "vtkfiles/velocity/"
+    jsonFile = baseDir / "parameters.json"
+    f = open(jsonFile)
+    parameters = json.load(f)
+    f.close()
+
+    V0 = parameters["info"]["conversions"]["V0"]
+
+    cFile = cDir / "C_5000000.vtk"
+    vFile = vDir / "u_5000000.vtk"
+
+    data = pv.read(cFile)
+    dataV = pv.read(vFile)
+    Lx, Ly, Lz = data.dimensions
+    cField = data.get_array("data")
+    cField = np.reshape(cField, (Lx, Ly, Lz, 6), "F")
+    vField = dataV.get_array("data") * V0
+    vField = np.reshape(vField, (Lx, Ly, Lz, 3), "F")
+
+    out = open(f"../setups/Nozzle/2/input.tsv", "w")
+    for y in range(Ly):
+        for z in range(Lz):
+            vx = vField[Lx // 2, y, z, 0]
+            vy = vField[Lx // 2, y, z, 1]
+            vz = vField[Lx // 2, y, z, 2]
+
+            xx = cField[Lx // 2, y, z, 0]
+            yy = cField[Lx // 2, y, z, 1]
+            zz = cField[Lx // 2, y, z, 2]
+            xy = cField[Lx // 2, y, z, 3]
+            yz = cField[Lx // 2, y, z, 4]
+            xz = cField[Lx // 2, y, z, 5]
+            out.write(
+                f"{1666}\t{y+(335-39)//2}\t{z+(335-39)//2}\t{vx}\t{vy}\t{vz}\t{xx}\t{yy}\t{zz}\t{xy}\t{yz}\t{xz}\n"
+            )
+
[…]

### 2023-10-14 assets/python/style.py

@@ -1,0 +1,63 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the style defenition.
+
+Created on Fri Apr 14 14:49:37 2023
+
+@author: Richard Kellnberger
+"""
+
+import matplotlib.colors as mcolors
+import matplotlib.pyplot as plt
+
+plt.rcParams.update({"font.size": 12})
+plt.rcParams.update({"text.usetex": True})
+plt.rcParams.update({"figure.autolayout": True})
+plt.rcParams.update(
+    {
+        "text.latex.preamble": "".join(
+            [
+                r"\usepackage[locale=US]{siunitx}"
+                r"\sisetup{per-mode=fraction}"
+                r"\sisetup{separate-uncertainty=true}"
+                r"\newcommand{\ma}[1]{\underline{#1}}"
+                r"\usepackage{amsmath}"
+                r"\DeclareMathOperator{\Tr}{Tr}"
+            ]
+        )
+    }
+)
+# plt.style.use("dark_background")
+
+
+def rgb(r, g, b):
+    return r / 255, g / 255, b / 255
+
+
+# backgroundColor = rgb(51, 51, 51)
+
+# plt.rcParams["figure.facecolor"] = rgb(51, 51, 51)
+# plt.rcParams["axes.facecolor"] = rgb(51, 51, 51)
+
+plt.rcParams["image.origin"] = "lower"
+
+# darkColors = []
+
+# for e in plt.rcParams["axes.prop_cycle"]():
+#    c = e["color"]
+#    if c in darkColors:
+#        break
+#    else:
+#        darkColors.append(c)
+
+# c = ["tab:blue", "tab:orange", "tab:green"]
+
+tabColors = list(mcolors.TABLEAU_COLORS.keys())
+
+
+def color(index):
+    index %= len(tabColors)
+    return tabColors[index]
+
+
+cm = 1 / 2.54

### 2023-10-14 assets/setups/2DParameterStudy/setup/setup.cpp

@@ -1,0 +1,193 @@
+#include "setup.hpp"
+#include "shapes.hpp"
+#include "opencl.hpp" // contains "options.hpp", "main.hpp"
+#include "ibm.hpp"
+#include <numeric>
+#include <sstream>
+
+#include <filesystem>
+using std::filesystem::path;
+#include <fstream>
+using std::ofstream;
+
+#include <fmt/core.h>
+// using fmt::format
+using fmt::print;
+#include <fmt/color.h>
+using fmt::color;
+
+#include <spdlog/spdlog.h>
+//using spdlog::info;
+
+#include "io.hpp"
+using fluidx3d::util::io::IO;
+#include "poiseuilleFlow.hpp"
+using fluidx3d::util::poiseuilleFlow::CircularPoiseuilleFlow;
+
+void example(SimulationOptions& options, Parameters& parameters) {
+	json raw = parameters.getRaw();
+	const int id = raw.at("id");
+	//const string path_files = "/tp6-gekle/nas/bt307867/cellsim/novel_2023-10-24/" + std::to_string(id) + "/";
+	const string path_files = fmt::format("2DParameterStudy/{}/", id);
+	const path filesPath(path_files);
+	const string path_vtk = path_files + "vtkfiles/";
+	const string path_vtk_velocity = path_vtk + "velocity/";
+	const string path_vtk_strainRateTensor = path_vtk + "strainRateTensor/";
+	const string path_vtk_viscousStressTensor = path_vtk + "viscousStressTensor/";
+	const string path_vtk_polymerConformationTensor = path_vtk + "polymerConformationTensor/";
+
+	/*
+	 * this parameter increases the time step
+	 * --> leads to larger relaxation time tau (not good, but acceptable)
+	 * --> leads to larger Ma (not good, but acceptable)
+	 * --> eventually may lead to inaccuracies
+	 */
+	const double dtScale = 1e0;  // decrease timestep
+
+	// Length of simulation box
+	uint Lx = 2;
+	uint Ly = 43;
+	uint Lz = 2;
+
+	/*
+	 * this parameter decreases the viscosity
+	 * simultaneously k1 and kb are increased to keep Ca and kbHat constant
+	 * --> leads to larger time step (good)
[…]

### 2023-10-14 assets/setups/3DParameterStudy/setup/setup.cpp

@@ -1,0 +1,193 @@
+#include "setup.hpp"
+#include "shapes.hpp"
+#include "opencl.hpp" // contains "options.hpp", "main.hpp"
+#include "ibm.hpp"
+#include <numeric>
+#include <sstream>
+
+#include <filesystem>
+using std::filesystem::path;
+#include <fstream>
+using std::ofstream;
+
+#include <fmt/core.h>
+// using fmt::format
+using fmt::print;
+#include <fmt/color.h>
+using fmt::color;
+
+#include <spdlog/spdlog.h>
+//using spdlog::info;
+
+#include "io.hpp"
+using fluidx3d::util::io::IO;
+#include "poiseuilleFlow.hpp"
+using fluidx3d::util::poiseuilleFlow::CircularPoiseuilleFlow;
+
+void example(SimulationOptions& options, Parameters& parameters) {
+	json raw = parameters.getRaw();
+	const int id = raw.at("id");
+	//const string path_files = "/tp6-gekle/nas/bt307867/cellsim/novel_2023-10-24/" + std::to_string(id) + "/";
+	const string path_files = fmt::format("3DParameterStudy/{}/", id);
+	const path filesPath(path_files);
+	const string path_vtk = path_files + "vtkfiles/";
+	const string path_vtk_velocity = path_vtk + "velocity/";
+	const string path_vtk_strainRateTensor = path_vtk + "strainRateTensor/";
+	const string path_vtk_viscousStressTensor = path_vtk + "viscousStressTensor/";
+	const string path_vtk_polymerConformationTensor = path_vtk + "polymerConformationTensor/";
+
+	/*
+	 * this parameter increases the time step
+	 * --> leads to larger relaxation time tau (not good, but acceptable)
+	 * --> leads to larger Ma (not good, but acceptable)
+	 * --> eventually may lead to inaccuracies
+	 */
+	const double dtScale = 1e0;  // decrease timestep
+
+	// Length of simulation box
+	uint Lx = 2;
+	uint Ly = 43;
+	uint Lz = 43;
+
+	/*
+	 * this parameter decreases the viscosity
+	 * simultaneously k1 and kb are increased to keep Ca and kbHat constant
+	 * --> leads to larger time step (good)
[…]

### 2023-10-14 assets/setups/Nozzle/0/setup/setup.cpp

@@ -1,0 +1,189 @@
+#include "setup.hpp"
+#include "shapes.hpp"
+#include "opencl.hpp" // contains "options.hpp", "main.hpp"
+#include "ibm.hpp"
+#include <numeric>
+#include <sstream>
+
+#include <filesystem>
+using std::filesystem::path;
+#include <fstream>
+using std::ofstream;
+
+#include <fmt/core.h>
+// using fmt::format
+using fmt::print;
+#include <fmt/color.h>
+using fmt::color;
+
+#include <spdlog/spdlog.h>
+//using spdlog::info;
+
+#include "io.hpp"
+using fluidx3d::util::io::IO;
+#include "poiseuilleFlow.hpp"
+using fluidx3d::util::poiseuilleFlow::CircularPoiseuilleFlow;
+
+void example(SimulationOptions& options, Parameters& parameters) {
+	json raw = parameters.getRaw();
+	const int id = raw.at("id");
+	//const string path_files = "/tp6-gekle/nas/bt307867/cellsim/novel_2023-10-24/" + std::to_string(id) + "/";
+	const string path_files = fmt::format("Nozzle/{}/", id);
+	const path filesPath(path_files);
+	const string path_vtk = path_files + "vtkfiles/";
+	const string path_vtk_velocity = path_vtk + "velocity/";
+	const string path_vtk_strainRateTensor = path_vtk + "strainRateTensor/";
+	const string path_vtk_viscousStressTensor = path_vtk + "viscousStressTensor/";
+	const string path_vtk_polymerConformationTensor = path_vtk + "polymerConformationTensor/";
+
+	/*
+	 * this parameter increases the time step
+	 * --> leads to larger relaxation time tau (not good, but acceptable)
+	 * --> leads to larger Ma (not good, but acceptable)
+	 * --> eventually may lead to inaccuracies
+	 */
+	const double dtScale = 1e0;  // decrease timestep
+
+	// Length of simulation box
+	uint Lx = 2;
+	uint Ly = 39;
+	uint Lz = 39;
+
+	/*
+	 * this parameter decreases the viscosity
+	 * simultaneously k1 and kb are increased to keep Ca and kbHat constant
+	 * --> leads to larger time step (good)
[…]

### 2023-10-14 assets/setups/Nozzle/1/setup/defines.hpp

@@ -1,0 +1,187 @@
+#pragma once
+// ############################################ file paths #############################################
+
+//#define PATH_DEBUG "/data2/s1molehm/FluidX3D/Bead/interpolation/"
+//#define PATH_DEBUG "/tp6_gekle/data2/bt703473/debug/test2/"
+#define PATH_DEBUG "./bin/debug/" // path for debug files (PTX, LOG, VALIDATION)
+#define PATH_IBM   "./bin/ibm/"   // path for IBM extension
+
+
+// ############################################ LBM options ############################################
+
+// There hides a D2Q5 in the code
+//#define D2Q9
+//#define D3Q7 // very very inaccurate
+//#define D3Q13 // very inaccurate; Only works with MRT according to Krüger book p. 87; Does not reproduce EQUILIBRIUM_STRESS correctly.
+
+// Only use these:
+//#define D3Q15
+#define D3Q19 // Best value
+//#define D3Q27 // Better for high Reynolds numbers.
+
+#define SRT // singe relaxation time
+//#define TRT // two relaxiation time (as fast as SRT, but more accurate)
+//#define MRT // multi relaxiation time (as fast as SRT, but more accurate), (### not fully validated for for D3Q7 and D3Q13, incomplete relaxation times for D3Q7 and D3Q27 ###)
+
+//#define UPDATE_RHO // update density field after every step (not necessary for pure LBM)
+//#define UPDATE_U // update velocity field after every step (not necessary for pure LBM, makes tracer particle calculation faster)
+
+//#define MOVING_WALLS // moving bounce-back boundaries (incompatible with EQUILIBRIUM_BOUNDARIES due to unnecessary flag recycling)
+//#define EQUILIBRIUM_BOUNDARIES // non-reflecting velocity boundaries, generally more stable, but less accurate (incompatible with MOVING_WALLS due to unnecessary flag recycling)
+//#define BOUNDARY_EXPRESSION // combinable with EQUILIBRIUM_BOUNDARIES xor MOVING_WALLS, !!!doesn't work on AMD for some reason!!!
+
+#define VISCOELASTIC
+#define EQUILIBRIUM_STRESS // Include viscoelastic forces by shifting the equilibrium populations (Onishi 2005) instead of via force
[…]

### 2023-10-14 assets/setups/Nozzle/1/setup/setup.cpp

@@ -1,0 +1,189 @@
+#include "setup.hpp"
+#include "shapes.hpp"
+#include "opencl.hpp" // contains "options.hpp", "main.hpp"
+#include "ibm.hpp"
+#include <numeric>
+#include <sstream>
+
+#include <filesystem>
+using std::filesystem::path;
+#include <fstream>
+using std::ofstream;
+
+#include <fmt/core.h>
+// using fmt::format
+using fmt::print;
+#include <fmt/color.h>
+using fmt::color;
+
+#include <spdlog/spdlog.h>
+//using spdlog::info;
+
+#include "io.hpp"
+using fluidx3d::util::io::IO;
+#include "poiseuilleFlow.hpp"
+using fluidx3d::util::poiseuilleFlow::CircularPoiseuilleFlow;
+
+void example(SimulationOptions& options, Parameters& parameters) {
+	json raw = parameters.getRaw();
+	const int id = raw.at("id");
+	//const string path_files = "/tp6-gekle/nas/bt307867/cellsim/novel_2023-10-24/" + std::to_string(id) + "/";
+	const string path_files = fmt::format("Nozzle/{}/", id);
+	const path filesPath(path_files);
+	const string path_vtk = path_files + "vtkfiles/";
+	const string path_vtk_velocity = path_vtk + "velocity/";
+	const string path_vtk_strainRateTensor = path_vtk + "strainRateTensor/";
+	const string path_vtk_viscousStressTensor = path_vtk + "viscousStressTensor/";
+	const string path_vtk_polymerConformationTensor = path_vtk + "polymerConformationTensor/";
+
+	/*
+	 * this parameter increases the time step
+	 * --> leads to larger relaxation time tau (not good, but acceptable)
+	 * --> leads to larger Ma (not good, but acceptable)
+	 * --> eventually may lead to inaccuracies
+	 */
+	const double dtScale = 1e0;  // decrease timestep
+
+	// Length of simulation box
+	uint Lx = 2;
+	uint Ly = 335;
+	uint Lz = 335;
+
+	/*
+	 * this parameter decreases the viscosity
+	 * simultaneously k1 and kb are increased to keep Ca and kbHat constant
+	 * --> leads to larger time step (good)
[…]

### 2023-10-14 assets/setups/Nozzle/2/setup/setup.cpp

@@ -1,0 +1,229 @@
+#include "setup.hpp"
+#include "shapes.hpp"
+#include "opencl.hpp" // contains "options.hpp", "main.hpp"
+#include "ibm.hpp"
+#include <numeric>
+#include <sstream>
+
+#include <filesystem>
+using std::filesystem::path;
+#include <fstream>
+using std::ofstream;
+#include <regex>
+using std::regex, std::regex_match, std::smatch;
+#include <string>
+using std::stof, std::stoi, std::string;
+
+#include <fmt/core.h>
+// using fmt::format
+using fmt::print;
+#include <fmt/color.h>
+using fmt::color;
+
+#include <spdlog/spdlog.h>
+//using spdlog::info;
+
+#include "io.hpp"
+using fluidx3d::util::io::IO;
+#include "stringTools.hpp"
+using fluidx3d::util::stringTools::split;
+#include "poiseuilleFlow.hpp"
+using fluidx3d::util::poiseuilleFlow::CircularPoiseuilleFlow;
+
+void example(SimulationOptions& options, Parameters& parameters) {
+	json raw = parameters.getRaw();
+	const int id = raw.at("id");
+	const string path_files = fmt::format("/tp6-gekle/nas/bt307867/cellsim/novel_2023-11-15/{}/", id);
+	//const string path_files = fmt::format("Nozzle/{}/", id);
+	const path filesPath(path_files);
+	const string path_vtk = path_files + "vtkfiles/";
+	const string path_vtk_velocity = path_vtk + "velocity/";
+	const string path_vtk_strainRateTensor = path_vtk + "strainRateTensor/";
+	const string path_vtk_viscousStressTensor = path_vtk + "viscousStressTensor/";
+	const string path_vtk_polymerConformationTensor = path_vtk + "polymerConformationTensor/";
+
+	/*
+	 * this parameter increases the time step
+	 * --> leads to larger relaxation time tau (not good, but acceptable)
+	 * --> leads to larger Ma (not good, but acceptable)
+	 * --> eventually may lead to inaccuracies
+	 */
+	const double dtScale = 1e0;  // decrease timestep
+
+	// Length of simulation box
[…]

### 2023-10-14 assets/setups/RT-DC/setup/setup.cpp

@@ -1,0 +1,194 @@
+#include "setup.hpp"
+#include "shapes.hpp"
+#include "opencl.hpp" // contains "options.hpp", "main.hpp"
+#include "ibm.hpp"
+#include <numeric>
+#include <sstream>
+
+#include <filesystem>
+using std::filesystem::path;
+#include <fstream>
+using std::ofstream;
+
+#include <fmt/core.h>
+// using fmt::format
+using fmt::print;
+#include <fmt/color.h>
+using fmt::color;
+
+#include <spdlog/spdlog.h>
+//using spdlog::info;
+
+#include "guck.hpp"
+using fluidx3d::util::geometry::guck::Guck;
+#include "io.hpp"
+using fluidx3d::util::io::IO;
+#include "poiseuilleFlow.hpp"
+using fluidx3d::util::poiseuilleFlow::CircularPoiseuilleFlow;
+
+void example(SimulationOptions& options, Parameters& parameters) {
+	json raw = parameters.getRaw();
+	const int id = raw.at("id");
+	//const string path_files = "/tp6-gekle/nas/bt307867/cellsim/novel_2023-10-24/" + std::to_string(id) + "/";
+	const string path_files = fmt::format("RT-DC/{}/", id);
+	const path filesPath(path_files);
+	const string path_vtk = path_files + "vtkfiles/";
+	const string path_vtk_velocity = path_vtk + "velocity/";
+	const string path_vtk_strainRateTensor = path_vtk + "strainRateTensor/";
+	const string path_vtk_viscousStressTensor = path_vtk + "viscousStressTensor/";
+	const string path_vtk_polymerConformationTensor = path_vtk + "polymerConformationTensor/";
+
+	/*
+	 * this parameter increases the time step
+	 * --> leads to larger relaxation time tau (not good, but acceptable)
+	 * --> leads to larger Ma (not good, but acceptable)
+	 * --> eventually may lead to inaccuracies
+	 */
+	const double dtScale = 1e0;  // decrease timestep
+
+	// Length of simulation box
+	const uint Lx = 405;
+	const uint Ly = 92;
+	const uint Lz = 32;
+
+	/*
+	 * this parameter decreases the viscosity
[…]

### 2023-10-14 assets/setups/SuffleParameterStudy/setup/setup.cpp

@@ -1,0 +1,193 @@
+#include "setup.hpp"
+#include "shapes.hpp"
+#include "opencl.hpp" // contains "options.hpp", "main.hpp"
+#include "ibm.hpp"
+#include <numeric>
+#include <sstream>
+
+#include <filesystem>
+using std::filesystem::path;
+#include <fstream>
+using std::ofstream;
+#include <iostream>
+using std::cout, std::endl; // TODO replace with spdlog
+
+#include <fmt/core.h>
+// using fmt::format
+using fmt::print;
+#include <fmt/color.h>
+using fmt::color;
+
+#include <spdlog/spdlog.h>
+//using spdlog::info;
+
+#include "io.hpp"
+using fluidx3d::util::io::IO;
+#include "poiseuilleFlow.hpp"
+using fluidx3d::util::poiseuilleFlow::CircularPoiseuilleFlow;
+
+void example(SimulationOptions& options, Parameters& parameters) {
+	json raw = parameters.getRaw();
+	const int id = raw.at("id");
+	//const string path_files = "/tp6-gekle/nas/bt307867/cellsim/novel_2023-10-24/" + std::to_string(id) + "/";
+	const string path_files = fmt::format("SuffleParameterStudy/{}/", id);
+	const path filesPath(path_files);
+	const string path_vtk = path_files + "vtkfiles/";
+	const string path_vtk_velocity = path_vtk + "velocity/";
+	const string path_vtk_strainRateTensor = path_vtk + "strainRateTensor/";
+	const string path_vtk_viscousStressTensor = path_vtk + "viscousStressTensor/";
+	const string path_vtk_polymerConformationTensor = path_vtk + "polymerConformationTensor/";
+
+	/*
+	 * this parameter increases the time step
+	 * --> leads to larger relaxation time tau (not good, but acceptable)
+	 * --> leads to larger Ma (not good, but acceptable)
+	 * --> eventually may lead to inaccuracies
+	 */
+	const double dtScale = 1e0;  // decrease timestep
+
+	// Length of simulation box
+	uint Lx = 2;
+	uint Ly = 43;
+	uint Lz = 2;
+
+	/*
+	 * this parameter decreases the viscosity
[…]

### 2023-10-14 assets/setups/malaspinas2010/setup/defines.hpp

@@ -1,0 +1,187 @@
+#pragma once
+// ############################################ file paths #############################################
+
+//#define PATH_DEBUG "/data2/s1molehm/FluidX3D/Bead/interpolation/"
+//#define PATH_DEBUG "/tp6_gekle/data2/bt703473/debug/test2/"
+#define PATH_DEBUG "./bin/debug/" // path for debug files (PTX, LOG, VALIDATION)
+#define PATH_IBM   "./bin/ibm/"   // path for IBM extension
+
+
+// ############################################ LBM options ############################################
+
+// There hides a D2Q5 in the code
+//#define D2Q9
+//#define D3Q7 // very very inaccurate
+//#define D3Q13 // very inaccurate; Only works with MRT according to Krüger book p. 87; Does not reproduce EQUILIBRIUM_STRESS correctly.
+
+// Only use these:
+//#define D3Q15
+#define D3Q19 // Best value
+//#define D3Q27 // Better for high Reynolds numbers.
+
+#define SRT // singe relaxation time
+//#define TRT // two relaxiation time (as fast as SRT, but more accurate)
+//#define MRT // multi relaxiation time (as fast as SRT, but more accurate), (### not fully validated for for D3Q7 and D3Q13, incomplete relaxation times for D3Q7 and D3Q27 ###)
+
+//#define UPDATE_RHO // update density field after every step (not necessary for pure LBM)
+//#define UPDATE_U // update velocity field after every step (not necessary for pure LBM, makes tracer particle calculation faster)
+
+//#define MOVING_WALLS // moving bounce-back boundaries (incompatible with EQUILIBRIUM_BOUNDARIES due to unnecessary flag recycling)
+//#define EQUILIBRIUM_BOUNDARIES // non-reflecting velocity boundaries, generally more stable, but less accurate (incompatible with MOVING_WALLS due to unnecessary flag recycling)
+//#define BOUNDARY_EXPRESSION // combinable with EQUILIBRIUM_BOUNDARIES xor MOVING_WALLS, !!!doesn't work on AMD for some reason!!!
+
+#define VISCOELASTIC
+#define EQUILIBRIUM_STRESS // Include viscoelastic forces by shifting the equilibrium populations (Onishi 2005) instead of via force
[…]

### 2023-10-14 assets/setups/malaspinas2010/setup/setup.cpp

@@ -1,0 +1,193 @@
+#include "setup.hpp"
+#include "shapes.hpp"
+#include "opencl.hpp" // contains "options.hpp", "main.hpp"
+#include "ibm.hpp"
+#include <numeric>
+#include <sstream>
+
+#include <filesystem>
+using std::filesystem::path;
+#include <fstream>
+using std::ofstream;
+#include <iostream>
+using std::cout, std::endl; // TODO replace with spdlog
+
+#include <fmt/core.h>
+// using fmt::format
+using fmt::print;
+#include <fmt/color.h>
+using fmt::color;
+
+#include <spdlog/spdlog.h>
+//using spdlog::info;
+
+#include "io.hpp"
+using fluidx3d::util::io::IO;
+#include "poiseuilleFlow.hpp"
+using fluidx3d::util::poiseuilleFlow::CircularPoiseuilleFlow;
+
+void example(SimulationOptions& options, Parameters& parameters) {
+	json raw = parameters.getRaw();
+	const int id = raw.at("id");
+	//const string path_files = "/tp6-gekle/nas/bt307867/cellsim/novel_2023-10-24/" + std::to_string(id) + "/";
+	const string path_files = fmt::format("SuffleParameterStudy/{}/", id);
+	const path filesPath(path_files);
+	const string path_vtk = path_files + "vtkfiles/";
+	const string path_vtk_velocity = path_vtk + "velocity/";
+	const string path_vtk_strainRateTensor = path_vtk + "strainRateTensor/";
+	const string path_vtk_viscousStressTensor = path_vtk + "viscousStressTensor/";
+	const string path_vtk_polymerConformationTensor = path_vtk + "polymerConformationTensor/";
+
+	/*
+	 * this parameter increases the time step
+	 * --> leads to larger relaxation time tau (not good, but acceptable)
+	 * --> leads to larger Ma (not good, but acceptable)
+	 * --> eventually may lead to inaccuracies
+	 */
+	const double dtScale = 1e0;  // decrease timestep
+
+	// Length of simulation box
+	uint Lx = 2;
+	uint Ly = 43;
+	uint Lz = 2;
+
+	/*
+	 * this parameter decreases the viscosity
[…]

### 2023-10-14 assets/setups/wiParameterStudy/setup/defines.hpp

@@ -1,0 +1,187 @@
+#pragma once
+// ############################################ file paths #############################################
+
+//#define PATH_DEBUG "/data2/s1molehm/FluidX3D/Bead/interpolation/"
+//#define PATH_DEBUG "/tp6_gekle/data2/bt703473/debug/test2/"
+#define PATH_DEBUG "./bin/debug/" // path for debug files (PTX, LOG, VALIDATION)
+#define PATH_IBM   "./bin/ibm/"   // path for IBM extension
+
+
+// ############################################ LBM options ############################################
+
+// There hides a D2Q5 in the code
+//#define D2Q9
+//#define D3Q7 // very very inaccurate
+//#define D3Q13 // very inaccurate; Only works with MRT according to Krüger book p. 87; Does not reproduce EQUILIBRIUM_STRESS correctly.
+
+// Only use these:
+//#define D3Q15
+#define D3Q19 // Best value
+//#define D3Q27 // Better for high Reynolds numbers.
+
+#define SRT // singe relaxation time
+//#define TRT // two relaxiation time (as fast as SRT, but more accurate)
+//#define MRT // multi relaxiation time (as fast as SRT, but more accurate), (### not fully validated for for D3Q7 and D3Q13, incomplete relaxation times for D3Q7 and D3Q27 ###)
+
+//#define UPDATE_RHO // update density field after every step (not necessary for pure LBM)
+//#define UPDATE_U // update velocity field after every step (not necessary for pure LBM, makes tracer particle calculation faster)
+
+#define MOVING_WALLS // moving bounce-back boundaries (incompatible with EQUILIBRIUM_BOUNDARIES due to unnecessary flag recycling)
+//#define EQUILIBRIUM_BOUNDARIES // non-reflecting velocity boundaries, generally more stable, but less accurate (incompatible with MOVING_WALLS due to unnecessary flag recycling)
+//#define BOUNDARY_EXPRESSION // combinable with EQUILIBRIUM_BOUNDARIES xor MOVING_WALLS, !!!doesn't work on AMD for some reason!!!
+
+#define VISCOELASTIC
+#define EQUILIBRIUM_STRESS // Include viscoelastic forces by shifting the equilibrium populations (Onishi 2005) instead of via force
[…]

### 2023-10-14 assets/setups/wiParameterStudy/setup/setup.cpp

@@ -1,0 +1,191 @@
+#include "setup.hpp"
+#include "shapes.hpp"
+#include "opencl.hpp" // contains "options.hpp", "main.hpp"
+#include "ibm.hpp"
+#include <numeric>
+#include <sstream>
+
+#include <filesystem>
+using std::filesystem::path;
+#include <fstream>
+using std::ofstream;
+
+#include <fmt/core.h>
+// using fmt::format
+using fmt::print;
+#include <fmt/color.h>
+using fmt::color;
+
+#include <spdlog/spdlog.h>
+//using spdlog::info;
+
+#include "io.hpp"
+using fluidx3d::util::io::IO;
+#include "poiseuilleFlow.hpp"
+using fluidx3d::util::poiseuilleFlow::CircularPoiseuilleFlow;
+
+void example(SimulationOptions& options, Parameters& parameters) {
+	json raw = parameters.getRaw();
+	const int id = raw.at("id");
+	//const string path_files = "/tp6-gekle/nas/bt307867/cellsim/novel_2023-10-24/" + std::to_string(id) + "/";
+	const string path_files = fmt::format("wiParameterStudy/{}/", id);
+	const path filesPath(path_files);
+	const string path_vtk = path_files + "vtkfiles/";
+	const string path_vtk_velocity = path_vtk + "velocity/";
+	const string path_vtk_strainRateTensor = path_vtk + "strainRateTensor/";
+	const string path_vtk_viscousStressTensor = path_vtk + "viscousStressTensor/";
+	const string path_vtk_polymerConformationTensor = path_vtk + "polymerConformationTensor/";
+
+	/*
+	 * this parameter increases the time step
+	 * --> leads to larger relaxation time tau (not good, but acceptable)
+	 * --> leads to larger Ma (not good, but acceptable)
+	 * --> eventually may lead to inaccuracies
+	 */
+	const double dtScale = 1e0;  // decrease timestep
+
+	// Length of simulation box
+	uint Lx = 2;
+	uint Ly = 43;
+	uint Lz = 2;
+
+	/*
+	 * this parameter decreases the viscosity
+	 * simultaneously k1 and kb are increased to keep Ca and kbHat constant
+	 * --> leads to larger time step (good)
[…]

### 2023-11-27 NovelLBM.tex
Nozzle

@@
 Knowing our simulations to be good we in the following show results for interesting systems, that are not analytically solvable.
-	\section{Results for non analytically solvable systems}\todo{do all of these with MC}
+	\section{Results for non analytically solvable systems}\todo{do all of these with MC}\todo{Do we want walls?}
 	\subsection{Conical nozzle}
 	\todo{do}
+		\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/Nozzle_v.eps}
+		\caption{Plot of the velocity in a conical nozzle.}
+		\label{fig:Nozzle_v}
+	\end{figure}
 	\subsection{Cell in shear flow}
@@
 	Failed for high Ma.
-
+	\subsection{Viscoelastic Reynolds-Scaling}
+	Does not reproduce transitory behavior\todo{NEEDS TO WORK}
 \end{document}

### 2023-11-27 assets/python/fig:Nozzle.py

@@ -1,0 +1,157 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the  class.
+
+Created on Tue Sep  5 10:51:20 2023
+
+@author: Richard Kellnberger
+"""
+
+import json
+import sys
+from multiprocessing import Pool
+from pathlib import Path
+from time import time
+
+import matplotlib.pyplot as plt
+import numpy as np
+import numpy.ma as ma
+import pyvista as pv
+import scipy
+from scipy.special import lambertw
+from style import *
+
+eta_s = 1e-3
+
+
+def process():
+    baseDir = Path("../data/Nozzle/2/")
+    cDir = baseDir / "vtkfiles/polymerConformationTensor/"
+    sDir = baseDir / "vtkfiles/strainRateTensor/"
+    vDir = baseDir / "vtkfiles/velocity/"
+    jsonFile = baseDir / "parameters.json"
+    f = open(jsonFile)
+    parameters = json.load(f)
+    f.close()
+
+    V0 = parameters["info"]["conversions"]["V0"]
+    L0 = parameters["info"]["conversions"]["L0"]
+    T0 = parameters["info"]["conversions"]["T0"]
+    rho0 = 1e3
+    p0 = rho0 * V0**2
+    # print("###")
+    # print(parameters["info"]["px"])
+    # print(p0 / L0)
+    # print(G)
+
+    # cFile = cDir / "C_500000.vtk"
+    # sFile = sDir / "S_500000.vtk"
+    vFile = vDir / "u_500000.vtk"
+    eta_p_SI = 18.7e-3
+    lambda_SI = 0.344e-3
+    epsilon = 0.27
+    # print(uHP(0, G, eta_p_SI))
+    # print("---")
+    # data = pv.read(cFile)
+    # dataS = pv.read(sFile)
+    dataV = pv.read(vFile)
+    Lx, Ly, Lz = dataV.dimensions
+    # tauField = data.get_array("data") * eta_p_SI / lambda_SI
+    # tauField = np.reshape(tauField, (Lx, Ly, Lz, 6), "F")
+    # sField = dataS.get_array("data") / T0
+    # sField = np.reshape(sField, (Lx, Ly, Lz, 6), "F")
+    vField = dataV.get_array("data") * V0
[…]

### 2023-11-27 assets/python/inputForNozzle.py

@@ -43,6 +43,9 @@ def process():
     vField = dataV.get_array("data") * V0
     vField = np.reshape(vField, (Lx, Ly, Lz, 3), "F")
 
+    outFlow = np.sum(vField[..., 0])
+    print(outFlow)
+
     out = open(f"../setups/Nozzle/2/input.tsv", "w")
     for y in range(Ly):
         for z in range(Lz):
@@ -57,7 +60,7 @@ def process():
             yz = cField[Lx // 2, y, z, 4]
             xz = cField[Lx // 2, y, z, 5]
             out.write(
-                f"{1666}\t{y+(335-39)//2}\t{z+(335-39)//2}\t{vx}\t{vy}\t{vz}\t{xx}\t{yy}\t{zz}\t{xy}\t{yz}\t{xz}\n"
+                f"{947-1}\t{y+(191-23)//2}\t{z+(191-23)//2}\t{vx}\t{vy}\t{vz}\t{xx}\t{yy}\t{zz}\t{xy}\t{yz}\t{xz}\n"
             )
 
     baseDir = Path(f"../data/Nozzle/{1}/")
@@ -80,6 +83,12 @@ def process():
     cField = np.reshape(cField, (Lx, Ly, Lz, 6), "F")
     vField = dataV.get_array("data") * V0
     vField = np.reshape(vField, (Lx, Ly, Lz, 3), "F")
+
+    inFlow = np.sum(vField[..., 0])
+    print(inFlow)
+
+    vField *= outFlow / inFlow  # Needed
+    cField *= outFlow / inFlow  # Might be approximately ok
 
     for y in range(Ly):
         for z in range(Lz):

### 2023-11-27 assets/setups/Nozzle/0/setup/setup.cpp

@@ -46,8 +46,8 @@ void example(SimulationOptions& options, Parameters& parameters) {
 
 	// Length of simulation box
 	uint Lx = 2;
-	uint Ly = 39;
-	uint Lz = 39;
+	uint Ly = 23;
+	uint Lz = 23;
 
 	/*
 	 * this parameter decreases the viscosity
@@ -62,7 +62,7 @@ void example(SimulationOptions& options, Parameters& parameters) {
 	initInfo(numberSteps);
 
 	const double R_SI = 200e-6;
-	const double R = 18.5;
+	const double R = 10.5;
 	const double grid_SI = R_SI/R; // Cell has a radius of 15 Lattice units
 	const double rho_SI = 1e3f;
 

### 2023-11-27 assets/setups/Nozzle/1/setup/setup.cpp

@@ -46,8 +46,8 @@ void example(SimulationOptions& options, Parameters& parameters) {
 
 	// Length of simulation box
 	uint Lx = 2;
-	uint Ly = 335;
-	uint Lz = 335;
+	uint Ly = 191;
+	uint Lz = 191;
 
 	/*
 	 * this parameter decreases the viscosity
@@ -62,7 +62,7 @@ void example(SimulationOptions& options, Parameters& parameters) {
 	initInfo(numberSteps);
 
 	const double R_SI = 1.8e-3;
-	const double R = 166.5;
+	const double R = 94.5;
 	const double grid_SI = R_SI/R; // Cell has a radius of 15 Lattice units
 	const double rho_SI = 1e3f;
 

### 2023-11-27 assets/setups/Nozzle/2/setup/setup.cpp

@@ -54,9 +54,9 @@ void example(SimulationOptions& options, Parameters& parameters) {
 	//uint Lx = 1847; // 369 * 5 +2
 	//uint Ly = 371; //43-2 = 41; 41*9+2
 	//uint Lz = 371; // 39 * 9 + 2
-	uint Lx = 1667; // 333 * 5 +2
-	uint Ly = 335; //39-2 = 37; 37*9+2
-	uint Lz = 335; // 37 * 9 + 2
+	uint Lx = 947; // 333 * 5 +2
+	uint Ly = 191; //39-2 = 37; 37*9+2
+	uint Lz = 191; // 37 * 9 + 2
 
 	/*
 	 * this parameter decreases the viscosity
@@ -71,7 +71,7 @@ void example(SimulationOptions& options, Parameters& parameters) {
 	initInfo(numberSteps);
 
 	const double R_SI = 1.8e-3;
-	const double R = 166.5;
+	const double R = 94.5;
 	const double grid_SI = R_SI/R; // Cell has a radius of 15 Lattice units
 	const double rho_SI = 1e3f;
 
@@ -144,12 +144,12 @@ void example(SimulationOptions& options, Parameters& parameters) {
 	double localR;
 	// Define geometry
 	for(uint n=0, x=0, y=0, z=0, sx=lattice.size_x(), sy=lattice.size_y(), sz=lattice.size_z(), s=sx*sy*sz; n<s; n++, x=n%(s/sz)%sx, y=n%(s/sz)/sx, z=n/sx/sy) {
-		localR = (18.5-166.5)/(Lx-3)*(x-1) + 166.5;
+		localR = (10.5-94.5)/(Lx-3)*(x-1) + 94.5;
 		if(x == 0) {
-			localR = 166.5;
+			localR = 94.5;
 		}
 		if(x == Lx-1) {
-			localR = 18.5;
+			localR = 10.5;
 		}
 		if(std::hypot(y - (Ly/2.) + 0.5, z - (Lz/2.) + 0.5) >= localR + 0.5) {
 			lattice.flags[n] = TYPE_W;

### 2023-11-30 assets/python/fig:Nozzle.py
Nozzle

@@ -44,7 +44,7 @@ def process():
     # print(p0 / L0)
     # print(G)
 
-    # cFile = cDir / "C_500000.vtk"
+    cFile = cDir / "C_500000.vtk"
     # sFile = sDir / "S_500000.vtk"
     vFile = vDir / "u_500000.vtk"
     eta_p_SI = 18.7e-3
@@ -52,12 +52,12 @@ def process():
     epsilon = 0.27
     # print(uHP(0, G, eta_p_SI))
     # print("---")
-    # data = pv.read(cFile)
+    data = pv.read(cFile)
     # dataS = pv.read(sFile)
     dataV = pv.read(vFile)
     Lx, Ly, Lz = dataV.dimensions
-    # tauField = data.get_array("data") * eta_p_SI / lambda_SI
-    # tauField = np.reshape(tauField, (Lx, Ly, Lz, 6), "F")
+    tauField = data.get_array("data") * eta_p_SI / lambda_SI
+    tauField = np.reshape(tauField, (Lx, Ly, Lz, 6), "F")
     # sField = dataS.get_array("data") / T0
     # sField = np.reshape(sField, (Lx, Ly, Lz, 6), "F")
     vField = dataV.get_array("data") * V0
@@ -77,6 +77,33 @@ def process():
         vField = ma.masked_array(vField, mask=mask)
 
     vSlice = vField[..., Lz // 2, 0]
+
+    deviator = [[0] * 3] * 3
+    idx = [[0, 3, 5], [3, 1, 4], [5, 4, 2]]
+
+    vonMieses = np.zeros((Lx, Ly, Lz))
+    for i in range(3):
+        for j in range(3):
+            deviator[i][j] = tauField[..., idx[i][j]] - (
+                np.sum(tauField[..., :3], axis=-1) / 3 if idx[i][j] < 3 else 0  # Assume correct?
+            )
+            # print(np.sum(tauField[..., :3], axis=-1)[-1, Ly // 2 + 10, Lz // 2])
+            # print(np.sum(tauField[..., :3], axis=-1)[-1, Ly // 2 - 10, Lz // 2])
+            # print("##")
+            # print(deviator[i][j][-1, Ly // 2 + 10, Lz // 2])
+            # print(deviator[i][j][-1, Ly // 2 - 10, Lz // 2])
+
+            # print(
[…]

### 2023-11-30 NovelLBM.tex
Nozzle
Estimation table

@@
 For some publications we have to estimate it using data extracted from plots and equation \ref{eq:R_eta_CY}.
+The exact details can be found in section \ref{app:viscosityRatio}.
 Publications often stay at or below $R_\eta = 1$\cite{gupta2015,onishi2006,wang2020,su2013_2,gupta2015_2}, while the ones trying higher ratios report being limited below $R_\eta = 10$\cite{malaspinas2010,ma2020,kuron2021} due to stability issues.
@@
 We calculate this 2D flow in 3D as the viscoelastic algorithm has not been validated for 2D velocity sets.
-Otherwise the geometry is identical.
+Otherwise, the geometry is identical.
 It is not entirely clear to us, how they define typical scales.
@@
 		\label{fig:Nozzle_v}
+	\end{figure}
+	\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/Nozzle_sigma_vM.eps}
+		\caption{Plot of the von Mises stress in a conical nozzle.}
+		\label{fig:Nozzle_sigma_vM}
 	\end{figure}
@@
 	Does not reproduce transitory behavior\todo{NEEDS TO WORK}
+	\section{Viscosity Ratio in literature}\label{app:viscosityRatio}
+		\begin{center}
+			\begin{tabular}{l|r|r|l}
+				Author & max(Wi) & max($R_\eta$) & $R_\eta$ estimation \\
+				\hline
+				Malaspinas\cite{malaspinas2010} & 10 & 9 & In 4.3: $R_\nu = \num{0.1}$ \& equation (38) \\
+				\rowcolor{secondaryBackground}
+				Gupta\cite{gupta2015} & 100 & 0.7 & In IV.B: $\frac{\eta_\text{p}}{\eta_\text{A} + \eta_\text{p}} = \num{0.4}$ \\
+				Dzanic\cite{dzanic2022} & 10 & 0.5 & In 4.1: $\beta = \frac{\nu_\text{p}}{\nu_\text{s}} = \num{0.5}$ \\
+				\rowcolor{secondaryBackground}
+				Ma\cite{ma2020} & 100 & 9 & In 4.1: $\beta = \frac{\mu_\text{s}}{\mu_\text{s} + \mu_\text{p}} = \num{0.1}$ \\
+				Onishi\cite{onishi2006} & ? & 1 & In 3.1: $\beta = \frac{\mu_\text{p}}{\mu_\text{s} + \mu_\text{p}}$ \& Table 1: $\beta=\num{0.5}$ \\
+				\rowcolor{secondaryBackground}
+				Wang\cite{wang2020} & \glqq up to O(1)\grqq & 5 & In II: $\eta_\text{p} = c\eta_\text{s}$ \& FIG. 9: $c = \num{5}$\\
+				Dzanic\cite{dzanic2022_2} & 10 & 9 & In 5.1: $\beta = \frac{\nu_\text{s}}{\nu_\text{s} + \nu_\text{p}}$ \& In 5.1.2: $\beta = \num{0.1}$ \\
+				\rowcolor{secondaryBackground}
+				Su\cite{su2013_2} & 10 & 1  & In II: $\beta = \frac{\eta_\text{s}}{\eta_\text{s} + \eta_\text{p}}$ \& In IV.A: $\beta = \num{0.5}$ \\
+				Gupta\cite{gupta2015_2} & ? & 0.7 & In 2: $\frac{\eta_\text{p}}{\eta_\text{d}} = \num{0.4}$ \& $\eta_\text{d} = \eta_\text{A} + \eta_\text{p}$ \\
+				\rowcolor{secondaryBackground}
+				Kuron\cite{kuron2021} & 1 & 9 & In 4.1: $\beta = \num{0.9}$ \& equations (14) \& (15) \\
+				Gupta\cite{gupta2016} & 80 & 0.7 & In 3: $\frac{\eta_\text{p}}{\eta_\text{c,d} + \eta_\text{p}} = \num{0.4}$ \\
+				\rowcolor{secondaryBackground}
+				Onishi\cite{onishi2005} & 1000 & 1 & In 3.2: $\frac{\eta_\text{p}}{\eta_\text{s}} = \num{1}$ \\
+			\end{tabular}
+		\end{center}
 \end{document}

### 2024-01-11 NovelLBM.tex
dark switch
some fixes

@@
 
+\def\dark{}
+
+\ifdefined\dark
 	\definecolor{background}{RGB}{51,51,51} % Because i can lol
@@
 	\pagecolor{background}
+\else
+	\definecolor{secondaryBackground}{RGB}{195,195,195} % Because i can lol
+\fi
 
@@
 The measurements were done using a plate-plate rheometer.
-The first normal stress difference $N_1$ was calculated from the measured normal force using the following equation\cite{kulicke1977}.\todo{data so far does not include second correction term; needed info: was this plate plate?
-where is shear rate in PP rheometer?
-we claim $N_2$ is 0, therefore PP is fine, but we would really prefer CP}\todo{confirm diameter}
+The first normal stress difference $N_1$ is calculated from the measured normal force using the following equation\cite{kulicke1977}.\todo{confirm diameter}
 	\begin{equation}
@@
 	Where $F$ is the measured normal force, $R$ is the radius of the rheometer, $\rho$ is the density of the fluid and $\omega$ is the angular velocity of the rheometer.
+The second term is usually omitted and as we found it to matter little, and as the quality of the data we have available is too limited to warrant such detailed corrections, we also choose to omit it.
+A cone-rheometer would be preferred here, but as $N_2 = 0$ for PTT with $\xi = 0$, the difference is negligible.
 
@@
 This is sufficient.
-While setting $\eta_\text{s} = \SI{1}{\milli\pascal\second}$, the parameters obtained are as follows.\todo{subject to change; different than before!!}
+While setting $\eta_\text{s} = \SI{1}{\milli\pascal\second}$, the parameters obtained are as follows.
 	\begin{align}
@@
 	\subsubsection{Other fluids}
-	\todo{mostly mention $R_\eta$ for different fluids}
-	\todo{do}
+	While the fluids mentioned above are of great importance, they are by no means the only ones used in such experiments.
+From these two examples alone, it can be seen, that the parameters of magnitude.
+As the viscosity can change be several orders of magnitude before the change in behavior of the fluid becomes noticeable to human perceptions, the fluids commonly referred to as shear thinning have a large viscosity ratio.
+In the following values from a few publications are listed to establish the typical values for the ratio.
+It is common (due to experimental limitations), that the shear rate is limited in the experiments in a way, that does not allow seeing both Newtonian plateaus.
+In these cases we provide an upper or lower bound.
+	\begin{center}
+		\begin{tabular}{l|p{3cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{2cm}}
+			Author & Material & $\eta_0/\unit{\pascal\second}$ & $\eta_\infty/\unit{\pascal\second}$ & $R_\eta$ & extracted from \\
+			\hline
+			Amorim\cite{amorim2021} & pre-crosslinked alginate &  >1e4 & <3e-1 & >3e4 & Fig. 3b \\
+			\rowcolor{secondaryBackground}
+			Pössl\cite{possl2021} & blend & 3e2 & 1e-4 & 3e6 & Table 4 \\
+			Paxton\cite{paxton2017} &Nivea Creme\n Alginate& 1e5\n5e4 & <1\n<5e1 & >1e5\n>1e3 & Fig. 4b \\
+			\rowcolor{secondaryBackground}
+			O'Connell\cite{oconnell2020} & pluronic F-127 & >1e6 & <8 & > 2e5 & Chapter 7 Fig. 13 \\
+		\end{tabular}
+	\end{center}
+	Many of these fractions are likely much larger than listed here.
+This is only a lower bound.
+There are many slightly shear thinning fluids, where this fraction is a lot smaller and it also decreases with concentration.
+However, such large values in the tens of thousands are typical for bio-inks and fluids used in adjacent fields.
+This is by design, as a very high zero shear viscosity is desirable to stabilize the construct after printing.
 	With the usual range of the parameters and $R_\eta$ established, we provide a quick overview about the current literature and capabilities in the following section.
@@
 However, this solution does not include $\eta_\text{s}$, which is required in general.
-With the inclusion of the solvent viscosity (for details see appendix \ref{app:PTT}), the solution reads as follows.\todo{also wrong}
-	\begin{equation}
-		u\left(r\right) = \frac{Gl^2}{2^{j+1}\eta_\text{s}}\left[\ln\left(1+\frac{\eta_\text{s}}{\eta_\text{p}}e^\frac{R^2}{l^2}\right)-\ln\left(1+\frac{\eta_\text{s}}{\eta_\text{p}}e^\frac{r^2}{l^2}\right)\right]
-	\end{equation}
+With the inclusion of the solvent viscosity an analytical solution can no longer be found and the use of a semi-analytic solution is required (for details see appendix \ref{app:PTT}).
 	In the following we compare results for channel and pipe flow to these equations for realistic parameters. Afterward we compare the accuracy of our simulation algorithm against literature.
@@
 	\subsection{2D Poiseuille vs theory}\todo{rename to channel flow?}\todo{include cylindrical nozzle from conical nozzle sim}
+	10 µm
 
@@
 	\todo{stability issue, fitting parameter, see fenep repo}
-	\section{Analytical solution for PTT}\label{app:PTT}\todo{This is wrong (to the best of my knoledge) not analytically solveable -> semi analytic solution}
+	\section{Analytical solution for PTT}\label{app:PTT}
 	Our derivation is analogous to Oliveira\cite{oliveira1999}.
@@
 	\begin{align}
-		\dot{\gamma} &= f\left(\frac{2\lambda}{\eta_\text{p}}\left[\partial_xp\right]^2\frac{r^2}{2^{2j}}\right)\frac{1}{\eta_\text{p}}\left(\partial_xp\frac{r}{2^j}-\eta_\text{s}\dot{\gamma}\right)
-		\intertext{This cannot be integrated as easily as without $\eta_\text{s}$, but is still solvable.}
-		\dot{\gamma}\left\{1+\frac{\eta_\text{s}}{\eta_\text{p}}f\left(\frac{2\lambda}{\eta_\text{p}}\left[\partial_xp\right]^2\frac{r^2}{2^{2j}}\right)\right\} &= f\left(\frac{2\lambda}{\eta_\text{p}}\left[\partial_xp\right]^2\frac{r^2}{2^{2j}}\right)\partial_xp\frac{r}{\eta_\text{p}2^j} \\
-		\dot{\gamma} &= \frac{f\left(...\right)}{1+\frac{\eta_\text{s}}{\eta_\text{p}}f\left(...\right)}\partial_xp\frac{r}{\eta_\text{p}2^j}
+		\dot{\gamma} &= f\left(\frac{2\lambda}{\eta_\text{p}}\left[\partial_xp\frac{r}{2^j} - \eta_\text{s}\dot{\gamma}\right]^2\right)\frac{1}{\eta_\text{p}}\left(\partial_xp\frac{r}{2^j}-\eta_\text{s}\dot{\gamma}\right)
+		\intertext{This cannot be integrated as easily as without $\eta_\text{s}$, and is only solvable semi-analytically.}
+		1 &= f\left(\frac{2\lambda}{\eta_\text{p}}\left[\partial_xp\frac{r}{2^j} - \eta_\text{s}\dot{\gamma}\right]^2\right)\frac{1}{\eta_\text{p}}\left(\partial_xp\frac{r}{2^j\dot{\gamma}}-\eta_\text{s}\right)
 	\end{align}
-	For the exponential version of PTT the following $f$ is defined as follows.
+	For the exponential version of PTT $f$ is defined as follows.
 	\begin{equation}
@@
 	\end{equation}
-	The equation can be solved by integration as $\dot{\gamma} = \partial_ru$. We start with the following substitution.
-	\begin{equation}
-		v = \frac{\epsilon\lambda^2}{\eta_\text{p}^2}\left(\partial_xp\right)^2\frac{r^2}{2^{2j-1}}
-	\end{equation}
-	With this $u$ is as follows.
+	This can be inserted in the above equation.
 	\begin{align}
-		u\left(r\right) &= \frac{\eta_\text{p}2^{j-2}}{\epsilon\lambda^2\partial_xp}\int\frac{e^v}{1+\frac{\eta_\text{s}}{\eta_\text{p}}e^v}dv
-		\intertext{Substitute $v^\prime = 1+\frac{\eta_\text{s}}{\eta_\text{p}}e^v$}
-		&= \frac{\eta_\text{p}2^{j-2}}{\epsilon\lambda^2\partial_xp}\frac{\eta_\text{p}}{\eta_\text{s}}\int\frac{1}{v^\prime}dv^\prime \\
-		&= \frac{\eta_\text{p}2^{j-2}}{\epsilon\lambda^2\partial_xp}\frac{\eta_\text{p}}{\eta_\text{s}}\left(\ln v^\prime + C\right) \\
-		&= \frac{\eta_\text{p}2^{j-2}}{\epsilon\lambda^2\partial_xp}\frac{\eta_\text{p}}{\eta_\text{s}}\left[\ln\left(1+\frac{\eta_\text{s}}{\eta_\text{p}}e^v\right) + C\right]
-		\intertext{Using $l^2:= \frac{r^2}{v^2}$}
-		&= \frac{\eta_\text{p}2^{j-2}}{\epsilon\lambda^2\partial_xp}\frac{\eta_\text{p}}{\eta_\text{s}}\left[\ln\left(1+\frac{\eta_\text{s}}{\eta_\text{p}}e^\frac{r^2}{l^2}\right) + C\right]
+		1 &= \exp\left(\frac{2\epsilon\lambda^2}{\eta_\text{p}^2}\left[\partial_xp\frac{r}{2^j} - \eta_\text{s}\dot{\gamma}\right]^2\right)\frac{1}{\eta_\text{p}}\left(\partial_xp\frac{r}{2^j\dot{\gamma}}-\eta_\text{s}\right) \\
+		0 &= \frac{2\epsilon\lambda^2}{\eta_\text{p}^2}\left[\partial_xp\frac{r}{2^j} - \eta_\text{s}\dot{\gamma}\right]^2 - \ln\eta_\text{p} + \ln\left(\partial_xp\frac{r}{2^j\dot{\gamma}}-\eta_\text{s}\right)
 	\end{align}
-	Using $u\left(R\right)\overset{!}{=}0$ and $G = -\partial_xp$ the following is recovered.
-	\begin{equation}
-		u\left(r\right) = \frac{Gl^2}{2^{j+1}\eta_\text{s}}\left[\ln\left(1+\frac{\eta_\text{s}}{\eta_\text{p}}e^\frac{R^2}{l^2}\right)-\ln\left(1+\frac{\eta_\text{s}}{\eta_\text{p}}e^\frac{r^2}{l^2}\right)\right]
-	\end{equation}
+	With this, $\dot{\gamma}$ can be found for each $r$ numerically.
+With $\dot{\gamma} = \partial_ru$, the result can be numerically integrated to find the velocity profile.
+To do this, the radial distance needs to be discretized.
+We split it into \num{1e5} steps and interpolate between them as needed.
+
 	\section{Parameter studies}

### 2024-01-12 NovelLBM.tex
numeric solution

@@
 		1 &= \exp\left(\frac{2\epsilon\lambda^2}{\eta_\text{p}^2}\left[\partial_xp\frac{r}{2^j} - \eta_\text{s}\dot{\gamma}\right]^2\right)\frac{1}{\eta_\text{p}}\left(\partial_xp\frac{r}{2^j\dot{\gamma}}-\eta_\text{s}\right) \\
-		0 &= \frac{2\epsilon\lambda^2}{\eta_\text{p}^2}\left[\partial_xp\frac{r}{2^j} - \eta_\text{s}\dot{\gamma}\right]^2 - \ln\eta_\text{p} + \ln\left(\partial_xp\frac{r}{2^j\dot{\gamma}}-\eta_\text{s}\right)
+		0 &= \frac{2\epsilon\lambda^2}{\eta_\text{p}^2}\left[\partial_xp\frac{r}{2^j} - \eta_\text{s}\dot{\gamma}\right]^2 - \ln\eta_\text{p} + \ln\left(\partial_xp\frac{r}{2^j\dot{\gamma}}-\eta_\text{s}\right) \\
+		0 &= 2\epsilon\lambda^2\dot{\gamma}^2\left[\partial_xp\frac{r}{2^j\dot{\gamma}\eta_\text{p}} - \frac{\eta_\text{s}}{\eta_\text{p}}\right]^2 + \ln\left(\partial_xp\frac{r}{2^j\dot{\gamma}\eta_\text{p}}-\frac{\eta_\text{s}}{\eta_\text{p}}\right) \\
+		0 &= 2\epsilon\lambda^2\dot{\gamma}^2\left[\partial_xp\frac{r}{2^j\dot{\gamma}\eta_\text{p}} - \frac{\eta_\text{s}}{\eta_\text{p}}\right]^2 + \ln\left(\partial_xp\frac{r}{2^j\dot{\gamma}\eta_\text{p}}-\frac{\eta_\text{s}}{\eta_\text{p}}\right)
+		\intertext{This has the following form}
+		0 &= ab^2 + \ln b
 	\end{align}
-	With this, $\dot{\gamma}$ can be found for each $r$ numerically.
-With $\dot{\gamma} = \partial_ru$, the result can be numerically integrated to find the velocity profile.
-To do this, the radial distance needs to be discretized.
-We split it into \num{1e5} steps and interpolate between them as needed.
+	This can be solved using the Lambert W function as follows.
+	\begin{align}
+		b &= -\sqrt{\frac{W_0\left(2a\right)}{2a}}
+		\intertext{Resolving for $r$ yields the following.}
+		r &=  \frac{2^j\eta_\text{s}}{\partial_xp}\dot{\gamma} - \frac{\eta_\text{p}2^{j-1}}{\lambda\sqrt{\epsilon}\partial_xp}\sqrt{W_0\left(4\epsilon\lambda^2\dot{\gamma}^2\right)}
+	\end{align}
+	We notice, that this is the solution for a poiseuille flow with viscosity $\eta_\text{s}$ expanded by a term that applies a nonuniform scaling of the profile  along the $r$-axis towards higher radii.
+We simplify again using $c < 0$ and $d > 0$.
+	\begin{equation}
+		r = c\dot{\gamma} - R_\eta\frac{c}{d}\sqrt{W_0\left(d^2\dot{\gamma}^2\right)}
+	\end{equation}
+	Finally this function needs to be inverted.
+This needs to be done numerically.
+We calculate a range of $\dot{\gamma}$ from $0$ to $\frac{R}{c}$ with a small step interval.
+Here $R$ is the radius of the channel or pipe.
+This is guaranteed to contain all relevant radii.
+We flip the axis and integrate numerically using scipy.integrate.cumulative\_trapezoid\todo{cite}.
+This is very accurate as we conveniently picked the spacing of our now $x$-axis in a way, that the $y$-axis ($\dot{\gamma}$) varies little for each step.
+From the recovered curve $u$ is calculated at each required $r$ through linear interpolation.
 

### 2024-01-12 assets/python/eval/PTT.py
Prepare PTT

@@ -1,0 +1,176 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the   class.
+
+Created on Fri Jan 12 19:03:29 2024
+
+@author: Richard Kellnberger
+"""
+
+import numpy as np
+from scipy.special import lambertw
+from scipy.integrate import cumulative_trapezoid, trapezoid
+
+
+channel = 0
+pipe = 1
+
+
+class PTT:
+    def __init__(self, eta_p, lambda_p, epsilon, eta_s, xi=0):
+        self.eta_p = eta_p
+        self.lambda_p = lambda_p
+        self.epsilon = epsilon
+        self.eta_s = eta_s
+        self.xi = xi
+
+    def prepareVelocityProfile(self, R, G, j):
+        c = 2**j * self.eta_s / (-G)
+        d = 2 * np.sqrt(self.epsilon) * self.lambda_p
+
+        guesses = np.arange(0, R / c * (1 + 1e-6), R / c * 1e-6)
+
+        def r(gd):
+            return c * gd - self.eta_p / self.eta_s * c / d * np.sqrt(
+                lambertw(d**2 * gd**2).real
+            )
+
+        rguesses = r(guesses)
+        idx = np.argmin(np.abs(rguesses - R))
+        if rguesses[idx] < R:
+            idx += 1
+
+        guessesFine = np.arange(
+            0, guesses[idx] * (1 + 3e-6), guesses[idx] * 1e-6
+        )  # The three is due tue offsets needing it
+        rguessesFine = r(guessesFine)
+
+        rVelocity = 0.5 * (rguessesFine[:-1] + rguessesFine[1:])
+        velocity = cumulative_trapezoid(guessesFine, rguessesFine)
+
+        def getInterpolGD():
+            def interpol(r):  # Can only handle scalar r
+                idx = np.argmin(np.abs(rguessesFine - r))
+                if rguessesFine[idx] > r:
+                    idx -= 1
+                elif rguessesFine[idx] == r:
+                    return guessesFine[idx] - offset
+                m = (guessesFine[idx + 1] - guessesFine[idx]) / (
+                    rguessesFine[idx + 1] - rguessesFine[idx]
+                )
+                return guessesFine[idx] + m * (r - rguessesFine[idx]) - offset
+
+            def interpolLoop(r):  # Slow Python loop
+                out = []
+                for i in range(r.size):
+                    out.append(interpol(r[i]))
+                return np.asarray(out)
+
+            def selector(r):
[…]

### 2024-01-14 assets/python/eval/PTT.py
Update PTT.py

@@ -10,6 +10,9 @@ Created on Fri Jan 12 19:03:29 2024
 import numpy as np
 from scipy.special import lambertw
 from scipy.integrate import cumulative_trapezoid, trapezoid
+import matplotlib.pyplot as plt
+from style import cm
+from style import *
 
 
 channel = 0
@@ -23,6 +26,8 @@ class PTT:
         self.epsilon = epsilon
         self.eta_s = eta_s
         self.xi = xi
+        if xi != 0:
+            print("xi != 0 is not implemented!")
 
     def prepareVelocityProfile(self, R, G, j):
         c = 2**j * self.eta_s / (-G)
@@ -54,11 +59,11 @@ class PTT:
                 if rguessesFine[idx] > r:
                     idx -= 1
                 elif rguessesFine[idx] == r:
-                    return guessesFine[idx] - offset
+                    return guessesFine[idx]
                 m = (guessesFine[idx + 1] - guessesFine[idx]) / (
                     rguessesFine[idx + 1] - rguessesFine[idx]
                 )
-                return guessesFine[idx] + m * (r - rguessesFine[idx]) - offset
+                return guessesFine[idx] + m * (r - rguessesFine[idx])
 
             def interpolLoop(r):  # Slow Python loop
                 out = []
@@ -150,12 +155,70 @@ class PTT:
             )
         )
 
+    def eta(self, gd):
+        return (
+            self.eta_p / np.exp(0.5 * lambertw(4 * self.epsilon * (gd * self.lambda_p) ** 2).real)
+            + self.eta_s
+        )
+
+    def N_1(self, gd):
+        return (
+            self.eta_p
+            / (2 * self.epsilon * self.lambda_p)
+            * lambertw(4 * self.epsilon * (self.lambda_p * gd) ** 2).real
+        )
+
+    def plot(self, r):
+        u = self.u(r)
+
+        plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+        plt.plot(r * 1e6, u, label=r"$v_x$")
+        plt.xlabel(r"$r/\unit{\micro\meter}$")
[…]

### 2024-01-14 assets/setups/2DAlginate/setup/setup.cpp
2DAlginate setup

@@ -1,0 +1,213 @@
+#include "setup.hpp"
+#include "shapes.hpp"
+#include "opencl.hpp" // contains "options.hpp", "main.hpp"
+#include "ibm.hpp"
+#include <numeric>
+#include <sstream>
+
+#include <filesystem>
+using std::filesystem::path;
+#include <fstream>
+using std::ofstream;
+
+#include <fmt/core.h>
+// using fmt::format
+using fmt::print;
+#include <fmt/color.h>
+using fmt::color;
+
+#include <spdlog/spdlog.h>
+//using spdlog::info;
+
+#include "fieldWriter.hpp"
+using fluidx3d::io::fieldWriter::FieldWriter;
+#include "io.hpp"
+using fluidx3d::util::io::IO;
+#include "poiseuilleFlow.hpp"
+using fluidx3d::util::poiseuilleFlow::CircularPoiseuilleFlow;
+#include "stringTools.hpp"
+using fluidx3d::util::stringTools::split;
+
+void example(SimulationOptions& options, Parameters& parameters) {
+	json raw = parameters.getRaw();
+	const int id = raw.at("id");
+	//const string path_files = "/tp6-gekle/nas/bt307867/cellsim/novel_2023-10-24/" + std::to_string(id) + "/";
+	const string path_files = fmt::format("Alg2D/{}/", id);
+	const path filesPath(path_files);
+	const string path_vtk = path_files + "vtkfiles/";
+	const string path_vtk_velocity = path_vtk + "velocity/";
+	const string path_vtk_strainRateTensor = path_vtk + "strainRateTensor/";
+	const string path_vtk_viscousStressTensor = path_vtk + "viscousStressTensor/";
+	const string path_vtk_polymerConformationTensor = path_vtk + "polymerConformationTensor/";
+
+	/*
+	 * this parameter increases the time step
+	 * --> leads to larger relaxation time tau (not good, but acceptable)
+	 * --> leads to larger Ma (not good, but acceptable)
+	 * --> eventually may lead to inaccuracies
+	 */
+	const double dtScale = 1e0;  // decrease timestep
+
+	// Length of simulation box
+	uint Lx = 2;
+	uint Ly = 43;
+	uint Lz = 2;
+
+	/*
[…]

### 2024-01-16 NovelLBM.tex
Prepare PTT
Update NovelLBM.tex
some text

@@
 	In the following we compare results for channel and pipe flow to these equations for realistic parameters. Afterward we compare the accuracy of our simulation algorithm against literature.
+	%We use richard/vtk 4dbc4d379842c538f084e68a5dcfe2555a674495 (2024-01-09)
+	\subsection{Channel flow vs theory}
+	Channel flow (also known as 2D Poiseuille) is one of the simplest flows and a very typical example.
+We pick a channel with a radius of \SI{10}{\micro\meter}, meaning the total width is \SI{20}{\micro\meter}.
+This is done with the parameters obtained for the alginate based solution, as these represent the worst case scenario with respect to simulability among the fluids we work with.
+While our scheme is capable of simulating flows of to our knowledge arbitrary parameters, it increases runtime.
+For this parameter set the simulation time on our hardware becomes unreasonable.
+Therefore, for the simulations with the alginate based solutions we, contrary to all our other simulations, do not start from $0$ in all fields.
+We initialize the polymers in an extended state.
+This reduces the initial overshoot in the velocity by orders of magnitude allowing for larger time steps.
+Furthermore, the time to equilibrium of the polymer stretch is shortened considerably.
+This initialization leads to the simulation not accurately reproducing the time dependent behavior during startup, but leaves the steady state valid.
+The cross-section of the resulting flow field can be seen in figure \todo{figure}.
+
+	\todo{describe figure and error}
+
+	\subsection{Pipe flow vs theory}
+	For the 2D case above, the walls are smooth.
+For the 3D case the round pipe has to be approximated leading to a staircase pattern that is not accurate.
+The error introduced by this depends on the lattice resolution.
+We use a diameter of 41 lattice points here.
+We use the same parameter set as above and also initialize the polymers in a stressed state.
+The resulting cross-section can be seen in figure \todo{figure}.
+
+	\todo{describe figure and error}
+
+	As can easily be seen in comparison to the 2D case, the approximation of the walls carries considerable error.
+Still the error is acceptable, particularly for this moderate lattice resolution.
+Further validation of our implementation (using the faster-to-simulate methyl cellulose parameters and initialization at $0$) ca be found in appendix \ref{app:validation}.
+
 	%We use richard/master fe0fc04115b9b6ea6628bcc6cb6593d3f72ac0ea (2023-11-05)
-	\subsection{2D Poiseuille vs theory}\todo{rename to channel flow?}\todo{include cylindrical nozzle from conical nozzle sim}
-	10 µm
-
-	\subsection{3D Poiseuille vs theory}\todo{rename to pipe flow?}
-
 	\subsection{Comparison with literature}
@@
 Knowing our simulations to be good we in the following show results for interesting systems, that are not analytically solvable.
-	\section{Results for non analytically solvable systems}\todo{do all of these with MC}\todo{Do we want walls?}
+	\section{Results for non analytically solvable systems}\todo{do all of these with MC}
+	With the validity and accuracy of our scheme firmly established, we can demonstrate its results for some systems that cannot be solved analytically.
+In the following we will show the flow profiles for a conical nozzle, a cell in shear flow, and a chip for RT-DC measurements\todo{cite?
+spell our RT-DC?}.
+For all of these the methyl cellulose parameters found for a concentration of \SI{0.49}{\percent} have been used.
 	\subsection{Conical nozzle}
-	\todo{do}
+	Conical nozzles are used for example in bio printing.
+For this use case in particular the stresses experienced within the nozzle are of importance.
+We simulate a cell with an inflow radius of \SI{1.8}{\milli\meter} and an outflow radius of \SI{200}{\micro\meter}.
+It has a length of \SI{18}{\milli\meter}.
+The boundary conditions for inflow and outflow are given as the result of a simulation of pipes of the respective radius with a fixed volume flow of \todo{find volume flow}.
+The resulting flow field can be seen in figure \ref{fig:Nozzle_v}.
+The von Mieses stress\todo{cite} can be seen in figure\ref{fig:Nozzle_sigma_vM}.
+It can be seen, that despite the high velocity in the center of the exit, the stress is actually smallest in the center.
+This means, that even for fast flows, given the bio ink and nozzle size is picked correctly, the cells flowing close to the center experience little stress.
+	\todo{complete sim is wrong due to init issue}
 	\begin{figure}[H]
@@
 	\subsection{RT-DC}
-	\todo{do}
+	Real-time deformability cytometry (RT-DC)\todo{cite} is a novel approach for single cell characterization.
+The cells are forced through a constriction.
+The observed deformation can be used to infer the mechanical properties of the cell.
+For this simulation we use periodic boundary conditions and a pressure gradient\todo{specify}.
+The resulting flow can be seen in figure \ref{fig:RT-DC_v}.
+The component typically associated with viscosity of the stress tensor can be see in figure \ref{fig:RT-DC_tau}.
+There are three qualitative differences compared to a purely viscous fluid.
+Directly after the inlet is a region of low stress.
+Due to the advection of the stress, the fluid here despite being inside the constriction has not reacted to it yet.
+This region therefore could produce unexpected cell behavior if one passes through it.
+Similarly directly after the constriction, the stress has not yet lowered.
+If one would divide the stress in these two regions by the strain rate in an attempt to obtain a viscosity one would find an extremely low and an extremely high viscosity respectively.
+Depending on the exact parameters \glqq viscosities\grqq{ } can be reached that cannot be obtained through rheological measurements with the fluid.
+Meaning these viscosities are not valid.
+This is even clearer along the walls directly after the outlet.
+Here the viscosites obtained in this manner become negative.
+This shows the breakdown of the viscosity interpretation in viscoelastic cases and signifies the regions of interesting behavior.
+This also shows why viscoelastic simulations cannot always be replaced by shear thinning models and should be considered despite the high computational cost.
 	\begin{figure}[H]
@@
 	\todo{stability issue, fitting parameter, see fenep repo}
-	\section{Analytical solution for PTT}\label{app:PTT}
+	\section{Velocity profile for PTT}\label{app:PTT}
 	Our derivation is analogous to Oliveira\cite{oliveira1999}.
@@
 
-	\section{Parameter studies}
+	\section{Parameter studies and validation}\label{app:validation}
 	\todo{do}
@@
 
-	\subsection{3D Poiseuille vs theory}\todo{not finished}
+	\subsection{3D Poiseuille vs theory}\todo{not finished}\todo{include cylindrical nozzle from conical nozzle sim for resolution dependency?}
 	Like above but 3D\n

### 2024-01-16 NovelLBM.tex
2DAlginate

@@
 We pick a channel with a radius of \SI{10}{\micro\meter}, meaning the total width is \SI{20}{\micro\meter}.
-This is done with the parameters obtained for the alginate based solution, as these represent the worst case scenario with respect to simulability among the fluids we work with.
+We pick periodic boundary conditions and drive the flow with a pressure gradient of \SI{-1e7}{\pascal\per\meter}.
+This simulation was done using the parameters obtained for the alginate based solution, as these represent the worst case scenario with respect to simulability among the fluids we work with.
 While our scheme is capable of simulating flows of to our knowledge arbitrary parameters, it increases runtime.
@@
 This initialization leads to the simulation not accurately reproducing the time dependent behavior during startup, but leaves the steady state valid.
-The cross-section of the resulting flow field can be seen in figure \todo{figure}.
-
-	\todo{describe figure and error}
+The cross-section of the resulting flow field can be seen in figure \ref{fig:2DAlginateU}.
+Due to the long runtime, we stopped the simulation, early compared to the others.
+This means, that the simulation had not yet reached full equilibrium.
+Consequently, the error obtained here (see figure \ref{fig:2DAlginateErr}) is likely higher than what it would be after full relaxation.
+The average error as obtained by a typical L2 norm is \num{9e-4}.
+	\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DAlginateU.eps}
+		\caption{Plot of the cross-section of the velocity of an alginate channel flow. Likely not fully in equilibrium.}
+		\label{fig:2DAlginateU}
+	\end{figure}
+	\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DAlginateErr.eps}
+		\caption{Plot of error of the cross-section of the velocity of an alginate channel flow. Likely not fully in equilibrium.}
+		\label{fig:2DAlginateErr}
+	\end{figure}
+	The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall.
+The same simulation is done for the 3D case in the following.
 
@@
 We use a diameter of 41 lattice points here.
-We use the same parameter set as above and also initialize the polymers in a stressed state.
+We use the same parameter set as above, aside from doubling the pressure gradient and also initialize the polymers in a stressed state.
 The resulting cross-section can be seen in figure \todo{figure}.

### 2024-01-16 assets/python/eval/PTT.py

@@ -1,248 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-File to house the   class.
-
-Created on Fri Jan 12 19:03:29 2024
-
-@author: Richard Kellnberger
-"""
-
-import matplotlib.pyplot as plt
-import numpy as np
-from scipy.integrate import cumulative_trapezoid, trapezoid
-from scipy.special import lambertw
-from style import *
-from style import cm
-
-channel = 0
-pipe = 1
-
-
-class PTT:
-    def __init__(self, eta_p, lambda_p, epsilon, eta_s, xi=0):
-        self.eta_p = eta_p
-        self.lambda_p = lambda_p
-        self.epsilon = epsilon
-        self.eta_s = eta_s
-        self.xi = xi
-        if xi != 0:
-            print("xi != 0 is not implemented!")
-
-    def prepareVelocityProfile(self, R, G, j):
-        c = 2**j * self.eta_s / (-G)
-        d = 2 * np.sqrt(self.epsilon) * self.lambda_p
-
-        guesses = np.arange(0, R / c * (1 + 1e-6), R / c * 1e-6)
-
-        def r(gd):
-            return c * gd - self.eta_p / self.eta_s * c / d * np.sqrt(
-                lambertw(d**2 * gd**2).real
-            )
-
-        rguesses = r(guesses)
-        idx = np.argmin(np.abs(rguesses - R))
-        if rguesses[idx] < R:
-            idx += 1
-
-        guessesFine = np.arange(
-            0, guesses[idx] * (1 + 3e-6), guesses[idx] * 1e-6
-        )  # The three is due tue offsets needing it
-        rguessesFine = r(guessesFine)
-
-        rVelocity = 0.5 * (rguessesFine[:-1] + rguessesFine[1:])
-        velocity = cumulative_trapezoid(guessesFine, rguessesFine)
-
-        def getInterpolGD():
-            def interpol(r):  # Can only handle scalar r
-                idx = np.argmin(np.abs(rguessesFine - r))
-                if rguessesFine[idx] > r:
-                    idx -= 1
-                elif rguessesFine[idx] == r:
-                    return guessesFine[idx]
-                m = (guessesFine[idx + 1] - guessesFine[idx]) / (
-                    rguessesFine[idx + 1] - rguessesFine[idx]
-                )
-                return guessesFine[idx] + m * (r - rguessesFine[idx])
-
-            def interpolLoop(r):  # Slow Python loop
-                out = []
[…]

### 2024-01-16 assets/python/fig:2DAlginate.py

@@ -1,0 +1,89 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the  class.
+
+Created on Tue Sep  5 10:51:20 2023
+
+@author: Richard Kellnberger
+"""
+
+import json
+from pathlib import Path
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pyvista as pv
+from style import cm
+from style import *
+from fluidx3d.eval.models import PTT
+
+
+def process(i):
+    baseDir = Path(f"../data/novel_2024-01-15/{i}/")
+    cDir = baseDir / "vtkfiles/polymer_conformationTensor/"
+    vDir = baseDir / "vtkfiles/velocity/"
+    jsonFile = baseDir / "parameters.json"
+    f = open(jsonFile)
+    parameters = json.load(f)
+    f.close()
+
+    V0 = parameters["info"]["conversions"]["V0"]
+    L0 = parameters["info"]["conversions"]["L0"]
+    T0 = parameters["info"]["conversions"]["T0"]
+    rho0 = 1e3
+    p0 = rho0 * V0**2
+    G = parameters["info"]["px"] * p0 / L0
+
+    cFile = cDir / "CT_2000000000.vtk"
+    vFile = vDir / "u_2000000000.vtk"
+
+    data = pv.read(cFile)
+    dataV = pv.read(vFile)
+    Lx, Ly, Lz = data.dimensions
+    origin = data.origin
+    R = (Ly - 2) / 2 * L0
+
+    tauField = data.get_array("data") * PTT.alginate.eta_p / PTT.alginate.lambda_p
+    tauField = np.reshape(tauField, (Lx, Ly, Lz, 6), "F")
+    vField = dataV.get_array("data") * V0
+    vField = np.reshape(vField, (Lx, Ly, Lz, 3), "F")
+
+    vSlice = vField[Lx // 2, ..., Lz // 2, 0]
+    r = (np.arange(0, Ly, 1, dtype=np.float128) + origin[1]) * L0
+    r[0] += L0 / 2
+    r[-1] -= L0 / 2
+    uErr = PTT.alginate.u(np.abs(r))
+
+    rTheory = np.arange(-R, R * (1 + 1e-3), R * 1e-3)
+    PTT.alginate.prepareVelocityProfile(R, G, PTT.channel)
+    u = PTT.alginate.u(np.abs(rTheory))
+
[…]

### 2024-01-16 assets/python/fluidx3d/eval/models/PTT.py

@@ -213,46 +213,3 @@ class PTT:
 
 
 alginate = PTT(48.2, 0.343, 0.545, 1e-3)
-
-R = 10e-6
-G = 1e8  # Looks nice
-G = 4e6  # Similar to steffen
-G = 2e7  # Used in sim
-alginate.prepareVelocityProfile(R, G, pipe)  # Q is per thickness for 2D case
-print(alginate.Q)
-
-µ = 1e6  # convert to µ
-l = 1e1**3  # convert to liter
-h = 1 / 3600  # convert to per hour
-print(alginate.Q * µ * l / h)
-
-r = np.arange(0, R * (1 + 1e-3), R * 1e-3)
-print(r)
-alginate.plot(r)
-
-step = R / 20.5
-points = np.arange(21)
-print(points * step)
-
-radii = []
-for y in points:
-    for z in points:
-        if np.sqrt(y**2 + z**2) < 20.5:
-            radii.append(np.sqrt(y**2 + z**2) * step)
-
-gd = alginate.gd(np.asarray(radii))
-N_1 = alginate.N_1(gd)
-vs = alginate.eta(gd) * gd
-
-plt.plot(radii, N_1)
-plt.plot(radii, vs)
-plt.show()
-
-f = open("preset3D.csv", "w")
-i = 0
-for y in points:
-    for z in points:
-        if np.sqrt(y**2 + z**2) < 20.5:
-            f.write(f"{y};{z};{N_1[i]:.20f};{vs[i]-1e-3*gd[i]:.20f}\n")
-            i += 1
-f.close()

### 2024-01-16 assets/python/prepare2DAlginate.py

@@ -1,0 +1,47 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the   class.
+
+Created on Tue Jan 16 20:35:58 2024
+
+@author: Richard Kellnberger
+"""
+
+# 2DAlginate is 2024-01-15/0
+
+import numpy as np
+import matplotlib.pyplot as plt
+from fluidx3d.eval.models import PTT
+
+R = 10e-6
+# G = 1e8  # Looks nice
+# G = 4e6  # Similar to steffen
+G = 1e7  # Used in sim
+PTT.alginate.prepareVelocityProfile(R, G, PTT.channel)  # Q is per thickness for 2D case
+print(PTT.alginate.Q)
+
+µ = 1e6  # convert to µ
+l = 1e1**3  # convert to liter
+h = 1 / 3600  # convert to per hour
+print(PTT.alginate.Q * µ * l / h)
+
+r = np.arange(0, R * (1 + 1e-3), R * 1e-3)
+print(r)
+PTT.alginate.plot(r)
+
+step = R / 20.5
+points = np.arange(21)
+print(points * step)
+
+gd = PTT.alginate.gd(points * step)
+N_1 = PTT.alginate.N_1(gd)
+vs = PTT.alginate.eta(gd) * gd
+
+plt.plot(points * step, N_1)
+plt.plot(points * step, vs)
+plt.show()
+
+f = open("preset.csv", "w")
+for i in points:
+    f.write(f"{i};{N_1[i]:.20f};{vs[i]-1e-3*gd[i]:.20f}\n")
+f.close()

### 2024-01-16 assets/python/prepare3DAlginate.py

@@ -1,0 +1,57 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the   class.
+
+Created on Tue Jan 16 20:35:58 2024
+
+@author: Richard Kellnberger
+"""
+
+# 3DAlginate is 2024-01-15/1
+
+import numpy as np
+import matplotlib.pyplot as plt
+from fluidx3d.eval.models import PTT
+
+R = 10e-6
+# G = 1e8  # Looks nice
+# G = 4e6  # Similar to steffen
+G = 2e7  # Used in sim
+PTT.alginate.prepareVelocityProfile(R, G, PTT.pipe)  # Q is per thickness for 2D case
+print(PTT.alginate.Q)
+
+µ = 1e6  # convert to µ
+l = 1e1**3  # convert to liter
+h = 1 / 3600  # convert to per hour
+print(PTT.alginate.Q * µ * l / h)
+
+r = np.arange(0, R * (1 + 1e-3), R * 1e-3)
+print(r)
+PTT.alginate.plot(r)
+
+step = R / 20.5
+points = np.arange(21)
+print(points * step)
+
+radii = []
+for y in points:
+    for z in points:
+        if np.sqrt(y**2 + z**2) < 20.5:
+            radii.append(np.sqrt(y**2 + z**2) * step)
+
+gd = PTT.alginate.gd(np.asarray(radii))
+N_1 = PTT.alginate.N_1(gd)
+vs = PTT.alginate.eta(gd) * gd
+
+plt.plot(radii, N_1)
+plt.plot(radii, vs)
+plt.show()
+
+f = open("preset3D.csv", "w")
+i = 0
+for y in points:
+    for z in points:
+        if np.sqrt(y**2 + z**2) < 20.5:
+            f.write(f"{y};{z};{N_1[i]:.20f};{vs[i]-1e-3*gd[i]:.20f}\n")
+            i += 1
+f.close()

### 2024-01-16 NovelLBM.tex
introduction

@@
 	\section{Introduction}
-	\todo{do}
+	For a solution to be well suited for usage as a bioink during bioprinting its rheology has to fulfill certain requirements.
+During the printing process it should flow easily through the nozzle, meaning the viscosity should be low.
+This is not only beneficial for ease of use, but is also crucial for survivability of the cells, as the stress they experience is dependent on the viscosity.
+However, after the printing process, it is desired, that the printed construct is stable.
+This can be temporarily archived by very high viscosities.
+Therefore, one approach to solve this is to use shear thinning fluids.
+Shear thinning fluids can easily be produced by dissolving polymers in water.
+This however, has the side effect of viscoelasticity.
+Due to the polymers the solution also exhibits elastic behavior.
+The influence of which on the printing process is not well understood yet.
+For realistic bioinks, the ratio of their zero shear viscosity and their infinite shear viscosity is large as is expected based on the desired attributes mentioned above.
+For such large viscosity ratios, simulating viscoelastic materials with Lattice Boltzmann methods was to our knowledge not yet possible.
+
+	Such simulations would however be very beneficial.
+They allow the \glqq measurement\grqq{ }of parameters that are otherwise hard or even impossible to access.
+They allow the prediction of the outcome of experiments without performing them, which is especially helpful if the experiment cannot be easily performed.
+An example would be the design of new and improved printing nozzles.
+With simulations, the geometry can be optimized to a degree, that would be near impossible using iterative experiments.
+The large amounts of data simulations can provide allow better understanding of the fundamental processes, that cause observed behavior.
+\todo{"List some simulations for bionprinting, bioinks that have been done (restrict to only viscoelastic sims)"}
+
+	Simulations using Lattice Boltzmann methods (LBM) are popular, as it has many advantages.
+It is very extensible and thus can deal with complex geometries, particles (e.g.
+cells) suspended in the fluid and many different interactions within and between those.
+Most importantly it is and easily parallelizable algorithm and thus can be run on GPUs or similar accelerators.
+This allows even large domains to be simulated in short amount of time with commodity GPUs and no need for any supercomputer.
+It is also easily possible to extend LBM to deal with viscoelastic fluids.
+This has been done before by multiple groups.
+There are many publications discussing such approaches in two dimensions\cite{ispolatov2002,wang2019,su2013,giraud1998,xie2018,dzanic2022,frank2006,zou2014,lee2017,dzanic2022_2,sedaghat2021,frantziskonis2011,qin2023,yoshino2008,papenkort2015,phillips2011,onishi2005}.
+Simulations in three dimensions have a higher computational cost and are not as abundant, but have also been performed by many\cite{malaspinas2010,gupta2015,lallemand2003,ma2020,onishi2006,wang2020,dellar2014,su2013_2,wang2021,kuron2021,gupta2016}.
+Among these many are concerned about stability.
+Some include diffusivity of the polymer stress in their model to increase stability\cite{malaspinas2010,ma2020,wang2020,wang2021}.
+Other remedies include special decompositions of the stress tensor\cite{dzanic2022} or optimization of the solvent contribution\cite{gupta2015}.
+However, none of these reach the relevant viscosity ratios for bioinks.
+
+	Here we show our novel simulation approach for bioinks.
+It is specifically tailored to support arbitrary viscosity ratios and thus is able to simulate common bioinks or any other viscoelastic material with similar properties while providing high accuracy and stability.
+This is archived by subtracting a viscous stress from the polymer stress calculated from the PTT model.
+This offset is corrected by increasing the viscosity of the base LBM algorithm accordingly.
 
@@
 In the following we will show the flow profiles for a conical nozzle, a cell in shear flow, and a chip for RT-DC measurements\todo{cite?
-spell our RT-DC?}.
+spell out RT-DC?}.
 For all of these the methyl cellulose parameters found for a concentration of \SI{0.49}{\percent} have been used.
@@
 If one would divide the stress in these two regions by the strain rate in an attempt to obtain a viscosity one would find an extremely low and an extremely high viscosity respectively.
-Depending on the exact parameters \glqq viscosities\grqq{ } can be reached that cannot be obtained through rheological measurements with the fluid.
+Depending on the exact parameters \glqq viscosities\grqq{ }can be reached that cannot be obtained through rheological measurements with the fluid.
 Meaning these viscosities are not valid.

### 2024-01-17 NovelLBM.tex
3D Alginate

@@
 We use the same parameter set as above, aside from doubling the pressure gradient and also initialize the polymers in a stressed state.
-The resulting cross-section can be seen in figure \todo{figure}.
-
-	\todo{describe figure and error}
-
-	As can easily be seen in comparison to the 2D case, the approximation of the walls carries considerable error.
+The resulting cross-section can be seen in figure \ref{fig:3DAlginateU}.
+
+	\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DAlginateU.eps}
+		\caption{Plot of the cross-section of the velocity of an alginate pipe flow. Likely not fully in equilibrium.}
+		\label{fig:3DAlginateU}
+	\end{figure}
+	\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DAlginateErr.eps}
+		\caption{Plot of error of the cross-section of the velocity of an alginate pipe flow. Likely not fully in equilibrium.}
+		\label{fig:3DAlginateErr}
+	\end{figure}
+	As can easily be seen in figure \ref{fig:3DAlginateErr} in comparison to the 2D case, the approximation of the walls carries considerable error.
+The L2 error is \num{0.014}.
 Still the error is acceptable, particularly for this moderate lattice resolution.

### 2024-01-17 assets/python/fig:3DAlginate.py

@@ -1,0 +1,89 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the  class.
+
+Created on Tue Sep  5 10:51:20 2023
+
+@author: Richard Kellnberger
+"""
+
+import json
+from pathlib import Path
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pyvista as pv
+from fluidx3d.eval.models import PTT
+from style import *
+from style import cm
+
+
+def process(i):
+    baseDir = Path(f"../data/novel_2024-01-15/{i}/")
+    cDir = baseDir / "vtkfiles/polymer_conformationTensor/"
+    vDir = baseDir / "vtkfiles/velocity/"
+    jsonFile = baseDir / "parameters.json"
+    f = open(jsonFile)
+    parameters = json.load(f)
+    f.close()
+
+    V0 = parameters["info"]["conversions"]["V0"]
+    L0 = parameters["info"]["conversions"]["L0"]
+    T0 = parameters["info"]["conversions"]["T0"]
+    rho0 = 1e3
+    p0 = rho0 * V0**2
+    G = parameters["info"]["px"] * p0 / L0
+
+    cFile = cDir / "CT_2000000000.vtk"
+    vFile = vDir / "u_2000000000.vtk"
+
+    data = pv.read(cFile)
+    dataV = pv.read(vFile)
+    Lx, Ly, Lz = data.dimensions
+    origin = data.origin
+    R = (Ly - 2) / 2 * L0
+
+    tauField = data.get_array("data") * PTT.alginate.eta_p / PTT.alginate.lambda_p
+    tauField = np.reshape(tauField, (Lx, Ly, Lz, 6), "F")
+    vField = dataV.get_array("data") * V0
+    vField = np.reshape(vField, (Lx, Ly, Lz, 3), "F")
+
+    vSlice = vField[Lx // 2, ..., Lz // 2, 0]
+    r = (np.arange(0, Ly, 1, dtype=np.float128) + origin[1]) * L0
+    r[0] += L0 / 2
+    r[-1] -= L0 / 2
+    PTT.alginate.prepareVelocityProfile(R, G, PTT.pipe)
+    uErr = PTT.alginate.u(np.abs(r))
+
+    rTheory = np.arange(-R, R * (1 + 1e-3), R * 1e-3)
+    u = PTT.alginate.u(np.abs(rTheory))
+
[…]

### 2024-01-23 assets/python/fig:2DAlginate.py
update plot scripts

@@ -13,9 +13,9 @@ from pathlib import Path
 import matplotlib.pyplot as plt
 import numpy as np
 import pyvista as pv
-from style import cm
-from style import *
 from fluidx3d.eval.models import PTT
+from style import *
+from style import cm
 
 
 def process(i):
@@ -52,10 +52,10 @@ def process(i):
     r = (np.arange(0, Ly, 1, dtype=np.float128) + origin[1]) * L0
     r[0] += L0 / 2
     r[-1] -= L0 / 2
+    PTT.alginate.prepareVelocityProfile(R, G, PTT.channel)
     uErr = PTT.alginate.u(np.abs(r))
 
     rTheory = np.arange(-R, R * (1 + 1e-3), R * 1e-3)
-    PTT.alginate.prepareVelocityProfile(R, G, PTT.channel)
     u = PTT.alginate.u(np.abs(rTheory))
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))

### 2024-01-23 assets/python/fig:2DParameterStudy.py

@@ -8,92 +8,14 @@ Created on Tue Sep  5 10:51:20 2023
 """
 
 import json
-import sys
 from pathlib import Path
 from time import time
 
 import matplotlib.pyplot as plt
 import numpy as np
 import pyvista as pv
-import scipy
-from scipy.special import lambertw
-from multiprocessing import Pool
-from style import *
-
-eta_s = 1e-3
-j = 0
-R = 10e-6
-
-
-def ptt_eta(gd, eta_p, lam, epsilon):
-    return eta_p / np.exp(0.5 * lambertw(4 * epsilon * (gd * lam) ** 2)) + eta_s
-
-
-def getl2(G, eta_p, lam, epsilon):
-    return np.float128(2 ** (2 * j - 1) * eta_p**2 / (epsilon * lam**2 * G**2))
-
-
-# According to Oliveira 1999
-def uS(r, G, eta_p, lam, epsilon):  # eta_s = 0
-    l2 = getl2(G, eta_p, lam, epsilon)
-    return G * l2 / (2 ** (j + 1) * (eta_p + eta_s)) * (np.exp(R**2 / l2) - np.exp(r**2 / l2))
-
-
-def uHP(r, G, eta_p):
-    return G / (2 * (eta_p + eta_s)) * (R**2 - r**2)
-
-
-def getFun(r, G, lam, eta_p, epsilon):
-    def fun(x):
-        return (
-            2 * epsilon * lam**2 / eta_p**2 * (-G * r / 2**j - eta_s * x) ** 2
-            - np.log(eta_p)
-            + np.log(-G * r / 2**j / x - eta_s)
-        )
-
-    return fun
-
-
-def calc(r, G, lam, eta_p, epsilon):
-    guess = -G * r / 2**j / eta_s / 10
-    fun = getFun(r, G, lam, eta_p, epsilon)
-    answ = scipy.optimize.root(fun, guess)
-    return answ.x[0]
-
-
-def findRoot(G, lam, eta_p, epsilon):
-    dr = R * 1e-5
-    r = np.arange(0, R, dr)
-    ru = np.arange(dr, R + dr, dr)
-
-    param = [(re, G, lam, eta_p, epsilon) for re in r[1:]]
-
-    with Pool(32) as p:
-        res = p.starmap(calc, param)
-
-    gds = np.concatenate(([0], res))
-
-    us = []
[…]

### 2024-01-23 assets/python/fig:3DParameterStudy.py

@@ -8,92 +8,14 @@ Created on Tue Sep  5 10:51:20 2023
 """
 
 import json
-import sys
 from pathlib import Path
 from time import time
 
 import matplotlib.pyplot as plt
 import numpy as np
 import pyvista as pv
-import scipy
-from scipy.special import lambertw
-from multiprocessing import Pool
-from style import *
-
-eta_s = 1e-3
-j = 1
-R = 10e-6
-
-
-def ptt_eta(gd, eta_p, lam, epsilon):
-    return eta_p / np.exp(0.5 * lambertw(4 * epsilon * (gd * lam) ** 2)) + eta_s
-
-
-def getl2(G, eta_p, lam, epsilon):
-    return np.float128(2 ** (2 * j - 1) * eta_p**2 / (epsilon * lam**2 * G**2))
-
-
-# According to Oliveira 1999
-def uS(r, G, eta_p, lam, epsilon):  # eta_s = 0
-    l2 = getl2(G, eta_p, lam, epsilon)
-    return G * l2 / (2 ** (j + 1) * (eta_p + eta_s)) * (np.exp(R**2 / l2) - np.exp(r**2 / l2))
-
-
-def uHP(r, G, eta_p):
-    return G / (4 * (eta_p + eta_s)) * (R**2 - r**2)
-
-
-def getFun(r, G, lam, eta_p, epsilon):
-    def fun(x):
-        return (
-            2 * epsilon * lam**2 / eta_p**2 * (-G * r / 2**j - eta_s * x) ** 2
-            - np.log(eta_p)
-            + np.log(-G * r / 2**j / x - eta_s)
-        )
-
-    return fun
-
-
-def calc(r, G, lam, eta_p, epsilon):
-    guess = -G * r / 2**j / eta_s / 10
-    fun = getFun(r, G, lam, eta_p, epsilon)
-    answ = scipy.optimize.root(fun, guess)
-    return answ.x[0]
-
-
-def findRoot(G, lam, eta_p, epsilon):
-    dr = R * 1e-5
-    r = np.arange(0, R, dr)
-    ru = np.arange(dr, R + dr, dr)
-
-    param = [(re, G, lam, eta_p, epsilon) for re in r[1:]]
-
-    with Pool(32) as p:
-        res = p.starmap(calc, param)
-
-    gds = np.concatenate(([0], res))
-
-    us = []
[…]

### 2024-01-23 assets/python/fluidx3d/eval/models/PTT.py

@@ -167,6 +167,12 @@ class PTT:
             * lambertw(4 * self.epsilon * (self.lambda_p * gd) ** 2).real
         )
 
+    def u(self, _):
+        raise Exception("Forgot to call prepareVelocityProfile before u")
+
+    def gd(self, _):
+        raise Exception("Forgot to call prepareVelocityProfile before gd")
+
     def plot(self, r):
         u = self.u(r)
 
@@ -213,3 +219,4 @@ class PTT:
 
 
 alginate = PTT(48.2, 0.343, 0.545, 1e-3)
+mc0_49 = PTT(18.7e-3, 0.344e-3, 0.27, 1e-3)

### 2024-01-23 NovelLBM.tex
finish validation

@@
 $\epsilon$ is the extensibility parameter and $\xi$ describes the slip in the polymer network.
-This model uses the upper convected derivative, which is defined as follows.\todo{clarify nabla u and fix Ts}
+This model uses the upper convected derivative, which is defined as follows.
 	\begin{equation}
@@
 	\end{equation}
-	Where $\vec{u}$ is the fluid velocity. This equation contains the material derivative defined as follows.
+	Where $\vec{u}$ is the fluid velocity and $\left(\nabla\vec{u}\right)_{ij} = \nabla_i\vec{u}_j$. This equation contains the material derivative defined as follows.
 	\begin{equation}
@@
 The measurements were done using a plate-plate rheometer.
-The first normal stress difference $N_1$ is calculated from the measured normal force using the following equation\cite{kulicke1977}.\todo{confirm diameter}
+The first normal stress difference $N_1$ is calculated from the measured normal force using the following equation\cite{kulicke1977}.
 	\begin{equation}
@@
 However, we modify the coupled stress as is explained in the following.
-	\subsection{Novel viscosity shuffling}
+	\subsection{Novel viscosity shuffling}\label{sec:shuffling}
 	Performing Chapman-Enskog analysis on the LBM reveals the total stress experienced by the fluid ($\ma{\sigma}$) to be as follows\cite{onishi2006}.
@@
 We stick with $\ma{A}$ as the Tensor containing the stress information, although its meaning is different for the different models listed here.
-This way, it can be seen, that all the models listed here can be brought to the common form listed below.\todo{claryfy nabla u and fix Ts}
+This way, it can be seen, that all the models listed here can be brought to the common form listed below.
 	\begin{equation}
@@
 	\section{Parameter studies and validation}\label{app:validation}
-	\todo{do}
+	To validate, that our algorithm is indeed valid, we use it to simulate some typical system and determine the observed error.
+First we vary the shuffle fraction to assure that its value is irrelevant as its introduction in section \ref{sec:shuffling} predicts.
+Following that we calculate the shear flow for varying shear rates to reproduce the predicted shear thinning.
+Finally 2D and 3D poiseuille flows are simulated for different pressure gradients.
+A high degree of accuracy is observed in all these tests showing the validity of our algorithm.
 	\subsection{Viscosity shuffle fraction dependency}\label{app:viscSuffleDependency}
@@
 The simulation gives $\eta = \SI{19.6999988048\pm0.0000000002}{\milli\pascal}$, while theory gives $\eta = \SI{19.699998805}{\milli\pascal}$.
-Therefore, the simulation is incredibly accurate.\todo{maybe add alphas < 1}
+Therefore, the simulation is incredibly accurate.
 	\begin{figure}[H]
@@
 	\end{figure}
-	\subsection{2D Poiseuille vs theory}\todo{not finished}
-	setup above R = 10µm; shear rate approximation to px\n
-	Worst $G$.
-	\iffalse
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU0.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyU0}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU1.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyU1}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU2.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyU2}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU3.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyU3}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU4.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyU4}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU5.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyU5}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU6.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyU6}
-	\end{figure}
-	\fi
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU7.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyU7}
-	\end{figure}
-	\iffalse
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU8.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyU8}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU9.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyU9}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU10.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyU10}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU11.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyU11}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU12.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyU12}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU13.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyU13}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyU14.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyU14}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr0.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyErr0}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr1.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyErr1}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr2.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyErr2}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr3.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyErr3}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr4.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyErr4}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr5.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyErr5}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr6.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyErr6}
-	\end{figure}
-	\fi
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr7.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyErr7}
-	\end{figure}
-	\iffalse
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr8.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyErr8}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr9.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyErr9}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr10.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyErr10}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr11.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyErr11}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr12.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyErr12}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr13.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyErr13}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr14.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:2DParameterStudyErr14}
-	\end{figure}
-	\fi
+	\subsection{2D Poiseuille vs theory}
+	The setup remains as above, but the imposed shear flow is replaced by a pressure gradient.
+The radius of the channel flow is set as \SI{10}{\micro\meter}.
+The simulations were run for multiple values for the pressure gradient spaced in a way to approximately cover the range of the Weissenberg number seen in the section before.
+The resulting errors can be seen in figure \ref{fig:2DParameterStudyErr}.
+Due to the shear thinning behavior the shear rate is not constant for the whole channel, therefore the direct relation of the pressure gradient to the Weissenberg number is not possible.
+Averaging the shear rate it becomes clear that the error maximum here corresponds to the maximum slope seen in figure \ref{fig:wiParameterStudy}.
+The plots for the velocity profile and its error of this worst case parameter can be seen in figure \ref{fig:2DParameterStudyUWorst} and figure \ref{fig:2DParameterStudyErrWorst} respectively.
+It is clear, that the simple bounce back boundaries employed on the wall are a major cause of the observed error.
+The error in total is insignificant.
 	\begin{figure}[H]
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
+		\caption{Plot of the simulation error in a channel flow as a dependency of the pressure gradient.}
 		\label{fig:2DParameterStudyErr}
 	\end{figure}
-	Interestingly, the last one work besides Ma being approx 10.\n
-	This error is not influenced by shuffling fraction or lattice resolution\n
-	The shape the sim returns can be obtained by the theory by modifying px and or etap\n
-	The resulting error is (approx) centered around Wi of max viscosity gradient.
-
-	\subsection{3D Poiseuille vs theory}\todo{not finished}\todo{include cylindrical nozzle from conical nozzle sim for resolution dependency?}
-	Like above but 3D\n
-	Worst $G$.
-	\iffalse
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU0.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyU0}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU1.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyU1}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU2.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyU2}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU3.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyU3}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU4.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyU4}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU5.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyU5}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU6.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyU6}
-	\end{figure}
-	\fi
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU7.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyU7}
-	\end{figure}
-	\iffalse
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU8.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyU8}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU9.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyU9}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU10.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyU10}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyU11.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyU11}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr0.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyErr0}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr1.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyErr1}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr2.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyErr2}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr3.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyErr3}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr4.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyErr4}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr5.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyErr5}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr6.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyErr6}
-	\end{figure}
-	\fi
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr7.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyErr7}
-	\end{figure}
-	\iffalse
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr8.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyErr8}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr9.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyErr9}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr10.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyErr10}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr11.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
-		\label{fig:3DParameterStudyErr11}
-	\end{figure}
-	\fi
+	\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyUWorst.eps}
+		\caption{Plot of the simulated velocity in a channel flow as a dependency of the radius. This is the same as figure \ref{fig:2DAlginateU} but for methyl cellulose.}
+		\label{fig:2DParameterStudyUWorst}
+	\end{figure}
+	\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErrWorst.eps}
+		\caption{Plot of the error of the simulated velocity in a channel flow as a dependency of the radius. This is the same as figure \ref{fig:2DAlginateErr} but for methyl cellulose.}
+		\label{fig:2DParameterStudyErrWorst}
+	\end{figure}
+	%Interestingly, the last one work besides Ma being approx 10.\n
+	%This error is not influenced by shuffling fraction or lattice resolution\n
+	%The shape the sim returns can be obtained by the theory by modifying px and or etap\n
+	%The resulting error is (approx) centered around Wi of max viscosity gradient.
+	This is now repeated for a three-dimensional flow.
+	\subsection{3D Poiseuille vs theory}
+	The simulation was run as described in the section above, but the 2D channel geometry was changed into a 3D pipe flow.
+The errors show a similar behavior (see figure \ref{fig:3DParameterStudyErr}), but are considerably larger.
+The maximum pressure gradient is smaller for this series is smaller than the 2D series as those simulations exceeded the stability criterion for the Mach number.
+The worst result was obtained using the same pressure gradient as in the 2D case and can be seen in figure \ref{fig:3DParameterStudyUWorst} and figure \ref{fig:3DParameterStudyErrWorst}.
+Notably the error here, while still tolerable is a lot worse than the 2D case.
+With the error being particularly high around the wall it is likely that the wall approximation, which is significantly worse in the 3D case due to the required stair stepping, is the main reason for the 3D case exhibiting larger errors.
 	\begin{figure}[H]
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr.eps}
-		\caption{Plot of the simulated velocity as a dependency of the radius.}
+		\caption{Plot of the simulation error in a pipe flow as a dependency of the pressure gradient}
 		\label{fig:3DParameterStudyErr}
 	\end{figure}
-	Worse due to wall approx.\n
-	Failed for high Ma.
-	\subsection{Viscoelastic Reynolds-Scaling}
-	Does not reproduce transitory behavior\todo{NEEDS TO WORK}
+	\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyUWorst.eps}
+		\caption{Plot of the simulated velocity in a pipe flow as a dependency of the radius.
+This was evaluated along a coordinate axis.
+This is the same as figure \ref{fig:3DAlginateU} but for methyl cellulose.}
+		\label{fig:3DParameterStudyUWorst}
+	\end{figure}
+	\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErrWorst.eps}
+		\caption{Plot of the error of the simulated velocity in a pipe flow as a dependency of the radius.
+This was evaluated along a coordinate axis.
+This is the same as figure \ref{fig:3DAlginateErr} but for methyl cellulose.}
+		\label{fig:3DParameterStudyErrWorst}
+	\end{figure}
+	\subsection{Validation summary}
+	The algorithm passes all typical test and behaves as expected.
+The error is very small for most problems.
+Only the pipe flow shows considerable error, however this is likely caused by the wall model and not by the viscosity shuffling method.
 	\section{Viscosity Ratio in literature}\label{app:viscosityRatio}
+		The viscosity ratios used in literature are limited.
+The following table contains overview of the maximum ratios typically used in literature.
+The last column shows how the ratio was calculated from the parameters given in the publications.
 		\begin{center}

### 2024-01-23 assets/setups/cellInShear/setup/defines.hpp
setup cellInShear

@@ -1,0 +1,184 @@
+#pragma once
+// ############################################ file paths #############################################
+
+//#define PATH_DEBUG "/data2/s1molehm/FluidX3D/Bead/interpolation/"
+//#define PATH_DEBUG "/tp6_gekle/data2/bt703473/debug/test2/"
+#define PATH_DEBUG "./bin/debug/" // path for debug files (PTX, LOG, VALIDATION)
+#define PATH_IBM   "./bin/ibm/"   // path for IBM extension
+
+
+// ############################################ LBM options ############################################
+
+// There hides a D2Q5 in the code
+//#define D2Q9
+//#define D3Q7 // very very inaccurate
+//#define D3Q13 // very inaccurate; Only works with MRT according to Krüger book p. 87; Does not reproduce EQUILIBRIUM_STRESS correctly.
+
+// Only use these:
+//#define D3Q15
+#define D3Q19 // Best value
+//#define D3Q27 // Better for high Reynolds numbers.
+
+#define SRT // singe relaxation time
+//#define TRT // two relaxiation time (as fast as SRT, but more accurate)
+//#define MRT // multi relaxiation time (as fast as SRT, but more accurate), (### not fully validated for for D3Q7 and D3Q13, incomplete relaxation times for D3Q7 and D3Q27 ###)
+
+//#define UPDATE_RHO // update density field after every step (not necessary for pure LBM)
+//#define UPDATE_U // update velocity field after every step (not necessary for pure LBM, makes tracer particle calculation faster)
+
+#define MOVING_WALLS // moving bounce-back boundaries
+//#define BOUNDARY_EXPRESSION // combinable with MOVING_WALLS, !!!doesn't work on AMD for some reason!!!
+
+#define VISCOELASTIC
+#define EQUILIBRIUM_STRESS // Include viscoelastic forces by shifting the equilibrium populations (Onishi 2005) instead of via force
+#define STRAIN_RATE_TENSOR_FROM_POP // If set, the strain rate tensor used for shuffling is calculated from the populations otherwise the one from the velocity gradient is used
+// Only one of the following models may be defined
+//#define OLDROYD_B
+//#define FENEP
+#define PTT // From Ferras 2019 eq (3) and (2) original PTT
+
[…]

### 2024-01-23 assets/setups/cellInShear/setup/setup.cpp

@@ -1,0 +1,244 @@
+#include "setup.hpp"
+#include "shapes.hpp"
+#include "opencl.hpp" // contains "options.hpp", "main.hpp"
+#include "ibm.hpp"
+#include <numeric>
+#include <sstream>
+
+#include <filesystem>
+using std::filesystem::path;
+#include <fstream>
+using std::ofstream;
+#include <iostream>
+using std::cout, std::endl; // TODO replace with spdlog
+
+#include <fmt/core.h>
+// using fmt::format
+using fmt::print;
+#include <fmt/color.h>
+using fmt::color;
+
+#include <spdlog/spdlog.h>
+//using spdlog::info;
+
+#include "cellWriter.hpp"
+using fluidx3d::io::cellWriter::CellWriter;
+#include "fieldWriter.hpp"
+using fluidx3d::io::fieldWriter::FieldWriter;
+#include "io.hpp"
+using fluidx3d::util::io::IO;
+#include "poiseuilleFlow.hpp"
+using fluidx3d::util::poiseuilleFlow::RectangularPoiseuilleFlow;
+
+void example(SimulationOptions& options, Parameters& parameters) {
+	json raw = parameters.getRaw();
+	const int id = raw["id"];
+	const string path_files = fmt::format("/tp6-gekle/nas/bt307867/cellsim/{}_{}/{}/", "cellInShear", "2024-01-23", id);
+	//const string path_files = fmt::format("{}_{}/{}/", "cellInShear", "2024-01-23", id);
+	const path filesPath(path_files);
+	const string path_vtk = path_files + "vtkfiles/";
+	const string path_vtk_cell = path_vtk + "cell/";
+	const string path_vtk_inout = path_vtk + "inout/";
+	const string path_vtk_velocity = path_vtk + "velocity/";
+	const string path_vtk_strainRateTensor = path_vtk + "strainRateTensor/";
+	const string path_ibm = "tables/smallTetraCell/";
+
+	/*
+	 * this parameter increases the time step
+	 * --> leads to larger relaxation time tau (not good, but acceptable)
+	 * --> leads to larger Ma (not good, but acceptable)
+	 * --> eventually may lead to inaccuracies
+	 */
[…]

### 2024-01-25 NovelLBM.tex
cellInShear

@@
 For all of these the methyl cellulose parameters found for a concentration of \SI{0.49}{\percent} have been used.
+	%We use richard/vtk 4dbc4d379842c538f084e68a5dcfe2555a674495 (2024-01-09)
 	\subsection{Conical nozzle}
@@
 	\end{figure}
+	%We use richard/vtk 4dbc4d379842c538f084e68a5dcfe2555a674495 (2024-01-09)
 	\subsection{Cell in shear flow}
-	\todo{do}
+	A cell with a radius of \SI{6}{\micro\meter} and Youngs Modulus of \SI{100}{\pascal} is placed in a shear flow with a shear rate of \SI{400}{\per\second}.
+The fluid is described by the parameters of \SI{0.49}{\percent} methyl cellulose solution mentioned above.
+The lattice with a resolution of \num{100} lattice points is chosen significantly bigger than the cell to assure negligible impact of the walls.
+The lattice is periodic in $x$ and $z$ direction.
+At the edges of the simulation box in $y$ direction Dirichlet boundary conditions are imposed.
+The influence of the cell placed in the center of the simulation volume can barely seen in the velocity field (see figure \ref{fig:cellInShear_v}).
+In the von Mieses stress seen in figure \ref{fig:cellInShear_vM} it is the dominant feature.
+One can clearly see the shape of the cell by the depression of the stress it causes.
+Notable from this shape outwards radiate section of high and low stress.
+These are particularly pronounced along the longest axis of the deformed cell.
+From these one can see that the cell disturbs the fluid far from itself.
+	\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/cellInShear_v.eps}
+		\caption{Plot of the velocity field around a cell in shear flow.}
+		\label{fig:cellInShear_v}
+	\end{figure}
+	\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/cellInShear_sigma_vM.eps}
+		\caption{Plot of the von Mises stress around a cell in shear flow.}
+		\label{fig:cellInShear_vM}
+	\end{figure}
+	%We use richard/master fe0fc04115b9b6ea6628bcc6cb6593d3f72ac0ea (2023-11-05)
 	\subsection{RT-DC}
@@
 The resulting flow can be seen in figure \ref{fig:RT-DC_v}.
-The component typically associated with viscosity of the stress tensor can be see in figure \ref{fig:RT-DC_tau}.
+The component typically associated with viscosity of the stress tensor can be seen in figure \ref{fig:RT-DC_tau}.
 There are three qualitative differences compared to a purely viscous fluid.
@@
 This region therefore could produce unexpected cell behavior if one passes through it.
-Similarly directly after the constriction, the stress has not yet lowered.
+Similarly, directly after the constriction, the stress has not yet lowered.
 If one would divide the stress in these two regions by the strain rate in an attempt to obtain a viscosity one would find an extremely low and an extremely high viscosity respectively.

### 2024-01-25 assets/python/fig:CellInShear.py

@@ -1,0 +1,152 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the  class.
+
+Created on Tue Sep  5 10:51:20 2023
+
+@author: Richard Kellnberger
+"""
+
+import json
+from pathlib import Path
+from time import time
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pyvista as pv
+from fluidx3d.eval.models import PTT
+from fluidx3d.eval.style import cm
+
+
+def process():
+    baseDir = Path("../data/cellInShear_2024-01-23/0/")
+    cDir = baseDir / "vtkfiles/polymer_conformationTensor/"
+    sDir = baseDir / "vtkfiles/strainRateTensor/"
+    vDir = baseDir / "vtkfiles/velocity/"
+    jsonFile = baseDir / "parameters.json"
+    f = open(jsonFile)
+    parameters = json.load(f)
+    f.close()
+
+    # V0 = parameters["info"]["conversions"]["V0"]
+    L0 = 1e-6  # parameters["info"]["conversions"]["L0"]
+    mu_SI = 1e-3 + 2 * PTT.mc0_49.eta_p
+    nu_SI = mu_SI / 1e3
+    nu0 = 6 * nu_SI
+    T0 = L0**2 / nu0  # parameters["info"]["conversions"]["T0"]
+    V0 = L0 / T0
+    rho0 = 1e3
+    p0 = rho0 * V0**2
+    # print("###")
+    # print(parameters["info"]["px"])
+    # print(p0 / L0)
+    # print(G)
+
+    cFile = cDir / "CT_40000000.vtk"
+    # sFile = sDir / "S_500000.vtk"
+    vFile = vDir / "u_40000000.vtk"
+
+    data = pv.read(cFile)
+    # dataS = pv.read(sFile)
+    dataV = pv.read(vFile)
+    Lx, Ly, Lz = dataV.dimensions
+    tauField = data.get_array("data") * PTT.mc0_49.eta_p / PTT.mc0_49.lambda_p
+    tauField = np.reshape(tauField, (Lx, Ly, Lz, 6), "F")
+    # sField = dataS.get_array("data") / T0
+    # sField = np.reshape(sField, (Lx, Ly, Lz, 6), "F")
+    vField = dataV.get_array("data") * V0
[…]

### 2024-01-25 NovelLBM.tex
Redo Nozzle

@@
 \author{Richard Kellnberger$^1$}
-\date{October, 2023}
+\date{January, 2024}
 \begin{document}
@@
 	%We use richard/vtk 4dbc4d379842c538f084e68a5dcfe2555a674495 (2024-01-09)
-	\subsection{Channel flow vs theory}
+	\subsection{Channel flow vs theory}\label{sec:channelFlow}
 	Channel flow (also known as 2D Poiseuille) is one of the simplest flows and a very typical example.
@@
 see diminishing returns.
-While these results are excellent, the error in our implementation is still dependent on the viscosity ratio.
-When going to significantly higher ratios, this needs to be checked to ensure it does not get too large.\todo{link to appendix where we validate this}
+While these results are excellent, the error in our implementation seemingly is still dependent on the viscosity ratio.
+As the error is still small using our alginate parameters (see section \ref{sec:channelFlow}), this effect is irrelevant.
 With this, one can see, that we are not only capable to simulate parameters not yet accessible, but our implementation is also better for the parameters used in literature.
 Knowing our simulations to be good we in the following show results for interesting systems, that are not analytically solvable.
-	\section{Results for non analytically solvable systems}\todo{do all of these with MC}
+	\section{Results for non analytically solvable systems}
 	With the validity and accuracy of our scheme firmly established, we can demonstrate its results for some systems that cannot be solved analytically.
@@
 It has a length of \SI{18}{\milli\meter}.
-The boundary conditions for inflow and outflow are given as the result of a simulation of pipes of the respective radius with a fixed volume flow of \todo{find volume flow}.
+The boundary conditions for inflow and outflow are given as the result of a simulation of pipes of the respective radius with a fixed volume flow of $\approx\SI{3}{\micro\liter\per\second}$.
 The resulting flow field can be seen in figure \ref{fig:Nozzle_v}.
@@
 This means, that even for fast flows, given the bio ink and nozzle size is picked correctly, the cells flowing close to the center experience little stress.
-	\todo{complete sim is wrong due to init issue}
 	\begin{figure}[H]
@@
 At the edges of the simulation box in $y$ direction Dirichlet boundary conditions are imposed.
-The influence of the cell placed in the center of the simulation volume can barely seen in the velocity field (see figure \ref{fig:cellInShear_v}).
+The influence of the cell placed in the center of the simulation volume can barely be seen in the velocity field.
 In the von Mieses stress seen in figure \ref{fig:cellInShear_vM} it is the dominant feature.
@@
 From these one can see that the cell disturbs the fluid far from itself.
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/cellInShear_v.eps}
-		\caption{Plot of the velocity field around a cell in shear flow.}
-		\label{fig:cellInShear_v}
-	\end{figure}
 	\begin{figure}[H]
@@
 The observed deformation can be used to infer the mechanical properties of the cell.
-For this simulation we use periodic boundary conditions and a pressure gradient\todo{specify}.
+For this simulation we use periodic boundary conditions and a pressure gradient of \SI{1e7}{\pascal}.
 The resulting flow can be seen in figure \ref{fig:RT-DC_v}.

### 2024-01-25 assets/python/fig:Nozzle.py

@@ -8,8 +8,6 @@ Created on Tue Sep  5 10:51:20 2023
 """
 
 import json
-import sys
-from multiprocessing import Pool
 from pathlib import Path
 from time import time
 
@@ -17,15 +15,12 @@ import matplotlib.pyplot as plt
 import numpy as np
 import numpy.ma as ma
 import pyvista as pv
-import scipy
-from scipy.special import lambertw
-from style import *
-
-eta_s = 1e-3
+from fluidx3d.eval.models import PTT
+from fluidx3d.eval.style import cm
 
 
 def process():
-    baseDir = Path("../data/Nozzle/2/")
+    baseDir = Path("../data/novel_2024-01-22/0/")
     cDir = baseDir / "vtkfiles/polymerConformationTensor/"
     sDir = baseDir / "vtkfiles/strainRateTensor/"
     vDir = baseDir / "vtkfiles/velocity/"
@@ -39,24 +34,16 @@ def process():
     T0 = parameters["info"]["conversions"]["T0"]
     rho0 = 1e3
     p0 = rho0 * V0**2
-    # print("###")
-    # print(parameters["info"]["px"])
-    # print(p0 / L0)
-    # print(G)
 
-    cFile = cDir / "C_500000.vtk"
+    cFile = cDir / "CT_5000000.vtk"
     # sFile = sDir / "S_500000.vtk"
-    vFile = vDir / "u_500000.vtk"
-    eta_p_SI = 18.7e-3
-    lambda_SI = 0.344e-3
-    epsilon = 0.27
-    # print(uHP(0, G, eta_p_SI))
-    # print("---")
+    vFile = vDir / "u_5000000.vtk"
+
     data = pv.read(cFile)
     # dataS = pv.read(sFile)
     dataV = pv.read(vFile)
     Lx, Ly, Lz = dataV.dimensions
-    tauField = data.get_array("data") * eta_p_SI / lambda_SI
+    tauField = data.get_array("data") * PTT.mc0_49.eta_p / PTT.mc0_49.lambda_p
     tauField = np.reshape(tauField, (Lx, Ly, Lz, 6), "F")
     # sField = dataS.get_array("data") / T0
     # sField = np.reshape(sField, (Lx, Ly, Lz, 6), "F")
@@ -87,18 +74,6 @@ def process():
[…]

### 2024-02-07 NovelLBM.tex
New fit figures and update to section 4

@@
 \usepackage{sidecap}
+
+\newcommand{\RK}[1]{{\color{orange}RK: #1}}
+\newcommand{\SG}[1]{{\color{red}SG: #1}}
 
@@
 
-\def\dark{}
+%\def\dark{}
 
@@
 
-	\section{Rheology of viscoelastic fluids}
-	Viscoelastic behavior in fluids was first discovered during the second world war when mixing flamethrower liquid\cite{franck2017}.
-Since then many models have been derived to describe the different effects exhibited by this class of material.
-In general the stress exhibited by these fluids is not only dependent on the current shear, but is also time-dependent.
-This complex behavior can often be decoupled into a shear dependent viscosity and a normal stress.
-These can be for the most part understood separately.
-The viscosity usually exhibits shear thinning behavior.
-This behavior is well understood because it has many technical applications and is a common side effect of increasing the viscosity of fluids which is also often desired.
-Therefore, there exist many phenomenological descriptions of shear thinning.
-A particularly general one is the Carreau-Yasuda model.
-It will be discussed in the following to illustrate qualitatively how such fluids behave.
-The elastic components will be discussed afterward.
-	\subsection{Carreau-Yasuda - phenomenological description for shear thinning viscosity}
-	In Yasudas 1979 PhD-Thesis\cite{yasuda1979} the earlier Carreau model\cite{carreau1972} was extended to describe the shear thinning behavior of polymers and polymer solutions for many parameters.
-The viscosity $\eta$ decreases with the shear rate $\dot{\gamma}$ as follows.
-	\begin{equation}
-		\eta\left(\dot{\gamma}\right) = \eta_\infty + \frac{\eta_0 - \eta_\infty}{\left[1+\left(\lambda\dot{\gamma}\right)^{a_1}\right]^\frac{a_2}{a_1}}
-	\end{equation}
-	Here $\eta_0$ is the zero shear viscosity, $\eta_\infty$ is the infinite shear viscosity, $\lambda$ is the relaxation time and $a_1$ and $a_2$ are parameters in regard to the slope.
-As can be seen in figure \ref{fig:CY}, the Carreau-Yasuda model describes two plateaus of constant viscosity ($\eta_0$ and $\eta_\infty$) connected by a $Wi^{-a_2}$ power law.
-$a_1$ governs how gradual the connection between the initial plateau and the power law is.
-Here the Weissenberg number $Wi = \lambda\dot{\gamma}$ has been introduced.
-The start of the actual thinning is around $Wi = 1$.
-Values below are often considered \glqq small\grqq{ } Weissenber numbers, while the ones above are considered \glqq large\grqq.
-The onset of the second plateau depends on a material parameter, which we term the viscosity ratio and define as follows.
-	\begin{equation}\label{eq:R_eta_CY}
-		R_\eta = \frac{\eta_0 - \eta_\infty}{\eta_\infty}
-	\end{equation}
-	As will be shown later, this is actually a crucial stability parameter for the simulations.
-This means, that the widely available parameters obtained by fitting this phenomenological model are sufficient to predict the stability of simulations.
-However, to actually simulate viscoelastic fluids, a model es required, that predicts a viscosity similar to the one shown here, and the normal stress exhibited by such fluids.
-This will be discussed in the following section.
+%%
+%%
+%%
+
+\section{Rheology of cell carrier fluids}
+
+\subsection{Experimental data}
+
+To illustrate our novel LBM algorithm, we consider two prototypical cell carrier fluids.
+The first is an alginate solution which is often used in biofabrication, i.e., the 3D printing of living cells, but can also serve as a common food additive.
+Our solution contains 4\% alginate solvated in PBS as was measured in a commerical plate-plate rheometer (see appendix  XX for experimental details).
+The shear-dependent viscosity $ \eta$ and the first normal stress difference $N_1$ are shown as function of shear rate in a frequency-sweep \SG{ ? } measurement in figure~\ref{fig:fit_alginate}.
+We note the very high zero-shear viscosity of more than $10000 \si{ mPa \cdot s}$.
+Carrier fluids in bioprinting, termed bioinks, are characterized in general by such high viscosities to guarantee stability of the printed construct.
+On the other hand, during the actual printing process when the material is flowing, the viscosity should be as low as possible to avoid excessive mechanical stress on the embedded cells.
 	\begin{figure}[H]
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/CY.eps}
-		\caption{Double logarithmic plot of the Carreau-Yasuda model for different $a_1$.}
-		\label{fig:CY}
+		\includegraphics[width=7.8cm]{assets/plots/fit_alginate_eta.eps}
+		\includegraphics[width=7.8cm]{assets/plots/fit_alginate_N.eps}
+%		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/fit_alginate_eta.eps}
+%		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/fit_alginate_N.eps}
+		\caption{Rheology data for alginate solution from 21 measurements of the viscosity (a) and normal stress (b).
+				Orange lines show a fit of the PTT rheological model. \SG{ larger font in figures }}
+		\label{fig:fit_alginate}
 	\end{figure}
-	\subsection{Constitutive equations for the polymer stress}
-	Both the viscosity and the normal stress can be viewed as components of a stress tensor.
-For some linear viscoelastic liquids simulations without modeling the constitutive equation of this tensor are possible using a slightly modified lattice Boltzmann method\cite{giraud1998,lallemand2003}.
-More general cases have used elastic dumbbells to model the polymers typically contained in viscoelastic fluids.
-The first of which was the Oldroyd-B model introduced in 1958\cite{oldroyd1958}.
-Also, it does not reproduce all effects shown by viscoelastic fluids (critically it is not shear thinning), it is still the most popular model today due to its simplicity.
-In elongational flow, the dumbbells modeled by Oldroyd-B can be stretched infinitely, leading to unphysical behavior.
-To avoid this the finite extensible FENE-P model was developed by Bird et al.\cite{bird1980,bird1987}.
-This model is also particularly popular, but we found it to be problematic, as fitting it to rheological data for some of the materials we work with results in unphysical parameters.
-Furthermore, using it is detrimental for stability, especially for high Weissenberg numbers (for details see appendix \ref{app:FENE-P}).
-There also exist many other derived or extended FENE type models one could choose from.
-Oliveira showed, that many of them follow a common formalism\cite{oliveira2009} and can be brought to a common form despite looking quite different in their original formulation.
-Among this group of models is also the Phan-Thien Tanner (PTT) model\cite{phan-thien1977,phan-thien1978}.
-It was originally derived for polymer networks in solution, but also fits well with the fluids we use.
-As these models all have similar mathematical forms and produce similar shapes, the physical background likely does not matter much.
-There exists an exponential version and a more general form of the PTT model using the gamma function\cite{ferras2019}.
-As our simulations algorithm is GPU based, using the more general form would necessitate the implementation of the gamma function incurring segnificant computational cost for limited gain.
-Therefore, we opted for the exponential version.
-For this the constitutive equation for the stress reads as follows.
+
+The second cell carrier fluid modeled in this work is a methyl cellulose solution which is commonly used in real-time-deformation-cytometry (RT-DC) experiments.
+RT-DC experiments allow very high-throughput measurements of cell mechanical properties and have been used successfully for disease detection by screening blood samples.
+We extract our data from \cite{buyukurganci2023} where the shear rheology of methyl cellulose was measured using a plate-plate and cone-plate rheometer.
+Three concentrations of \SI{0.49}{\percent}, \SI{0.59}{\percent} and \SI{0.83}{\percent} methyl cellulose in PBS were investigated and their rheology is shown in figure~\ref{fig:fit_mc}.
+Even at the highest concentration the zero-shear viscosity is two orders of magnitude lower than for the considered alginate solution.
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=7.8cm]{assets/plots/fit_mc_eta.eps}
+		\includegraphics[width=7.8cm]{assets/plots/fit_mc_N.eps}
+		\caption{Rheology data of a methyl cellulose solution from \cite{buyukurganci2023}.
+				Orange lines show a fit of the PTT rheological model. \SG{ include legend into figure. Maybe give color coding only in caption? }\SG{ larger font in figures }}
+		\label{fig:fit_mc}
+	\end{figure}
+
+\subsection{Fitting data with the PTT model}
+
+Due to the complexity of viscoelastic fluids, there is an abundance of (semi-)empirical models to describe rheological data.
+Common options include the Oldroyd-B \cite{oldroyd1958} and the FENE-P model \cite{bird1980,bird1987}.
+The Oldroyd-B model is not appropriate for most real complex fluids as it features a shear-independent viscosity in clear contradiction to the experimental data presented in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}.
+Although the FENE-P does reproduce shear-thinning, we were not able to obtain a satisfactory fit to our data for alginate and methyl cellulose with physically reasonable values of the model parameters.
+The best fit was obtained with the so-called PTT model due to Phan-Thien and Tanner \cite{phan-thien1977,phan-thien1978} which was for explicitly derived for polymer networks in solution and thus appears to capture well the essential physics behind the alginate solution.
+\SG{ check that these papers have the exponentail version }.
+
+The PTT model is specified by a constitutive equation for the polymer stress $ \ma{\tau}$:
 	\begin{equation}
 		\overset{\nabla}{\ma{\tau}} = -\xi\left(\ma{\tau}\cdot\ma{D} + \ma{D}\cdot\ma{\tau}\right) - e^{\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}}\frac{\ma{\tau}}{\lambda} + 2\frac{\eta_\text{p}}{\lambda}\ma{D}
+		\label{eq:polymerStress}
 	\end{equation}
-	Here, $\ma{\tau}$ is the polymer stress tensor and $\ma{D}$ is the strain rate tensor.
-$\eta_\text{p}$ is the polymer viscosity and $\lambda$ is the relaxation time.
-$\epsilon$ is the extensibility parameter and $\xi$ describes the slip in the polymer network.
-This model uses the upper convected derivative, which is defined as follows.
+where $\ma{D}$ is the strain rate tensor. 
+The polymer viscosity is denoted $\eta_\text{p}$ and $\lambda$ is the corresponding relaxation time.  \SG{ are they actually independent? }
+$\epsilon$ is the so-called extensibility parameter which controls at which shear rates thinning takes place and $\xi$ describes the slip in the polymer network which we will set to zero in the following.
+The upper convected derivative is defined as follows:
 	\begin{equation}
@@
 	\end{equation}
-	Where $\vec{u}$ is the fluid velocity and $\left(\nabla\vec{u}\right)_{ij} = \nabla_i\vec{u}_j$. This equation contains the material derivative defined as follows.
+where $\vec{u}$ is the fluid velocity and $\left(\nabla\vec{u}\right)_{ij} = \nabla_i\vec{u}_j$. 
+The material derivative is
 	\begin{equation}
-		\frac{\Dif\ma{A}}{\Dif t} = \frac{\partial\ma{A}}{\partial t} + \vec{u}\cdot\nabla\ma{A}
+		\frac{\Dif\ma{A}}{\Dif t} = \frac{\partial\ma{A}}{\partial t} + \vec{u}\cdot\nabla\ma{A}.
 	\end{equation}	
-	The semi analytical solution reads as follows\cite{ferras2019}.
+Finally, the total fluid stress is the sum of the polymer stress $ \tau $ and a solvent stress $ \tau _ \mathrm{s}$ due to the Newtonian solvent with viscosity $ \eta _ \mathrm{s}$.
+
+For a simple shear flow in the $xy$-plane, an analytical expression for $ \eta $ and $N_1$ is given by \cite{ferras2019} which (with $\xi=0$) reads
 	\begin{equation}
-		\exp\left[\frac{\epsilon\lambda}{\eta_\text{p}}\left(\frac{2-2\xi}{2-\xi}\right)\tau_{xx}\right]^2\tau_{xx}=\left(2-\xi\right)\left(\lambda\dot{\gamma}\right)^2\left(\frac{\eta_\text{p}}{\lambda} - \tau_{xx}\xi\right)
+		\eta\left(\dot{\gamma}\right) = \frac{\eta_\text{p}}{\exp\left[0.5W_0\left(4\epsilon \mathrm{Wi}^2\right)\right]} + \eta _\mathrm{s} \ma{D}
 	\end{equation}
 	\begin{equation}
-		\tau_{xy}\left(\dot{\gamma}\right) = \frac{\eta_\text{p}\dot{\gamma}-\tau_{xx}Wi\xi}{\exp\left[\frac{\epsilon\lambda}{\eta_\text{p}}\left(\frac{2-2\xi}{2-\xi}\right)\tau_{xx}\right]}
+		N_1 = \frac{\eta_\text{p}}{2\epsilon\lambda}W_0\left(4\epsilon \mathrm{Wi}^2\right)
 	\end{equation}
-	\begin{equation}
-		\eta\left(\dot{\gamma}\right) = \frac{\tau_{xy}\left(\dot{\gamma}\right)}{\dot{\gamma}}
-	\end{equation}
-	\begin{equation}
-		N_1 = \frac{2\tau_{xx}}{2-\xi}
-	\end{equation}
-	Where $N_1$ is the first normal stress difference.
-
-	The shear dependent viscosity in this model can be seen in figure \ref{fig:ptt_eta}.
-One can see a Newtonian plateau and a $Wi{-1}$ power law.
-Other constitutive equations lead to other power laws.
-Therefore, one can pick a model, that fits the data best.
-The parameter $\epsilon$ controls the $Wi$ at which thinning takes place.
-Compared to the phenomenological CY model, PTT does not have a minimum viscosity and keeps trending towards zero.
-This is unphysical and current lattice Boltzmann methods require a viscosity to be present.
-This is remedied by adding an offset $\eta_\text{s}$ to the viscosity.
-The resulting curve can be seen in figure \ref{fig:ptt_eta_s}.
-The resulting curve is very similar to the CY model and thus is also suited to describe many different viscoelastic liquids.
-Furthermore, this allows to see some similarities.
-The $\eta_\text{s}$ parameter is equivalent to $\eta_\infty$ and $\eta_\text{p} + \eta_\text{s} = \eta_0$.
-With this the viscosity ratio defined in equation \ref{eq:R_eta_CY} can be rewritten with these parameters as follows.
-	\begin{equation}\label{eq:R_eta_ptt}
-		R_\eta = \frac{\eta_\text{p}}{\eta_\text{s}}
-	\end{equation}
-	The index p expresses the viscosity from polymers, while the s means viscosity from solvent.
-This alleges, that the viscosity for infinite shear becomes the solvent viscosity.
-This however is not entirely accurate in general.
-That being said, the exact value of $\eta_\text{s}$ is not relevant given $Wi$ is low enough, which it often is.
-Given, that data is rarely available at shear rates high enough to determine $\eta_\text{s}$ reliably, due to technical difficulties, it can usually not be determined from data.
-Therefore, it is common to just use the solvent viscosity.
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/ptt_eta.eps}
-		\caption{Double logarithmic plot of the PTT model for $\xi=0$ and different $\epsilon$.}
-		\label{fig:ptt_eta}
-	\end{figure}
-		\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/ptt_eta_s.eps}
-		\caption{Double logarithmic plot of the PTT model for $\xi=0$ and different $\epsilon$ with an offset.}
-		\label{fig:ptt_eta_s}
-	\end{figure}
-	For the polymers solutions we work with, $\xi$ is effectively zero, as can be suspected from its physical interpretation.
-Therefore, we set it to zero for the rest of this work.
-This also simplifies the model significantly and allows it to be solved analytically using the Lambert $W$ function.
-In the following we show fits for several viscoelastic fluids, to show, that PTT does fit and to establish an expected range for the parameters.
-	\subsection{Fitting PTT to experimental data}
-	For $\xi = 0$ and using the Lambert $W$ function, the solutions for PTT are as follows.
-	\begin{equation}
-		\eta\left(\dot{\gamma}\right) = \frac{\eta_\text{p}}{\exp\left[0.5W_0\left(4\epsilon Wi^2\right)\right]}
-	\end{equation}
-	\begin{equation}
-		N_1 = \frac{\eta_\text{p}}{2\epsilon\lambda}W_0\left(4\epsilon Wi^2\right)
-	\end{equation}
-	From this, one can see, that it is not sufficient to fit the viscosity as it could be formulated using two parameters ($\eta_\text{p}$ and $\epsilon\lambda^2$).
-Therefore, it has to many parameters and the fit has a one dimensional solution space.
-	The same holds for $N_1$ using $\eta_\text{p}\lambda$ and $\epsilon\lambda^2$.
-Therefore, it is necessary to fit both curves at the same time.
-This is not a unique feature of PTT, it is also the case for e.g.
-FENE-P (see appendix \ref{app:FENE-P}).
-In the following we show the fit results for an Alginate solution, for several concentrations of methyl cellulose solution and for a few other fluids.
-	\subsubsection{Alginate}
-	Alginate solutions are very important as bioinks or as scaffolding in the field of biofabrication.
-Alginate is also a common food additive.
-The solutions used here are \SI{4}{\percent} by weight of DuPont VIVAPHARM Alginate PH176 in PBS (essentially water)\todo{cite email from Tomasz Jüngst from 23.03.2023?}.
-The solution were prepared and measured by the Group of Tomasz Jüngst\todo{cite properly}.
-The measurements were done using a plate-plate rheometer.
-The first normal stress difference $N_1$ is calculated from the measured normal force using the following equation\cite{kulicke1977}.
-	\begin{equation}
-		N_1 = \frac{2F}{\pi R^2} + \frac{3}{20}\rho\omega^2R^2
-	\end{equation}
-	Where $F$ is the measured normal force, $R$ is the radius of the rheometer, $\rho$ is the density of the fluid and $\omega$ is the angular velocity of the rheometer.
-The second term is usually omitted and as we found it to matter little, and as the quality of the data we have available is too limited to warrant such detailed corrections, we also choose to omit it.
-A cone-rheometer would be preferred here, but as $N_2 = 0$ for PTT with $\xi = 0$, the difference is negligible.
-
-	The data for viscosity and first normal stress difference was fitted simultaneously for all 21 individual measurements in the dataset.
-The results can be seen in figures \ref{fig:fit_alginate_eta} and \ref{fig:fit_alginate_N}.
-The steps that can be seen in the plot of the first normal stress difference are due to the limited resolution of the rheometer used.
-It can be seen, that the data varies significantly, due to variations on preparation and/or measurement.
-The fit does not reproduce the shape perfectly but does always stay within the variation of the data.
-This is sufficient.
-While setting $\eta_\text{s} = \SI{1}{\milli\pascal\second}$, the parameters obtained are as follows.
+where $ \mathrm{Wi} = \lambda \dot{ \gamma  }$ is the Weissenberg number and $W_0$ is the Lambert $W$-function. \SG{ check that $ \eta _ \mathrm{s}$ is correct }
+\SG{ I did not find these equations in \cite{ferras2019}? }
+Fitting these equations to the rheological data for alginate and methy cellulose leads to satisfactory agreement as shown in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}.
+In the fit, the solvent viscosity was fixed at $ \eta _ \mathrm{s} = 1 \si{ mPa } \cdot \si{ s }$ as the viscosity of the PBS buffer. \SG{ give ref }
+At very high shear rates, the contained polymers are completely stretched and the viscosity asymptotically approaches the solvent values $ \eta _ \mathrm{s}$.
+The obtained parameters for alginate are
 	\begin{align}
@@
 		\lambda &= \SI{0.343 \pm 0.004}{\second}\\
-		\epsilon &= \num{0.545 \pm 0.010}
+		\epsilon &= \num{0.545 \pm 0.010}.
 	\end{align}
-	With this the viscosity ratio becomes $R_\eta = \num{48.2\pm0.4e3}$.
-However, this carries the assumption of $\eta_\text{s}$.
-Strictly from the data, we can only specify $R_\eta > 70$, using $\eta_\text{s} < \min\left(\eta\right)$.
-Given, the data shows no sign of flattening the actual value of $R_\eta$ is significantly higher than $70$.
-
-	These parameters (predominately $\eta_\text{p}$) are dependent on concentration. This will be shown in the next section with the example of methyl cellulose.
-	\begin{figure}[H]
+while the parameters for the three concentrations of methyl cellulose are given in table~\ref{tab:MC_parameters}.
+	\begin{table}[H]
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/fit_alginate_eta.eps}
-		\caption{Double logarithmic plot of 21 measurements of the viscosity of an alginate solution and a PTT fit.}
-		\label{fig:fit_alginate_eta}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/fit_alginate_N.eps}
-		\caption{Double logarithmic plot of 21 measurements of the normal force (converted to stress) of an alginate solution and a PTT fit.}
-		\label{fig:fit_alginate_N}
-	\end{figure}
-	\subsubsection{Methyl cellulose}
-	Methyl cellulose is also used in research involving cells as a nontoxic thickening agent.
-It is also widely used in the food industry.
-The data used here\cite{buyukurganci2023}, was measured using plate-plate and cone-plate rheometer geometry.
-The three solutions measured are \SI{0.49}{\percent}, \SI{0.59}{\percent} and \SI{0.83}{\percent} methyl cellulose in PBS.
-The measured data as well as the fit results can be seen in figures \ref{fig:fit_mc_eta} and \ref{fig:fit_mc_N}.
-One can see, that while PTT is not the optimal model for this solution, the agreement is still acceptable.
-The fit gives the following parameters.
-	\begin{center}
 		\begin{tabular}{c|c|c|c}
-			Concentration/\unit{\percent} & $\eta_\text{p}/\unit{\milli\pascal\second}$ & $\lambda/\unit{\milli\second}$ & $\epsilon$ \\
+%			Concentration/\unit{\percent} & $\eta_\text{p}/\unit{\milli\pascal\second}$ & $\lambda/\unit{\milli\second}$ & $\epsilon$ \\
+			Concentration/ percent & $\eta_\text{p}/mPas$ & $\lambda/ms$ & $\epsilon$ \\
 			\hline
@@
 		\end{tabular}
-	\end{center}
-	From the derivation of the model it would be expected, that only $\eta_\text{p}$ scales with the concentration.
-However, all the parameter show a significant dependency on concentration.
-$R_\eta$ can be approximated from the data as $R_\eta > 3$, $R_\eta > 4$ and $R_\eta > 9$ for \SI{0.49}{\percent}, \SI{0.59}{\percent} and \SI{0.83}{\percent} receptively.
-They again are likely much higher.
-The expected values based on the assumed $\eta_\text{s}$ are $R_\eta = \num{18.7\pm0.4}$, $R_\eta = \num{32.5\pm0.7}$ and $R_\eta = \num{81\pm2}$ respectively.
-	\begin{figure}[H]
+		\caption{Parameters of the PTT modelobtained when fitting the methyl cellulose solutions.}
+		\label{tab:MC_parameters}
+	\end{table}
+
+We introduce the ratio between the zero-shear and the infinite-shear (i.e.\ solvent) viscosity as 
+\begin{align}
+	R_ \eta  = \frac{ \eta _ \mathrm{p} } { \eta _ \mathrm{s} }		\label{eq:R_eta}
+\end{align}
+which will turn out to be an important parameter to determine numerical stability of LB simulations.
+\SG{ do we actually need a ratio?
+Since $ \eta _\mathrm{s}$ is probably always water-like, would it not be enough to state whether $ \eta _ \mathrm{p}$ is high or low } \SG{ do we actually show that $R_ \eta  $ determines stability?
+}
+This ratio can in a similar fashion be defined for other models such as FENE-P or the inelastic, but shear-thinning Carreau-Yasuda model \cite{carreau1972, yasuda1979}.
+For our alginate solution we obtain $R _ \eta = \num{48.2\pm0.4e3}$, indicating that the solution viscosity at very low shear rates is more than four orders of magnitude larger than the solvent viscosity which represents a severe challenge to standard numerical algorithms.
+That this characteristic is not unique to alginate, but is in fact a generic feature of cell carrier fluids used in bioprinting is shown in table~\ref{tab:bioinks} where rheological from various literature sources have been compiled into a single format to determine $ R_ \eta $.
+The 0.49 \% methyl cellulose solution used in RT-DC measurements, in contrast, features a much lower value of $R_\eta = \num{18.7\pm0.4}$.
+\begin{table}
 	\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/fit_mc_eta.eps}
-		\caption{Double logarithmic plot of measurements of the viscosity of three methyl cellulose solutions and a PTT fit.}
-		\label{fig:fit_mc_eta}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/fit_mc_N.eps}
-		\caption{Double logarithmic plot of measurements of the normal force (converted to stress) of three methyl cellulose solutions and a PTT fit.}
-		\label{fig:fit_mc_N}
-	\end{figure}
-	\subsubsection{Other fluids}
-	While the fluids mentioned above are of great importance, they are by no means the only ones used in such experiments.
-From these two examples alone, it can be seen, that the parameters of magnitude.
-As the viscosity can change be several orders of magnitude before the change in behavior of the fluid becomes noticeable to human perceptions, the fluids commonly referred to as shear thinning have a large viscosity ratio.
-In the following values from a few publications are listed to establish the typical values for the ratio.
-It is common (due to experimental limitations), that the shear rate is limited in the experiments in a way, that does not allow seeing both Newtonian plateaus.
-In these cases we provide an upper or lower bound.
-	\begin{center}
 		\begin{tabular}{l|p{3cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{2cm}}
-			Author & Material & $\eta_0/\unit{\pascal\second}$ & $\eta_\infty/\unit{\pascal\second}$ & $R_\eta$ & extracted from \\
+%			Author & Material & $\eta_0/\unit{\pascal\second}$ & $\eta_\infty/\unit{\pascal\second}$ & $R_\eta$ & extracted from \\
+			Author & Material & $\eta_0/Pas$ & $\eta_\infty/Pas$ & $R_\eta$ & extracted from \\
 			\hline
@@
 			Pössl\cite{possl2021} & blend & 3e2 & 1e-4 & 3e6 & Table 4 \\
-			Paxton\cite{paxton2017} &Nivea Creme\n Alginate& 1e5\n5e4 & <1\n<5e1 & >1e5\n>1e3 & Fig. 4b \\
+%			Paxton\cite{paxton2017} &Nivea Creme\n Alginate& 1e5\n5e4 & <1\n<5e1 & >1e5\n>1e3 & Fig. 4b \\
+			Paxton\cite{paxton2017} & Alginate& 5e4 & <5e1 & >1e3 & Fig. 4b \\
 			\rowcolor{secondaryBackground}
@@
 		\end{tabular}
-	\end{center}
-	Many of these fractions are likely much larger than listed here.
-This is only a lower bound.
-There are many slightly shear thinning fluids, where this fraction is a lot smaller and it also decreases with concentration.
-However, such large values in the tens of thousands are typical for bio-inks and fluids used in adjacent fields.
-This is by design, as a very high zero shear viscosity is desirable to stabilize the construct after printing.
-	With the usual range of the parameters and $R_\eta$ established, we provide a quick overview about the current literature and capabilities in the following section.
+	\caption{Compilation of literature data on typical bioinks showing that a very viscosity ratio $ R_ \eta $ is a generic feature of these liquids. }
+	\label{tab:bioinks}
+\end{table}
+
+%%
+%% LBM
+%%
 
 \section{Existing LBM methods}
-	There are many existing LBM methods to simulate viscoelastic materials in three dimensions.
-Some simple linear viscoelastic effects can be described through multi-relaxation-time models \cite{lallemand2003}, but in general more complicated methods are required.
-For more general cases the solving of a second equation is required.
-There are several options for the equation describing the polymer.
-Among these are the constitutive equation\cite{gupta2015} and a Fokker-Planck equation\cite{onishi2005}.
-Solving these equations can be done through multiple ways.
-These include a finite volume solver, a finite difference solver\cite{gupta2015}, another LBM like solver\cite{ma2020} and an advection-diffusion scheme\cite{onishi2005}.
-These secondary solvers need to be coupled to the primary LBM solver.
-Options to do that include introducing an additional forcing term to the LBM and altering the LBM stress directly\cite{dzanic2022}.
 
-	Among the publications implementing a constitutive equation most use Oldroyd-B or older models.
-Many also use FENE-P despite its shortcomings.
-The PTT model, which is currently the model used by us is rarely employed, though many authors do mention it.
+Since the early days of LBM methods for viscoelastic fluids have been developed. 
+Keeping in mind our target geometries, we focus here on three dimensional formulations.
+The first approaches avoided an explicit modeling of a viscoelastic constitutive equation and simply modified the LB collision operator to obtain a fluid obeying Jeffery's viscoelastic model \cite{lallemand2003}.
+\SG{ can we say more about Jeffery?
+Why is it bad?
+Is it shear-thinning?
+}
+More advcanced approaches include the work of Onishi \textit{et al.} \cite{onishi2005, onishi2006} who considered a non-shear-thinning Oldroyd-B model using a microscopic Fokker-Planck equation for the polymer dumbbells.
+The work of \cite{malaspinas2010} and \cite{ma2020} considered in addition the FENE-P model solving the advection part of the model using a second LBM running in parallel to the Navier-Stokes LBM while \cite{wang2020} used this approach for the Oldroyd-B model.
+Later, hybrid schemes coupling an LB solver for the solvent to a finite-difference \cite{gupta2015_2, gupta2015, gupta2016} or finite-volume \cite{kuron2021} scheme for the polymer stress (or, alternatively, the polymer conformation) tensor were introduced.
+To improve numerical stability, some authors propose the inclusion of an artificial diffusivity \SG{ cite }, which introduces a small error compared to the analytical solution of the constitutive equation.
+Coupling of the resulting polymer stress to the Navier-Stokes LBM can be achieved via the inclusion of point forces or via a modification of the equilibrium populations.
+A recent comparison in 2D found that the former in general leads to higher stability \cite{dzanic2022}.
 
-	While these options lead to wide range of different coupled solvers, the results are similar.
-Some authors note, that the Weissenberg number could be extremely high using their scheme\cite{malaspinas2010}, the simulations actually presented in the publications usually only go up to $Wi = 10$\cite{malaspinas2010,su2013_2} or $Wi = 100$\cite{gupta2015,ma2020,gupta2016}.
-As can be seen in figure \ref{fig:ptt_eta_s} above, $Wi \leq 100$ covers most of the range already, and it seems plausible, that current capabilities cover most of not all experiments in this regard.
+The stable range of Weissenberg numbers covered by existing methods is up to $ \mathrm{Wi}  \approx  10$ for the method of \cite{malaspinas2010} and up to $ \mathrm{Wi}  \approx 100$ in \cite{gupta2015,ma2020,gupta2016}.
+However, another stability criterion, which is often overlooked is the viscosity ratio $ R_ \eta $ as defined in XX. 
+Existing methods often stay at or below $R_\eta = 1$\cite{gupta2015,onishi2006,wang2020,su2013_2,gupta2015_2}, while the ones trying higher ratios report being limited below $R_\eta = 10$\cite{malaspinas2010,ma2020,kuron2021} due to stability issues.
+The details are listed in table~\ref{tab:viscRatio}.
+Comparing to the rheological data presented in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}, we conclude that existing LB methods appear to be appropriate only for relatively dilute solutions and in particular do not cover the viscosity ratio required by these technologically important cell carrier fluids.
+We therefore set out to develop a novel viscoelastic LB scheme which we will present in the next section.
 
-	However, another stability criterion, which only some others mention is the viscosity ratio.
-Its definition in literature varies significantly.
-We use equation \ref{eq:R_eta_ptt} whenever possible.
-For some publications we have to estimate it using data extracted from plots and equation \ref{eq:R_eta_CY}.
-The exact details can be found in section \ref{app:viscosityRatio}.
-Publications often stay at or below $R_\eta = 1$\cite{gupta2015,onishi2006,wang2020,su2013_2,gupta2015_2}, while the ones trying higher ratios report being limited below $R_\eta = 10$\cite{malaspinas2010,ma2020,kuron2021} due to stability issues.
-There are several options being explored in the literature to increase stability.
-The most prominent among them is the inclusion of an artificial diffusivity, which introduces a small error compared to the analytical solution of th constitutive equation.
-All of these ultimately fail to extend the range of stable viscosity ratios significantly.
-This means, that for the existing simulation approaches, the zero shear viscosity and the infinite shear viscosity are similar, which is only sufficient for very dilute solutions.
-The methods currently available do not allow the simulation of the real fluids mentioned before.
-Therefore, we developed a new method capable of much higher viscosity ratios.
-This novel approach will be discussed in the following section.
+\begin{table}
+\begin{center}
+			\begin{tabular}{l|r|r|l}
+				Author & max(Wi) & max($R_\eta$) & $R_\eta$ estimation \\
+				\hline
+				Malaspinas\cite{malaspinas2010} & 10 & 9 & In 4.3: $R_\nu = \num{0.1}$ \& equation (38) \\
+				\rowcolor{secondaryBackground}
+				Gupta\cite{gupta2015} & 100 & 0.7 & In IV.B: $\frac{\eta_\text{p}}{\eta_\text{A} + \eta_\text{p}} = \num{0.4}$ \\
+%				Dzanic\cite{dzanic2022} & 10 & 0.5 & In 4.1: $\beta = \frac{\nu_\text{p}}{\nu_\text{s}} = \num{0.5}$ \\
+				Ma\cite{ma2020} & 100 & 9 & In 4.1: $\beta = \frac{\mu_\text{s}}{\mu_\text{s} + \mu_\text{p}} = \num{0.1}$ \\
+				\rowcolor{secondaryBackground}
+				Onishi\cite{onishi2006} & ? & 1 & In 3.1: $\beta = \frac{\mu_\text{p}}{\mu_\text{s} + \mu_\text{p}}$ \& Table 1: $\beta=\num{0.5}$ \\
+				Wang\cite{wang2020} & \glqq up to O(1)\grqq & 5 & In II: $\eta_\text{p} = c\eta_\text{s}$ \& FIG. 9: $c = \num{5}$\\
+				\rowcolor{secondaryBackground}
+%				Dzanic\cite{dzanic2022_2} & 10 & 9 & In 5.1: $\beta = \frac{\nu_\text{s}}{\nu_\text{s} + \nu_\text{p}}$ \& In 5.1.2: $\beta = \num{0.1}$ \\
+				Su\cite{su2013_2} & 10 & 1  & In II: $\beta = \frac{\eta_\text{s}}{\eta_\text{s} + \eta_\text{p}}$ \& In IV.A: $\beta = \num{0.5}$ \\
+				Gupta\cite{gupta2015_2} & ? & 0.7 & In 2: $\frac{\eta_\text{p}}{\eta_\text{d}} = \num{0.4}$ \& $\eta_\text{d} = \eta_\text{A} + \eta_\text{p}$ \\
+				\rowcolor{secondaryBackground}
+				Kuron\cite{kuron2021} & 1 & 9 & In 4.1: $\beta = \num{0.9}$ \& equations (14) \& (15) \\
+				Gupta\cite{gupta2016} & 80 & 0.7 & In 3: $\frac{\eta_\text{p}}{\eta_\text{c,d} + \eta_\text{p}} = \num{0.4}$ \\
+				\rowcolor{secondaryBackground}
+				Onishi\cite{onishi2005} & 1000 & 1 & In 3.2: $\frac{\eta_\text{p}}{\eta_\text{s}} = \num{1}$ \\
+			\end{tabular}
+		\end{center}
 
-	\section{Numerical method}
-	Our numerical consists of several well known methods and our novel viscosity shuffling.
-In the following we provide a brief overview about the well known basics and an in depth explanation of our novel method.
-	\subsection{Basics}
-	To solve the fluid we use a lattice Boltzmann algorithm with a single relaxation time.
-One could also use multi relaxation time, but we found the benefit to be negligible.
-For the velocity set we use D3Q19 as D3Q27 did not provide significant benefit for us but increases computational cost significantly.
-We solve the constitutive equation with a finite volume solver.
-This simplifies the boundary conditions significantly as we set the stress flux through the walls to zero.
-The advection term in the constitutive equation is handled with the corner transport upwind scheme.
+\caption{Covered ranges of $ \mathrm{Wi}$ and $ R_ \eta $ for existing 3D LB methods.}
+\end{table}
+
+%%
+%% Our method
+%%
+
+\section{Viscosity shuffling algorithm}
+
+Our algorithm contains a Lattice-Boltzmann solver for the Navier-Stokes equations of the solvent, a finite-volume solver for integrating the polymer stress and finally our newly developed viscosity shuffling method.
+
+\subsection{Lattice-Boltzmann for Navier-Stokes}
+
+The Lattice-Boltzmann method (LBM) has become a standard tool in numerical fluid mechanics \cite{Kruger_book} and we therefore describe it here only very briefly.
+We use a D3Q19 lattice in full three dimensions together with a single relaxation time collission operator.
+Our implementation is based on FluidX3D which has been extensively used and validated in earlier publications \cite{Lehmann.20229da}.
+The core of the algorithm is implemented in OpenCL and thus capable of running on GPUs from different vendors.
+Boundaries are modeled using the half-way bounce back algorithm.
+
+Physical units are mapped to lattice units to obtain a dimensionless relaxation time of 1.
+The employed lattice dimensions vary for the different applications and are specified below. \SG{ to do }
+To drive the flow, we use either a constant body force (modeling a physical pressure gradient) or inflow-outflow boundaries as specified in the different application scenarios below.
+\SG{ check, specify }
+
+\subsection{Finite-volume for polymer stress }
+
+The spatio-temporal dynamics of the polymer stress $ \ma{ \tau  }$ is given by equation~(\ref{eq:polymerStress}) in the form of an advection-reaction equation.
+We solve this equation with a finite-volume running in parallel (with identical time step) with the LBM solver.
+Advection is handled using the corner transport upwind scheme \cite{kuron2021}.
+At the walls, a zero-flux boundary condition for the stress is used.
 The source terms are integrated using the Euler method.
-The exact implemented and its derivation can be found in appendix \ref{app:implementation}.
-The coupling to the main lattice Boltzmann solver happens using the stress directly according to Dzanic et al.\cite{dzanic2022_2}.
-However, we modify the coupled stress as is explained in the following.
+
+To include the polymer stress into the LBM, we use the stress coupling scheme according to Dzanic et al.\cite{dzanic2022_2, gupta2015, onishi2006}. 
+For this, ... \SG{ give some more details, especially since we do SRT }.
+The total stress experienced by the fluid ($\ma{\sigma}$) is then \cite{onishi2006}:
+	\begin{align}
+		\ma{\sigma} &= 2\eta_\text{s}\ma{D} + \ma{\tau} 		\label{eq:totalStress}
+	\end{align}
+
 \subsection{Novel viscosity shuffling}\label{sec:shuffling}
-	Performing Chapman-Enskog analysis on the LBM reveals the total stress experienced by the fluid ($\ma{\sigma}$) to be as follows\cite{onishi2006}.
+
+The key difficulty for simulating many realistic viscoelastic fluids is the unbalance between the viscous stress of the solvent and the polymer stress.
+While the former is handled efficiently and reliably by the LBM streaming-collision scheme, the latter enters the LB equations as an additional source term.
+The relative magnitude of the two terms is given by the viscosity ratio $R_ \eta $ as defined in equation~\ref{eq:R_eta} which for many situations is of the order of $10^2-10^4$ (see figure~\ref{fig:fit_alginate} and \ref{tab:bioinks}).
+The key idea of our scheme is to artificially increase the LBM viscous stress while at the same time reducing the polmer stress by the same amount.
+Starting from equation~\ref{eq:totalStress}, we write
 \begin{align}
-		\ma{\sigma} &= 2\eta_\text{s}\ma{D} + \ma{\tau}
-		\intertext{We now add a zero.}
-		&= 2\eta_\text{s}\ma{D} + \ma{\tau}_\text{shuffle} + \ma{\tau} - \ma{\tau}_\text{shuffle}
-		\intertext{With $\ma{\tau}_\text{shuffle} = 2\alpha_\text{s}\eta_\text{p}\ma{D}$}
-		&= 2\left(\eta_\text{s} + \alpha_\text{s}\eta_\text{p}\right)\ma{D} + \left(\ma{\tau} - 2\alpha_\text{s}\eta_\text{p}\ma{D}\right)
+	\ma{\sigma} &= 2\eta_\text{s}\ma{D} + \ma{\tau}_\text{shuffle} + \ma{\tau} - \ma{\tau}_\text{shuffle}	
 \end{align}
-	With this new parameter $\alpha_\text{s}$ we can shuffle an arbitrary amount of viscosity around, as we use $\eta_\text{s} + \alpha_\text{s}\eta_\text{p}$ as the viscosity in the LBM algorithm, and the stress calculated via the constitutive equation gets a relatively simple offset applied to it before being included in the LBM.
-This allows for the first time to our knowledge to pick $\eta_\text{s} = 0$.
-This allows for accurate comparisons to the analytical solutions of the constitutive equation, as these usually do not include $\eta_\text{s}$.
-Furthermore, instead of using artificial diffusivity to stabilize the simulation or employing any other artificial remedy, this scheme allows to not modify the parameters and to simulate the exact physical system that is desired.
-The reason for the instability is, simply speaking, that the polymer contribution overpowers the LBM stress.
-This can be compared to the inclusion of very large forces, which cause some equilibrium populations to become negative resulting in the LBM become unstable.
-The viscosity shuffling allows us to increase the LBM stress while decreasing the polymer contribution.
-This shifts the balance towards stability.
-Crucially, this happens without altering the physical system simulated.
-In terms of stability, we could define an effective $R_\eta$, calculated from the stress contributions as follows.
-	\begin{equation}
-		R_{\eta\text{, eff}} = \frac{\eta_\text{p}-\alpha_\text{s}\eta_\text{p}}{\eta_\text{s} + \alpha_\text{s}\eta_\text{p}} = \frac{1-\alpha_\text{s}}{\frac{\eta_\text{s}}{\eta_\text{p}} + \alpha_\text{s}} = \frac{1-\alpha_\text{s}}{1 + \alpha_\text{s}R_{\eta}}R_{\eta} \overset{\alpha_\text{s}R_{\eta}\gg1}{=} \frac{1-\alpha_\text{s}}{\alpha_\text{s}}
-	\end{equation}
-	Given $\alpha_\text{s}$ is large enough, arbitrary $R_{\eta\text{, eff}}$ can be reached, bringing the simulation within the range, that is stable with current methods, and thus arbitrary $R_{\eta}$ become stable.
-A trade-off is, that $\alpha_\text{s}$ decreases the time-step.
-In the following section we validate this novel approach against analytical solutions for realistic parameters.
-Furthermore, we compare the accuracy of this scheme with literature.
+with the transfered (''shuffled'') stress
+\begin{align}
+	\ma{ \tau }_ \mathrm{shuffle} = 2 \alpha _ \mathrm{s} \eta _ \mathrm{p} \ma{D}
+\end{align}
+containing an arbitrary parameter $0 < \alpha _ \mathrm{s} < 1$.
+Finally, this results in
+\begin{align}
+	\ma{ \sigma } &=  2\left(\eta_\text{s} + \alpha_\text{s}\eta_\text{p}\right)\ma{D} + \left(\ma{\tau} - 2\alpha_\text{s}\eta_\text{p}\ma{D}\right).
+\end{align}
+In practice, the shuffling parameter $ \alpha _ \mathrm{s}$ is chosen before the start of the simulation.
+The LBM solver is run with $\eta_\text{s} + \alpha_\text{s}\eta_\text{p}$ as its viscosity while from the polymer stress determined by equation~\ref{eq:polymerStress} the amount $\alpha_\text{s}\eta_\text{p} \ma{D}$ is subtracted at every time step before it is coupled into the LBM.
 
-	\section{Validation and comparison}
+Using this procedure, we balance the stress contributions of the LB and the polymer components which vastly improves numerical stability.
+We emphasize that, in contrast to other remedies such as adding artificial diffusivity \SG{ refs }, our viscosity shuffling algorithm is mathematically exact and does not affect the physics of the simulated system.
+\SG{ re-include effective $R_ \eta $? }
+%	In terms of stability, we could define an effective $R_\eta$, calculated from the stress contributions as follows.
+%	\begin{equation}
+%		R_{\eta\text{, eff}} = \frac{\eta_\text{p}-\alpha_\text{s}\eta_\text{p}}{\eta_\text{s} + \alpha_\text{s}\eta_\text{p}} = \frac{1-\alpha_\text{s}}{\frac{\eta_\text{s}}{\eta_\text{p}} + \alpha_\text{s}} = \frac{1-\alpha_\text{s}}{1 + \alpha_\text{s}R_{\eta}}R_{\eta} \overset{\alpha_\text{s}R_{\eta}\gg1}{=} \frac{1-\alpha_\text{s}}{\alpha_\text{s}}
+%	\end{equation}
+	%Given $\alpha_\text{s}$ is large enough, arbitrary $R_{\eta\text{, eff}}$ can be reached, bringing the simulation within the range, that is stable with current methods, and thus arbitrary $R_{\eta}$ become stable.
+The only trade-off of our viscosity shuffling scheme is that the increased LB viscosity decreases the LB time step if the lattice relaxation time is maintained at its optimal value of 1.
+In the following section we validate this novel approach against analytical solutions for realistic parameters and compare its accuracy to existing algorithms.
+
+%%
+%% Validation and accuracy
+%%
+
+\section{Validation and accuracy}
 	To validate the simulations we compare the simulated velocity field of analytically solvable geometries to theory.
@@
 
+%%
+%% Appendix
+%%
+
 	\appendix
 	\appendixpage
+
+%%
+%% Exp protocol
+%%
+
+\section{Rheology measurements of alginate solutions}
+
+\SG{ Tomasz should extend this paragraph }
+The solutions used here are 4\% by weight of DuPont VIVAPHARM Alginate PH176 in PBS. 
+The measurements were done using a plate-plate rheometer. 
+Data is agglomerated from 21 independent measurements.
+The first normal stress difference $N_1$ is calculated from the measured normal force using the following equation\cite{kulicke1977}.
+	\begin{equation}
+		N_1 = \frac{2F}{\pi R^2} + \frac{3}{20}\rho\omega^2R^2
+	\end{equation}
+	Where $F$ is the measured normal force, $R$ is the radius of the rheometer, $\rho$ is the density of the fluid and $\omega$ is the angular velocity of the rheometer.
+The second term is usually omitted and as we found it to matter little, and as the quality of the data we have available is too limited to warrant such detailed corrections, we also choose to omit it.
+A cone-rheometer would be preferred here, but as $N_2 = 0$ for PTT with $\xi = 0$, the difference is negligible.
+
 	\section{Implementation of constitutive equations}\label{app:implementation}\todo{Note available analytical solutions}
@@
 Only the pipe flow shows considerable error, however this is likely caused by the wall model and not by the viscosity shuffling method.
-	\section{Viscosity Ratio in literature}\label{app:viscosityRatio}
-		The viscosity ratios used in literature are limited.
-The following table contains overview of the maximum ratios typically used in literature.
-The last column shows how the ratio was calculated from the parameters given in the publications.
-		\begin{center}
-			\begin{tabular}{l|r|r|l}
-				Author & max(Wi) & max($R_\eta$) & $R_\eta$ estimation \\
-				\hline
-				Malaspinas\cite{malaspinas2010} & 10 & 9 & In 4.3: $R_\nu = \num{0.1}$ \& equation (38) \\
-				\rowcolor{secondaryBackground}
-				Gupta\cite{gupta2015} & 100 & 0.7 & In IV.B: $\frac{\eta_\text{p}}{\eta_\text{A} + \eta_\text{p}} = \num{0.4}$ \\
-				Dzanic\cite{dzanic2022} & 10 & 0.5 & In 4.1: $\beta = \frac{\nu_\text{p}}{\nu_\text{s}} = \num{0.5}$ \\
-				\rowcolor{secondaryBackground}
-				Ma\cite{ma2020} & 100 & 9 & In 4.1: $\beta = \frac{\mu_\text{s}}{\mu_\text{s} + \mu_\text{p}} = \num{0.1}$ \\
-				Onishi\cite{onishi2006} & ? & 1 & In 3.1: $\beta = \frac{\mu_\text{p}}{\mu_\text{s} + \mu_\text{p}}$ \& Table 1: $\beta=\num{0.5}$ \\
-				\rowcolor{secondaryBackground}
-				Wang\cite{wang2020} & \glqq up to O(1)\grqq & 5 & In II: $\eta_\text{p} = c\eta_\text{s}$ \& FIG. 9: $c = \num{5}$\\
-				Dzanic\cite{dzanic2022_2} & 10 & 9 & In 5.1: $\beta = \frac{\nu_\text{s}}{\nu_\text{s} + \nu_\text{p}}$ \& In 5.1.2: $\beta = \num{0.1}$ \\
-				\rowcolor{secondaryBackground}
-				Su\cite{su2013_2} & 10 & 1  & In II: $\beta = \frac{\eta_\text{s}}{\eta_\text{s} + \eta_\text{p}}$ \& In IV.A: $\beta = \num{0.5}$ \\
-				Gupta\cite{gupta2015_2} & ? & 0.7 & In 2: $\frac{\eta_\text{p}}{\eta_\text{d}} = \num{0.4}$ \& $\eta_\text{d} = \eta_\text{A} + \eta_\text{p}$ \\
-				\rowcolor{secondaryBackground}
-				Kuron\cite{kuron2021} & 1 & 9 & In 4.1: $\beta = \num{0.9}$ \& equations (14) \& (15) \\
-				Gupta\cite{gupta2016} & 80 & 0.7 & In 3: $\frac{\eta_\text{p}}{\eta_\text{c,d} + \eta_\text{p}} = \num{0.4}$ \\
-				\rowcolor{secondaryBackground}
-				Onishi\cite{onishi2005} & 1000 & 1 & In 3.2: $\frac{\eta_\text{p}}{\eta_\text{s}} = \num{1}$ \\
-			\end{tabular}
-		\end{center}
+
 		\end{document}

### 2024-02-07 assets/python/cellInHighShearRoscoe.py
CY

@@ -40,7 +40,8 @@ def process(i: int):
 
 def evaluate():
     T0 = 4.34028e-10  # TODO read prom parameters.json
-    i = np.arange(13552)
+    # i = np.arange(13552)
+    i = np.arange(27735)
     t = i * vtkIntervall * T0
     with Pool() as p:
         p1, p5 = np.swapaxes(p.map(process, i), 0, 1)
@@ -78,6 +79,7 @@ def evaluate():
 if __name__ == "__main__":
     evaluate()
     """
+    fit until 13552
     ((1.2480270945678713, 0.8261143904399001, 0.9749198, 0.5968765741610025, -1185.6738191957973, 5.542810806299429),
      (0.00014202758184686743, 0.00021278553442287667, 0.0010112725, 0.00017041897443233707, 0.06290683004371966, 0.0009521456788392505))
     ((1.2012968072932848, 0.829716787675813, 1.0032745597513146, 0.6044463844657088, 3999.99974499707, -1870.448988898043),

### 2024-02-07 assets/python/fig:RT-DC_CY.py

@@ -1,0 +1,103 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the  class.
+
+Created on Tue Sep  5 10:51:20 2023
+
+@author: Richard Kellnberger
+"""
+
+import json
+from pathlib import Path
+from time import time
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pyvista as pv
+
+from fluidx3d.eval.models.CY import mc0_49
+from fluidx3d.eval.style import cm
+
+
+def process():
+    baseDir = Path("../data/RT-DC/1/")
+    sDir = baseDir / "vtkfiles/strainRateTensor/"
+    vDir = baseDir / "vtkfiles/velocity/"
+    jsonFile = baseDir / "parameters.json"
+    f = open(jsonFile)
+    parameters = json.load(f)
+    f.close()
+
+    V0 = parameters["info"]["conversions"]["V0"]
+    L0 = parameters["info"]["conversions"]["L0"]
+    T0 = parameters["info"]["conversions"]["T0"]
+    rho0 = 1e3
+    p0 = rho0 * V0**2
+    G = parameters["info"]["px"] * p0 / L0
+    # print("###")
+    # print(parameters["info"]["px"])
+    # print(p0 / L0)
+    # print(G)
+
+    sFile = sDir / "S_500000.vtk"
+    vFile = vDir / "u_500000.vtk"
+    # print(uHP(0, G, eta_p_SI))
+    # print("---")
+    dataS = pv.read(sFile)
+    dataV = pv.read(vFile)
+    Lx, Ly, Lz = dataS.dimensions
+    sField = dataS.get_array("data") / T0
+    sField = np.reshape(sField, (Lx, Ly, Lz, 6), "F")
+    vField = dataV.get_array("data") * V0
+    vField = np.reshape(vField, (Lx, Ly, Lz, 3), "F")
+
+    vSlice = vField[..., Lz // 2, 0]
+    D12 = sField[..., Lz // 2, 3]
+    eta = mc0_49.eta(np.abs(D12))
+    tau12 = 2 * eta * D12
+
+    plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
[…]

### 2024-02-07 assets/python/fig:fit_alginate.py

@@ -14,7 +14,8 @@ import matplotlib.pyplot as plt
 import numpy as np
 import scipy
 from scipy.special import lambertw
-from style import *
+
+from fluidx3d.eval.style import cm, color
 
 
 def CY(eta0, etaInf, Wi, a1, a2):
@@ -141,7 +142,7 @@ if __name__ == "__main__":
     print(f"fit:")
     print(params)
     print(err)
-    gd = np.logspace(np.log10(np.min(gdet)), np.log10(np.max(gdet)), 1000)
+    gd = np.logspace(np.log10(np.min(gdet)), np.log10(np.max(gdet)) + 5.5, 1000)
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
     plt.plot(gdet, et, "x", label="Data")
     plt.plot(gd, ptt_eta(gd, *params), label="PTT fit")

### 2024-02-07 assets/python/fig:fit_mc.py

@@ -14,7 +14,8 @@ import matplotlib.pyplot as plt
 import numpy as np
 import scipy
 from scipy.special import lambertw
-from style import *
+
+from fluidx3d.eval.style import cm, color
 
 
 def CY(eta0, etaInf, Wi, a1, a2):
@@ -97,7 +98,7 @@ if __name__ == "__main__":
         if i == 83:
             return 2
 
-    gd = np.logspace(np.log10(np.min(gde)), np.log10(np.max(gde)), 1000)
+    gd = np.logspace(np.log10(np.min(gde)), np.log10(np.max(gde)) + 4, 1000)
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
     for i in [49, 59, 83]:
         gde, e, gdn, n = readFile(i)
@@ -123,7 +124,7 @@ if __name__ == "__main__":
     plt.ylabel(r"$\eta/\unit{\pascal\second}$")
     plt.legend(loc="center left", bbox_to_anchor=(1, 0.5))
     plt.savefig("../plots/fit_mc_eta.eps")
-    gd = np.logspace(np.log10(np.min(gdn)), np.log10(np.max(gdn)), 1000)
+    gd = np.logspace(np.log10(np.min(gdn)), np.log10(np.max(gdn)) + 4, 1000)
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
     for i in [49, 59, 83]:
         gde, e, gdn, n = readFile(i)

### 2024-02-07 assets/python/fluidx3d/eval/models/CY.py

@@ -1,11 +1,12 @@
 # -*- coding: utf-8 -*-
 """
-File to house the   class.
+File to house the  class.
 
-Created on Fri Jan 12 19:03:29 2024
+Created on Wed Feb  7 14:25:38 2024
 
 @author: Richard Kellnberger
 """
+
 
 import matplotlib.pyplot as plt
 import numpy as np
@@ -18,17 +19,15 @@ channel = 0
 pipe = 1
 
 
-class PTT:
-    def __init__(self, eta_p, lambda_p, epsilon, eta_s, xi=0):
+class CY:
+    def __init__(self, eta_p, lambda_p, eta_s, a1, a2):
         self.eta_p = eta_p
         self.lambda_p = lambda_p
-        self.epsilon = epsilon
         self.eta_s = eta_s
-        self.xi = xi
-        if xi != 0:
-            print("xi != 0 is not implemented!")
+        self.a1 = a1
+        self.a2 = a2
 
-    def prepareVelocityProfile(self, R, G, j):
+    def prepareVelocityProfile(self, R, G, j):  # TODO
         c = 2**j * self.eta_s / (-G)
         d = 2 * np.sqrt(self.epsilon) * self.lambda_p
 
@@ -154,15 +153,7 @@ class PTT:
 
     def eta(self, gd):
         return (
-            self.eta_p / np.exp(0.5 * lambertw(4 * self.epsilon * (gd * self.lambda_p) ** 2).real)
-            + self.eta_s
-        )
-
-    def N_1(self, gd):
-        return (
-            self.eta_p
-            / (2 * self.epsilon * self.lambda_p)
-            * lambertw(4 * self.epsilon * (self.lambda_p * gd) ** 2).real
+            self.eta_p / (1 + (self.lambda_p * gd) ** self.a1) ** (self.a2 / self.a1) + self.eta_s
         )
 
     def u(self, _):
@@ -216,5 +207,5 @@ class PTT:
         plt.show()
 
 
-alginate = PTT(48.2, 0.343, 0.545, 1e-3)
-mc0_49 = PTT(18.7e-3, 0.344e-3, 0.27, 1e-3)
+# alginate = PTT(48.2, 0.343, 0.545, 1e-3)
+mc0_49 = CY(18.7e-3, 0.321e-3, 1e-3, 1.697, 0.773)

### 2024-02-07 assets/python/prepareCY.py

@@ -1,0 +1,46 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the  class.
+
+Created on Tue Feb  6 15:58:51 2024
+
+@author: Richard Kellnberger
+"""
+
+import matplotlib.pyplot as plt
+import numpy as np
+from scipy.optimize import curve_fit
+
+from fluidx3d.eval.models.PTT import mc0_49
+
+gd = np.logspace(0, 10, 1000)
+eta = mc0_49.eta(gd)
+
+
+def CY(gd, lambda_p, a1, a2):  # Fix viscosities
+    return mc0_49.eta_p / (1 + (lambda_p * gd) ** a1) ** (a2 / a1) + mc0_49.eta_s
+
+
+p, cov = curve_fit(CY, gd, eta, [0.5 * mc0_49.lambda_p, 1, 1])
+err = np.sqrt(np.diag(cov))
+print(p)
+print(err)
+
+"""
+[3.21435421e-04 1.69720860e+00 7.73490872e-01]
+[1.19610108e-06 4.60219462e-03 1.49667878e-03]
+Use as:
+(0.321 +- 0.001)1e-3
+1.697 +- 0.005
+0.773 +- 0.001
+"""
+
+# One could argue that fitting the lof curve would be better. In fact the discrapency for high gd
+# reduces while the one at the first bend increases. As this es our primary area of interest we do
+# not perform a log fit
+
+plt.plot(gd, eta)
+plt.plot(gd, CY(gd, *p))
+plt.xscale("log")
+plt.yscale("log")
+plt.show()

### 2024-02-07 assets/setups/RT-DC/1/setup/defines.hpp

@@ -1,0 +1,180 @@
+#pragma once
+// ############################################ file paths #############################################
+
+//#define PATH_DEBUG "/data2/s1molehm/FluidX3D/Bead/interpolation/"
+//#define PATH_DEBUG "/tp6_gekle/data2/bt703473/debug/test2/"
+#define PATH_DEBUG "./bin/debug/" // path for debug files (PTX, LOG, VALIDATION)
+#define PATH_IBM   "./bin/ibm/"   // path for IBM extension
+
+
+// ############################################ LBM options ############################################
+
+// There hides a D2Q5 in the code
+//#define D2Q9
+//#define D3Q7 // very very inaccurate
+//#define D3Q13 // very inaccurate; Only works with MRT according to Krüger book p. 87; Does not reproduce EQUILIBRIUM_STRESS correctly.
+
+// Only use these:
+//#define D3Q15
+#define D3Q19 // Best value
+//#define D3Q27 // Better for high Reynolds numbers.
+
+#define SRT // singe relaxation time
+//#define TRT // two relaxiation time (as fast as SRT, but more accurate)
+//#define MRT // multi relaxiation time (as fast as SRT, but more accurate), (### not fully validated for for D3Q7 and D3Q13, incomplete relaxation times for D3Q7 and D3Q27 ###)
+
+//#define UPDATE_RHO // update density field after every step (not necessary for pure LBM)
+//#define UPDATE_U // update velocity field after every step (not necessary for pure LBM, makes tracer particle calculation faster)
+
+//#define MOVING_WALLS // moving bounce-back boundaries
+//#define BOUNDARY_EXPRESSION // combinable with MOVING_WALLS, !!!doesn't work on AMD for some reason!!!
+
+#define VISCOELASTIC
+// Only one of the following models may be defined
+//#define OLDROYD_B
+//#define FENEP
+//#define PTT // From Ferras 2019 eq (3) and (2) original PTT
+#define CARREAU_YASUDA
+
+//#define IBM // immersed boundary method (### under construction ###)
+//#define IBM_CELLS // simulate RBCs with the immersed-boundary method
+//#define INOUT // activate volume tracking for RBCs
+//#define INOUT_CHANGE // mark change of inside/outside in second bit
+
[…]

### 2024-02-07 assets/setups/RT-DC/1/setup/setup.cpp

@@ -1,0 +1,199 @@
+#include "setup.hpp"
+#include "shapes.hpp"
+#include "opencl.hpp" // contains "options.hpp", "main.hpp"
+#include "ibm.hpp"
+#include <numeric>
+#include <sstream>
+
+#include <filesystem>
+using std::filesystem::path;
+#include <fstream>
+using std::ofstream;
+
+#include <fmt/core.h>
+// using fmt::format
+using fmt::print;
+#include <fmt/color.h>
+using fmt::color;
+
+#include <spdlog/spdlog.h>
+//using spdlog::info;
+
+#include "fieldWriter.hpp"
+using fluidx3d::io::fieldWriter::FieldWriter;
+#include "guck.hpp"
+using fluidx3d::util::geometry::guck::Guck;
+#include "io.hpp"
+using fluidx3d::util::io::IO;
+#include "poiseuilleFlow.hpp"
+using fluidx3d::util::poiseuilleFlow::CircularPoiseuilleFlow;
+
+void example(SimulationOptions& options, Parameters& parameters) {
+	json raw = parameters.getRaw();
+	const int id = raw.at("id");
+	//const string path_files = "/tp6-gekle/nas/bt307867/cellsim/novel_2023-10-24/" + std::to_string(id) + "/";
+	const string path_files = fmt::format("RT-DC/{}/", id);
+	const path filesPath(path_files);
+	const string path_vtk = path_files + "vtkfiles/";
+	const string path_vtk_velocity = path_vtk + "velocity/";
+	const string path_vtk_strainRateTensor = path_vtk + "strainRateTensor/";
+	const string path_vtk_viscousStressTensor = path_vtk + "viscousStressTensor/";
+	const string path_vtk_polymerConformationTensor = path_vtk + "polymerConformationTensor/";
+
+	/*
+	 * this parameter increases the time step
+	 * --> leads to larger relaxation time tau (not good, but acceptable)
+	 * --> leads to larger Ma (not good, but acceptable)
+	 * --> eventually may lead to inaccuracies
+	 */
+	const double dtScale = 1e0;  // decrease timestep
+
+	// Length of simulation box
+	const uint Lx = 405;
+	const uint Ly = 92;
+	const uint Lz = 32;
+
+	/*
[…]

### 2024-02-08 NovelLBM.tex
Sections 5 and 6

@@
 
-\section{Viscosity shuffling algorithm}
+\section{Numerical methods}
+\label{sec:Methods}
 
@@
 Boundaries are modeled using the half-way bounce back algorithm. 
+\SG{ and inflow/outflow: give details }
 
@@
 For this, ... \SG{ give some more details, especially since we do SRT }.
+\SG{ also include inflow/outflow BCs }
+\SG{ do you advect polymer stress or polymer conformation? }
+
 The total stress experienced by the fluid ($\ma{\sigma}$) is then \cite{onishi2006}:
@@
 \section{Validation and accuracy}
-	To validate the simulations we compare the simulated velocity field of analytically solvable geometries to theory.
-For pressure gradient driven channel and pipe geometries, the analytical solution is as follows\cite{oliveira1999}.
-	\begin{equation}
-		u\left(r\right) = \frac{Gl^2}{2^{j+1}\eta_\text{p}}\left(e^\frac{R^2}{l^2}-e^\frac{r^2}{l^2}\right)
+
+To validate our viscosity shuffling algorithm and to assess its accuracy, we compare the velocity fields to semi-analytical solutions in plane and cylindrical Poiseuille flow.
+For the PTT model given in equation~(\ref{eq:polymerStress}) with an additional solvent stress contribution as in equation~(\ref{eq:totalStress}) a full analytical solution is not known for the considered geometries.
+Based on the work of \cite{oliveira1999} we derive a semi-analytical solution in Appendix~\ref{app:PTT}.
+
+We start by simulating the alginate and 0.49\% methyl cellulose solutions with a viscosity ratio $R_ \eta = 48 \cdot 10 ^3$ and $R_ \eta = 18.7$, respectively, in 2D planar Poiseuille flow.
+In physical units the channel has a height of \SI{20}{\micro\meter} which are discretized with \SG{ XX } LBM nodes.
+For the viscosity shuffling, we set $ \alpha _ \mathrm{s} = XX$.
+Along the flow direction, the channel is periodic and the flow is driven by a pressure gradient of \SI{-1e7}{\pascal\per\meter}. \SG{ pressure for MC? }
+The velocity field is initialized with zero.
+For methyl cellulose, we simulate the full temporal evolution with the polymers starting in the unstretched configuration.
+In the case of alginate, we speed up the convergence and start from a situation in which the polymers are pre-stretched \SG{ give details }.
+After \SG{ XX } LBM time steps corresponding to \SG{ XX } of physical time, the simulation is stopped and the flow field $u(y)$ is compared to the semi-analytical solution.
+As shown in figure~\ref{fig:2DAlginateU}, very good agreement is found.
+For a quantitative assessment, we compute the L2 error as
+	\begin{equation}\label{eq:l2error}
+		E_\text{u} = \frac{1}{u_\text{max}}\sqrt{\frac{1}{N}\sum\abs{u_\text{simulation}-u_\text{theory}}^2}.
 	\end{equation}
-	Where $u\left(r\right)$ is the radius dependent velocity, $G = -\partial_xp$ is the pressure gradient in the direction of the pipe and $l$ is a constant defined as follows.
-	\begin{equation}
-	l^2 = \frac{2^{2j-1}\eta_\text{p}^2}{\epsilon\lambda^2G^2}
-	\end{equation}
-	The index $j$ gives the solution for the channel for $j=0$ and the pipe for $j=1$.
-
-	We need this solution to compare to literature.
-However, this solution does not include $\eta_\text{s}$, which is required in general.
-With the inclusion of the solvent viscosity an analytical solution can no longer be found and the use of a semi-analytic solution is required (for details see appendix \ref{app:PTT}).
-	In the following we compare results for channel and pipe flow to these equations for realistic parameters. Afterward we compare the accuracy of our simulation algorithm against literature.
-	%We use richard/vtk 4dbc4d379842c538f084e68a5dcfe2555a674495 (2024-01-09)
-	\subsection{Channel flow vs theory}\label{sec:channelFlow}
-	Channel flow (also known as 2D Poiseuille) is one of the simplest flows and a very typical example.
-We pick a channel with a radius of \SI{10}{\micro\meter}, meaning the total width is \SI{20}{\micro\meter}.
-We pick periodic boundary conditions and drive the flow with a pressure gradient of \SI{-1e7}{\pascal\per\meter}.
-This simulation was done using the parameters obtained for the alginate based solution, as these represent the worst case scenario with respect to simulability among the fluids we work with.
-While our scheme is capable of simulating flows of to our knowledge arbitrary parameters, it increases runtime.
-For this parameter set the simulation time on our hardware becomes unreasonable.
-Therefore, for the simulations with the alginate based solutions we, contrary to all our other simulations, do not start from $0$ in all fields.
-We initialize the polymers in an extended state.
-This reduces the initial overshoot in the velocity by orders of magnitude allowing for larger time steps.
-Furthermore, the time to equilibrium of the polymer stretch is shortened considerably.
-This initialization leads to the simulation not accurately reproducing the time dependent behavior during startup, but leaves the steady state valid.
-The cross-section of the resulting flow field can be seen in figure \ref{fig:2DAlginateU}.
-Due to the long runtime, we stopped the simulation, early compared to the others.
-This means, that the simulation had not yet reached full equilibrium.
-Consequently, the error obtained here (see figure \ref{fig:2DAlginateErr}) is likely higher than what it would be after full relaxation.
-The average error as obtained by a typical L2 norm is \num{9e-4}.
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DAlginateU.eps}
-		\caption{Plot of the cross-section of the velocity of an alginate channel flow. Likely not fully in equilibrium.}
-		\label{fig:2DAlginateU}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DAlginateErr.eps}
-		\caption{Plot of error of the cross-section of the velocity of an alginate channel flow. Likely not fully in equilibrium.}
-		\label{fig:2DAlginateErr}
-	\end{figure}
-	The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall.
-The same simulation is done for the 3D case in the following.
-
-	\subsection{Pipe flow vs theory}
-	For the 2D case above, the walls are smooth.
-For the 3D case the round pipe has to be approximated leading to a staircase pattern that is not accurate.
-The error introduced by this depends on the lattice resolution.
-We use a diameter of 41 lattice points here.
-We use the same parameter set as above, aside from doubling the pressure gradient and also initialize the polymers in a stressed state.
-The resulting cross-section can be seen in figure \ref{fig:3DAlginateU}.
+The spatially resolved errors are shown in figure~\ref{fig:2DAlginateErr} in the appendix.
+Averaging over the channel diameter, we obtain an L2 error of \num{9e-4} and \SG{ XX } for alginate and methyl cellulose, respectively..
 
@@
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DAlginateU.eps}
-		\caption{Plot of the cross-section of the velocity of an alginate pipe flow. Likely not fully in equilibrium.}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/2DAlginateU.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/2DParameterStudyUWorst.eps}
+		\caption{(a) Velocity profile of alginate in planar channel flow. \SG{use $y$ instead of $r$ in 2D}. 
+		The time evolution of the center-line velocity when starting from a pre-stretched configuration (see main text) is shown in the inset.
+		(b) Velocity profile for methyl cellulose.}
+		\label{fig:2DAlginateU}
+	\end{figure}
+
+We now proceed to evaluate the viscosity shuffling method for a cylindrical pipe flow.
+The semi-analytical solution for this situation can be derived in a similar fashion as for the planar case and is given in appendix ~\ref{app:semianalyticalPoiseuille}.
+Numerically, the cylindrical sitation is slightly more complex due to discretization errors (''staircase effect'') when mapping the rounded channel walls onto the rectilinear LBM grid \cite{Lehmann.20229da}.
+We use the same material parameter set as above, but double the pressure gradient to \SG{ XX }. \SG{ why? }
+The channel has a diameter of \SG{ XX } and is discretized with 41 lattice points.
+Again, we initialize the polymers in the unstretched state for methyl cellulose and in the stretched state for alginate.
+The resulting velocity profile can be seen in figure \ref{fig:3DAlginateU} and shows almost equally good agreement as for the planar case with an L2 error of \num{0.014}.
+The spatially resolved error shows that this larger average is indeed mainly attributable to the staircase effect as the error near the walls increases significantly.
+
+	\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/3DAlginateU.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/3DParameterStudyUWorst.eps}
+		\caption{(a) Velocity profile of alginate in cylindrical channel flow. 
+		The time evolution of the center-line velocity when starting from a pre-stretched configuration (see main text) is shown in the inset.
+		(b) Velocity profile for methyl cellulose.}
 		\label{fig:3DAlginateU}
 	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DAlginateErr.eps}
-		\caption{Plot of error of the cross-section of the velocity of an alginate pipe flow. Likely not fully in equilibrium.}
-		\label{fig:3DAlginateErr}
-	\end{figure}
-	As can easily be seen in figure \ref{fig:3DAlginateErr} in comparison to the 2D case, the approximation of the walls carries considerable error.
-The L2 error is \num{0.014}.
-Still the error is acceptable, particularly for this moderate lattice resolution.
-Further validation of our implementation (using the faster-to-simulate methyl cellulose parameters and initialization at $0$) ca be found in appendix \ref{app:validation}.
 
@@
 	%Beware equation 61 in the paper is wrong. It should have an 8 instead of the 4.
-	The parameters from the paper ($R_\nu$, $Wi$ and $N$) are varied as in the paper. The error is calculated as follows.
-	\begin{equation}\label{eq:l2error}
-		E_\text{u} = \frac{1}{u_\text{max}}\sqrt{\frac{1}{N}\sum\abs{u_\text{simulation}-u_\text{theory}}^2}
-	\end{equation}
+	The parameters from the paper ($R_\nu$, $Wi$ and $N$) are varied as in the paper. 
 	\begin{figure}[H]
@@
 Knowing our simulations to be good we in the following show results for interesting systems, that are not analytically solvable.
-	\section{Results for non analytically solvable systems}
-	With the validity and accuracy of our scheme firmly established, we can demonstrate its results for some systems that cannot be solved analytically.
-In the following we will show the flow profiles for a conical nozzle, a cell in shear flow, and a chip for RT-DC measurements\todo{cite?
-spell out RT-DC?}.
-For all of these the methyl cellulose parameters found for a concentration of \SI{0.49}{\percent} have been used.
-	%We use richard/vtk 4dbc4d379842c538f084e68a5dcfe2555a674495 (2024-01-09)
-	\subsection{Conical nozzle}
-	Conical nozzles are used for example in bio printing.
-For this use case in particular the stresses experienced within the nozzle are of importance.
-We simulate a cell with an inflow radius of \SI{1.8}{\milli\meter} and an outflow radius of \SI{200}{\micro\meter}.
-It has a length of \SI{18}{\milli\meter}.
-The boundary conditions for inflow and outflow are given as the result of a simulation of pipes of the respective radius with a fixed volume flow of $\approx\SI{3}{\micro\liter\per\second}$.
-The resulting flow field can be seen in figure \ref{fig:Nozzle_v}.
-The von Mieses stress\todo{cite} can be seen in figure\ref{fig:Nozzle_sigma_vM}.
-It can be seen, that despite the high velocity in the center of the exit, the stress is actually smallest in the center.
-This means, that even for fast flows, given the bio ink and nozzle size is picked correctly, the cells flowing close to the center experience little stress.
+
+%	For pressure gradient driven channel and pipe geometries, the analytical solution is as follows.
+%	\begin{equation}
+%		u\left(r\right) = \frac{Gl^2}{2^{j+1}\eta_\text{p}}\left(e^\frac{R^2}{l^2}-e^\frac{r^2}{l^2}\right)
+%	\end{equation}
+%	Where $u\left(r\right)$ is the radius dependent velocity, $G = -\partial_xp$ is the pressure gradient in the direction of the pipe and $l$ is a constant defined as follows.
+%	\begin{equation}
+%	l^2 = \frac{2^{2j-1}\eta_\text{p}^2}{\epsilon\lambda^2G^2}
+%	\end{equation}
+%	The index $j$ gives the solution for the channel for $j=0$ and the pipe for $j=1$.
+%	
+%	We need this solution to compare to literature.
+However, this solution does not include $\eta_\text{s}$, which is required in general.
+With the inclusion of the solvent viscosity an analytical solution can no longer be found and the use of a semi-analytic solution is required (for details see appendix \ref{app:PTT}).
+%	In the following we compare results for channel and pipe flow to these equations for realistic parameters. Afterward we compare the accuracy of our simulation algorithm against literature.
+
+%%
+%% Example applications
+%%
+
+\section{Example applications}
+
+To illustrate the use of viscosity shuffling in realistic applications, we study three typical experimentally relevant situations.
+For ease of comparison, we use the 0.49\% methyl cellulose in all three situations.
+
+The first application stems from bioprinting where the bioink is pushed through a conical nozzle \SG{ ref }.
+The nozzle radius is \SI{1.8}{\milli\meter} at the inlet and \SI{200}{\micro\meter} at the outlet. 
+The nozzle has a length of \SI{18}{\milli\meter}.
+Due to the difference in inlet/outlet radii, the system cannot be modeled with periodic boundary conditions and we use inflow-/outflow boundary conditions as described in section~\ref{sec:Methods} instead.
+The required values for velocity and polymer conformation are obtained from simulations of pipes of the respective radii and a fixed volume flow of $\approx\SI{3}{\micro\liter\per\second}$.
+The resulting flow field can be seen in figure \ref{fig:Nozzle_v}~(a). 
+To quantify the total stress as a single number, we use the von Mises stress which is defined as \cite{Mueller.2023}: 
+\begin{align}
+	\sigma _ \mathrm{vM} = \sqrt{ \frac{ 1 } { 2 } \left[ \left( \sigma _1 - \sigma _2 \right)^2 + \left( \sigma _2 - \sigma _3 \right)^2 + \left( \sigma _3 - \sigma _1 \right)^2 \right]}.
+\end{align}
+It can be seen that the highest stresses aries at the nozzle exit in direct vicinity to the wall.
+This means that even for fast flows,  cells flowing close to the center experience less stress than cells flowing near the walls in agreement with earlier results in Newtonian fluids \cite{Mueller.2023}.
 	\begin{figure}[H]
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/Nozzle_v.eps}
-		\caption{Plot of the velocity in a conical nozzle.}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/Nozzle_v.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/Nozzle_sigma_vM.eps}
+		\caption{Velocity profile (a) and von Mises stress (b) for methyl cellulose in a conical nozzle as used for bioprinting. \SG{ draw nozzle contour with black lines }}
 		\label{fig:Nozzle_v}
 	\end{figure}
+
+% nozzle: We use richard/vtk 4dbc4d379842c538f084e68a5dcfe2555a674495 (2024-01-09)
+% shear: 	We use richard/vtk 4dbc4d379842c538f084e68a5dcfe2555a674495 (2024-01-09)
+% RT-DC: We use richard/master fe0fc04115b9b6ea6628bcc6cb6593d3f72ac0ea (2023-11-05)
+
+Our next example is the RT-DC geometry in which cells from a reservoir are squeezed through a narrow observation channel \cite{Toepfner.2018, Fregin:2019gx} with a square cross-section of 20x20 $\mu m$.
+For this simulation we use periodic boundary conditions and a constant body force corresponding to a pressure gradient of \SI{1e7}{\pascal}. 
+In figure~\ref{fig:RT-DC}, we show the velocity profile and the shear component of the stress which is the relevant component if a local shear viscosity is to be defined.
+There are three qualitative differences compared to a purely viscous fluid. 
+Directly after the inlet we find a region of low stress. 
+Due to the fast advection, the polymers, despite being inside the constriction, have not reacted to the increased fluid stress yet.
+Similarly, directly after the constriction, the high stress inside the observation channel persists over a certain distance that is needed for the polymer stress to decay.
+
  	\begin{figure}[H]
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/Nozzle_sigma_vM.eps}
-		\caption{Plot of the von Mises stress in a conical nozzle.}
-		\label{fig:Nozzle_sigma_vM}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/RT-DC_v.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/RT-DC_tau.eps}
+		\caption{Velocity profile (a) and shear stress (b) for methyl cellulose in a typical RT-DC geometry. \SG{ draw channel contour with black lines }
+		\SG{ change to von Mises instead of $ \tau _{ 12 }$? }}
+		\label{fig:RT-DC}
 	\end{figure}
-	%We use richard/vtk 4dbc4d379842c538f084e68a5dcfe2555a674495 (2024-01-09)
-	\subsection{Cell in shear flow}
-	A cell with a radius of \SI{6}{\micro\meter} and Youngs Modulus of \SI{100}{\pascal} is placed in a shear flow with a shear rate of \SI{400}{\per\second}.
-The fluid is described by the parameters of \SI{0.49}{\percent} methyl cellulose solution mentioned above.
-The lattice with a resolution of \num{100} lattice points is chosen significantly bigger than the cell to assure negligible impact of the walls.
-The lattice is periodic in $x$ and $z$ direction.
-At the edges of the simulation box in $y$ direction Dirichlet boundary conditions are imposed.
-The influence of the cell placed in the center of the simulation volume can barely be seen in the velocity field.
-In the von Mieses stress seen in figure \ref{fig:cellInShear_vM} it is the dominant feature.
-One can clearly see the shape of the cell by the depression of the stress it causes.
-Notable from this shape outwards radiate section of high and low stress.
-These are particularly pronounced along the longest axis of the deformed cell.
-From these one can see that the cell disturbs the fluid far from itself.
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/cellInShear_sigma_vM.eps}
-		\caption{Plot of the von Mises stress around a cell in shear flow.}
-		\label{fig:cellInShear_vM}
-	\end{figure}
-	%We use richard/master fe0fc04115b9b6ea6628bcc6cb6593d3f72ac0ea (2023-11-05)
-	\subsection{RT-DC}
-	Real-time deformability cytometry (RT-DC)\todo{cite} is a novel approach for single cell characterization.
-The cells are forced through a constriction.
-The observed deformation can be used to infer the mechanical properties of the cell.
-For this simulation we use periodic boundary conditions and a pressure gradient of \SI{1e7}{\pascal}.
-The resulting flow can be seen in figure \ref{fig:RT-DC_v}.
-The component typically associated with viscosity of the stress tensor can be seen in figure \ref{fig:RT-DC_tau}.
-There are three qualitative differences compared to a purely viscous fluid.
-Directly after the inlet is a region of low stress.
-Due to the advection of the stress, the fluid here despite being inside the constriction has not reacted to it yet.
-This region therefore could produce unexpected cell behavior if one passes through it.
-Similarly, directly after the constriction, the stress has not yet lowered.
+
+\SG{ decide whether we want to show a viscosity plot and remove or leave this part:
 If one would divide the stress in these two regions by the strain rate in an attempt to obtain a viscosity one would find an extremely low and an extremely high viscosity respectively.
@@
 This also shows why viscoelastic simulations cannot always be replaced by shear thinning models and should be considered despite the high computational cost.
+}
+
+With the third example we demonstrate the versatility of our approach which allows easy coupling to other LBM extensions such as the immersed-boundary method.
+Here, we include a homogeneously elastic particle as a simple, yet reasonably accurate, model for the mechanics of a living, biological cell \cite{Wohlrab.2023}.
+Coupling to the LBM solver is achieved with the immersed-boundary method as described in earlier publications \cite{Mueller.2021}.
+For simplicity, we consider the viscoelastic fluid inside and outside of the cell to be identical.
+The cell is initially spherical with a radius of \SI{6}{\micro\meter} and possesses Youngs Modulus of \SI{100}{\pascal} and a Poisson ratio of \SG{ XX }.
+It is placed into a shear flow with a shear rate of \SI{400}{\per\second} where the cell quickly reaches a steady state in which it deforms into a tank-treading ellipsoid.
+For the discretization of the cell we use \SG{ xx } tetrahedrons and a radius of \SG{ xx } lattice units.
+The lattice with a resolution of \num{100} lattice points is chosen significantly bigger than the cell to assure negligible impact of the walls. 
+The lattice is periodic in $x$ and $z$ direction.
+At the edges of the simulation box in $y$ direction Dirichlet boundary conditions are imposed.
+
+In the von Mises stress seen in figure \ref{fig:cellInShear_vM} the effect of the cell is clearly visible. 
+We observe four distinct regions of high stress radiating outwards from the cell body.
+These are particularly pronounced along the longest axis of the deformed cell. 
+\SG{ connect to the ''viscoelastic wings'' paper }
+
 	\begin{figure}[H]
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_v.eps}
-		\caption{Plot of the velocity in the RT-DC channel.}
-		\label{fig:RT-DC_v}
-	\end{figure}
-	\begin{figure}[H]
-	\centering
-	\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_tau.eps}
-	\caption{Plot of the polymer stress in the RT-DC channel.}
-	\label{fig:RT-DC_tau}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/cellInShear_sigma_vM.eps}
+		\caption{The von Mises stress around a cell in shear flow.}
+		\label{fig:cellInShear_vM}
 	\end{figure}
 
+%%
+%% Conclusion
+%%
+
 \section{Conclusion}
-	\todo{do}
 
@@
 	\todo{stability issue, fitting parameter, see fenep repo}
-	\section{Velocity profile for PTT}\label{app:PTT}
+
+%%
+%% Semi-analytical
+%%
+
+\section{Semi-analytical solution for Poiseuille flows of PTT fluids with solvent viscosity}
+\label{app:semianalyticalPoiseuille}
 Our derivation is analogous to Oliveira\cite{oliveira1999}.
@@
 	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyUWorst.eps}
-		\caption{Plot of the simulated velocity in a channel flow as a dependency of the radius. This is the same as figure \ref{fig:2DAlginateU} but for methyl cellulose.}
-		\label{fig:2DParameterStudyUWorst}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErrWorst.eps}
-		\caption{Plot of the error of the simulated velocity in a channel flow as a dependency of the radius. This is the same as figure \ref{fig:2DAlginateErr} but for methyl cellulose.}
-		\label{fig:2DParameterStudyErrWorst}
-	\end{figure}
+%	\begin{figure}[H]
+%		\centering
+%		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyUWorst.eps}
+%		\caption{Plot of the simulated velocity in a channel flow as a dependency of the radius. This is the same as figure \ref{fig:2DAlginateU} but for methyl cellulose.}
+%		\label{fig:2DParameterStudyUWorst}
+%	\end{figure}
+%	\begin{figure}[H]
+%		\centering
+%		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErrWorst.eps}
+%		\caption{Plot of the error of the simulated velocity in a channel flow as a dependency of the radius. This is the same as figure \ref{fig:2DAlginateErr} but for methyl cellulose.}
+%		\label{fig:2DParameterStudyErrWorst}
+%	\end{figure}
 	%Interestingly, the last one work besides Ma being approx 10.\n
@@
 	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyUWorst.eps}
-		\caption{Plot of the simulated velocity in a pipe flow as a dependency of the radius.
+%	\begin{figure}[H]
+%		\centering
+%		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyUWorst.eps}
+%		\caption{Plot of the simulated velocity in a pipe flow as a dependency of the radius.
 This was evaluated along a coordinate axis.
 This is the same as figure \ref{fig:3DAlginateU} but for methyl cellulose.}
-		\label{fig:3DParameterStudyUWorst}
-	\end{figure}
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErrWorst.eps}
-		\caption{Plot of the error of the simulated velocity in a pipe flow as a dependency of the radius.
+%		\label{fig:3DParameterStudyUWorst}
+%	\end{figure}
+%	\begin{figure}[H]
+%		\centering
+%		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErrWorst.eps}
+%		\caption{Plot of the error of the simulated velocity in a pipe flow as a dependency of the radius.
 This was evaluated along a coordinate axis.
 This is the same as figure \ref{fig:3DAlginateErr} but for methyl cellulose.}
-		\label{fig:3DParameterStudyErrWorst}
-	\end{figure}
+%		\label{fig:3DParameterStudyErrWorst}
+%	\end{figure}
 	\subsection{Validation summary}
@@
 
+		\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/2DAlginateErr.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/2DParameterStudyErrWorst.eps}
+		\caption{(a) L2 error of the velocity profile in \ref{fig:2DAlginateU} with respect to the semi-analytical theory in a planar Poiseuille flow.  
+			The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall. 
+		(b) For methyl cellulose.}
+		\label{fig:2DAlginateErr}
+	\end{figure}
+
+		\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/3DAlginateErr.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/3DParameterStudyErrWorst.eps}
+		\caption{(a) L2 error of the velocity profile in \ref{fig:2DAlginateU} with respect to the semi-analytical theory in a cylindrical Poiseuille flow.  
+			The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall. 
+		(b) For methyl cellulose.
+		\SG{ The error seems to reverse. For 2D alginate has the larger error, for cylinder MC has the larger error. Do we have an explanation why? }}
+		\label{fig:3DAlginateErr}
+	\end{figure}
+
 		\end{document}

### 2024-02-12 assets/python/fluidx3d/eval/models/PTT.py
fix PTT interpol
only affected interpolations at r < R/1e6

@@ -83,7 +83,7 @@ class PTT:
                 idx = np.argmin(np.abs(rVelocity - r))
                 if idx == 0:
                     m = (velocity[idx + 1] - velocity[idx]) / (rVelocity[idx + 1] - rVelocity[idx])
-                    return velocity[idx] - m * (r - rVelocity[idx]) - offset
+                    return velocity[idx] + m * (r - rVelocity[idx]) - offset
                 if rVelocity[idx] > r:
                     idx -= 1
                 elif rVelocity[idx] == r:

### 2024-02-12 NovelLBM.tex
First round complete

@@
 
+%%
+%% Abstract
+%%
+
+\section*{Abstract}
+
+The simulation of viscoelastic liquids using the Lattice-Boltzmann method in full three dimensions remains a formidable numerical challenge.
+In particular the simulation of strongly shear-thinnig fluids, where the ratio between the high-shear and low-shear viscosities is large, is often prevented by stability problems.
+Here we present a novel approach to overcome these issues.
+The central idea is to artificially increase the solvent viscosity which allows the method to benefit from the very good stability properties of the LBM.
+To compensate for this additional viscous stress, we reduce the polymer stress by the same amount.
+We apply this novel method to simulate two realistic cell carrier liquids, methyl cellulose and alginate solutions, of which the latter exhibits a viscosity ratio of more than 10,000.
+
+\clearpage
+
+%%
+%% Introduction
+%%
+
 \section{Introduction}
-	For a solution to be well suited for usage as a bioink during bioprinting its rheology has to fulfill certain requirements.
+
+Microfluidic technoglogies involving living cells are becoming increasingly popular. 
+Examples include medical diagnostics, where the pathological alteration of cell properties can serve as a marker for disease detection \cite{Toepfner.2018} or biofabrication where living cells are printed to create artificial tissues \cite{possl2021, Poologasundarampillai.2021, oconnell2022}.
+In all these applications cells are suspended in a cell carrier fluid which typically contains dissolved polymers making the fluid highly viscoelastic. 
+The motivation behind using viscoelastic fluids differs between applications. 
+In medical diagnostics, the viscous stress must be large enough to achieve detectable cell deformation, while in biofabrication the printed construct must be stable enough to retain its shape after the printing process.
+To satisfy the latter requirement, cell carriers used in biofabrication („bioinks“) typically exhibit a very high viscosity ratio with the zero-shear viscosity being many orders of magnitude larger than the pure solvent viscosity \cite{paxton2017}.
+
+To understand the rheology of such complex liquids in non-trivial geometries, computer simulations are an invaluable tool. 
+While a number of numerical techniques have been developed, the simulation of viscoelastic liquids remain an involved subject \cite{Alves.2020}, in particular for high viscosity ratios. 
+A very popular simulation technique for Newtonian fluids is the Lattice Boltzmann method \cite{Kruger_book} due to its simplicity and high parallelizability. 
+LBM has also been extended to viscoelastic situations, mainly in two \cite{ispolatov2002,wang2019,su2013,giraud1998,xie2018,dzanic2022,frank2006,zou2014,lee2017,dzanic2022_2,sedaghat2021,frantziskonis2011,qin2023,yoshino2008,papenkort2015,phillips2011,onishi2005} but occassionally also in three \cite{malaspinas2010,gupta2015,lallemand2003,ma2020,onishi2006,wang2020,dellar2014,su2013_2,wang2021,kuron2021,gupta2016} dimensions.
+To alleviate stability problems, some of these works include an artificial diffusivity of the polymer stress \cite{malaspinas2010,ma2020,wang2020,wang2021}. 
+Other remedies include special decompositions of the stress tensor\cite{dzanic2022} or optimization of the solvent contribution\cite{gupta2015}. 
+So far, however, none of these methods has been applied to very high viscosity ratio fluids which are often used as cell carrier fluids in lab experiments or technological applications.
+
+To fill this gap, here we develop a new variant of viscoelastic LBM which allows the stable and accurate simulation of very high viscosity ratio fluids.
+Our technique is based on the insight that stability issues in tradtional viscoelastic LBMs arise dure to an unbalance between the very large polymer stress and the much smaller viscous stress of the solvent.
+We overcome this issue by including („shuffling“) part of the polymer stress into the viscous part of the LBM algorithm.
+
+%	For a solution to be well suited for usage as a bioink during bioprinting its rheology has to fulfill certain requirements.
 During the printing process it should flow easily through the nozzle, meaning the viscosity should be low.
@@
 
-	Such simulations would however be very beneficial.
+%	Such simulations would however be very beneficial.
 They allow the \glqq measurement\grqq{ }of parameters that are otherwise hard or even impossible to access.
@@
 
-	Simulations using Lattice Boltzmann methods (LBM) are popular, as it has many advantages.
+%	Simulations using Lattice Boltzmann methods (LBM) are popular, as it has many advantages.
 It is very extensible and thus can deal with complex geometries, particles (e.g.
@@
 
-	Here we show our novel simulation approach for bioinks.
+%	Here we show our novel simulation approach for bioinks.
 It is specifically tailored to support arbitrary viscosity ratios and thus is able to simulate common bioinks or any other viscoelastic material with similar properties while providing high accuracy and stability.
@@
 The best fit was obtained with the so-called PTT model due to Phan-Thien and Tanner \cite{phan-thien1977,phan-thien1978} which was for explicitly derived for polymer networks in solution and thus appears to capture well the essential physics behind the alginate solution.
-\SG{ check that these papers have the exponentail version }.
+\SG{ check that these papers have the exponential version }.
 
@@
 	\begin{equation}
-		\eta\left(\dot{\gamma}\right) = \frac{\eta_\text{p}}{\exp\left[0.5W_0\left(4\epsilon \mathrm{Wi}^2\right)\right]} + \eta _\mathrm{s} \ma{D}
+		\eta\left(\dot{\gamma}\right) = \frac{\eta_\text{p}}{\exp\left[0.5W_0\left(4\epsilon \mathrm{Wi}^2\right)\right]} + \eta _\mathrm{s} \ma{D} \label{eq:shearEta}
 	\end{equation}
 	\begin{equation}
-		N_1 = \frac{\eta_\text{p}}{2\epsilon\lambda}W_0\left(4\epsilon \mathrm{Wi}^2\right)
+		N_1 = \frac{\eta_\text{p}}{2\epsilon\lambda}W_0\left(4\epsilon \mathrm{Wi}^2\right) \label{eq:shearN}
 	\end{equation}
@@
 
+\SG{ make sure that all papers cited in the introduction as ''3D'' are discussed here as well }
+\SG{ and vice versa: make sure that all papers discussed here are also cited in the introduction }
 Since the early days of LBM methods for viscoelastic fluids have been developed. 
@@
 \caption{Covered ranges of $ \mathrm{Wi}$ and $ R_ \eta $ for existing 3D LB methods.}
+\label{tab:viscRatio}
 \end{table}
@@
 \begin{align}
-	\ma{\sigma} &= 2\eta_\text{s}\ma{D} + \ma{\tau}_\text{shuffle} + \ma{\tau} - \ma{\tau}_\text{shuffle}	
+	\ma{\sigma} &= 2\eta_\text{s}\ma{D} + \ma{\tau}_\text{shuffle} + \ma{\tau} - \ma{\tau}_\text{shuffle}	 \label{eq:shuffleStress}
 \end{align}
@@
 As shown in figure~\ref{fig:2DAlginateU}, very good agreement is found.
-For a quantitative assessment, we compute the L2 error as
-	\begin{equation}\label{eq:l2error}
-		E_\text{u} = \frac{1}{u_\text{max}}\sqrt{\frac{1}{N}\sum\abs{u_\text{simulation}-u_\text{theory}}^2}.
-	\end{equation}
+For a quantitative assessment, we compute the L2 error as \SG{ give correct equn. }
+
 The spatially resolved errors are shown in figure~\ref{fig:2DAlginateErr} in the appendix.
@@
 		The time evolution of the center-line velocity when starting from a pre-stretched configuration (see main text) is shown in the inset.
-		(b) Velocity profile for methyl cellulose.}
+		(b) Velocity profile for methyl cellulose.
+		\SG{ make these plots for different $ \alpha _ \mathrm{s}$, either include or put into Si }}
 		\label{fig:2DAlginateU}
@@
 The spatially resolved error shows that this larger average is indeed mainly attributable to the staircase effect as the error near the walls increases significantly.
+These conclusions remain robust even when varying the pressure gradient, and thus the flow velocity, over many orders of magnitude as shown in figure~\ref{fig:2DParameterStudyErr} of the appendix.
 
@@
 		The time evolution of the center-line velocity when starting from a pre-stretched configuration (see main text) is shown in the inset.
-		(b) Velocity profile for methyl cellulose.}
+		(b) Velocity profile for methyl cellulose.
+				\SG{ make these plots for different $ \alpha _ \mathrm{s}$, either include or put into Si }}
 		\label{fig:3DAlginateU}
@@
 
-	%We use richard/master fe0fc04115b9b6ea6628bcc6cb6593d3f72ac0ea (2023-11-05)
-	\subsection{Comparison with literature}
-	Malaspinas et al.\cite{ma2020} provide a detailed validation and claim very high accuracy.
-Therefore, we pick this as a comparison.
-We aim at the reproduction of figures 17 and 18 from said paper.
+%Malaspinas: We use richard/master fe0fc04115b9b6ea6628bcc6cb6593d3f72ac0ea (2023-11-05)
+Finally, we compare the quality of our algorithm by comparing to an existing study on viscoelastic LBM by Malapsinas \textit{et al.} \cite{malaspinas2010}.
+The authors studied an Oldroyd-B fluid in a planar Poiseuille flow and compared the error in the simulated velocity profile to an exact analytical solution.
+The Oldroyd-B model is a special case of the PTT model which is obtained by setting $ \xi  = \epsilon  = 0$ in eq.~(\ref{eq:polymerStress}) and is thus easily tractable with our code.
+In figure~\ref{fig:malaspinas2010} we show the L2 error as function of lattice resolution for different Weissenberg numbers $ \mathrm{Wi}$ and \SG{ XX } $R_ \nu $.
+To match with \cite{malaspinas2010}, we defined these as 
+\begin{align}
+	XX
+\end{align}
+with \SG{ ... }. \SG{ comment whether these definitions are identical or different than the definitions above. }
+Furthermore, in agreement with \cite{malaspinas2010}, also the L2 error is defined slightly differently than above, namely:
+	\begin{equation}\label{eq:l2error}
+		E_\text{u} = \frac{1}{u_\text{max}}\sqrt{\frac{1}{N}\sum\abs{u_\text{simulation}-u_\text{theory}}^2}.
+	\end{equation}
+\SG{ Beware equation 61 in the paper is wrong. It should have an 8 instead of the 4. Do you use equation 61? }
+
+	\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/malaspinas2010.eps}
+		\caption{L2 error as defined in equation \ref{eq:l2error} from Malaspinas et al.\cite{malaspinas2010} (dots) compared to our algorithm (x) as a function of grid resolution.
+		Blue and green crosses are not visible as they overlap exactly with the orange and red crosses, respectively, showing that the accuracy of our method is.
+independent of $ \mathrm{Wi}$ in the studied parameter range.}
+		\label{fig:malaspinas2010}
+	\end{figure}
+
+As can be seen in figure~\ref{fig:malaspinas2010}, the accuracy of our method does not depend on the Weissenberg Number and is generally somewhat better than the method of \cite{malaspinas2010}.
+We note a certain dependence of the accuracy on $R_ \nu $ which we consider nevertheless acceptable given the overall smallness of the error.
+Finally, we find that the error of our method decreases with lattice resolution to the power of \SG{ give number, show dashed line in plot }.
+
+%e aim at the reproduction of figures 17 and 18 from said paper.
 We calculate this 2D flow in 3D as the viscoelastic algorithm has not been validated for 2D velocity sets.
@@
 Nevertheless, our lattice units do not line up exactly with those from Malaspinas, as our viscosity is different due to the shuffling.
-	%Beware equation 61 in the paper is wrong. It should have an 8 instead of the 4.
-	The parameters from the paper ($R_\nu$, $Wi$ and $N$) are varied as in the paper. 
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/malaspinas2010.eps}
-		\caption{Double logarithmic plot of the L2 error as defined in equation \ref{eq:l2error} from Malaspinas et al.\cite{malaspinas2010} (dots) compared to our algorithm (x) as a function of grid resolution.}
-		\label{fig:malaspinas2010}
-	\end{figure}
-	As can be seen in figure \ref{fig:malaspinas2010}, our results notably do not depend on the Weissenberg Number.
-While our error decreases with N with a constant power, Malaspinas et al.
-see diminishing returns.
-While these results are excellent, the error in our implementation seemingly is still dependent on the viscosity ratio.
-As the error is still small using our alginate parameters (see section \ref{sec:channelFlow}), this effect is irrelevant.
-With this, one can see, that we are not only capable to simulate parameters not yet accessible, but our implementation is also better for the parameters used in literature.
-Knowing our simulations to be good we in the following show results for interesting systems, that are not analytically solvable.
+%	The parameters from the paper ($R_\nu$, $Wi$ and $N$) are varied as in the paper.
 
@@
 
-The first application stems from bioprinting where the bioink is pushed through a conical nozzle \SG{ ref }.
+The first application stems from bioprinting where the bioink is pushed through a conical nozzle \cite{possl2021, Poologasundarampillai.2021, oconnell2022}.
 The nozzle radius is \SI{1.8}{\milli\meter} at the inlet and \SI{200}{\micro\meter} at the outlet. 
@@
 
-\section{Conclusion}
+\section{Summary and conclusion}
+
+In this work, we developed a novel simulation algorithm for viscoelastic fluids.
+Our method is based on the LBM for the solvent combined with a finite-volume solver for the polymer dynamics.
+Its key novel ingredient is the introduction of a shuffling parameter $ \alpha _ \mathrm{s}$ which shifts a substantial part of the polymer stress into the solvent contribution by artificially increasing the solvent viscosity.
+The algorithm compensates for this extra solvent stress by lowering - by the same amount - the polymer stress thus leaving the total stress invariant.
+This procedure is mathematically exact and does not introduce any additional physical approximations, but significantly increases numerical stability.
+
+We applied the method to the simulation of two realistic cell carrier fluids: an alginate and a methyl cellulose suspension.
+For simple situations such as shear and Poiseuille flow, we found very good agreement with (semi-)analytical theories.
+Importantly, the outcome of the viscostiy shuffling simulations is independent of the shuffling parameter $ \alpha _ \mathrm{s}$.
+We finally demonstrated the usability of our approach in realistic geometries such as those constricting microchannels and conical bioprinting nozzles.
 
@@
 %%
-%% Exp protocol
+%% Appendix: Exp protocol
 %%
@@
 
-	\section{Implementation of constitutive equations}\label{app:implementation}\todo{Note available analytical solutions}
-	There is a large amount of viscoelastic models.
-It is also common to extend these to create new models.
-As Oliveira shows\cite{oliveira2009} many of these can be expressed to a common form and thus actually are variants of a common idea.
-This allows both to easily find new models and implement them.
-In the following polymer contributions $\ma{\tau}$ of the models we have currently implemented are described.
-For notation, we mostly follow close to Oliveira\cite{oliveira2009}.
-	\parab{Implementation}
-	The actual implementation uses tensors related to $\tau$ to unify the calculations as much as possible.
-We denote these tensors as $\ma{A}$ and give the relation for each model.
-Whenever we explicitly need $\ma{\tau}$, we convert it.
-For Oldroyd-B this does not seem necessary and might even be slightly detrimental to performance.
-However, such a replacement simplifies the constitutive equation for FENE-P significantly and doing it for the other models as well allows a unified code with little adaptation for each model.
-It also makes the equations easier to understand and analyze.
-We stick with $\ma{A}$ as the Tensor containing the stress information, although its meaning is different for the different models listed here.
-This way, it can be seen, that all the models listed here can be brought to the common form listed below.
-	\begin{equation}
-		\frac{\partial\ma{A}}{\partial t} + \vec{u}\cdot\nabla\ma{A} = \left(\left(\nabla\vec{u}\right)^\text{T}\cdot\ma{A} + \ma{A}\cdot\left(\nabla\vec{u}\right)\right)+\ma{S}_\text{R} + 2\ma{D}
-	\end{equation}
-	Where $\ma{S}_\text{R}$ is a model-dependent term.
-In the following only this will be specified as all other terms are the same for all models.
-The second term on the left-hand side is handled via CTU, the rest is Euler-integrated.
-
-	\subsection{Oldroyd-B}
-	This model was originally developed by Oldroyd\cite{oldroyd1958}. The constitutive equation reads as follows.
-	\begin{equation}
-		\overset{\nabla}{\ma{\tau}} = -\frac{\ma{\tau}}{\lambda} + 2\frac{\eta}{\lambda}\ma{D}
-	\end{equation}
-	$\lambda$ is the polymer relaxation time and $\eta$ is the polymer viscosity.
-This viscosity also defines the magnitude of the elastic forces.
-Both these parameters also appear in the other models.
-We usually do not use this model, as it is not shear thinning.
-	\parab{Implementation}
-	\begin{equation}
-		\ma{S}_\text{R} = -\frac{\ma{A}}{\lambda}
-	\end{equation}
-	\begin{equation}
-		\ma{\tau} = \frac{\eta}{\lambda}\ma{A}
-	\end{equation}
-
-	\subsection{FENE-P}\todo{cite oliveira for theory}\todo{a lot more detail can be found in my dedicated FENE-P repo -> include derivation?}
-	This model was originally developed by Bird\cite{bird1980}\cite{bird1987}.
-It can be viewed as an Extension of the Oldroyd-B by limiting the polymers to finite extensibility.
-It has particularly many derivatives.
-Its constitutive equation reads as follows.
-	\begin{equation}
-		\overset{\nabla}{\ma{\tau}} = -Z\frac{\ma{\tau}}{\lambda} + \left(\ma{\tau}+(1-e b)\frac{\eta}{\lambda}\uT\right)\frac{\Dif\ln Z}{\Dif t} + 2(1-eb)\frac{\eta}{\lambda}\ma{D}
-	\end{equation}
-	With the extensibility parameter b, $e = \frac{2}{b\left(b + 2\right)}$ and
-	\begin{equation}
-		Z = 1 + \frac{3}{b}\left(\frac{b}{b + 2}+\frac{\Tr\ma{\tau}}{3\frac{\eta}{\lambda}}\right)
-	\end{equation}
-	Note, that the sign of $\ma{\tau}$ differs from Birds formulation.
-Also, the relation $nk_\text{B}\theta = \frac{\eta}{\lambda}$ has already been used to avoid introducing additional parameters.
-Particularly for large shear rates, it is numerically possible, that the polymer exceeds its maximal extensibility.
-If it is extended beyond the maximum the equations cause it to extend further, making this model unstable for high shear rates.
-Even with the decomposition proposed by Dzanic\cite{dzanic2022}, we were not yet able to get it stable.
-Thus, it is currently unused.
-	\parab{Implementation}
-	\begin{equation}
-		\ma{S}_\text{R} = \frac{\Tr\ma{A}\uT + \left(b + 2\right)\ma{A}}{\lambda\frac{b+2}{b+5}\left(\Tr\ma{A}-b-2\right)}
-	\end{equation}
-	\begin{equation}
-		\ma{\tau} = \frac{\eta}{\lambda}\frac{b}{b+2-\Tr\ma{A}}\left(\ma{A}+\frac{\Tr\ma{A}}{b+2}\uT\right)
-	\end{equation}
-	This seems complicated, but removes the highly problematic $\frac{\Dif\ln Z}{\Dif t}$ term, which causes issues in implementation details.
-
-	\subsection{PTT}
-	Originating from Phan-Thien and Tanner\cite{phan-thien1977} it was soon after slightly extended by Phan-Thien\cite{phan-thien1978} to the exponential form we use.
-There is also an even more general form from Ferrás\cite{ferras2019}, which due to its use of the Gamma function is hard to implement on GPUs.
-The constitutive equation reads as follows.
-	\begin{equation}
-		\overset{\nabla}{\ma{\tau}} = -\xi\left(\ma{\tau}\cdot\ma{D} + \ma{D}\cdot\ma{\tau}\right) - e^{\frac{\epsilon\lambda}{\eta}\Tr\ma{\tau}}\frac{\ma{\tau}}{\lambda} + 2\frac{\eta}{\lambda}\ma{D}
-	\end{equation}
-	Where $\epsilon$ and $\xi$ are additional parameters related to the network this model is supposed to model. For our polymer solutions $\xi$ is always (effectively) zero.
-	\parab{Implementation}
-	\begin{equation}
-		\ma{S}_\text{R} = -\xi\left(\ma{A}\cdot\ma{D} + \ma{D}\cdot\ma{A}\right) - e^{\epsilon\Tr\ma{A}}\frac{\ma{A}}{\lambda}
-	\end{equation}
-	\begin{equation}
-		\ma{\tau} = \frac{\eta}{\lambda}\ma{A}
-	\end{equation}
-
-	\section{FENE-P}\label{app:FENE-P}
-	\todo{stability issue, fitting parameter, see fenep repo}
-
 %%
-%% Semi-analytical
+%% Appendix: Semi-analytical
 %%
@@
 \label{app:semianalyticalPoiseuille}
+\SG{ make a self-contained derivation which is understandable even without reading Oliveira \\}
+\SG{ use Gl.~(\ref{eq:polymerStress}) as starting point and end with Poiseuille solution, but also shear solution Gl.~(\ref{eq:shearN}, \ref{eq:shearEta}) \\}
 Our derivation is analogous to Oliveira\cite{oliveira1999}.
@@
 
-	\section{Parameter studies and validation}\label{app:validation}
-	To validate, that our algorithm is indeed valid, we use it to simulate some typical system and determine the observed error.
-First we vary the shuffle fraction to assure that its value is irrelevant as its introduction in section \ref{sec:shuffling} predicts.
-Following that we calculate the shear flow for varying shear rates to reproduce the predicted shear thinning.
-Finally 2D and 3D poiseuille flows are simulated for different pressure gradients.
-A high degree of accuracy is observed in all these tests showing the validity of our algorithm.
-	\subsection{Viscosity shuffle fraction dependency}\label{app:viscSuffleDependency}
-	We use PTT with the methyl cellulose parameters.
-In a shear flow with the very small shearrate of $\dot{\gamma} = \SI{1}{\per\second}$, the viscosity shuffle fraction is varied.
-As can be seen in figure \ref{fig:suffleParameterStudy}, the observed viscosity does not depend on $\alpha_\text{s}$.
-The simulation gives $\eta = \SI{19.6999988048\pm0.0000000002}{\milli\pascal}$, while theory gives $\eta = \SI{19.699998805}{\milli\pascal}$.
-Therefore, the simulation is incredibly accurate.
+%%
+%% Appendix: Shear flow
+%%
+
+\section{Validation in pure shear flow}
+\label{sec:shearFlow}
+
+As additional quantitative validation, we simulate a pure shear flow driven by imposing a fixed velocity at the top and bottom of the computational box and using periodic boundary conditions in the other two directions.
+The box dimension is \SG{ xx }.
+We use PTT with the methyl cellulose parameters and vary the shear rate to cover the full range starting from the zero-shear all the way to the infinite-shear plateau displayed in figure~\ref{fig:fit_mc} of the main text.
+The shuffling is fixed at $ \alpha _ \mathrm{s} = 1$ and the viscosity as function of shear rate is computed by dividing the total fluid stress at the center of the box by the shear rate.
+Figure~\ref{fig:wiParameterStudy}~(a) shows that our simulations are in very good agreement with the semi-analytical solution as calculated in \SG{ XX } with a maximum error of \num{2e-11}.
+Importantly, we show in figure~\ref{fig:wiParameterStudy}~(b) that this very good agreement is independent of the shuffling parameter $ \alpha _ \mathrm{s}$.
 	\begin{figure}[H]
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/suffleParameterStudy.eps}
-		\caption{Plot of the simulated viscosity as a dependency of the viscosity shuffle fraction. The axis label does not have enough digits to reflect the precision archived.}
-		\label{fig:suffleParameterStudy}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/wiParameterStudy.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/suffleParameterStudy.eps}
+		\caption{(a) The local viscosity determined by a shear flow simulation is in very good agreement with the semi-analytical theory.
+		(b) The error is negligibly small independent of the shuffling parameter $ \alpha _ \mathrm{s}$.}
+		\label{fig:wiParameterStudy}
 	\end{figure}
-	\subsection{Weissenberg number dependency}
-	We use the same setup as in section \ref{app:viscSuffleDependency}, but vary the shear rate instead of $\alpha_\text{s}$, which is equal to unity here.
-As can be seen in figure \ref{fig:wiParameterStudy}, the agreement is very good.
-The maximum relative error is \num{2e-11}.
-The simulation becomes asymptotic.
-For higher shear, it equilibrates faster.
-Those data points have significantly smaller errors (\num{7e-16}) suggesting, that the simulation was not fully equilibrated for the smaller shear rates.
-Also, this suggests, that when the simulation has fully equilibrated the error is smaller than can be captured in a 32-bit float.
+
+%%
+%% Appendix: Supplementary figures
+%%	
+\section{Supplementary figures}
+\label{sec:supplementaryFigures}
+
 	\begin{figure}[H]
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/wiParameterStudy.eps}
-		\caption{Plot of the simulated viscosity as a dependency of the Weissenber number.}
-		\label{fig:wiParameterStudy}
-	\end{figure}
-	\subsection{2D Poiseuille vs theory}
-	The setup remains as above, but the imposed shear flow is replaced by a pressure gradient.
-The radius of the channel flow is set as \SI{10}{\micro\meter}.
-The simulations were run for multiple values for the pressure gradient spaced in a way to approximately cover the range of the Weissenberg number seen in the section before.
-The resulting errors can be seen in figure \ref{fig:2DParameterStudyErr}.
-Due to the shear thinning behavior the shear rate is not constant for the whole channel, therefore the direct relation of the pressure gradient to the Weissenberg number is not possible.
-Averaging the shear rate it becomes clear that the error maximum here corresponds to the maximum slope seen in figure \ref{fig:wiParameterStudy}.
-The plots for the velocity profile and its error of this worst case parameter can be seen in figure \ref{fig:2DParameterStudyUWorst} and figure \ref{fig:2DParameterStudyErrWorst} respectively.
-It is clear, that the simple bounce back boundaries employed on the wall are a major cause of the observed error.
-The error in total is insignificant.
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr.eps}
-		\caption{Plot of the simulation error in a channel flow as a dependency of the pressure gradient.}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/2DParameterStudyErr.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/3DParameterStudyErr.eps}
+		\caption{Average error of the velocity for a planar (a) and a cylindrical (b) Poiseuille flow  of methyl cellulose at different pressure gradients. 
+		All other parameters are as in figure~\ref{fig:2DAlginateU}~(b) of the main text.
+		The peak in the error profile appears when the average shear rate across the channel corresponds to the maximum slope in the viscosity profile of figure~\ref{fig:wiParameterStudy}. }
 		\label{fig:2DParameterStudyErr}
 	\end{figure}
-%	\begin{figure}[H]
-%		\centering
-%		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyUWorst.eps}
-%		\caption{Plot of the simulated velocity in a channel flow as a dependency of the radius. This is the same as figure \ref{fig:2DAlginateU} but for methyl cellulose.}
-%		\label{fig:2DParameterStudyUWorst}
-%	\end{figure}
-%	\begin{figure}[H]
-%		\centering
-%		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErrWorst.eps}
-%		\caption{Plot of the error of the simulated velocity in a channel flow as a dependency of the radius. This is the same as figure \ref{fig:2DAlginateErr} but for methyl cellulose.}
-%		\label{fig:2DParameterStudyErrWorst}
-%	\end{figure}
-	%Interestingly, the last one work besides Ma being approx 10.\n
-	%This error is not influenced by shuffling fraction or lattice resolution\n
-	%The shape the sim returns can be obtained by the theory by modifying px and or etap\n
-	%The resulting error is (approx) centered around Wi of max viscosity gradient.
-	This is now repeated for a three-dimensional flow.
-	\subsection{3D Poiseuille vs theory}
-	The simulation was run as described in the section above, but the 2D channel geometry was changed into a 3D pipe flow.
-The errors show a similar behavior (see figure \ref{fig:3DParameterStudyErr}), but are considerably larger.
-The maximum pressure gradient is smaller for this series is smaller than the 2D series as those simulations exceeded the stability criterion for the Mach number.
-The worst result was obtained using the same pressure gradient as in the 2D case and can be seen in figure \ref{fig:3DParameterStudyUWorst} and figure \ref{fig:3DParameterStudyErrWorst}.
-Notably the error here, while still tolerable is a lot worse than the 2D case.
-With the error being particularly high around the wall it is likely that the wall approximation, which is significantly worse in the 3D case due to the required stair stepping, is the main reason for the 3D case exhibiting larger errors.
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr.eps}
-		\caption{Plot of the simulation error in a pipe flow as a dependency of the pressure gradient}
-		\label{fig:3DParameterStudyErr}
-	\end{figure}
-%	\begin{figure}[H]
-%		\centering
-%		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyUWorst.eps}
-%		\caption{Plot of the simulated velocity in a pipe flow as a dependency of the radius.
-This was evaluated along a coordinate axis.
-This is the same as figure \ref{fig:3DAlginateU} but for methyl cellulose.}
-%		\label{fig:3DParameterStudyUWorst}
-%	\end{figure}
-%	\begin{figure}[H]
-%		\centering
-%		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErrWorst.eps}
-%		\caption{Plot of the error of the simulated velocity in a pipe flow as a dependency of the radius.
-This was evaluated along a coordinate axis.
-This is the same as figure \ref{fig:3DAlginateErr} but for methyl cellulose.}
-%		\label{fig:3DParameterStudyErrWorst}
-%	\end{figure}
-	\subsection{Validation summary}
-	The algorithm passes all typical test and behaves as expected.
-The error is very small for most problems.
-Only the pipe flow shows considerable error, however this is likely caused by the wall model and not by the viscosity shuffling method.
 

### 2024-02-13 NovelLBM.tex
First re-read

@@
 To compensate for this additional viscous stress, we reduce the polymer stress by the same amount.
-We apply this novel method to simulate two realistic cell carrier liquids, methyl cellulose and alginate solutions, of which the latter exhibits a viscosity ratio of more than 10,000.
+We apply this novel method to simulate two realistic cell carrier fluids, methyl cellulose and alginate solutions, of which the latter exhibits a viscosity ratio exceeding 10,000.
 
@@
 Examples include medical diagnostics, where the pathological alteration of cell properties can serve as a marker for disease detection \cite{Toepfner.2018} or biofabrication where living cells are printed to create artificial tissues \cite{possl2021, Poologasundarampillai.2021, oconnell2022}.
-In all these applications cells are suspended in a cell carrier fluid which typically contains dissolved polymers making the fluid highly viscoelastic. 
+In all these applications cells are suspended in a cell carrier fluid which typically contains dissolved polymers making the fluid highly viscoelastic and shear-thinning. 
 The motivation behind using viscoelastic fluids differs between applications. 
@@
 To alleviate stability problems, some of these works include an artificial diffusivity of the polymer stress \cite{malaspinas2010,ma2020,wang2020,wang2021}. 
-Other remedies include special decompositions of the stress tensor\cite{dzanic2022} or optimization of the solvent contribution\cite{gupta2015}. 
-So far, however, none of these methods has been applied to very high viscosity ratio fluids which are often used as cell carrier fluids in lab experiments or technological applications.
+Other remedies include special decompositions of the stress tensor\cite{dzanic2022} or optimization of the solvent contribution\cite{gupta2015} \SG{ what is this? }.  
+Despite these improvements, however, none of these methods has been applied to very high viscosity ratio fluids which are often used as cell carrier fluids in lab experiments or technological applications.
 
@@
 We overcome this issue by including („shuffling“) part of the polymer stress into the viscous part of the LBM algorithm.
-
-%	For a solution to be well suited for usage as a bioink during bioprinting its rheology has to fulfill certain requirements.
-During the printing process it should flow easily through the nozzle, meaning the viscosity should be low.
-This is not only beneficial for ease of use, but is also crucial for survivability of the cells, as the stress they experience is dependent on the viscosity.
-However, after the printing process, it is desired, that the printed construct is stable.
-This can be temporarily archived by very high viscosities.
-Therefore, one approach to solve this is to use shear thinning fluids.
-Shear thinning fluids can easily be produced by dissolving polymers in water.
-This however, has the side effect of viscoelasticity.
-Due to the polymers the solution also exhibits elastic behavior.
-The influence of which on the printing process is not well understood yet.
-For realistic bioinks, the ratio of their zero shear viscosity and their infinite shear viscosity is large as is expected based on the desired attributes mentioned above.
-For such large viscosity ratios, simulating viscoelastic materials with Lattice Boltzmann methods was to our knowledge not yet possible.
-
-%	Such simulations would however be very beneficial.
-They allow the \glqq measurement\grqq{ }of parameters that are otherwise hard or even impossible to access.
-They allow the prediction of the outcome of experiments without performing them, which is especially helpful if the experiment cannot be easily performed.
-An example would be the design of new and improved printing nozzles.
-With simulations, the geometry can be optimized to a degree, that would be near impossible using iterative experiments.
-The large amounts of data simulations can provide allow better understanding of the fundamental processes, that cause observed behavior.
-\todo{"List some simulations for bionprinting, bioinks that have been done (restrict to only viscoelastic sims)"}
-
-%	Simulations using Lattice Boltzmann methods (LBM) are popular, as it has many advantages.
-It is very extensible and thus can deal with complex geometries, particles (e.g.
-cells) suspended in the fluid and many different interactions within and between those.
-Most importantly it is and easily parallelizable algorithm and thus can be run on GPUs or similar accelerators.
-This allows even large domains to be simulated in short amount of time with commodity GPUs and no need for any supercomputer.
-It is also easily possible to extend LBM to deal with viscoelastic fluids.
-This has been done before by multiple groups.
-There are many publications discussing such approaches in two dimensions\cite{ispolatov2002,wang2019,su2013,giraud1998,xie2018,dzanic2022,frank2006,zou2014,lee2017,dzanic2022_2,sedaghat2021,frantziskonis2011,qin2023,yoshino2008,papenkort2015,phillips2011,onishi2005}.
-		Simulations in three dimensions have a higher computational cost and are not as abundant, but have also been performed by many\cite{malaspinas2010,gupta2015,lallemand2003,ma2020,onishi2006,wang2020,dellar2014,su2013_2,wang2021,kuron2021,gupta2016}.
-Among these many are concerned about stability.
-Some include diffusivity of the polymer stress in their model to increase stability\cite{malaspinas2010,ma2020,wang2020,wang2021}.
-Other remedies include special decompositions of the stress tensor\cite{dzanic2022} or optimization of the solvent contribution\cite{gupta2015}.
-However, none of these reach the relevant viscosity ratios for bioinks.
-
-%	Here we show our novel simulation approach for bioinks.
-It is specifically tailored to support arbitrary viscosity ratios and thus is able to simulate common bioinks or any other viscoelastic material with similar properties while providing high accuracy and stability.
-This is archived by subtracting a viscous stress from the polymer stress calculated from the PTT model.
-This offset is corrected by increasing the viscosity of the base LBM algorithm accordingly.
 
@@
 To illustrate our novel LBM algorithm, we consider two prototypical cell carrier fluids.
-The first is an alginate solution which is often used in biofabrication, i.e., the 3D printing of living cells, but can also serve as a common food additive.
-Our solution contains 4\% alginate solvated in PBS as was measured in a commerical plate-plate rheometer (see appendix  XX for experimental details).
-The shear-dependent viscosity $ \eta$ and the first normal stress difference $N_1$ are shown as function of shear rate in a frequency-sweep \SG{ ? } measurement in figure~\ref{fig:fit_alginate}.
+The first is an alginate solution which is often used in biofabrication but can also serve as a common food additive.
+Our solution contains 4\% alginate solvated in PBS and was measured in a commerical plate-plate rheometer (see appendix  \ref{app:experiment} for experimental details).
+The shear-dependent viscosity $ \eta$ and the first normal stress difference $N_1$ are shown as function of shear rate in figure~\ref{fig:fit_alginate}.
 We note the very high zero-shear viscosity of more than $10000 \si{ mPa \cdot s}$.
-Carrier fluids in bioprinting, termed bioinks, are characterized in general by such high viscosities to guarantee stability of the printed construct.
-On the other hand, during the actual printing process when the material is flowing, the viscosity should be as low as possible to avoid excessive mechanical stress on the embedded cells.
+Bioinks in biofabrication are characterized in general by such high viscosities to guarantee stability of the printed construct.
+At the same time, during the actual printing process when the material is flowing, the viscosity should be as low as possible to avoid excessive mechanical stress on the embedded cells.
+This motivates the use of highly shear-thinning viscoelastic fluids in biofabrication.
 	\begin{figure}[H]
 		\centering
-		\includegraphics[width=7.8cm]{assets/plots/fit_alginate_eta.eps}
-		\includegraphics[width=7.8cm]{assets/plots/fit_alginate_N.eps}
-%		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/fit_alginate_eta.eps}
-%		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/fit_alginate_N.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/fit_alginate_eta.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/fit_alginate_N.eps}
 		\caption{Rheology data for alginate solution from 21 measurements of the viscosity (a) and normal stress (b).
@@
 The Oldroyd-B model is not appropriate for most real complex fluids as it features a shear-independent viscosity in clear contradiction to the experimental data presented in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}.
-Although the FENE-P does reproduce shear-thinning, we were not able to obtain a satisfactory fit to our data for alginate and methyl cellulose with physically reasonable values of the model parameters.
-The best fit was obtained with the so-called PTT model due to Phan-Thien and Tanner \cite{phan-thien1977,phan-thien1978} which was for explicitly derived for polymer networks in solution and thus appears to capture well the essential physics behind the alginate solution.
-\SG{ check that these papers have the exponential version }.
+%Although the FENE-P does reproduce shear-thinning, we were not able to obtain a satisfactory fit to our data for alginate and methyl cellulose with physically reasonable values of the model parameters.
+A good fit to our data was obtained with the so-called PTT model due to Phan-Thien and Tanner \cite{phan-thien1977,phan-thien1978} which has been developed explicitly for polymer networks in solution and thus appears to capture well the essential physics behind the alginate and methyl cellulose solutions.
 
-The PTT model is specified by a constitutive equation for the polymer stress $ \ma{\tau}$:
+The PTT model is specified by a differential equation for the polymer stress $ \ma{\tau}$:
 	\begin{equation}
@@
 where $\ma{D}$ is the strain rate tensor. 
-The polymer viscosity is denoted $\eta_\text{p}$ and $\lambda$ is the corresponding relaxation time.  \SG{ are they actually independent? }
+\SG{ check that PTT is given in this form in \cite{phan-thien1977,phan-thien1978} or cite other source }
+The polymer viscosity is denoted $\eta_\text{p}$ and $\lambda$ is the corresponding relaxation time.  
 $\epsilon$ is the so-called extensibility parameter which controls at which shear rates thinning takes place and $\xi$ describes the slip in the polymer network which we will set to zero in the following.
-The upper convected derivative is defined as follows:
+The upper convected derivative of an arbitrary tensor $ \ma{ A }$ is defined as follows:
 	\begin{equation}
@@
 	\end{equation}	
-Finally, the total fluid stress is the sum of the polymer stress $ \tau $ and a solvent stress $ \tau _ \mathrm{s}$ due to the Newtonian solvent with viscosity $ \eta _ \mathrm{s}$.
+Finally, the total fluid stress $\ma{\sigma}$ is the sum of the polymer stress $ \tau $ and a solvent stress due to the Newtonian solvent with viscosity $ \eta _ \mathrm{s}$:
+	\begin{align}
+		\ma{\sigma} &=  \ma{\tau} + 2\eta_\text{s}\ma{D} 		\label{eq:totalStress}
+	\end{align}
 
-For a simple shear flow in the $xy$-plane, an analytical expression for $ \eta $ and $N_1$ is given by \cite{ferras2019} which (with $\xi=0$) reads
+For a simple shear flow in the $xy$-plane of a PTT fluid with $ \xi =0$, an analytical expression for $ \eta $ and $N_1$ can be derived as detailed in appendix \ref{app:semianalyticalPoiseuille}:
 	\begin{equation}
-		\eta\left(\dot{\gamma}\right) = \frac{\eta_\text{p}}{\exp\left[0.5W_0\left(4\epsilon \mathrm{Wi}^2\right)\right]} + \eta _\mathrm{s} \ma{D} \label{eq:shearEta}
+		\eta\left(\dot{\gamma}\right) = \frac{\eta_\text{p}}{\exp\left[0.5W_0\left(4\epsilon \mathrm{Wi}^2\right)\right]} + \eta _\mathrm{s} \label{eq:shearEta}
 	\end{equation}
@@
 where $ \mathrm{Wi} = \lambda \dot{ \gamma  }$ is the Weissenberg number and $W_0$ is the Lambert $W$-function. \SG{ check that $ \eta _ \mathrm{s}$ is correct }
-\SG{ I did not find these equations in \cite{ferras2019}? }
 Fitting these equations to the rheological data for alginate and methy cellulose leads to satisfactory agreement as shown in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}.
 In the fit, the solvent viscosity was fixed at $ \eta _ \mathrm{s} = 1 \si{ mPa } \cdot \si{ s }$ as the viscosity of the PBS buffer. \SG{ give ref }
-At very high shear rates, the contained polymers are completely stretched and the viscosity asymptotically approaches the solvent values $ \eta _ \mathrm{s}$.
-The obtained parameters for alginate are
-	\begin{align}
-		\eta_\text{p} &= \SI{48.2\pm0.4}{\pascal\second}\\
-		\lambda &= \SI{0.343 \pm 0.004}{\second}\\
-		\epsilon &= \num{0.545 \pm 0.010}.
-	\end{align}
-while the parameters for the three concentrations of methyl cellulose are given in table~\ref{tab:MC_parameters}.
+%At very high shear rates, the contained polymers are completely stretched and the viscosity asymptotically approaches the solvent value $ \eta _ \mathrm{s}$.
+The obtained parameters are given in table~\ref{tab:PTTparameters}.
 	\begin{table}[H]
@@
 %			Concentration/\unit{\percent} & $\eta_\text{p}/\unit{\milli\pascal\second}$ & $\lambda/\unit{\milli\second}$ & $\epsilon$ \\
-			Concentration/ percent & $\eta_\text{p}/mPas$ & $\lambda/ms$ & $\epsilon$ \\
+			Fluid & $\eta_\text{p}/mPas$ & $\lambda/ms$ & $\epsilon$ \\
 			\hline
-			\num{0.49} & \num{18.7\pm0.4} & \num{0.344\pm0.003} & \num{0.270\pm0.003} \\
-			\num{0.59} & \num{32.5\pm0.7} & \num{0.433\pm0.004} & \num{0.365\pm0.004} \\
-			\num{0.83} & \num{81\pm2} & \num{0.714\pm0.009} & \num{0.496\pm0.006}
+			alginate \num{4} & \num{48,200\pm0.4} & \num{343 \pm 0.004}. & \num{0.545 \pm 0.010}\\
+			methyl c. \num{0.49} & \num{18.7\pm0.4} & \num{0.344\pm0.003} & \num{0.270\pm0.003} \\
+			methyl c. \num{0.59} & \num{32.5\pm0.7} & \num{0.433\pm0.004} & \num{0.365\pm0.004} \\
+			methyl c. \num{0.83} & \num{81\pm2} & \num{0.714\pm0.009} & \num{0.496\pm0.006}
 		\end{tabular}
-		\caption{Parameters of the PTT modelobtained when fitting the methyl cellulose solutions.}
-		\label{tab:MC_parameters}
+		\caption{Parameters of the PTT model obtained by fitting to the rheological measurements in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}.
+		\SG{ add a column with $R_ \eta $ }}
+		\label{tab:PTTparameters}
 	\end{table}
@@
 which will turn out to be an important parameter to determine numerical stability of LB simulations. 
-\SG{ do we actually need a ratio?
-Since $ \eta _\mathrm{s}$ is probably always water-like, would it not be enough to state whether $ \eta _ \mathrm{p}$ is high or low } \SG{ do we actually show that $R_ \eta  $ determines stability?
-}
+\SG{ wo don't actually show that $R_ \eta  $ determines stability? }
 This ratio can in a similar fashion be defined for other models such as FENE-P or the inelastic, but shear-thinning Carreau-Yasuda model \cite{carreau1972, yasuda1979}.
 For our alginate solution we obtain $R _ \eta = \num{48.2\pm0.4e3}$, indicating that the solution viscosity at very low shear rates is more than four orders of magnitude larger than the solvent viscosity which represents a severe challenge to standard numerical algorithms.
-That this characteristic is not unique to alginate, but is in fact a generic feature of cell carrier fluids used in bioprinting is shown in table~\ref{tab:bioinks} where rheological from various literature sources have been compiled into a single format to determine $ R_ \eta $.
+That this characteristic is not unique to alginate, but is in fact a generic feature of cell carrier fluids used in bioprinting is shown in table~\ref{tab:bioinks} where rheological data from various literature sources have been compiled into a single format to determine $ R_ \eta $.
 The 0.49 \% methyl cellulose solution used in RT-DC measurements, in contrast, features a much lower value of $R_\eta = \num{18.7\pm0.4}$.
-\begin{table}
+
+\begin{table}[H]
 	\centering
@@
 		\end{tabular}
-	\caption{Compilation of literature data on typical bioinks showing that a very viscosity ratio $ R_ \eta $ is a generic feature of these liquids. }
+	\caption{Compilation of literature data on typical bioinks showing that a very viscosity ratio $ R_ \eta $ is a generic feature of these liquids. 
+	\SG{ cross-check these values }
+	}
 	\label{tab:bioinks}
@@
 \SG{ and vice versa: make sure that all papers discussed here are also cited in the introduction }
-Since the early days of LBM methods for viscoelastic fluids have been developed. 
+Since the early days of LBM variants for viscoelastic fluids have been developed. 
 Keeping in mind our target geometries, we focus here on three dimensional formulations.
@@
 More advcanced approaches include the work of Onishi \textit{et al.} \cite{onishi2005, onishi2006} who considered a non-shear-thinning Oldroyd-B model using a microscopic Fokker-Planck equation for the polymer dumbbells.
-The work of \cite{malaspinas2010} and \cite{ma2020} considered in addition the FENE-P model solving the advection part of the model using a second LBM running in parallel to the Navier-Stokes LBM while \cite{wang2020} used this approach for the Oldroyd-B model.
+The work of \cite{wang2020} solved the advection part of the model using a second LBM running in parallel to the Navier-Stokes LBM.
+The same technique was used by \cite{malaspinas2010} and \cite{ma2020} for the Oldroyd-B and FENE-P models.
 Later, hybrid schemes coupling an LB solver for the solvent to a finite-difference \cite{gupta2015_2, gupta2015, gupta2016} or finite-volume \cite{kuron2021} scheme for the polymer stress (or, alternatively, the polymer conformation) tensor were introduced.
-To improve numerical stability, some authors propose the inclusion of an artificial diffusivity \SG{ cite }, which introduces a small error compared to the analytical solution of the constitutive equation.
+To improve numerical stability, some authors propose the inclusion of an artificial diffusivity \cite{malaspinas2010,ma2020,wang2020,wang2021}, which introduces a small error compared to the analytical solution of the constitutive equation.
+Other remedies include special decompositions of the stress tensor\cite{dzanic2022} or optimization of the solvent contribution\cite{gupta2015} \SG{ rephrase and give some more details }.  
 Coupling of the resulting polymer stress to the Navier-Stokes LBM can be achieved via the inclusion of point forces or via a modification of the equilibrium populations.
-A recent comparison in 2D found that the former in general leads to higher stability \cite{dzanic2022}.
+A recent comparison in 2D found that the former in general leads to better stability \cite{dzanic2022}.
 
 The stable range of Weissenberg numbers covered by existing methods is up to $ \mathrm{Wi}  \approx  10$ for the method of \cite{malaspinas2010} and up to $ \mathrm{Wi}  \approx 100$ in \cite{gupta2015,ma2020,gupta2016}.
-However, another stability criterion, which is often overlooked is the viscosity ratio $ R_ \eta $ as defined in XX. 
-Existing methods often stay at or below $R_\eta = 1$\cite{gupta2015,onishi2006,wang2020,su2013_2,gupta2015_2}, while the ones trying higher ratios report being limited below $R_\eta = 10$\cite{malaspinas2010,ma2020,kuron2021} due to stability issues.
+However, another stability criterion, which is often overlooked is the viscosity ratio $ R_ \eta $ as defined in eq.~(\ref{eq:R_eta}). 
+Existing methods often stay at or below $R_\eta = 1$ \cite{gupta2015,onishi2006,wang2020,su2013_2,gupta2015_2}, while others report being limited below $R_\eta = 10$ \cite{malaspinas2010,ma2020,kuron2021} due to stability issues.
 The details are listed in table~\ref{tab:viscRatio}.
-Comparing to the rheological data presented in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}, we conclude that existing LB methods appear to be appropriate only for relatively dilute solutions and in particular do not cover the viscosity ratio required by these technologically important cell carrier fluids.
-We therefore set out to develop a novel viscoelastic LB scheme which we will present in the next section.
+Comparing to the rheological data presented in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}, we conclude that existing LB methods appear to be appropriate only for relatively dilute solutions and in particular do not cover the viscosity ratio required by technologically important cell carrier fluids such alginate and methyl cellulose.
+We therefore set out to develop a novel viscoelastic LBM scheme which we will present in the next section.
 
@@
 The Lattice-Boltzmann method (LBM) has become a standard tool in numerical fluid mechanics \cite{Kruger_book} and we therefore describe it here only very briefly.
-We use a D3Q19 lattice in full three dimensions together with a single relaxation time collission operator.
+We use a D3Q19 lattice in full three dimensions together with a single relaxation time collision operator.
 Our implementation is based on FluidX3D which has been extensively used and validated in earlier publications \cite{Lehmann.20229da}.
@@
 Physical units are mapped to lattice units to obtain a dimensionless relaxation time of 1.
-The employed lattice dimensions vary for the different applications and are specified below. \SG{ to do }
+The employed lattice dimensions vary for the different applications and are specified below. 
 To drive the flow, we use either a constant body force (modeling a physical pressure gradient) or inflow-outflow boundaries as specified in the different application scenarios below.
-\SG{ check, specify }
 
@@
 The spatio-temporal dynamics of the polymer stress $ \ma{ \tau  }$ is given by equation~(\ref{eq:polymerStress}) in the form of an advection-reaction equation.
-We solve this equation with a finite-volume running in parallel (with identical time step) with the LBM solver.
+We solve this equation by a finite-volume scheme running in parallel (with identical time step) to the LBM solver.
 Advection is handled using the corner transport upwind scheme \cite{kuron2021}.
@@
 To include the polymer stress into the LBM, we use the stress coupling scheme according to Dzanic et al.\cite{dzanic2022_2, gupta2015, onishi2006}. 
-For this, ... \SG{ give some more details, especially since we do SRT }.
+For this, ... \SG{ do we really do stress coupling? Above it said that force coupling is better? }
+\SG{ give some more details, especially since we do SRT }.
 \SG{ also include inflow/outflow BCs }
 \SG{ do you advect polymer stress or polymer conformation? }
-
-The total stress experienced by the fluid ($\ma{\sigma}$) is then \cite{onishi2006}:
-	\begin{align}
-		\ma{\sigma} &= 2\eta_\text{s}\ma{D} + \ma{\tau} 		\label{eq:totalStress}
-	\end{align}
 
@@
 While the former is handled efficiently and reliably by the LBM streaming-collision scheme, the latter enters the LB equations as an additional source term.
-The relative magnitude of the two terms is given by the viscosity ratio $R_ \eta $ as defined in equation~\ref{eq:R_eta} which for many situations is of the order of $10^2-10^4$ (see figure~\ref{fig:fit_alginate} and \ref{tab:bioinks}).
+The relative magnitude of the two terms is given by the viscosity ratio $R_ \eta $ as defined in equation~\ref{eq:R_eta} which for many situations is of the order of $10^2-10^3$ (see figures~\ref{fig:fit_alginate}, \ref{tab:bioinks} and table~\ref{tab:bioinks}).
 The key idea of our scheme is to artificially increase the LBM viscous stress while at the same time reducing the polmer stress by the same amount.
@@
 \end{align}
-containing an arbitrary parameter $0 < \alpha _ \mathrm{s} < 1$.
+containing an arbitrary parameter $\alpha _ \mathrm{s}$. \SG{ is there an allowed range for $ \alpha _ \mathrm{s}$? }
 Finally, this results in
@@
 In practice, the shuffling parameter $ \alpha _ \mathrm{s}$ is chosen before the start of the simulation.
-The LBM solver is run with $\eta_\text{s} + \alpha_\text{s}\eta_\text{p}$ as its viscosity while from the polymer stress determined by equation~\ref{eq:polymerStress} the amount $\alpha_\text{s}\eta_\text{p} \ma{D}$ is subtracted at every time step before it is coupled into the LBM.
+The LBM solver is run with $\eta_\text{s} + \alpha_\text{s}\eta_\text{p}$ as its viscosity.
+The polymer stress determined by equation~\ref{eq:polymerStress} is reduced by the amount $\alpha_\text{s}\eta_\text{p} \ma{D}$ at every time step before it is coupled into the LBM.
 
 Using this procedure, we balance the stress contributions of the LB and the polymer components which vastly improves numerical stability.
-We emphasize that, in contrast to other remedies such as adding artificial diffusivity \SG{ refs }, our viscosity shuffling algorithm is mathematically exact and does not affect the physics of the simulated system.
-\SG{ re-include effective $R_ \eta $? }
+We emphasize that, in contrast to other remedies such as adding artificial diffusivity \cite{malaspinas2010,ma2020,wang2020,wang2021}, our viscosity shuffling algorithm is mathematically exact and does not affect the physics of the simulated system.
 %	In terms of stability, we could define an effective $R_\eta$, calculated from the stress contributions as follows.
@@
 
-To validate our viscosity shuffling algorithm and to assess its accuracy, we compare the velocity fields to semi-analytical solutions in plane and cylindrical Poiseuille flow.
-For the PTT model given in equation~(\ref{eq:polymerStress}) with an additional solvent stress contribution as in equation~(\ref{eq:totalStress}) a full analytical solution is not known for the considered geometries.
-Based on the work of \cite{oliveira1999} we derive a semi-analytical solution in Appendix~\ref{app:PTT}.
+To validate our viscosity shuffling algorithm and to assess its accuracy, we compare simulated velocity fields to semi-analytical solutions in planar and cylindrical Poiseuille flow.
+For the PTT model given in equation~(\ref{eq:polymerStress}) with an additional solvent stress contribution as in equation~(\ref{eq:totalStress}) a full analytical solution is not known for planar or cylindrical Poiseuille flow.
+Based on the work of \cite{oliveira1999} we can nevertheless derive a semi-analytical solution in appendix~\ref{app:semianalyticalPoiseuille} which will serve to validate our numerical algorithm.
+A validation in simple shear flow can be found in appendix~\ref{sec:shearFlow}.
 
@@
 After \SG{ XX } LBM time steps corresponding to \SG{ XX } of physical time, the simulation is stopped and the flow field $u(y)$ is compared to the semi-analytical solution.
-As shown in figure~\ref{fig:2DAlginateU}, very good agreement is found.
+As shown in figure~\ref{fig:2Dvel}, very good agreement is found.
 For a quantitative assessment, we compute the L2 error as \SG{ give correct equn. }
 
-The spatially resolved errors are shown in figure~\ref{fig:2DAlginateErr} in the appendix.
-Averaging over the channel diameter, we obtain an L2 error of \num{9e-4} and \SG{ XX } for alginate and methyl cellulose, respectively..
+The spatially resolved errors are shown in figure~\ref{fig:2DvelErr} in the appendix.
+Averaging over the channel diameter, we obtain an L2 error of \num{9e-4} and \SG{ XX } for alginate and methyl cellulose, respectively.
+These conclusions remain robust even when varying the pressure gradient, and thus the flow velocity, over many orders of magnitude as shown in figure~\ref{fig:pressureErr}~(a) of the appendix.
 
@@
 		\caption{(a) Velocity profile of alginate in planar channel flow. \SG{use $y$ instead of $r$ in 2D}. 
-		The time evolution of the center-line velocity when starting from a pre-stretched configuration (see main text) is shown in the inset.
+		The time evolution of the center-line velocity is shown in the inset \SG{ to do }.
 		(b) Velocity profile for methyl cellulose.
-		\SG{ make these plots for different $ \alpha _ \mathrm{s}$, either include or put into Si }}
-		\label{fig:2DAlginateU}
+		\SG{ make these plots for different $ \alpha _ \mathrm{s}$, either include here or put into appendix }}
+		\label{fig:2Dvel}
 	\end{figure}
 
-We now proceed to evaluate the viscosity shuffling method for a cylindrical pipe flow.
+We proceed to evaluate the viscosity shuffling method for a cylindrical Poiseuille flow.
 The semi-analytical solution for this situation can be derived in a similar fashion as for the planar case and is given in appendix ~\ref{app:semianalyticalPoiseuille}.
-Numerically, the cylindrical sitation is slightly more complex due to discretization errors (''staircase effect'') when mapping the rounded channel walls onto the rectilinear LBM grid \cite{Lehmann.20229da}.
-We use the same material parameter set as above, but double the pressure gradient to \SG{ XX }. \SG{ why? }
+Numerically, the cylindrical situation is slightly more complex due to discretization errors (''staircase effect'') when mapping the rounded channel walls onto the rectilinear LBM grid \cite{Lehmann.20229da}.
+We use the same material parameters as above, but double the pressure gradient to \SG{ XX }. \SG{ why? }
 The channel has a diameter of \SG{ XX } and is discretized with 41 lattice points.
 Again, we initialize the polymers in the unstretched state for methyl cellulose and in the stretched state for alginate.
-The resulting velocity profile can be seen in figure \ref{fig:3DAlginateU} and shows almost equally good agreement as for the planar case with an L2 error of \num{0.014}.
-The spatially resolved error shows that this larger average is indeed mainly attributable to the staircase effect as the error near the walls increases significantly.
-These conclusions remain robust even when varying the pressure gradient, and thus the flow velocity, over many orders of magnitude as shown in figure~\ref{fig:2DParameterStudyErr} of the appendix.
+The resulting velocity profile can be seen in figure~\ref{fig:3Dvel} and shows almost equally good agreement as for the planar case with an L2 error of \num{0.014} and \SG{ XX }, respectively.
+The spatially resolved error in figure~\ref{fig:3DvelErr} of the appendix shows that this larger average is indeed mainly attributable to the staircase effect as the error near the walls increases significantly.
+The robustness against pressure gradient changes is shown in figure~\ref{fig:pressureErr}~(b) of the appendix.
 
@@
 				\SG{ make these plots for different $ \alpha _ \mathrm{s}$, either include or put into Si }}
-		\label{fig:3DAlginateU}
+		\label{fig:3Dvel}
 	\end{figure}
@@
 %Malaspinas: We use richard/master fe0fc04115b9b6ea6628bcc6cb6593d3f72ac0ea (2023-11-05)
-Finally, we compare the quality of our algorithm by comparing to an existing study on viscoelastic LBM by Malapsinas \textit{et al.} \cite{malaspinas2010}.
+Finally, we assess the quality of our algorithm by comparing to an existing study on viscoelastic LBM by Malapsinas \textit{et al.} \cite{malaspinas2010}.
 The authors studied an Oldroyd-B fluid in a planar Poiseuille flow and compared the error in the simulated velocity profile to an exact analytical solution.
@@
 		\caption{L2 error as defined in equation \ref{eq:l2error} from Malaspinas et al.\cite{malaspinas2010} (dots) compared to our algorithm (x) as a function of grid resolution.
-		Blue and green crosses are not visible as they overlap exactly with the orange and red crosses, respectively, showing that the accuracy of our method is.
-independent of $ \mathrm{Wi}$ in the studied parameter range.}
+		Blue and green crosses are not visible as they overlap exactly with the orange and red crosses, respectively, showing that the accuracy of our method is independent of $ \mathrm{Wi}$ in the studied parameter range.}
 		\label{fig:malaspinas2010}
@@
 \end{align}
-It can be seen that the highest stresses aries at the nozzle exit in direct vicinity to the wall.
+It can be seen that the highest stresses arise at the nozzle exit in direct vicinity to the wall.
 This means that even for fast flows,  cells flowing close to the center experience less stress than cells flowing near the walls in agreement with earlier results in Newtonian fluids \cite{Mueller.2023}.
@@
 For simplicity, we consider the viscoelastic fluid inside and outside of the cell to be identical.
-The cell is initially spherical with a radius of \SI{6}{\micro\meter} and possesses Youngs Modulus of \SI{100}{\pascal} and a Poisson ratio of \SG{ XX }.
+The cell is initially spherical with a radius of \SI{6}{\micro\meter} and possesses a Youngs modulus of \SI{100}{\pascal} and a Poisson ratio of \SG{ XX }.
 It is placed into a shear flow with a shear rate of \SI{400}{\per\second} where the cell quickly reaches a steady state in which it deforms into a tank-treading ellipsoid.
+This is in qualitative agreement with simulations \cite{Mueller.2021} and classical theories \cite{Roscoe.1967}.
 For the discretization of the cell we use \SG{ xx } tetrahedrons and a radius of \SG{ xx } lattice units.
-The lattice with a resolution of \num{100} lattice points is chosen significantly bigger than the cell to assure negligible impact of the walls. 
+The lattice with a resolution of \num{100} lattice points is chosen significantly larger than the cell to assure negligible impact of the walls. 
 The lattice is periodic in $x$ and $z$ direction.
@@
 
-In the von Mises stress seen in figure \ref{fig:cellInShear_vM} the effect of the cell is clearly visible. 
+In the von Mises stress shown in figure \ref{fig:cellInShear_vM} the effect of the cell is clearly visible. 
 We observe four distinct regions of high stress radiating outwards from the cell body.
 These are particularly pronounced along the longest axis of the deformed cell. 
-\SG{ connect to the ''viscoelastic wings'' paper }
+\SG{ connect to the ''viscoelastic wings'' paper \cite{Zhang.2020}}
 
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/cellInShear_sigma_vM.eps}
-		\caption{The von Mises stress around a cell in shear flow.}
+		\caption{The von Mises stress around a cell in viscoelastic shear flow.}
 		\label{fig:cellInShear_vM}
@@
 Importantly, the outcome of the viscostiy shuffling simulations is independent of the shuffling parameter $ \alpha _ \mathrm{s}$.
-We finally demonstrated the usability of our approach in realistic geometries such as those constricting microchannels and conical bioprinting nozzles.
+We finally demonstrated the usability of our approach in realistic geometries such as constricting microchannels and conical bioprinting nozzles.
 
@@
 \section{Rheology measurements of alginate solutions}
+\label{app:experiment}
 
@@
 The shuffling is fixed at $ \alpha _ \mathrm{s} = 1$ and the viscosity as function of shear rate is computed by dividing the total fluid stress at the center of the box by the shear rate.
-Figure~\ref{fig:wiParameterStudy}~(a) shows that our simulations are in very good agreement with the semi-analytical solution as calculated in \SG{ XX } with a maximum error of \num{2e-11}.
+Figure~\ref{fig:wiParameterStudy}~(a) shows that our simulations are in very good agreement with the semi-analytical solution with a maximum error of \num{2e-11}.
 Importantly, we show in figure~\ref{fig:wiParameterStudy}~(b) that this very good agreement is independent of the shuffling parameter $ \alpha _ \mathrm{s}$.
@@
 		\caption{(a) The local viscosity determined by a shear flow simulation is in very good agreement with the semi-analytical theory.
-		(b) The error is negligibly small independent of the shuffling parameter $ \alpha _ \mathrm{s}$.}
+		(b) The error is negligibly small and independent of the shuffling parameter $ \alpha _ \mathrm{s}$.
+		\SG{ plot over shear rate instead of $ \mathrm{Wi}$. Fix units of $ \eta $. }}
 		\label{fig:wiParameterStudy}
@@
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/2DParameterStudyErr.eps}
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/3DParameterStudyErr.eps}
-		\caption{Average error of the velocity for a planar (a) and a cylindrical (b) Poiseuille flow  of methyl cellulose at different pressure gradients. 
-		All other parameters are as in figure~\ref{fig:2DAlginateU}~(b) of the main text.
-		The peak in the error profile appears when the average shear rate across the channel corresponds to the maximum slope in the viscosity profile of figure~\ref{fig:wiParameterStudy}. }
-		\label{fig:2DParameterStudyErr}
-	\end{figure}
-
-	\begin{figure}[H]
-		\centering
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/2DAlginateErr.eps}
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/2DParameterStudyErrWorst.eps}
-		\caption{(a) L2 error of the velocity profile in \ref{fig:2DAlginateU} with respect to the semi-analytical theory in a planar Poiseuille flow.  
-			The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall. 
-		(b) For methyl cellulose.}
-		\label{fig:2DAlginateErr}
+		\caption{L2 error of the velocity profile in figure~\ref{fig:2Dvel} with respect to the semi-analytical theory in a planar Poiseuille flow for alginate (a) and methyl cellulose (b).  
+			The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall. }
+		\label{fig:2DvelErr}
 	\end{figure}
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/3DParameterStudyErrWorst.eps}
-		\caption{(a) L2 error of the velocity profile in \ref{fig:2DAlginateU} with respect to the semi-analytical theory in a cylindrical Poiseuille flow.  
-			The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall. 
-		(b) For methyl cellulose.
-		\SG{ The error seems to reverse. For 2D alginate has the larger error, for cylinder MC has the larger error. Do we have an explanation why? }}
-		\label{fig:3DAlginateErr}
+		\caption{L2 error of the velocity profile in \ref{fig:3Dvel} with respect to the semi-analytical theory in a cylindrical Poiseuille flow for alginate (a) and methyl cellulose (b).
+			The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall. }
+		\label{fig:3DvelErr}
+	\end{figure}
+
+		\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/2DParameterStudyErr.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/3DParameterStudyErr.eps}
+		\caption{Average error of the velocity for a planar (a) and a cylindrical (b) Poiseuille flow  of methyl cellulose at different pressure gradients. 
+		The peak in the error profile appears when the average shear rate across the channel corresponds to the maximum slope in the viscosity profile of figure~\ref{fig:wiParameterStudy}. }
+		\label{fig:pressureErr}
 	\end{figure}

### 2024-02-13 assets/python/fluidx3d/eval/models/PTT.py
simplify condition

@@ -81,10 +81,7 @@ class PTT:
         def getInterpol(offset=0):
             def interpol(r):  # Can only handle scalar r
                 idx = np.argmin(np.abs(rVelocity - r))
-                if idx == 0:
-                    m = (velocity[idx + 1] - velocity[idx]) / (rVelocity[idx + 1] - rVelocity[idx])
-                    return velocity[idx] + m * (r - rVelocity[idx]) - offset
-                if rVelocity[idx] > r:
+                if rVelocity[idx] > r and idx != 0:
                     idx -= 1
                 elif rVelocity[idx] == r:
                     return velocity[idx] - offset

### 2024-02-13 assets/python/fluidx3d/eval/models/CY.py
CY profile

@@ -11,7 +11,7 @@ Created on Wed Feb  7 14:25:38 2024
 import matplotlib.pyplot as plt
 import numpy as np
 from scipy.integrate import cumulative_trapezoid, trapezoid
-from scipy.special import lambertw
+from scipy.optimize import root_scalar  # type: ignore
 
 from fluidx3d.eval.style import cm
 
@@ -27,39 +27,36 @@ class CY:
         self.a1 = a1
         self.a2 = a2
 
-    def prepareVelocityProfile(self, R, G, j):  # TODO
-        c = 2**j * self.eta_s / (-G)
-        d = 2 * np.sqrt(self.epsilon) * self.lambda_p
+    def prepareVelocityProfile(self, R, G, j):  # TODO check j
+        stepSize = 1e-6
 
-        guesses = np.arange(0, R / c * (1 + 1e-6), R / c * 1e-6)
+        def stressBalance(gd):
+            return self.eta(gd) * gd + G / 2**j * R
 
-        def r(gd):
-            return c * gd - self.eta_p / self.eta_s * c / d * np.sqrt(lambertw(d**2 * gd**2).real)
+        sol = root_scalar(
+            stressBalance,
+            method="toms748",
+            bracket=[-G / 2**j * R / self.eta_s, -G / 2**j * R / self.eta_p],
+        )
 
-        rguesses = r(guesses)
-        idx = np.argmin(np.abs(rguesses - R))
-        if rguesses[idx] < R:
-            idx += 1
+        if not sol.converged:
+            print(f"{sol=}")
+            raise Exception("Could not find alpha2")
 
-        guessesFine = np.arange(
-            0, guesses[idx] * (1 + 3e-6), guesses[idx] * 1e-6
-        )  # The three is due tue offsets needing it
-        rguessesFine = r(guessesFine)
+        edgeGD = sol.root
 
-        rVelocity = 0.5 * (rguessesFine[:-1] + rguessesFine[1:])
-        velocity = cumulative_trapezoid(guessesFine, rguessesFine)
+        gds = np.arange(0, 1 + stepSize, stepSize) * edgeGD
+        rs = -2 / G * self.eta(gds) * gds
 
         def getInterpolGD():
             def interpol(r):  # Can only handle scalar r
-                idx = np.argmin(np.abs(rguessesFine - r))
-                if rguessesFine[idx] > r:
+                idx = np.argmin(np.abs(rs - r))
[…]

### 2024-02-15 NovelLBM.tex
typos grammar consistency minor points

@@
 
-\newcommand{\RK}[1]{{\color{orange}RK: #1}}
+\newcommand{\RK}[1]{{\color{cyan}RK: #1}}
 \newcommand{\SG}[1]{{\color{red}SG: #1}}
@@
 
-%\def\dark{}
+\def\dark{}
 
@@
 The simulation of viscoelastic liquids using the Lattice-Boltzmann method in full three dimensions remains a formidable numerical challenge.
-In particular the simulation of strongly shear-thinnig fluids, where the ratio between the high-shear and low-shear viscosities is large, is often prevented by stability problems.
+In particular the simulation of strongly shear-thinning fluids, where the ratio between the high-shear and low-shear viscosities is large, is often prevented by stability problems.
 Here we present a novel approach to overcome these issues.
@@
 To compensate for this additional viscous stress, we reduce the polymer stress by the same amount.
-We apply this novel method to simulate two realistic cell carrier fluids, methyl cellulose and alginate solutions, of which the latter exhibits a viscosity ratio exceeding 10,000.
+We apply this novel method to simulate two realistic cell carrier fluids, methyl cellulose and alginate solutions, of which the latter exhibits a viscosity ratio exceeding \num{10000}.
 
@@
 
-Microfluidic technoglogies involving living cells are becoming increasingly popular. 
+Microfluidic technologies involving living cells are becoming increasingly popular.
 Examples include medical diagnostics, where the pathological alteration of cell properties can serve as a marker for disease detection \cite{Toepfner.2018} or biofabrication where living cells are printed to create artificial tissues \cite{possl2021, Poologasundarampillai.2021, oconnell2022}.
@@
 In medical diagnostics, the viscous stress must be large enough to achieve detectable cell deformation, while in biofabrication the printed construct must be stable enough to retain its shape after the printing process.
-To satisfy the latter requirement, cell carriers used in biofabrication („bioinks“) typically exhibit a very high viscosity ratio with the zero-shear viscosity being many orders of magnitude larger than the pure solvent viscosity \cite{paxton2017}.
+To satisfy the latter requirement, cell carriers used in biofabrication ("bioinks") typically exhibit a very high viscosity ratio with the zero-shear viscosity being many orders of magnitude larger than the pure solvent viscosity \cite{paxton2017}.
 
@@
 A very popular simulation technique for Newtonian fluids is the Lattice Boltzmann method \cite{Kruger_book} due to its simplicity and high parallelizability.
-LBM has also been extended to viscoelastic situations, mainly in two \cite{ispolatov2002,wang2019,su2013,giraud1998,xie2018,dzanic2022,frank2006,zou2014,lee2017,dzanic2022_2,sedaghat2021,frantziskonis2011,qin2023,yoshino2008,papenkort2015,phillips2011,onishi2005} but occassionally also in three \cite{malaspinas2010,gupta2015,lallemand2003,ma2020,onishi2006,wang2020,dellar2014,su2013_2,wang2021,kuron2021,gupta2016} dimensions.
+LBM has also been extended to viscoelastic situations, mainly in two \cite{ispolatov2002,wang2019,su2013,giraud1998,xie2018,dzanic2022,frank2006,zou2014,lee2017,dzanic2022_2,sedaghat2021,frantziskonis2011,qin2023,yoshino2008,papenkort2015,phillips2011,onishi2005} but occasionally also in three \cite{malaspinas2010,gupta2015,lallemand2003,ma2020,onishi2006,wang2020,dellar2014,su2013_2,wang2021,kuron2021,gupta2016} dimensions.
 To alleviate stability problems, some of these works include an artificial diffusivity of the polymer stress \cite{malaspinas2010,ma2020,wang2020,wang2021}.
-Other remedies include special decompositions of the stress tensor\cite{dzanic2022} or optimization of the solvent contribution\cite{gupta2015} \SG{ what is this? }.  
+Other remedies include special decompositions of the stress tensor \cite{dzanic2022} or optimization of the solvent contribution \cite{gupta2015} \SG{ what is this?
+}\RK{Gupta is not specific in what he does but states to "optimize" $\eta_\text{s}$.
+I suspect an artificial increase but do not know}.\todo{reread gupta}
 Despite these improvements, however, none of these methods has been applied to very high viscosity ratio fluids which are often used as cell carrier fluids in lab experiments or technological applications.
@@
 To fill this gap, here we develop a new variant of viscoelastic LBM which allows the stable and accurate simulation of very high viscosity ratio fluids.
-Our technique is based on the insight that stability issues in tradtional viscoelastic LBMs arise dure to an unbalance between the very large polymer stress and the much smaller viscous stress of the solvent.
-We overcome this issue by including („shuffling“) part of the polymer stress into the viscous part of the LBM algorithm.
+Our technique is based on the insight that stability issues in traditional viscoelastic LBMs arise due to an imbalance between the very large polymer stress and the much smaller viscous stress of the solvent.
+We overcome this issue by including ("shuffling") part of the polymer stress into the viscous part of the LBM algorithm.\RK{moving instead of including?}
 
@@
 The first is an alginate solution which is often used in biofabrication but can also serve as a common food additive.
-Our solution contains 4\% alginate solvated in PBS and was measured in a commerical plate-plate rheometer (see appendix  \ref{app:experiment} for experimental details).
-The shear-dependent viscosity $ \eta$ and the first normal stress difference $N_1$ are shown as function of shear rate in figure~\ref{fig:fit_alginate}.
-We note the very high zero-shear viscosity of more than $10000 \si{ mPa \cdot s}$.
-Bioinks in biofabrication are characterized in general by such high viscosities to guarantee stability of the printed construct.
+Our solution contains \SI{4}{\percent} alginate dissolved in PBS and was measured in a commercial plate-plate rheometer (see appendix~\ref{app:experiment} for experimental details).
+The shear-dependent viscosity $\eta$ and the first normal stress difference $N_1$ are shown as function of shear rate in figure~\ref{fig:fit_alginate}.
+We note the very high zero-shear viscosity of more than \SI{10000}{\milli\pascal\second}.
+Bioinks in biofabrication are in general characterized by such high viscosities to guarantee stability of the printed construct.
 At the same time, during the actual printing process when the material is flowing, the viscosity should be as low as possible to avoid excessive mechanical stress on the embedded cells.
@@
 		\label{fig:fit_alginate}
-	\end{figure}
+	\end{figure}\todo{larger fonts in all figures}
 
@@
 We extract our data from \cite{buyukurganci2023} where the shear rheology of methyl cellulose was measured using a plate-plate and cone-plate rheometer.
-Three concentrations of \SI{0.49}{\percent}, \SI{0.59}{\percent} and \SI{0.83}{\percent} methyl cellulose in PBS were investigated and their rheology is shown in figure~\ref{fig:fit_mc}.
+Three concentrations of \SI{0.49}{\percent}, \SI{0.59}{\percent} and \SI{0.83}{\percent} methyl cellulose in PBS were investigated, and their rheology is shown in figure~\ref{fig:fit_mc}.
 Even at the highest concentration the zero-shear viscosity is two orders of magnitude lower than for the considered alginate solution.
@@
 		\caption{Rheology data of a methyl cellulose solution from \cite{buyukurganci2023}.
-				Orange lines show a fit of the PTT rheological model. \SG{ include legend into figure. Maybe give color coding only in caption? }\SG{ larger font in figures }}
+				Orange lines show a fit of the PTT rheological model.
+\SG{ include legend into figure.
+Maybe give color coding only in caption?
+}\RK{meaning ony one legend for both plots?}\SG{ larger font in figures }}
 		\label{fig:fit_mc}
@@
 %Although the FENE-P does reproduce shear-thinning, we were not able to obtain a satisfactory fit to our data for alginate and methyl cellulose with physically reasonable values of the model parameters.
-A good fit to our data was obtained with the so-called PTT model due to Phan-Thien and Tanner \cite{phan-thien1977,phan-thien1978} which has been developed explicitly for polymer networks in solution and thus appears to capture well the essential physics behind the alginate and methyl cellulose solutions.
+A good fit to our data was obtained with the so-called PTT model due to Phan-Thien and Tanner \cite{phan-thien1977,phan-thien1978} which has been developed explicitly for polymer networks in solution and thus appears to capture well the essential physics behind the alginate and methyl cellulose solutions.\RK{due to sounds bad}
 
-The PTT model is specified by a differential equation for the polymer stress $ \ma{\tau}$:
+The PTT model is specified by a differential equation for the polymer stress $\ma{\tau}$:
 	\begin{equation}
@@
 The polymer viscosity is denoted $\eta_\text{p}$ and $\lambda$ is the corresponding relaxation time.
-$\epsilon$ is the so-called extensibility parameter which controls at which shear rates thinning takes place and $\xi$ describes the slip in the polymer network which we will set to zero in the following.
-The upper convected derivative of an arbitrary tensor $ \ma{ A }$ is defined as follows:
+$\epsilon$ is the so-called extensibility parameter which controls at what shear rates thinning takes place and $\xi$ describes the slip in the polymer network which we will set to zero in the following.
+The upper convected derivative of an arbitrary tensor $\ma{A}$ is defined as follows:
 	\begin{equation}
-		\overset{\nabla}{\ma{A}} = \frac{\Dif\ma{A}}{\Dif t} - \left(\left(\nabla\vec{u}\right)^\text{T}\cdot\ma{A} + \ma{A}\cdot\left(\nabla\vec{u}\right)\right)
+		\overset{\nabla}{\ma{A}} = \frac{\Dif\ma{A}}{\Dif t} - \left(\left(\nabla\vec{u}\right)^\mathrm{T}\cdot\ma{A} + \ma{A}\cdot\left(\nabla\vec{u}\right)\right)
 	\end{equation}
@@
 	\end{equation}
-Finally, the total fluid stress $\ma{\sigma}$ is the sum of the polymer stress $ \tau $ and a solvent stress due to the Newtonian solvent with viscosity $ \eta _ \mathrm{s}$:
+Finally, the total fluid stress $\ma{\sigma}$ is the sum of the polymer stress $\ma{\tau}$ and a solvent stress due to the Newtonian solvent with viscosity $\eta_\text{s}$:
 	\begin{align}
@@
 
-For a simple shear flow in the $xy$-plane of a PTT fluid with $ \xi =0$, an analytical expression for $ \eta $ and $N_1$ can be derived as detailed in appendix \ref{app:semianalyticalPoiseuille}:
+For a simple shear flow in the $xy$-plane of a PTT fluid with $ \xi =0$, an analytical expression for $ \eta $ and $N_1$ can be derived as detailed in appendix~\ref{app:semianalyticalPoiseuille}:
 	\begin{equation}
-		\eta\left(\dot{\gamma}\right) = \frac{\eta_\text{p}}{\exp\left[0.5W_0\left(4\epsilon \mathrm{Wi}^2\right)\right]} + \eta _\mathrm{s} \label{eq:shearEta}
+		\eta\left(\dot{\gamma}\right) = \frac{\eta_\text{p}}{\exp\left[0.5W_0\left(4\epsilon \mathrm{Wi}^2\right)\right]} + \eta_\text{s} \label{eq:shearEta}
 	\end{equation}
@@
 	\end{equation}
-where $ \mathrm{Wi} = \lambda \dot{ \gamma  }$ is the Weissenberg number and $W_0$ is the Lambert $W$-function. \SG{ check that $ \eta _ \mathrm{s}$ is correct }
-Fitting these equations to the rheological data for alginate and methy cellulose leads to satisfactory agreement as shown in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}.
-In the fit, the solvent viscosity was fixed at $ \eta _ \mathrm{s} = 1 \si{ mPa } \cdot \si{ s }$ as the viscosity of the PBS buffer. \SG{ give ref }
+where $\mathrm{Wi} = \lambda\dot{\gamma}$ is the Weissenberg number and $W_0$ is the Lambert $W$-function. \SG{ check that $ \eta _ \mathrm{s}$ is correct }\RK{what do you mean by correct?}
+Fitting these equations to the rheological data for alginate and methyl cellulose leads to satisfactory agreement as shown in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}.
+In the fit, the solvent viscosity was fixed at $\eta_\text{s} = \SI{1}{\milli\pascal\second}$ as the viscosity of the PBS buffer. \SG{ give ref }\todo{made it up}
 %At very high shear rates, the contained polymers are completely stretched and the viscosity asymptotically approaches the solvent value $ \eta _ \mathrm{s}$.
@@
 		\begin{tabular}{c|c|c|c}
-%			Concentration/\unit{\percent} & $\eta_\text{p}/\unit{\milli\pascal\second}$ & $\lambda/\unit{\milli\second}$ & $\epsilon$ \\
-			Fluid & $\eta_\text{p}/mPas$ & $\lambda/ms$ & $\epsilon$ \\
+			Fluid & $\eta_\text{p}/\unit{\milli\pascal\second}$ & $\lambda/\unit{\milli\second}$ & $\epsilon$ \\
 			\hline
-			alginate \num{4} & \num{48,200\pm0.4} & \num{343 \pm 0.004}. & \num{0.545 \pm 0.010}\\
+			alginate \num{4} & \num{48.2\pm0.4e3} & \num{343 \pm 4} & \num{0.545 \pm 0.010} \\
 			methyl c. \num{0.49} & \num{18.7\pm0.4} & \num{0.344\pm0.003} & \num{0.270\pm0.003} \\
@@
 		\caption{Parameters of the PTT model obtained by fitting to the rheological measurements in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}.
-		\SG{ add a column with $R_ \eta $ }}
+		\SG{ add a column with $R_ \eta $ }}\RK{would be identical to the content of the $\eta_p$ column, also would be used before introduced}
 		\label{tab:PTTparameters}
-	\end{table}
+	\end{table}\todo{names are fucked}
 
-We introduce the ratio between the zero-shear and the infinite-shear (i.e.\ solvent) viscosity as 
+We introduce the ratio between the zero-shear and the infinite-shear (i.e.\ solvent) viscosity as\todo{nope $\eta_p$ is not zero shear viscosity!}
 \begin{align}
-	R_ \eta  = \frac{ \eta _ \mathrm{p} } { \eta _ \mathrm{s} }		\label{eq:R_eta}
+	R_\eta = \frac{\eta_\text{p}}{\eta_\text{s}}		\label{eq:R_eta}
 \end{align}
 which will turn out to be an important parameter to determine numerical stability of LB simulations.
-\SG{ wo don't actually show that $R_ \eta  $ determines stability? }
-This ratio can in a similar fashion be defined for other models such as FENE-P or the inelastic, but shear-thinning Carreau-Yasuda model \cite{carreau1972, yasuda1979}.
-For our alginate solution we obtain $R _ \eta = \num{48.2\pm0.4e3}$, indicating that the solution viscosity at very low shear rates is more than four orders of magnitude larger than the solvent viscosity which represents a severe challenge to standard numerical algorithms.
-That this characteristic is not unique to alginate, but is in fact a generic feature of cell carrier fluids used in bioprinting is shown in table~\ref{tab:bioinks} where rheological data from various literature sources have been compiled into a single format to determine $ R_ \eta $.
-The 0.49 \% methyl cellulose solution used in RT-DC measurements, in contrast, features a much lower value of $R_\eta = \num{18.7\pm0.4}$.
+\SG{ wo don't actually show that $R_ \eta  $ determines stability? }\RK{we do not. We could do a plot with $alpha_s$ decreasing until the sim breaks if you want}
+This ratio can similarly be defined for other models such as FENE-P or the inelastic, but shear-thinning Carreau-Yasuda model \cite{carreau1972, yasuda1979}.
+For our alginate solution we obtain $R_\eta = \num{48.2\pm0.4e3}$, indicating that the solution viscosity at very low shear rates is more than four orders of magnitude larger than the solvent viscosity which represents a severe challenge to standard numerical algorithms.
+That this characteristic is not unique to alginate, but is in fact a generic feature of cell carrier fluids used in bioprinting is shown in table~\ref{tab:bioinks} where rheological data from various literature sources have been compiled into a single format to determine $R_\eta$.
+The \SI{0.49}{\percent} methyl cellulose solution used in RT-DC measurements, in contrast, features a much lower value of $R_\eta = \num{18.7\pm0.4}$.
 
@@
 		\begin{tabular}{l|p{3cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{2cm}}
-%			Author & Material & $\eta_0/\unit{\pascal\second}$ & $\eta_\infty/\unit{\pascal\second}$ & $R_\eta$ & extracted from \\
-			Author & Material & $\eta_0/Pas$ & $\eta_\infty/Pas$ & $R_\eta$ & extracted from \\
+			Author & Material & $\eta_0/\unit{\pascal\second}$ & $\eta_\infty/\unit{\pascal\second}$ & $R_\eta$ & extracted from \\
 			\hline
@@
 	\caption{Compilation of literature data on typical bioinks showing that a very viscosity ratio $ R_ \eta $ is a generic feature of these liquids.
-	\SG{ cross-check these values }
+	\SG{ cross-check these values }\RK{as in with other literature?}
 	}
@@
 \end{table}
+\RK{While $\eta_0/\eta_\infty$ would have been sensible for $R_\eta$ definition, i used $(\eta_0-\eta_\infty)/\eta_\infty$ instead.
+This plays nicer with our models and does not make a difference, but the notation above is now inconsistent since del of CY}
 
@@
 \SG{ and vice versa: make sure that all papers discussed here are also cited in the introduction }
-Since the early days of LBM variants for viscoelastic fluids have been developed. 
-Keeping in mind our target geometries, we focus here on three dimensional formulations.
+Since the early days of LBM, variants for viscoelastic fluids have been developed.
+Keeping in mind our target geometries, we focus here on three-dimensional formulations.
 The first approaches avoided an explicit modeling of a viscoelastic constitutive equation and simply modified the LB collision operator to obtain a fluid obeying Jeffery's viscoelastic model \cite{lallemand2003}.
@@
 }
-More advcanced approaches include the work of Onishi \textit{et al.} \cite{onishi2005, onishi2006} who considered a non-shear-thinning Oldroyd-B model using a microscopic Fokker-Planck equation for the polymer dumbbells.
+More advanced approaches include the work of Onishi \textit{et al.} \cite{onishi2005, onishi2006} who considered a non-shear-thinning Oldroyd-B model using a microscopic Fokker-Planck equation for the polymer dumbbells.
 The work of \cite{wang2020} solved the advection part of the model using a second LBM running in parallel to the Navier-Stokes LBM.
@@
 Coupling of the resulting polymer stress to the Navier-Stokes LBM can be achieved via the inclusion of point forces or via a modification of the equilibrium populations.
-A recent comparison in 2D found that the former in general leads to better stability \cite{dzanic2022}.
+A recent comparison in 2D found that the former in general leads to better stability \cite{dzanic2022}.\todo{check}
 
-The stable range of Weissenberg numbers covered by existing methods is up to $ \mathrm{Wi}  \approx  10$ for the method of \cite{malaspinas2010} and up to $ \mathrm{Wi}  \approx 100$ in \cite{gupta2015,ma2020,gupta2016}.
-However, another stability criterion, which is often overlooked is the viscosity ratio $ R_ \eta $ as defined in eq.~(\ref{eq:R_eta}). 
-Existing methods often stay at or below $R_\eta = 1$ \cite{gupta2015,onishi2006,wang2020,su2013_2,gupta2015_2}, while others report being limited below $R_\eta = 10$ \cite{malaspinas2010,ma2020,kuron2021} due to stability issues.
+The stable range of Weissenberg numbers covered by existing methods is up to $\mathrm{Wi}\approx\num{10}$ for the method of \cite{malaspinas2010} and up to $\mathrm{Wi}\approx\num{100}$ in \cite{gupta2015,ma2020,gupta2016}.
+However, another stability criterion, which is often overlooked is the viscosity ratio $R_\eta$ as defined in eq.~(\ref{eq:R_eta}).
+Existing methods often stay at or below $R_\eta = \num{1}$ \cite{gupta2015,onishi2006,wang2020,su2013_2,gupta2015_2}, while others report being limited below $R_\eta = \num{10}$ \cite{malaspinas2010,ma2020,kuron2021} due to stability issues.
 The details are listed in table~\ref{tab:viscRatio}.
@@
 
-\caption{Covered ranges of $ \mathrm{Wi}$ and $ R_ \eta $ for existing 3D LB methods.}
+\caption{Covered ranges of $\mathrm{Wi}$ and $R_\eta$ for existing 3D LB methods.}
 \label{tab:viscRatio}
@@
 
-The Lattice-Boltzmann method (LBM) has become a standard tool in numerical fluid mechanics \cite{Kruger_book} and we therefore describe it here only very briefly.
+The Lattice-Boltzmann method (LBM) has become a standard tool in numerical fluid mechanics \cite{Kruger_book}, and we therefore describe it here only very briefly.
 We use a D3Q19 lattice in full three dimensions together with a single relaxation time collision operator.
@@
 
-The spatio-temporal dynamics of the polymer stress $ \ma{ \tau  }$ is given by equation~(\ref{eq:polymerStress}) in the form of an advection-reaction equation.
+The spatio-temporal dynamics of the polymer stress $\ma{\tau}$ is given by equation~(\ref{eq:polymerStress}) in the form of an advection-reaction equation.
 We solve this equation by a finite-volume scheme running in parallel (with identical time step) to the LBM solver.
@@
 
-To include the polymer stress into the LBM, we use the stress coupling scheme according to Dzanic et al.\cite{dzanic2022_2, gupta2015, onishi2006}. 
-For this, ... \SG{ do we really do stress coupling? Above it said that force coupling is better? }
+To include the polymer stress into the LBM, we use the stress coupling scheme according to Dzanic et al. \cite{dzanic2022_2, gupta2015, onishi2006}.
+For this, ... \SG{ do we really do stress coupling? Above it said that force coupling is better? }\RK{yes, no idea why you said that}
 \SG{ give some more details, especially since we do SRT }.
 \SG{ also include inflow/outflow BCs }
-\SG{ do you advect polymer stress or polymer conformation? }
+\SG{ do you advect polymer stress or polymer conformation? }\RK{A}
 
@@
 
-The key difficulty for simulating many realistic viscoelastic fluids is the unbalance between the viscous stress of the solvent and the polymer stress.
+The key difficulty for simulating many realistic viscoelastic fluids is the imbalance between the viscous stress of the solvent and the polymer stress.
 While the former is handled efficiently and reliably by the LBM streaming-collision scheme, the latter enters the LB equations as an additional source term.
-The relative magnitude of the two terms is given by the viscosity ratio $R_ \eta $ as defined in equation~\ref{eq:R_eta} which for many situations is of the order of $10^2-10^3$ (see figures~\ref{fig:fit_alginate}, \ref{tab:bioinks} and table~\ref{tab:bioinks}).
-The key idea of our scheme is to artificially increase the LBM viscous stress while at the same time reducing the polmer stress by the same amount.
+The relative magnitude of the two terms is given by the viscosity ratio $R_\eta$ as defined in equation~\ref{eq:R_eta} which for many situations is of the order of $10^2-10^3$ (see figures~\ref{fig:fit_alginate}, \ref{tab:bioinks} and table~\ref{tab:bioinks}).
+The key idea of our scheme is to artificially increase the LBM viscous stress while at the same time reducing the polymer stress by the same amount.
 Starting from equation~\ref{eq:totalStress}, we write
 \begin{align}
-	\ma{\sigma} &= 2\eta_\text{s}\ma{D} + \ma{\tau}_\text{shuffle} + \ma{\tau} - \ma{\tau}_\text{shuffle}	 \label{eq:shuffleStress}
+	\ma{\sigma} = 2\eta_\text{s}\ma{D} + \ma{\tau}_\text{shuffle} + \ma{\tau} - \ma{\tau}_\text{shuffle}	\label{eq:shuffleStress}
 \end{align}
-with the transfered (''shuffled'') stress
+with the transferred ("shuffled") stress
 \begin{align}
-	\ma{ \tau }_ \mathrm{shuffle} = 2 \alpha _ \mathrm{s} \eta _ \mathrm{p} \ma{D}
+	\ma{\tau}_\text{shuffle} = 2\alpha_\text{s}\eta_\text{p}\ma{D}
 \end{align}
-containing an arbitrary parameter $\alpha _ \mathrm{s}$. \SG{ is there an allowed range for $ \alpha _ \mathrm{s}$? }
+containing an arbitrary parameter $\alpha_\text{s}$. \SG{ is there an allowed range for $ \alpha _ \mathrm{s}$? }
 Finally, this results in
 \begin{align}
-	\ma{ \sigma } &=  2\left(\eta_\text{s} + \alpha_\text{s}\eta_\text{p}\right)\ma{D} + \left(\ma{\tau} - 2\alpha_\text{s}\eta_\text{p}\ma{D}\right).
+	\ma{\sigma} = 2\left(\eta_\text{s} + \alpha_\text{s}\eta_\text{p}\right)\ma{D} + \left(\ma{\tau} - 2\alpha_\text{s}\eta_\text{p}\ma{D}\right).
 \end{align}
-In practice, the shuffling parameter $ \alpha _ \mathrm{s}$ is chosen before the start of the simulation.
+In practice, the shuffling parameter $\alpha_\text{s}$ is chosen before the start of the simulation.
 The LBM solver is run with $\eta_\text{s} + \alpha_\text{s}\eta_\text{p}$ as its viscosity.
-The polymer stress determined by equation~\ref{eq:polymerStress} is reduced by the amount $\alpha_\text{s}\eta_\text{p} \ma{D}$ at every time step before it is coupled into the LBM.
+The polymer stress determined by equation~\ref{eq:polymerStress} is reduced by the amount $\alpha_\text{s}\eta_\text{p}\ma{D}$ at every time step before it is coupled into the LBM.
 
@@
 
-We start by simulating the alginate and 0.49\% methyl cellulose solutions with a viscosity ratio $R_ \eta = 48 \cdot 10 ^3$ and $R_ \eta = 18.7$, respectively, in 2D planar Poiseuille flow.
-In physical units the channel has a height of \SI{20}{\micro\meter} which are discretized with \SG{ XX } LBM nodes.
-For the viscosity shuffling, we set $ \alpha _ \mathrm{s} = XX$.
-Along the flow direction, the channel is periodic and the flow is driven by a pressure gradient of \SI{-1e7}{\pascal\per\meter}. \SG{ pressure for MC? }
+We start by simulating the alginate and \SI{0.49}{\percent} methyl cellulose solutions with a viscosity ratio $R_\eta = \num{48.2e3}$ and $R_\eta = \num{18.7}$, respectively, in 2D planar Poiseuille flow.
+In physical units the channel has a height of \SI{20}{\micro\meter} which are discretized with 41 \SG{ XX }\RK{pipe is 41 box is 43} LBM nodes.
+For the viscosity shuffling, we set $\alpha_\text{s} = 1$.
+Along the flow direction, the channel is periodic, and the flow is driven by a pressure gradient of \SI{-1e7}{\pascal\per\meter}. \SG{ pressure for MC? }
+\RK{
+	2D Param (MC) 12459373.981063413
+	3D Param (MC) 24918747.962126825
+	2D Alg -1e7
+	3D Alg -2e7
+}
 The velocity field is initialized with zero.
 For methyl cellulose, we simulate the full temporal evolution with the polymers starting in the unstretched configuration.
-In the case of alginate, we speed up the convergence and start from a situation in which the polymers are pre-stretched \SG{ give details }.
+In the case of alginate, we speed up the convergence and start from a situation in which the polymers are pre-stretched \SG{ give details }\RK{initialized to the semianalytical solution}.
 After \SG{ XX } LBM time steps corresponding to \SG{ XX } of physical time, the simulation is stopped and the flow field $u(y)$ is compared to the semi-analytical solution.
+\RK{
+	Alg 2e9 1.6455647956111251 ms (reveals the sim to be a scam)
+	MC 5e6 2.439024390243903 s
+}
 As shown in figure~\ref{fig:2Dvel}, very good agreement is found.
@@
 Averaging over the channel diameter, we obtain an L2 error of \num{9e-4} and \SG{ XX } for alginate and methyl cellulose, respectively.
-These conclusions remain robust even when varying the pressure gradient, and thus the flow velocity, over many orders of magnitude as shown in figure~\ref{fig:pressureErr}~(a) of the appendix.
+These conclusions remain robust even when varying the pressure gradient, and thus the flow velocity, over many orders of magnitude as shown in figure~\ref{fig:pressureErr}~(a) of the appendix.\RK{This is the worst case error for MC and it is tiny "remain robust" is too weak here}
 
@@
 		(b) Velocity profile for methyl cellulose.
-		\SG{ make these plots for different $ \alpha _ \mathrm{s}$, either include here or put into appendix }}
+		\SG{ make these plots for different $ \alpha _ \mathrm{s}$, either include here or put into appendix }}\RK{Why? Is identical down to fp32 precision (see appendix C)}
 		\label{fig:2Dvel}
-	\end{figure}
+	\end{figure}\todo{maybe try if it is this identical for different $\alpha_s$ first}
 
 We proceed to evaluate the viscosity shuffling method for a cylindrical Poiseuille flow.
-The semi-analytical solution for this situation can be derived in a similar fashion as for the planar case and is given in appendix ~\ref{app:semianalyticalPoiseuille}.
-Numerically, the cylindrical situation is slightly more complex due to discretization errors (''staircase effect'') when mapping the rounded channel walls onto the rectilinear LBM grid \cite{Lehmann.20229da}.
-We use the same material parameters as above, but double the pressure gradient to \SG{ XX }. \SG{ why? }
-The channel has a diameter of \SG{ XX } and is discretized with 41 lattice points.
+The semi-analytical solution for this situation can be derived similarly as for the planar case and is given in appendix~\ref{app:semianalyticalPoiseuille}.
+Numerically, the cylindrical situation is slightly more complex due to discretization errors ("staircase effect") when mapping the rounded channel walls onto the rectilinear LBM grid \cite{Lehmann.20229da}.
+We use the same material parameters as above, but double the pressure gradient to \SG{ XX }.
+\SG{ why?
+} \RK{where analytical solutions exist in Poiseuille geometry the 3D solution differs from the 2D solution by a factor 2.
+See the velocities in our sims being the same with this scaling}
+The channel has a diameter of \SI{20}{\micro\meter}\SG{ XX }\RK{done} and is discretized with 41 lattice points.
 Again, we initialize the polymers in the unstretched state for methyl cellulose and in the stretched state for alginate.
@@
 		\label{fig:3Dvel}
-	\end{figure}
+	\end{figure}\todo{see above}
 
@@
 The authors studied an Oldroyd-B fluid in a planar Poiseuille flow and compared the error in the simulated velocity profile to an exact analytical solution.
-The Oldroyd-B model is a special case of the PTT model which is obtained by setting $ \xi  = \epsilon  = 0$ in eq.~(\ref{eq:polymerStress}) and is thus easily tractable with our code.
-In figure~\ref{fig:malaspinas2010} we show the L2 error as function of lattice resolution for different Weissenberg numbers $ \mathrm{Wi}$ and \SG{ XX } $R_ \nu $.
+The Oldroyd-B model is a special case of the PTT model which is obtained by setting $\xi = \epsilon = 0$ in eq.~(\ref{eq:polymerStress}) and is thus easily tractable with our code.\RK{was simulated with a direct Oldroyd-B implementation, which I now see was unnecessary...}
+In figure~\ref{fig:malaspinas2010}, we show the L2 error as function of lattice resolution for different Weissenberg numbers $\mathrm{Wi}$ and \SG{ XX } $R_ \nu $.
 To match with \cite{malaspinas2010}, we defined these as
 \begin{align}
-	XX
+	R_\nu = \frac{\nu_\text{s}}{\nu_\text{p}+\nu_\text{s}}
 \end{align}
-with \SG{ ... }. \SG{ comment whether these definitions are identical or different than the definitions above. }
-Furthermore, in agreement with \cite{malaspinas2010}, also the L2 error is defined slightly differently than above, namely:
+with the kinematic solvent and the polymer viscosity $\nu_\text{s}$ and $\nu_\text{p}$ \SG{ ...
+}.
+\SG{ comment whether these definitions are identical or different than the definitions above.
+}\RK{different but can be transformed into each other $\frac{1}{R_\nu}-1=R_\eta$}
+Furthermore, in agreement with \cite{malaspinas2010}, also the L2 error is defined slightly differently than above, namely:\todo{slightly?}
 	\begin{equation}\label{eq:l2error}
@@
 		\caption{L2 error as defined in equation \ref{eq:l2error} from Malaspinas et al.\cite{malaspinas2010} (dots) compared to our algorithm (x) as a function of grid resolution.
-		Blue and green crosses are not visible as they overlap exactly with the orange and red crosses, respectively, showing that the accuracy of our method is independent of $ \mathrm{Wi}$ in the studied parameter range.}
+		Blue and green crosses are not visible as they overlap exactly with the orange and red crosses, respectively, showing that the accuracy of our method is independent of $\mathrm{Wi}$ in the studied parameter range.}
 		\label{fig:malaspinas2010}
@@
 As can be seen in figure~\ref{fig:malaspinas2010}, the accuracy of our method does not depend on the Weissenberg Number and is generally somewhat better than the method of \cite{malaspinas2010}.
-We note a certain dependence of the accuracy on $R_ \nu $ which we consider nevertheless acceptable given the overall smallness of the error.
-Finally, we find that the error of our method decreases with lattice resolution to the power of \SG{ give number, show dashed line in plot }.
+We note a certain dependence of the accuracy on $R_\nu$ which we consider nevertheless acceptable given the overall smallness of the error.
+Finally, we find that the error of our method decreases with lattice resolution to the power of \SG{ give number, show dashed line in plot }.\RK{They see diminishing returns we don't}
 
@@
 To illustrate the use of viscosity shuffling in realistic applications, we study three typical experimentally relevant situations.
-For ease of comparison, we use the 0.49\% methyl cellulose in all three situations.
+For ease of comparison, we use the \SI{0.49}{\percent} methyl cellulose in all three situations.
 
@@
 The nozzle has a length of \SI{18}{\milli\meter}.
-Due to the difference in inlet/outlet radii, the system cannot be modeled with periodic boundary conditions and we use inflow-/outflow boundary conditions as described in section~\ref{sec:Methods} instead.
+Due to the difference in inlet/outlet radii, the system cannot be modeled with periodic boundary conditions, and we use inflow/outflow boundary conditions as described in section~\ref{sec:Methods} instead.
 The required values for velocity and polymer conformation are obtained from simulations of pipes of the respective radii and a fixed volume flow of $\approx\SI{3}{\micro\liter\per\second}$.
@@
 \begin{align}
-	\sigma _ \mathrm{vM} = \sqrt{ \frac{ 1 } { 2 } \left[ \left( \sigma _1 - \sigma _2 \right)^2 + \left( \sigma _2 - \sigma _3 \right)^2 + \left( \sigma _3 - \sigma _1 \right)^2 \right]}.
+	\sigma_\text{vM} = \sqrt{\frac{1}{2}\left[\left(\sigma_1 - \sigma_2\right)^2 + \left(\sigma_2 - \sigma_3\right)^2 + \left(\sigma_3 - \sigma_1\right)^2\right]}.
 \end{align}
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/Nozzle_sigma_vM.eps}
-		\caption{Velocity profile (a) and von Mises stress (b) for methyl cellulose in a conical nozzle as used for bioprinting. \SG{ draw nozzle contour with black lines }}
+		\caption{Velocity profile (a) and von Mises stress (b) for methyl cellulose in a conical nozzle as used for bioprinting. \SG{ draw nozzle contour with black lines }}\RK{looks terrible}
 		\label{fig:Nozzle_v}
@@
 
-Our next example is the RT-DC geometry in which cells from a reservoir are squeezed through a narrow observation channel \cite{Toepfner.2018, Fregin:2019gx} with a square cross-section of 20x20 $\mu m$.
+Our next example is the RT-DC geometry in which cells from a reservoir are squeezed through a narrow observation channel \cite{Toepfner.2018, Fregin:2019gx} with a square cross-section of 20x20 \unit{\micro\meter}.
 For this simulation we use periodic boundary conditions and a constant body force corresponding to a pressure gradient of \SI{1e7}{\pascal}.
@@
 Similarly, directly after the constriction, the high stress inside the observation channel persists over a certain distance that is needed for the polymer stress to decay.
+\RK{There are three, proceeds to name two}
 
@@
 If one would divide the stress in these two regions by the strain rate in an attempt to obtain a viscosity one would find an extremely low and an extremely high viscosity respectively.
-Depending on the exact parameters \glqq viscosities\grqq{ }can be reached that cannot be obtained through rheological measurements with the fluid.
+Depending on the exact parameters "viscosities" can be reached that cannot be obtained through rheological measurements with the fluid.
 Meaning these viscosities are not valid.
@@
 This also shows why viscoelastic simulations cannot always be replaced by shear thinning models and should be considered despite the high computational cost.
-}
+}\RK{plot would probably be better}
 
@@
 Coupling to the LBM solver is achieved with the immersed-boundary method as described in earlier publications \cite{Mueller.2021}.
-For simplicity, we consider the viscoelastic fluid inside and outside of the cell to be identical.
-The cell is initially spherical with a radius of \SI{6}{\micro\meter} and possesses a Youngs modulus of \SI{100}{\pascal} and a Poisson ratio of \SG{ XX }.
+For simplicity, we consider the viscoelastic fluid inside and outside the cell to be identical.
+The cell is initially spherical with a radius of \SI{6}{\micro\meter} and possesses a Youngs modulus of \SI{100}{\pascal} and a Poisson ratio of \num{0.48}\SG{ XX }\RK{done}.
 It is placed into a shear flow with a shear rate of \SI{400}{\per\second} where the cell quickly reaches a steady state in which it deforms into a tank-treading ellipsoid.
 This is in qualitative agreement with simulations \cite{Mueller.2021} and classical theories \cite{Roscoe.1967}.
-For the discretization of the cell we use \SG{ xx } tetrahedrons and a radius of \SG{ xx } lattice units.
+For the discretization of the cell we use \num{5179}\SG{ xx }\RK{done} tetrahedrons and a radius of 6\SG{ xx }\RK{done} lattice units.
 The lattice with a resolution of \num{100} lattice points is chosen significantly larger than the cell to assure negligible impact of the walls.
@@
 Our method is based on the LBM for the solvent combined with a finite-volume solver for the polymer dynamics.
-Its key novel ingredient is the introduction of a shuffling parameter $ \alpha _ \mathrm{s}$ which shifts a substantial part of the polymer stress into the solvent contribution by artificially increasing the solvent viscosity.
+Its key novel ingredient is the introduction of a shuffling parameter $\alpha_\text{s}$ which shifts a substantial part of the polymer stress into the solvent contribution by artificially increasing the solvent viscosity.
 The algorithm compensates for this extra solvent stress by lowering - by the same amount - the polymer stress thus leaving the total stress invariant.
@@
 For simple situations such as shear and Poiseuille flow, we found very good agreement with (semi-)analytical theories.
-Importantly, the outcome of the viscostiy shuffling simulations is independent of the shuffling parameter $ \alpha _ \mathrm{s}$.
+Importantly, the outcome of the viscosity shuffling simulations is independent of the shuffling parameter $\alpha_\text{s}$.
 We finally demonstrated the usability of our approach in realistic geometries such as constricting microchannels and conical bioprinting nozzles.
@@
 \SG{ Tomasz should extend this paragraph }
-The solutions used here are 4\% by weight of DuPont VIVAPHARM Alginate PH176 in PBS. 
+The solutions used here are \SI{4}{\percent} by weight of DuPont VIVAPHARM Alginate PH176 in PBS.
 The measurements were done using a plate-plate rheometer.
@@
 As additional quantitative validation, we simulate a pure shear flow driven by imposing a fixed velocity at the top and bottom of the computational box and using periodic boundary conditions in the other two directions.
-The box dimension is \SG{ xx }.
+The box dimension is 2x43x2\SG{ xx }\RK{done}.
 We use PTT with the methyl cellulose parameters and vary the shear rate to cover the full range starting from the zero-shear all the way to the infinite-shear plateau displayed in figure~\ref{fig:fit_mc} of the main text.
-The shuffling is fixed at $ \alpha _ \mathrm{s} = 1$ and the viscosity as function of shear rate is computed by dividing the total fluid stress at the center of the box by the shear rate.
+The shuffling is fixed at $\alpha_\text{s} = 1$ and the viscosity as function of shear rate is computed by dividing the total fluid stress at the center of the box by the shear rate.
 Figure~\ref{fig:wiParameterStudy}~(a) shows that our simulations are in very good agreement with the semi-analytical solution with a maximum error of \num{2e-11}.
-Importantly, we show in figure~\ref{fig:wiParameterStudy}~(b) that this very good agreement is independent of the shuffling parameter $ \alpha _ \mathrm{s}$.
+Importantly, we show in figure~\ref{fig:wiParameterStudy}~(b) that this very good agreement is independent of the shuffling parameter $\alpha_\text{s}$.
 	\begin{figure}[H]
@@
 		\caption{(a) The local viscosity determined by a shear flow simulation is in very good agreement with the semi-analytical theory.
-		(b) The error is negligibly small and independent of the shuffling parameter $ \alpha _ \mathrm{s}$.
+		(b) The error is negligibly small and independent of the shuffling parameter $\alpha_\text{s}$.
 		\SG{ plot over shear rate instead of $ \mathrm{Wi}$. Fix units of $ \eta $. }}
@@
 		\caption{L2 error of the velocity profile in figure~\ref{fig:2Dvel} with respect to the semi-analytical theory in a planar Poiseuille flow for alginate (a) and methyl cellulose (b).
-			The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall. }
+			The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall.}\RK{this is linear error}
 		\label{fig:2DvelErr}
@@
 		\caption{L2 error of the velocity profile in \ref{fig:3Dvel} with respect to the semi-analytical theory in a cylindrical Poiseuille flow for alginate (a) and methyl cellulose (b).
-			The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall. }
+			The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall.}\RK{this is linear error}
 		\label{fig:3DvelErr}
@@
 		\caption{Average error of the velocity for a planar (a) and a cylindrical (b) Poiseuille flow of methyl cellulose at different pressure gradients.
-		The peak in the error profile appears when the average shear rate across the channel corresponds to the maximum slope in the viscosity profile of figure~\ref{fig:wiParameterStudy}. }
+		The peak in the error profile appears when the average shear rate across the channel corresponds to the maximum slope in the viscosity profile of figure~\ref{fig:wiParameterStudy}.
+}\RK{this is L2 error norm not "average"}
 		\label{fig:pressureErr}

### 2024-02-20 NovelLBM.tex
plots

@@
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/fit_alginate_eta.eps}
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/fit_alginate_N.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/fit_alginate_eta.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/fit_alginate_N.pdf}
 		\caption{Rheology data for alginate solution from 21 measurements of the viscosity (a) and normal stress (b).
-				Orange lines show a fit of the PTT rheological model. \SG{ larger font in figures }}
+				Orange lines show a fit of the PTT rheological model. \SG{ larger font in figures }\RK{done}}
 		\label{fig:fit_alginate}
-	\end{figure}\todo{larger fonts in all figures}
+	\end{figure}
 
@@
 		\centering
-		\includegraphics[width=7.8cm]{assets/plots/fit_mc_eta.eps}
-		\includegraphics[width=7.8cm]{assets/plots/fit_mc_N.eps}
-		\caption{Rheology data of a methyl cellulose solution from \cite{buyukurganci2023}.
-				Orange lines show a fit of the PTT rheological model.
-\SG{ include legend into figure.
-Maybe give color coding only in caption?
-}\RK{meaning ony one legend for both plots?}\SG{ larger font in figures }}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/fit_mc_eta.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/fit_mc_N.pdf}
+		\caption{The viscosity (a) and normal stress (b) of a methyl cellulose solution from \cite{buyukurganci2023}.
+				Lines show a fit of the PTT rheological model. \SG{ include legend into figure. Maybe give color coding only in caption? }\RK{Done}\SG{ larger font in figures }\RK{done}}
 		\label{fig:fit_mc}
@@
 where $\ma{D}$ is the strain rate tensor.
-\SG{ check that PTT is given in this form in \cite{phan-thien1977,phan-thien1978} or cite other source }
+\SG{ check that PTT is given in this form in \cite{phan-thien1977,phan-thien1978} or cite other source }\RK{The given form is most similar to \cite{ferras2019}, which you removed?}
 The polymer viscosity is denoted $\eta_\text{p}$ and $\lambda$ is the corresponding relaxation time.
@@
 which will turn out to be an important parameter to determine numerical stability of LB simulations.
-\SG{ wo don't actually show that $R_ \eta  $ determines stability? }\RK{we do not. We could do a plot with $alpha_s$ decreasing until the sim breaks if you want}
+\SG{ wo don't actually show that $R_ \eta  $ determines stability? }\RK{we do not. We could do a plot with $\alpha_s$ decreasing until the sim breaks if you want}
 This ratio can similarly be defined for other models such as FENE-P or the inelastic, but shear-thinning Carreau-Yasuda model \cite{carreau1972, yasuda1979}.
@@
 The spatially resolved errors are shown in figure~\ref{fig:2DvelErr} in the appendix.
-Averaging over the channel diameter, we obtain an L2 error of \num{9e-4} and \SG{ XX } for alginate and methyl cellulose, respectively.
+Averaging over the channel diameter, we obtain an L2 error of \num{9e-4} and \num{1e-3}\SG{ XX }\RK{done}\RK{we do not "average" over the diameter, we calculate the L2 error along the diameter} for alginate and methyl cellulose, respectively.
 These conclusions remain robust even when varying the pressure gradient, and thus the flow velocity, over many orders of magnitude as shown in figure~\ref{fig:pressureErr}~(a) of the appendix.\RK{This is the worst case error for MC and it is tiny "remain robust" is too weak here}
@@
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/2DAlginateU.eps}
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/2DParameterStudyUWorst.eps}
-		\caption{(a) Velocity profile of alginate in planar channel flow. \SG{use $y$ instead of $r$ in 2D}.
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DAlginateU.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyUWorst.pdf}
+		\caption{(a) Velocity profile of alginate in planar channel flow. \SG{use $y$ instead of $r$ in 2D}\RK{done}.
 		The time evolution of the center-line velocity is shown in the inset \SG{ to do }.
@@
 Again, we initialize the polymers in the unstretched state for methyl cellulose and in the stretched state for alginate.
-The resulting velocity profile can be seen in figure~\ref{fig:3Dvel} and shows almost equally good agreement as for the planar case with an L2 error of \num{0.014} and \SG{ XX }, respectively.
+The resulting velocity profile can be seen in figure~\ref{fig:3Dvel} and shows almost equally good agreement as for the planar case with an L2 error of \num{0.014} and \num{0.06}\SG{ XX }\RK{done}, respectively.
 The spatially resolved error in figure~\ref{fig:3DvelErr} of the appendix shows that this larger average is indeed mainly attributable to the staircase effect as the error near the walls increases significantly.
@@
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/3DAlginateU.eps}
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/3DParameterStudyUWorst.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DAlginateU.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyUWorst.pdf}
 		\caption{(a) Velocity profile of alginate in cylindrical channel flow.
@@
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/malaspinas2010.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/malaspinas2010.pdf}
 		\caption{L2 error as defined in equation \ref{eq:l2error} from Malaspinas et al.\cite{malaspinas2010} (dots) compared to our algorithm (x) as a function of grid resolution.
@@
 We note a certain dependence of the accuracy on $R_\nu$ which we consider nevertheless acceptable given the overall smallness of the error.
-Finally, we find that the error of our method decreases with lattice resolution to the power of \SG{ give number, show dashed line in plot }.\RK{They see diminishing returns we don't}
+Finally, we find that the error of our method decreases with lattice resolution to the power of \num{-2} \SG{ give number, show dashed line in plot }\RK{done}.\RK{They see diminishing returns we don't}
 
@@
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/Nozzle_v.eps}
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/Nozzle_sigma_vM.eps}
-		\caption{Velocity profile (a) and von Mises stress (b) for methyl cellulose in a conical nozzle as used for bioprinting. \SG{ draw nozzle contour with black lines }}\RK{looks terrible}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/Nozzle_v.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/Nozzle_sigma_vM.pdf}
+		\caption{Velocity profile (a) and von Mises stress (b) for methyl cellulose in a conical nozzle as used for bioprinting. \SG{ draw nozzle contour with black lines }}\RK{Done}
 		\label{fig:Nozzle_v}
@@
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/RT-DC_v.eps}
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/RT-DC_tau.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_v.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_tau.pdf}
 		\caption{Velocity profile (a) and shear stress (b) for methyl cellulose in a typical RT-DC geometry. \SG{ draw channel contour with black lines }
@@
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/cellInShear_sigma_vM.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/cellInShear_sigma_vM.pdf}
 		\caption{The von Mises stress around a cell in viscoelastic shear flow.}
@@
 Our derivation is analogous to Oliveira\cite{oliveira1999}.
-To account for the added viscous stress due to $\eta_\text{s}$, equilibrium is reached at lower polymer stresses.
-Therefore, Oliveiras equation (7) needs to be modified as follows.
+
+For both Poiseuille flow and shear flow the following holds.
+\begin{equation}
+	\vec{u} = \dot{\gamma}\left(y\right)\hat{e}_x
+\end{equation}
+With this the constitutive equation\todo{link} fo $\xi=0$ in steady state reduces to the following.
+\begin{align}
+	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xx} &= 2\lambda\dot{\gamma}\tau_{xy} \\
+	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xy} &= \eta_\text{p}\dot{\gamma}
+\end{align}
+With $\Tr\ma{\tau} = \tau_{xy}$. In the three-dimensional case $y$ refers to the radial coordinate.
+
+To account for the added viscous stress due to $\eta_\text{s}$, equilibrium is reached at lower polymer stresses. Therefore, Oliveiras equation (7) needs to be modified as follows.
 	\begin{equation}
@@
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/wiParameterStudy.eps}
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/suffleParameterStudy.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/wiParameterStudy.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/suffleParameterStudy.pdf}
 		\caption{(a) The local viscosity determined by a shear flow simulation is in very good agreement with the semi-analytical theory.
 		(b) The error is negligibly small and independent of the shuffling parameter $\alpha_\text{s}$.
-		\SG{ plot over shear rate instead of $ \mathrm{Wi}$. Fix units of $ \eta $. }}
+		\SG{ plot over shear rate instead of $ \mathrm{Wi}$. Fix units of $ \eta $. }\RK{done, done}}
 		\label{fig:wiParameterStudy}
@@
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/2DAlginateErr.eps}
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/2DParameterStudyErrWorst.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DAlginateErr.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErrWorst.pdf}
 		\caption{L2 error of the velocity profile in figure~\ref{fig:2Dvel} with respect to the semi-analytical theory in a planar Poiseuille flow for alginate (a) and methyl cellulose (b).
@@
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/3DAlginateErr.eps}
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/3DParameterStudyErrWorst.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DAlginateErr.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErrWorst.pdf}
 		\caption{L2 error of the velocity profile in \ref{fig:3Dvel} with respect to the semi-analytical theory in a cylindrical Poiseuille flow for alginate (a) and methyl cellulose (b).
@@
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/2DParameterStudyErr.eps}
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.5]{assets/plots/3DParameterStudyErr.eps}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr.pdf}
 		\caption{Average error of the velocity for a planar (a) and a cylindrical (b) Poiseuille flow of methyl cellulose at different pressure gradients.

### 2024-02-20 assets/python/fig:2DAlginate.py

@@ -13,8 +13,8 @@ from pathlib import Path
 import matplotlib.pyplot as plt
 import numpy as np
 import pyvista as pv
+
 from fluidx3d.eval.models import PTT
-from style import *
 from style import cm
 
 
@@ -59,25 +59,27 @@ def process(i):
     u = PTT.alginate.u(np.abs(rTheory))
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
-    plt.plot(rTheory * 1e6, u, "k", label="Semi-analytical solution")
-    plt.plot(r * 1e6, vSlice, "rx", label="Simulation result")
-    plt.xlabel(r"$r/\unit{\micro\meter}$")
-    plt.ylabel(r"$u_\text{x}/\unit{\meter\per\second}$")
+    plt.title("(a)", loc="left")
+    plt.plot(rTheory * 1e6, u * 1e6, "k", label="Semi-analytical solution")
+    plt.plot(r * 1e6, vSlice * 1e6, "rx", label="Simulation result")
+    plt.xlabel(r"$y/\unit{\micro\meter}$")
+    plt.ylabel(r"$u_\text{x}/\unit{\micro\meter\per\second}$")
     plt.legend()
-    plt.savefig("../plots/2DAlginateU.eps")
+    plt.savefig("../plots/2DAlginateU.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+    plt.title("(a)", loc="left")
     plt.plot(
         r[1:-1] * 1e6,
         vSlice[1:-1] / uErr[1:-1] - 1,
         "rx",
         # label=f"{i}",
     )
-    plt.xlabel(r"$r/\unit{\micro\meter}$")
+    plt.xlabel(r"$y/\unit{\micro\meter}$")
     plt.ylabel(r"$error$")
     # plt.legend()
-    plt.savefig("../plots/2DAlginateErr.eps")
+    plt.savefig("../plots/2DAlginateErr.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()
 
     err = np.sqrt(np.sum((vSlice[1:-1] - uErr[1:-1]) ** 2) / np.sum(uErr[1:-1] ** 2))

### 2024-02-20 assets/python/fig:2DParameterStudy.py

@@ -14,6 +14,7 @@ from time import time
 import matplotlib.pyplot as plt
 import numpy as np
 import pyvista as pv
+
 from fluidx3d.eval.models import PTT
 from fluidx3d.eval.style import cm
 
@@ -79,7 +80,7 @@ def process(index):
     plt.xlabel(r"$r/\unit{\micro\meter}$")
     plt.ylabel(r"$u_\text{x}/\unit{\meter\per\second}$")
     plt.legend()
-    plt.savefig(f"../plots/2DParameterStudyU{i}.eps")
+    plt.savefig(f"../plots/2DParameterStudyU{i}.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
@@ -92,7 +93,7 @@ def process(index):
     plt.xlabel(r"$r/\unit{\micro\meter}$")
     plt.ylabel(r"$error$")
     plt.legend()
-    plt.savefig(f"../plots/2DParameterStudyErr{i}.eps")
+    plt.savefig(f"../plots/2DParameterStudyErr{i}.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()
 
     err = np.sqrt(np.sum((vSlice[1:-1] - uErr[1:-1]) ** 2) / np.sum(uErr[1:-1] ** 2))
@@ -156,25 +157,27 @@ def plotWorst(index=7):
     u = PTT.mc0_49.u(np.abs(rTheory))
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+    plt.title("(b)", loc="left")
     plt.plot(rTheory * 1e6, u, "k", label="Semi-analytical solution")
     plt.plot(r * 1e6, vSlice, "rx", label="Simulation result")
-    plt.xlabel(r"$r/\unit{\micro\meter}$")
+    plt.xlabel(r"$y/\unit{\micro\meter}$")
     plt.ylabel(r"$u_\text{x}/\unit{\meter\per\second}$")
     plt.legend()
-    plt.savefig("../plots/2DParameterStudyUWorst.eps")
+    plt.savefig("../plots/2DParameterStudyUWorst.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+    plt.title("(b)", loc="left")
     plt.plot(
[…]

### 2024-02-20 assets/python/fig:3DAlginate.py

@@ -13,9 +13,9 @@ from pathlib import Path
 import matplotlib.pyplot as plt
 import numpy as np
 import pyvista as pv
+
 from fluidx3d.eval.models import PTT
-from style import *
-from style import cm
+from fluidx3d.eval.style import cm
 
 
 def process(i):
@@ -59,15 +59,17 @@ def process(i):
     u = PTT.alginate.u(np.abs(rTheory))
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
-    plt.plot(rTheory * 1e6, u, "k", label="Semi-analytical solution")
-    plt.plot(r * 1e6, vSlice, "rx", label="Simulation result")
+    plt.title("(a)", loc="left")
+    plt.plot(rTheory * 1e6, u * 1e6, "k", label="Semi-analytical solution")
+    plt.plot(r * 1e6, vSlice * 1e6, "rx", label="Simulation result")
     plt.xlabel(r"$r/\unit{\micro\meter}$")
-    plt.ylabel(r"$u_\text{x}/\unit{\meter\per\second}$")
+    plt.ylabel(r"$u_\text{x}/\unit{\micro\meter\per\second}$")
     plt.legend()
-    plt.savefig("../plots/3DAlginateU.eps")
+    plt.savefig("../plots/3DAlginateU.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+    plt.title("(a)", loc="left")
     plt.plot(
         r[1:-1] * 1e6,
         vSlice[1:-1] / uErr[1:-1] - 1,
@@ -77,7 +79,7 @@ def process(i):
     plt.xlabel(r"$r/\unit{\micro\meter}$")
     plt.ylabel(r"$error$")
     # plt.legend()
-    plt.savefig("../plots/3DAlginateErr.eps")
+    plt.savefig("../plots/3DAlginateErr.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()
 
     err = np.sqrt(np.sum((vSlice[1:-1] - uErr[1:-1]) ** 2) / np.sum(uErr[1:-1] ** 2))

### 2024-02-20 assets/python/fig:3DParameterStudy.py

@@ -14,6 +14,7 @@ from time import time
 import matplotlib.pyplot as plt
 import numpy as np
 import pyvista as pv
+
 from fluidx3d.eval.models import PTT
 from fluidx3d.eval.style import cm
 
@@ -79,7 +80,7 @@ def process(index):
     plt.xlabel(r"$r/\unit{\micro\meter}$")
     plt.ylabel(r"$u_\text{x}/\unit{\meter\per\second}$")
     plt.legend()
-    plt.savefig(f"../plots/3DParameterStudyU{i}.eps")
+    plt.savefig(f"../plots/3DParameterStudyU{i}.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
@@ -92,7 +93,7 @@ def process(index):
     plt.xlabel(r"$r/\unit{\micro\meter}$")
     plt.ylabel(r"$error$")
     plt.legend()
-    plt.savefig(f"../plots/3DParameterStudyErr{i}.eps")
+    plt.savefig(f"../plots/3DParameterStudyErr{i}.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()
 
     err = np.sqrt(np.sum((vSlice[1:-1] - uErr[1:-1]) ** 2) / np.sum(uErr[1:-1] ** 2))
@@ -156,15 +157,17 @@ def plotWorst(index=7):
     u = PTT.mc0_49.u(np.abs(rTheory))
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+    plt.title("(b)", loc="left")
     plt.plot(rTheory * 1e6, u, "k", label="Semi-analytical solution")
     plt.plot(r * 1e6, vSlice, "rx", label="Simulation result")
     plt.xlabel(r"$r/\unit{\micro\meter}$")
     plt.ylabel(r"$u_\text{x}/\unit{\meter\per\second}$")
     plt.legend()
-    plt.savefig("../plots/3DParameterStudyUWorst.eps")
+    plt.savefig("../plots/3DParameterStudyUWorst.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+    plt.title("(b)", loc="left")
     plt.plot(
         r[1:-1] * 1e6,
[…]

### 2024-02-20 assets/python/fig:CellInShear.py

@@ -14,6 +14,7 @@ from time import time
 import matplotlib.pyplot as plt
 import numpy as np
 import pyvista as pv
+
 from fluidx3d.eval.models import PTT
 from fluidx3d.eval.style import cm
 
@@ -90,7 +91,7 @@ def process():
     plt.colorbar(location="right", label=r"$v_x/\unit{\meter\per\second}$")
     # plt.gca().spines["top"].set_visible(False)
     # plt.gca().spines["right"].set_visible(False)
-    plt.savefig("../plots/cellInShear_v.eps")
+    plt.savefig("../plots/cellInShear_v.pdf", dpi=1200, bbox_inches="tight", pad_inches=0)
     plt.show()
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
@@ -108,7 +109,7 @@ def process():
     plt.xlabel(r"$x/\unit{\milli\meter}$")
     plt.ylabel(r"$y/\unit{\milli\meter}$")
     plt.colorbar(location="right", label=r"$\sigma_\text{vM}/\unit{\pascal}$")
-    plt.savefig("../plots/cellInShear_sigma_vM.eps")
+    plt.savefig("../plots/cellInShear_sigma_vM.pdf", dpi=1200, bbox_inches="tight", pad_inches=0)
     plt.show()
 
     r"""

### 2024-02-20 assets/python/fig:Nozzle.py

@@ -15,6 +15,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 import numpy.ma as ma
 import pyvista as pv
+
 from fluidx3d.eval.models import PTT
 from fluidx3d.eval.style import cm
 
@@ -50,7 +51,7 @@ def process():
     vField = dataV.get_array("data") * V0
     vField = np.reshape(vField, (Lx, Ly, Lz, 3), "F")
 
-    if False:
+    if True:
         mask = np.zeros(vField.shape)
 
         for x in range(Lx):
@@ -77,6 +78,18 @@ def process():
 
             vonMieses += 3 / 2 * deviator[i][j] * deviator[i][j]
     vonMieses = np.sqrt(vonMieses)
+    if True:
+        mask = np.zeros(vonMieses.shape)
+
+        for x in range(Lx):
+            localR = (10.5 - 94.5) / (Lx - 3) * (x - 1) + 94.5
+            for y in range(Ly):
+                for z in range(Lz):
+                    if np.hypot(y - (Ly / 2.0) + 0.5, z - (Lz / 2.0) + 0.5) >= localR + 0.5:
+                        mask[x, y, z] = 1
+
+        vonMieses = ma.masked_array(vonMieses, mask=mask)
+
     vonMiesesSlice = vonMieses[..., Lz // 2]
 
     # tau12 = tauField[..., Lz // 2, 3]
@@ -88,52 +101,58 @@ def process():
     print(inflow)
     print(outflow)
 
-    x = np.arange(0, Lx) - 0.5  # Offset?
+    x = np.arange(0, Lx + 1) - 0.5  # Offset?
     localR = (10.5 - 94.5) / (Lx - 3) * (x - 1) + 94.5
     # lower = 94.58898305084746 - localR
     # upper = 94.58898305084746 + localR
-    upper = 95 + localR
+    upper = 95 + localR + 0.5 - (Ly / 2 - 0.5)  # Actual radius simulated is off by 0.5?
     # print(upper)
-    lower = 95 - localR + 1  # Something is wrong here
+    lower = 95 - localR - 0.5 - (Ly / 2 - 0.5)
     # print(lower)
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
-    # plt.plot(x * L0 * 1e3, upper * L0 * 1e3, "k")
[…]

### 2024-02-20 assets/python/fig:RT-DC.py

@@ -8,19 +8,15 @@ Created on Tue Sep  5 10:51:20 2023
 """
 
 import json
-import sys
-from multiprocessing import Pool
 from pathlib import Path
 from time import time
 
 import matplotlib.pyplot as plt
 import numpy as np
+import numpy.ma as ma
 import pyvista as pv
-import scipy
-from scipy.special import lambertw
-from style import *
 
-eta_s = 1e-3
+from fluidx3d.eval.style import cm
 
 
 def process():
@@ -63,25 +59,93 @@ def process():
     vField = dataV.get_array("data") * V0
     vField = np.reshape(vField, (Lx, Ly, Lz, 3), "F")
 
+    if True:
+        mask = np.zeros(vField.shape)
+        mask2 = np.zeros(tauField.shape)
+        width = 30
+        length = 225
+        padding = 60
+
+        for x in range(Lx):
+            for y in range(Ly):
+                for z in range(Lz):
+                    if x < padding:
+                        if y == 0 or y == Ly - 1 or z == 0 or z == Lz - 1:
+                            for i in range(3):
+                                mask[x, y, z, i] = 1
+                                mask2[x, y, z, 2 * i] = 1
+                                mask2[x, y, z, 2 * i + 1] = 1
+                    elif x < padding + width:
+                        if (
+                            y < x - (padding - 2)
+                            or y >= Ly - x + (padding - 2)
+                            or z == 0
+                            or z == Lz - 1
+                        ):
+                            for i in range(3):
+                                mask[x, y, z, i] = 1
+                                mask2[x, y, z, 2 * i] = 1
+                                mask2[x, y, z, 2 * i + 1] = 1
+                    elif x < padding + width + length:
+                        if y < width + 1 or y >= 2 * width + 1 or z == 0 or z == Lz - 1:
+                            for i in range(3):
+                                mask[x, y, z, i] = 1
+                                mask2[x, y, z, 2 * i] = 1
+                                mask2[x, y, z, 2 * i + 1] = 1
+                    elif x < padding + 2 * width + length:
+                        if (
[…]

### 2024-02-20 assets/python/fig:fit_alginate.py

@@ -144,6 +144,7 @@ if __name__ == "__main__":
     print(err)
     gd = np.logspace(np.log10(np.min(gdet)), np.log10(np.max(gdet)) + 5.5, 1000)
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+    plt.title("(a)", loc="left")
     plt.plot(gdet, et, "x", label="Data")
     plt.plot(gd, ptt_eta(gd, *params), label="PTT fit")
     plt.xscale("log")
@@ -151,8 +152,9 @@ if __name__ == "__main__":
     plt.xlabel(r"$\dot{\gamma}/\unit{\per\second}$")
     plt.ylabel(r"$\eta/\unit{\pascal\second}$")
     plt.legend()
-    plt.savefig("../plots/fit_alginate_eta.eps")
+    plt.savefig("../plots/fit_alginate_eta.pdf", bbox_inches="tight", pad_inches=0)
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+    plt.title("(b)", loc="left")
     plt.plot(gdnt, nt, "x", label="Data")
     plt.plot(gd, ptt_N(gd, *params), label="PTT fit")
     plt.xscale("log")
@@ -160,4 +162,4 @@ if __name__ == "__main__":
     plt.xlabel(r"$\dot{\gamma}/\unit{\per\second}$")
     plt.ylabel(r"$N_1/\unit{\pascal}$")
     plt.legend()
-    plt.savefig("../plots/fit_alginate_N.eps")
+    plt.savefig("../plots/fit_alginate_N.pdf", bbox_inches="tight", pad_inches=0)

### 2024-02-20 assets/python/fig:fit_mc.py

@@ -100,6 +100,7 @@ if __name__ == "__main__":
 
     gd = np.logspace(np.log10(np.min(gde)), np.log10(np.max(gde)) + 4, 1000)
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+    plt.title("(a)", loc="left")
     for i in [49, 59, 83]:
         gde, e, gdn, n = readFile(i)
         plt.plot(gde, e, "x", color=color(f(i)), label=f"Data $\\SI{{0.{i}}}{{\\percent}}$")
@@ -122,10 +123,11 @@ if __name__ == "__main__":
     plt.yscale("log")
     plt.xlabel(r"$\dot{\gamma}/\unit{\per\second}$")
     plt.ylabel(r"$\eta/\unit{\pascal\second}$")
-    plt.legend(loc="center left", bbox_to_anchor=(1, 0.5))
-    plt.savefig("../plots/fit_mc_eta.eps")
+    plt.legend()
+    plt.savefig("../plots/fit_mc_eta.pdf", bbox_inches="tight", pad_inches=0)
     gd = np.logspace(np.log10(np.min(gdn)), np.log10(np.max(gdn)) + 4, 1000)
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+    plt.title("(b)", loc="left")
     for i in [49, 59, 83]:
         gde, e, gdn, n = readFile(i)
         x, y, fun = merge(ptt_eta, gde, e, ptt_N, gdn, n)
@@ -140,5 +142,5 @@ if __name__ == "__main__":
     plt.yscale("log")
     plt.xlabel(r"$\dot{\gamma}/\unit{\per\second}$")
     plt.ylabel(r"$N_1/\unit{\pascal}$")
-    plt.legend(loc="center left", bbox_to_anchor=(1, 0.5))
-    plt.savefig("../plots/fit_mc_N.eps")
+    plt.legend()
+    plt.savefig("../plots/fit_mc_N.pdf", bbox_inches="tight", pad_inches=0)

### 2024-02-20 assets/python/fig:malaspinas2010.py

@@ -15,7 +15,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 import pyvista as pv
 
-from style import *
+from fluidx3d.eval.style import cm, color
 
 R = 10e-6
 
@@ -61,6 +61,12 @@ def process(index):
 
 N = [25, 50, 100, 200]  # It is clear, that these are the exact values
 plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+Ns = np.logspace(np.log10(24), np.log10(210), 100)
+N2 = (1.0 * np.asarray(Ns)) ** -2
+N20 = (1.0 * np.asarray(25)) ** -2
+plt.plot(Ns, N2 / N20 * 0.0014831067649990915, "k--")
+plt.plot(Ns, N2 / N20 * 0.0008435723395897114, "k--")
+plt.plot(Ns, N2 / N20 * 2.09733499e-03, "k--")
 i = 0
 for fig, R_nu in zip([17, 18], [0.1, 0.7]):
     for Wi in [0.1, 1]:
@@ -101,5 +107,5 @@ plt.xticks(
 plt.xlabel("N")
 plt.ylabel("L2 error")
 plt.legend(loc="center left", bbox_to_anchor=(1, 0.5))
-plt.savefig("../plots/malaspinas2010.eps")
+plt.savefig("../plots/malaspinas2010.pdf", bbox_inches="tight", pad_inches=0)
 plt.show()

### 2024-02-20 assets/python/fig:shuffleParameterStudy.py

@@ -8,20 +8,15 @@ Created on Tue Sep  5 10:51:20 2023
 """
 
 import json
-import sys
 from pathlib import Path
 
 import matplotlib.pyplot as plt
 import numpy as np
 import pyvista as pv
 from scipy.special import lambertw
-from style import *
 
-eta_s = 1e-3
-
-
-def ptt_eta(gd, eta_p, lam, epsilon):
-    return eta_p / np.exp(0.5 * lambertw(4 * epsilon * (gd * lam) ** 2)) + eta_s
+from fluidx3d.eval.models import PTT
+from fluidx3d.eval.style import cm
 
 
 def process(index):
@@ -40,12 +35,10 @@ def process(index):
 
     cFile = cDir / "C_10000000.vtk"
     sFile = sDir / "S_10000000.vtk"
-    eta_p_SI = 18.7e-3
-    lambda_SI = 0.344e-3
     data = pv.read(cFile)
     dataS = pv.read(sFile)
     Lx, Ly, Lz = data.dimensions
-    tauField = data.get_array("data") * eta_p_SI / lambda_SI
+    tauField = data.get_array("data") * PTT.mc0_49.eta_p / PTT.mc0_49.lambda_p
     tauField = np.reshape(tauField, (Lx, Ly, Lz, 6), "F")
     sField = dataS.get_array("data") / T0
     sField = np.reshape(sField, (Lx, Ly, Lz, 6), "F")
@@ -68,11 +61,12 @@ alpha_s = np.arange(1, 2.1, 0.1)
 etas = np.asarray(etas) * 1e3
 
 plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+plt.title("(b)", loc="left")
 plt.plot(alpha_s, etas, "rx")
-# plt.plot(alpha_s, [ptt_eta(1, 18.7e-3, 0.344e-3, 0.27) * 1e3] * len(alpha_s))
+# plt.plot(alpha_s, [PTT.mc0_49.eta(1) * 1e3] * len(alpha_s))
 plt.xlabel(r"$\alpha_\text{s}$")
-plt.ylabel(r"$\eta/\unit{\milli\pascal}$")
+plt.ylabel(r"$\eta/\unit{\milli\pascal\second}$")
 # plt.legend(loc="center left", bbox_to_anchor=(1, 0.5))
 # plt.ylim(19.699998804, 19.699998806)
[…]

### 2024-02-20 assets/python/fig:wiParameterStudy.py

@@ -8,20 +8,14 @@ Created on Tue Sep  5 10:51:20 2023
 """
 
 import json
-import sys
 from pathlib import Path
 
 import matplotlib.pyplot as plt
 import numpy as np
 import pyvista as pv
-from scipy.special import lambertw
-from style import *
 
-eta_s = 1e-3
-
-
-def ptt_eta(gd, eta_p, lam, epsilon):
-    return eta_p / np.exp(0.5 * lambertw(4 * epsilon * (gd * lam) ** 2)) + eta_s
+from fluidx3d.eval.models import PTT
+from fluidx3d.eval.style import cm
 
 
 def process(index):
@@ -40,12 +34,10 @@ def process(index):
 
     cFile = cDir / "C_5000000.vtk"
     sFile = sDir / "S_5000000.vtk"
-    eta_p_SI = 18.7e-3
-    lambda_SI = 0.344e-3
     data = pv.read(cFile)
     dataS = pv.read(sFile)
     Lx, Ly, Lz = data.dimensions
-    tauField = data.get_array("data") * eta_p_SI / lambda_SI
+    tauField = data.get_array("data") * PTT.mc0_49.eta_p / PTT.mc0_49.lambda_p
     tauField = np.reshape(tauField, (Lx, Ly, Lz, 6), "F")
     sField = dataS.get_array("data") / T0
     sField = np.reshape(sField, (Lx, Ly, Lz, 6), "F")
@@ -69,21 +61,21 @@ gds = np.logspace(0, 7, 151)
 etas = np.asarray(etas) * 1e3
 
 plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
-plt.plot(gds * 0.344e-3, ptt_eta(gds, 18.7e-3, 0.344e-3, 0.27) * 1e3, "k", label="Theory")
-plt.plot(gd * 0.344e-3, etas, "rx", label="Simulation")
+plt.title("(a)", loc="left")
+plt.plot(gds, PTT.mc0_49.eta(gds) * 1e3, "k", label="Theory")
+plt.plot(gd, etas, "rx", label="Simulation")
 plt.xscale("log")
 plt.yscale("log")
-plt.xlabel(r"$Wi$")
-plt.ylabel(r"$\eta/\unit{\milli\pascal}$")
+plt.xlabel(r"$\dot{\gamma}/\unit{\per\second}$")
[…]

### 2024-02-20 NovelLBM.tex
derivation PTT sol

@@
 \begin{align}
-	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xx} &= 2\lambda\dot{\gamma}\tau_{xy} \\
-	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xy} &= \eta_\text{p}\dot{\gamma}
+	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xx} &= 2\lambda\dot{\gamma}\tau_{xy} \label{eq:PTTDerivation1}\\
+	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xy} &= \eta_\text{p}\dot{\gamma} \label{eq:PTTDerivation2}
 \end{align}
 With $\Tr\ma{\tau} = \tau_{xy}$. In the three-dimensional case $y$ refers to the radial coordinate.
-
-To account for the added viscous stress due to $\eta_\text{s}$, equilibrium is reached at lower polymer stresses. Therefore, Oliveiras equation (7) needs to be modified as follows.
+Eliminating $\tau_{xy}$ yields the following.
+\begin{equation}
+	\exp\left(2\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xx} = 2\lambda\dot{\gamma}^2\eta_\text{p}
+\end{equation}
+This is solved by the Lambert $W$ function as follows.
+\begin{equation}
+	\tau_{xx} = \frac{\eta_\text{p}}{2\epsilon\lambda}W_0\left(4\epsilon\lambda^2\dot{\gamma}^2\right)
+\end{equation}
+With $\tau_{yy} = 0$ this yields the following.
+\begin{equation}
+	N_1 = \sigma_{xx} - \sigma_{yy} = \tau_{xx} = \frac{\eta_\text{p}}{2\epsilon\lambda}W_0\left(4\epsilon \mathrm{Wi}^2\right) %\label{eq:shearN}
+\end{equation}
+For the viscosity, we insert this into equation~(\ref{eq:PTTDerivation2}) and retrieve the following.
+\begin{align}
+	\eta &= \frac{\sigma_{xy}}{\dot{\gamma}} \\
+	&= \frac{\tau_{xy} + \eta_\text{s}\dot{\gamma}}{\dot{\gamma}} \\
+	&= \eta\left(\dot{\gamma}\right) = \frac{\eta_\text{p}}{\exp\left[0.5W_0\left(4\epsilon \mathrm{Wi}^2\right)\right]} + \eta_\text{s} %\label{eq:shearEta}
+\end{align}
+This gives the relevant solutions for the shear flow. For Poiseuille flow, we start with the Cauchy momentum equation (neglecting gravity), which reads as follows.
+\begin{equation}
+	\rho\frac{\Dif\vec{u}}{\Dif t} = -\nabla p + \nabla\cdot\sigma
+\end{equation}
+In steady state for this geometry, once integrated along $y$, this reduces to the following.
+\begin{equation}
+	\sigma_{xy} = \frac{\partial p}{\partial x}\frac{y}{2^j}
+\end{equation}
+Here $j$ is $0$ for the two-dimensional case and $1$ in the three-dimensional flow.
+The total stress experienced by the fluid is the one described by the constitutive equation plus the solvent contribution and thus the following holds.
 \begin{equation}
@@
 \end{equation}
-	Where the second term is added due to the presence of the solvent viscosity. This term also propagates to Oliveiras equation (9) as follows.
+Here we switched from y to writing $y$ to $r$ in order to clarify, that this is a radial coordinate being $0$ in the center of the channel for both cases.
+Dividing equation~(\ref{eq:PTTDerivation1}) by equation~(\ref{eq:PTTDerivation2}) leads to the following relation.
+\begin{equation}
+	\tau_{xx} = \frac{2\lambda}{\eta_\text{p}}\tau_{xy}^2 =  \frac{2\lambda}{\eta_\text{p}}\left(\partial_xp\frac{r}{2^j} - \eta_\text{s}\dot{\gamma}\right)^2
+\end{equation}
+Inserting this back into equation~(\ref{eq:PTTDerivation2}) yields the following.
 	\begin{align}
-		\dot{\gamma} &= f\left(\frac{2\lambda}{\eta_\text{p}}\left[\partial_xp\frac{r}{2^j} - \eta_\text{s}\dot{\gamma}\right]^2\right)\frac{1}{\eta_\text{p}}\left(\partial_xp\frac{r}{2^j}-\eta_\text{s}\dot{\gamma}\right)
+		\dot{\gamma} &= \exp\left(\frac{2\epsilon\lambda^2}{\eta_\text{p}^2}\left[\partial_xp\frac{r}{2^j} - \eta_\text{s}\dot{\gamma}\right]^2\right)\frac{1}{\eta_\text{p}}\left(\partial_xp\frac{r}{2^j}-\eta_\text{s}\dot{\gamma}\right)
 		\intertext{This cannot be integrated as easily as without $\eta_\text{s}$, and is only solvable semi-analytically.}
-		1 &= f\left(\frac{2\lambda}{\eta_\text{p}}\left[\partial_xp\frac{r}{2^j} - \eta_\text{s}\dot{\gamma}\right]^2\right)\frac{1}{\eta_\text{p}}\left(\partial_xp\frac{r}{2^j\dot{\gamma}}-\eta_\text{s}\right)
-	\end{align}
-	For the exponential version of PTT $f$ is defined as follows.
-	\begin{equation}
-		f\left(\Tr\ma{\tau}\right) = \exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)
-	\end{equation}
-	This can be inserted in the above equation.
-	\begin{align}
 		1 &= \exp\left(\frac{2\epsilon\lambda^2}{\eta_\text{p}^2}\left[\partial_xp\frac{r}{2^j} - \eta_\text{s}\dot{\gamma}\right]^2\right)\frac{1}{\eta_\text{p}}\left(\partial_xp\frac{r}{2^j\dot{\gamma}}-\eta_\text{s}\right) \\
@@
 	\end{align}
-	This can be solved using the Lambert W function as follows.
+	This can be solved using the Lambert $W$ function as follows.
 	\begin{align}

### 2024-02-21 NovelLBM.tex
answers

@@
 }\RK{Gupta is not specific in what he does but states to "optimize" $\eta_\text{s}$.
-I suspect an artificial increase but do not know}.\todo{reread gupta}
+I suspect an artificial increase but do not know}.
 Despite these improvements, however, none of these methods has been applied to very high viscosity ratio fluids which are often used as cell carrier fluids in lab experiments or technological applications.
@@
 Fitting these equations to the rheological data for alginate and methyl cellulose leads to satisfactory agreement as shown in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}.
-In the fit, the solvent viscosity was fixed at $\eta_\text{s} = \SI{1}{\milli\pascal\second}$ as the viscosity of the PBS buffer. \SG{ give ref }\todo{made it up}
+In the fit, the solvent viscosity was fixed at $\eta_\text{s} = \SI{1}{\milli\pascal\second}$ as the viscosity of the PBS buffer.
+\SG{ give ref }\RK{PBS is 99\% water.
+If you really want a citation tho we could use doi: 10.1063/1.4823586}
 %At very high shear rates, the contained polymers are completely stretched and the viscosity asymptotically approaches the solvent value $ \eta _ \mathrm{s}$.
@@
 		\caption{Parameters of the PTT model obtained by fitting to the rheological measurements in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}.
-		\SG{ add a column with $R_ \eta $ }}\RK{would be identical to the content of the $\eta_p$ column, also would be used before introduced}
+		\SG{ add a column with $R_ \eta $ }}\RK{would be identical to the content of the $\eta_p$ column, also would be used before introduced}\RK{names are not clear}
 		\label{tab:PTTparameters}
-	\end{table}\todo{names are fucked}
+	\end{table}
 
-We introduce the ratio between the zero-shear and the infinite-shear (i.e.\ solvent) viscosity as\todo{nope $\eta_p$ is not zero shear viscosity!}
+We introduce the ratio between the zero-shear and the infinite-shear (i.e.\ solvent) viscosity as\RK{nope $\eta_p$ is not zero shear viscosity!}
 \begin{align}
@@
 
-\SG{ make sure that all papers cited in the introduction as ''3D'' are discussed here as well }
-\SG{ and vice versa: make sure that all papers discussed here are also cited in the introduction }
+\SG{ make sure that all papers cited in the introduction as ''3D'' are discussed here as well }\RK{dellar is missing}
+\SG{ and vice versa: make sure that all papers discussed here are also cited in the introduction }\RK{gupta2015\_2 not in intro}
 Since the early days of LBM, variants for viscoelastic fluids have been developed.
@@
 Is it shear-thinning?
-}
+}\RK{not shear thinning in steady state as far as i know}
 More advanced approaches include the work of Onishi \textit{et al.} \cite{onishi2005, onishi2006} who considered a non-shear-thinning Oldroyd-B model using a microscopic Fokker-Planck equation for the polymer dumbbells.
@@
 To improve numerical stability, some authors propose the inclusion of an artificial diffusivity \cite{malaspinas2010,ma2020,wang2020,wang2021}, which introduces a small error compared to the analytical solution of the constitutive equation.
-Other remedies include special decompositions of the stress tensor\cite{dzanic2022} or optimization of the solvent contribution\cite{gupta2015} \SG{ rephrase and give some more details }.
+Other remedies include special decompositions of the stress tensor\cite{dzanic2022} or optimization of the solvent contribution\cite{gupta2015} \SG{ rephrase and give some more details }\RK{I have not the slightest clue what gupta is doing.
+I assume optimize is code for increase until stable but I do not know.}.
 Coupling of the resulting polymer stress to the Navier-Stokes LBM can be achieved via the inclusion of point forces or via a modification of the equilibrium populations.
-A recent comparison in 2D found that the former in general leads to better stability \cite{dzanic2022}.\todo{check}
+A recent comparison in 2D found that the former in general leads to better stability \cite{dzanic2022}.\RK{No in fact, it uses the latter and found to be more accurate than a paper using the former, stability was entirely attributed to the decomposition and artificial diffusivity.}
 
@@
 The core of the algorithm is implemented in OpenCL and thus capable of running on GPUs from different vendors.
-Boundaries are modeled using the half-way bounce back algorithm.
-\SG{ and inflow/outflow: give details }
+Non-periodic boundaries are modeled using the half-way bounce back algorithm.
+To model fixed inflow/outflow, bounce back boundaries using a Dirichlet boundary condition as described by Krüger \textit{et al.} \cite{Kruger_book} are used.
+\SG{ and inflow/outflow: give details }\RK{done}
 
@@
 
-To include the polymer stress into the LBM, we use the stress coupling scheme according to Dzanic et al. \cite{dzanic2022_2, gupta2015, onishi2006}.
+To include the polymer stress into the LBM, we use the stress coupling scheme according to Dzanic \textit{et al.} \cite{dzanic2022_2, gupta2015, onishi2006}.
 For this, ... \SG{ do we really do stress coupling? Above it said that force coupling is better? }\RK{yes, no idea why you said that}
-\SG{ give some more details, especially since we do SRT }.
-\SG{ also include inflow/outflow BCs }
-\SG{ do you advect polymer stress or polymer conformation? }\RK{A}
+\SG{ give some more details, especially since we do SRT }.\RK{what does this have to do with SRT?}
+\SG{ also include inflow/outflow BCs }\RK{done}
+\SG{ do you advect polymer stress or polymer conformation? }\RK{A, which is most similar to polymer conformation}
+To handle inflow/outflow boundaries, the polymer conformation tensor is specified on the boundary and advected using the corner transport upwind scheme.
 
@@
 \end{align}
-containing an arbitrary parameter $\alpha_\text{s}$. \SG{ is there an allowed range for $ \alpha _ \mathrm{s}$? }
+containing an arbitrary parameter $\alpha_\text{s}$.
+\SG{ is there an allowed range for $ \alpha _ \mathrm{s}$?
+}\RK{LBM viscosity should stay positive; While $\alpha_s > 1$ stops decreasing the polymer stress and increases it again it can still be sensible as the relation of the stresses will still drop (which is desirable)}
 Finally, this results in
@@
 For the viscosity shuffling, we set $\alpha_\text{s} = 1$.
-Along the flow direction, the channel is periodic, and the flow is driven by a pressure gradient of \SI{-1e7}{\pascal\per\meter}. \SG{ pressure for MC? }
+Along the flow direction, the channel is periodic, and the flow is driven by a pressure gradient of \SI{-1e7}{\pascal\per\meter} for alginate and  approximately \SI{-1.2e7}{\pascal\per\meter} for methyl cellulose.
+\SG{ pressure for MC?
+}\RK{done}
 \RK{
-	2D Param (MC) 12459373.981063413
-	3D Param (MC) 24918747.962126825
+	2D Param (MC) -12459373.981063413
+	3D Param (MC) -24918747.962126825
 	2D Alg -1e7
@@
 In the case of alginate, we speed up the convergence and start from a situation in which the polymers are pre-stretched \SG{ give details }\RK{initialized to the semianalytical solution}.
-After \SG{ XX } LBM time steps corresponding to \SG{ XX } of physical time, the simulation is stopped and the flow field $u(y)$ is compared to the semi-analytical solution.
+After \num{2e9} LBM time steps for alginate and \num{5e6} LBM time steps for methyl cellulose \SG{ XX }\RK{done} corresponding to approximately \SI{1.6}{\milli\second} and \SI{2.4}{\second} \SG{ XX }\RK{done} of physical time respectively, the simulation is stopped and the flow field $u(y)$ is compared to the semi-analytical solution.
 \RK{
@@
 As shown in figure~\ref{fig:2Dvel}, very good agreement is found.
-For a quantitative assessment, we compute the L2 error as \SG{ give correct equn. }
+For a quantitative assessment, we compute the L2 error as follows.
+\begin{equation}
+	e_\text{L2} = \sqrt{\frac{\sum_i\left[\vec{u_i} - \vec{u}\left(y_i\right)\right]^2}{\sum_i\vec{u}\left(y_i\right)^2}}
+\end{equation}
+\SG{ give correct equn. }\RK{done}
 
@@
 		\caption{(a) Velocity profile of alginate in planar channel flow. \SG{use $y$ instead of $r$ in 2D}\RK{done}.
-		The time evolution of the center-line velocity is shown in the inset \SG{ to do }.
+		The time evolution of the center-line velocity is shown in the inset \SG{ to do }\RK{you really want this?}.
 		(b) Velocity profile for methyl cellulose.
-		\SG{ make these plots for different $ \alpha _ \mathrm{s}$, either include here or put into appendix }}\RK{Why? Is identical down to fp32 precision (see appendix C)}
+		\SG{ make these plots for different $ \alpha _ \mathrm{s}$, either include here or put into appendix }\RK{Why? Is likely identical down to fp32 precision (see appendix C)}}
 		\label{fig:2Dvel}
-	\end{figure}\todo{maybe try if it is this identical for different $\alpha_s$ first}
+	\end{figure}
 
@@
 Numerically, the cylindrical situation is slightly more complex due to discretization errors ("staircase effect") when mapping the rounded channel walls onto the rectilinear LBM grid \cite{Lehmann.20229da}.
-We use the same material parameters as above, but double the pressure gradient to \SG{ XX }.
+We use the same material parameters as above, but double the pressure gradient to \SI{-2e7}{\pascal\per\meter} and approximately \SI{-2.5e7}{\pascal\per\meter} respectively\SG{ XX }\RK{done}.
 \SG{ why?
-} \RK{where analytical solutions exist in Poiseuille geometry the 3D solution differs from the 2D solution by a factor 2.
+} \RK{where analytical solutions exist in Poiseuille geometry the 3D solution differs from the 2D solution by a factor 2 (Due to the gradient of the stress in the derivation having a form in cylinder coordinates that can be solved by a factor 2).
 See the velocities in our sims being the same with this scaling}
@@
 		(b) Velocity profile for methyl cellulose.
-				\SG{ make these plots for different $ \alpha _ \mathrm{s}$, either include or put into Si }}
+				\SG{ make these plots for different $ \alpha _ \mathrm{s}$, either include or put into Si }\RK{Why? Is likely identical down to fp32 precision (see appendix C)}}
 		\label{fig:3Dvel}
-	\end{figure}\todo{see above}
+	\end{figure}
 
@@
 The Oldroyd-B model is a special case of the PTT model which is obtained by setting $\xi = \epsilon = 0$ in eq.~(\ref{eq:polymerStress}) and is thus easily tractable with our code.\RK{was simulated with a direct Oldroyd-B implementation, which I now see was unnecessary...}
-In figure~\ref{fig:malaspinas2010}, we show the L2 error as function of lattice resolution for different Weissenberg numbers $\mathrm{Wi}$ and \SG{ XX } $R_ \nu $.
+In figure~\ref{fig:malaspinas2010}, we show the L2 error as function of lattice resolution for different Weissenberg numbers $\mathrm{Wi}$ and \SG{ XX }\RK{It is a viscosity ratio, but I cannot name it like that for obvious reasons.} $R_ \nu $.
 To match with \cite{malaspinas2010}, we defined these as
@@
 with the kinematic solvent and the polymer viscosity $\nu_\text{s}$ and $\nu_\text{p}$ \SG{ ...
-}.
+}\RK{done}.
 \SG{ comment whether these definitions are identical or different than the definitions above.
 }\RK{different but can be transformed into each other $\frac{1}{R_\nu}-1=R_\eta$}
-Furthermore, in agreement with \cite{malaspinas2010}, also the L2 error is defined slightly differently than above, namely:\todo{slightly?}
+Furthermore, in agreement with \cite{malaspinas2010}, also the L2 error is defined slightly differently than above, namely:\RK{slightly?}
 	\begin{equation}\label{eq:l2error}
@@
 	\end{equation}
-\SG{ Beware equation 61 in the paper is wrong. It should have an 8 instead of the 4. Do you use equation 61? }
+\SG{ Beware equation 61 in the paper is wrong. It should have an 8 instead of the 4. Do you use equation 61? }\RK{was used for reproduction}
 
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/malaspinas2010.pdf}
-		\caption{L2 error as defined in equation \ref{eq:l2error} from Malaspinas et al.\cite{malaspinas2010} (dots) compared to our algorithm (x) as a function of grid resolution.
+		\caption{L2 error as defined in equation \ref{eq:l2error} from Malaspinas \textit{et al.}\cite{malaspinas2010} (dots) compared to our algorithm (x) as a function of grid resolution.
 		Blue and green crosses are not visible as they overlap exactly with the orange and red crosses, respectively, showing that the accuracy of our method is independent of $\mathrm{Wi}$ in the studied parameter range.}
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_tau.pdf}
-		\caption{Velocity profile (a) and shear stress (b) for methyl cellulose in a typical RT-DC geometry. \SG{ draw channel contour with black lines }
-		\SG{ change to von Mises instead of $ \tau _{ 12 }$? }}
+		\caption{Velocity profile (a) and shear stress (b) for methyl cellulose in a typical RT-DC geometry. \SG{ draw channel contour with black lines }\RK{done something else instead. Better?}
+		\SG{ change to von Mises instead of $ \tau _{ 12 }$? }}\RK{what plots do we want v, $\tau$, vM and $\eta$?; For nozzle as well?}
 		\label{fig:RT-DC}
@@
 These are particularly pronounced along the longest axis of the deformed cell.
-\SG{ connect to the ''viscoelastic wings'' paper \cite{Zhang.2020}}
+\SG{ connect to the ''viscoelastic wings'' paper \cite{Zhang.2020}}\RK{we have a sim with higher shear, this might be better here}
 
@@
 Data is agglomerated from 21 independent measurements.
-The first normal stress difference $N_1$ is calculated from the measured normal force using the following equation\cite{kulicke1977}.
+The first normal stress difference $N_1$ is calculated from the measured normal force using the following equation \cite{kulicke1977}.
 	\begin{equation}
@@
 \label{app:semianalyticalPoiseuille}
-\SG{ make a self-contained derivation which is understandable even without reading Oliveira \\}
-\SG{ use Gl.~(\ref{eq:polymerStress}) as starting point and end with Poiseuille solution, but also shear solution Gl.~(\ref{eq:shearN}, \ref{eq:shearEta}) \\}
-Our derivation is analogous to Oliveira\cite{oliveira1999}.
-
-For both Poiseuille flow and shear flow the following holds.
+\SG{ make a self-contained derivation which is understandable even without reading Oliveira \\}\RK{done}
+\SG{ use Gl.~(\ref{eq:polymerStress}) as starting point and end with Poiseuille solution, but also shear solution Gl.~(\ref{eq:shearN}, \ref{eq:shearEta}) \\}\RK{done}
+Our derivation is in principal similar to Oliveira \cite{oliveira1999}. For both Poiseuille flow and shear flow the following holds.
 \begin{equation}
@@
 \end{equation}
-With this the constitutive equation\todo{link} fo $\xi=0$ in steady state reduces to the following.
+With this the constitutive equation~(\ref{eq:polymerStress}) for $\xi=0$ in steady state reduces to the following.
 \begin{align}
@@
 This is guaranteed to contain all relevant radii.
-We flip the axis and integrate numerically using scipy.integrate.cumulative\_trapezoid\todo{cite}.
+We flip the axis and integrate numerically using \pyth{scipy.integrate.cumulative_trapezoid} \cite{scipy}.
 This is very accurate as we conveniently picked the spacing of our now $x$-axis in a way, that the $y$-axis ($\dot{\gamma}$) varies little for each step.

### 2024-02-21 assets/python/fig:malaspinas2010.py

@@ -104,8 +104,8 @@ plt.xticks(
     ],
     minor=True,
 )
-plt.xlabel("N")
-plt.ylabel("L2 error")
+plt.xlabel(r"$N$")
+plt.ylabel(r"$E_u$")
 plt.legend(loc="center left", bbox_to_anchor=(1, 0.5))
 plt.savefig("../plots/malaspinas2010.pdf", bbox_inches="tight", pad_inches=0)
 plt.show()

### 2024-02-21 NovelLBM.tex
clarify

@@
 which will turn out to be an important parameter to determine numerical stability of LB simulations.
-\SG{ wo don't actually show that $R_ \eta  $ determines stability? }\RK{we do not. We could do a plot with $\alpha_s$ decreasing until the sim breaks if you want}
+\SG{ wo don't actually show that $R_ \eta  $ determines stability? }\RK{we do not. We could do a few simulations with $\alpha_s = 0$ and increasing $R_\eta$ until the sim breaks if you want}
 This ratio can similarly be defined for other models such as FENE-P or the inelastic, but shear-thinning Carreau-Yasuda model \cite{carreau1972, yasuda1979}.
@@
 These are particularly pronounced along the longest axis of the deformed cell.
-\SG{ connect to the ''viscoelastic wings'' paper \cite{Zhang.2020}}\RK{we have a sim with higher shear, this might be better here}
+\SG{ connect to the ''viscoelastic wings'' paper \cite{Zhang.2020}}\RK{Our "wings" look very different}
 

### 2024-02-22 assets/python/fig:Nozzle.py
Nozzle & RT-DC plots

@@ -37,17 +37,17 @@ def process():
     p0 = rho0 * V0**2
 
     cFile = cDir / "CT_5000000.vtk"
-    # sFile = sDir / "S_500000.vtk"
+    sFile = sDir / "S_500000.vtk"
     vFile = vDir / "u_5000000.vtk"
 
     data = pv.read(cFile)
-    # dataS = pv.read(sFile)
+    dataS = pv.read(sFile)
     dataV = pv.read(vFile)
     Lx, Ly, Lz = dataV.dimensions
     tauField = data.get_array("data") * PTT.mc0_49.eta_p / PTT.mc0_49.lambda_p
     tauField = np.reshape(tauField, (Lx, Ly, Lz, 6), "F")
-    # sField = dataS.get_array("data") / T0
-    # sField = np.reshape(sField, (Lx, Ly, Lz, 6), "F")
+    sField = dataS.get_array("data") / T0
+    sField = np.reshape(sField, (Lx, Ly, Lz, 6), "F")
     vField = dataV.get_array("data") * V0
     vField = np.reshape(vField, (Lx, Ly, Lz, 3), "F")
 
@@ -90,11 +90,28 @@ def process():
 
         vonMieses = ma.masked_array(vonMieses, mask=mask)
 
+    if True:
+        mask = np.zeros(tauField.shape)
+
+        for x in range(Lx):
+            localR = (10.5 - 94.5) / (Lx - 3) * (x - 1) + 94.5
+            for y in range(Ly):
+                for z in range(Lz):
+                    if np.hypot(y - (Ly / 2.0) + 0.5, z - (Lz / 2.0) + 0.5) >= localR + 0.5:
+                        for i in range(6):
+                            mask[x, y, z, i] = 1
+
+        tauField = ma.masked_array(tauField, mask=mask)
+
     vonMiesesSlice = vonMieses[..., Lz // 2]
 
-    # tau12 = tauField[..., Lz // 2, 3]
-    # D12 = sField[..., Lz // 2, 3]
-    # eta = tau12 / D12 / 2 + 1e-3
+    tau12 = tauField[..., Lz // 2, 3]
+    D12 = sField[..., Lz // 2, 3]
+    eta = tau12 / D12 / 2 + PTT.mc0_49.eta_s
+
+    mask = np.zeros(eta.shape)
[…]

### 2024-02-22 assets/python/fig:RT-DC.py

@@ -16,6 +16,7 @@ import numpy as np
 import numpy.ma as ma
 import pyvista as pv
 
+from fluidx3d.eval.models import PTT
 from fluidx3d.eval.style import cm
 
 
@@ -59,7 +60,21 @@ def process():
     vField = dataV.get_array("data") * V0
     vField = np.reshape(vField, (Lx, Ly, Lz, 3), "F")
 
+    deviator = [[0] * 3] * 3
+    idx = [[0, 3, 5], [3, 1, 4], [5, 4, 2]]
+
+    vonMieses = np.zeros((Lx, Ly, Lz))
+    for i in range(3):
+        for j in range(3):
+            deviator[i][j] = tauField[..., idx[i][j]] - (
+                np.sum(tauField[..., :3], axis=-1) / 3 if idx[i][j] < 3 else 0  # Assume correct?
+            )
+
+            vonMieses += 3 / 2 * deviator[i][j] * deviator[i][j]
+    vonMieses = np.sqrt(vonMieses)
+
     if True:
+        maskvM = np.zeros(vonMieses.shape)
         mask = np.zeros(vField.shape)
         mask2 = np.zeros(tauField.shape)
         width = 30
@@ -71,6 +86,7 @@ def process():
                 for z in range(Lz):
                     if x < padding:
                         if y == 0 or y == Ly - 1 or z == 0 or z == Lz - 1:
+                            maskvM[x, y, z] = 1
                             for i in range(3):
                                 mask[x, y, z, i] = 1
                                 mask2[x, y, z, 2 * i] = 1
@@ -82,12 +98,14 @@ def process():
                             or z == 0
                             or z == Lz - 1
                         ):
+                            maskvM[x, y, z] = 1
                             for i in range(3):
                                 mask[x, y, z, i] = 1
                                 mask2[x, y, z, 2 * i] = 1
                                 mask2[x, y, z, 2 * i + 1] = 1
                     elif x < padding + width + length:
                         if y < width + 1 or y >= 2 * width + 1 or z == 0 or z == Lz - 1:
+                            maskvM[x, y, z] = 1
                             for i in range(3):
[…]

### 2024-02-22 assets/python/fig:iDAlginate_timeEvolution.py
time evolution plots

@@ -1,0 +1,55 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the  class.
+
+Created on Tue Sep  5 10:51:20 2023
+
+@author: Richard Kellnberger
+"""
+
+import json
+from pathlib import Path
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pyvista as pv
+
+from style import cm
+
+
+def process(idx):
+    baseDir = Path(f"../data/novel_2024-01-15/{idx}/")
+    vDir = baseDir / "vtkfiles/velocity/"
+    jsonFile = baseDir / "parameters.json"
+    f = open(jsonFile)
+    parameters = json.load(f)
+    f.close()
+
+    V0 = parameters["info"]["conversions"]["V0"]
+    L0 = parameters["info"]["conversions"]["L0"]
+    T0 = parameters["info"]["conversions"]["T0"]
+
+    vs = []
+
+    for i in range(4001):
+        vFile = vDir / f"u_{500000*i}.vtk"
+
+        dataV = pv.read(vFile)
+        Lx, Ly, Lz = dataV.dimensions
+        vField = dataV.get_array("data") * V0
+        vField = np.reshape(vField, (Lx, Ly, Lz, 3), "F")
+
+        vs.append(vField[Lx // 2, Ly // 2, Lz // 2, 0])
+
+    plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+    plt.title("(a)", loc="left")
+    plt.plot(np.arange(4001) * 500000 * T0 * 1e3, np.asarray(vs) * 1e6)
+    plt.xlabel(r"$t/\unit{\milli\second}$")
+    plt.ylabel(r"$u_\text{x}/\unit{\micro\meter\per\second}$")
+    plt.savefig(f"../plots/{idx+2}DAlginate_timeEvolution.pdf", bbox_inches="tight", pad_inches=0)
+    plt.show()
+
+
+if __name__ == "__main__":
+    process(0)
+    process(1)

### 2024-02-22 assets/python/fig:iDMC_timeEvolution.py

@@ -1,0 +1,55 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the  class.
+
+Created on Tue Sep  5 10:51:20 2023
+
+@author: Richard Kellnberger
+"""
+
+import json
+from pathlib import Path
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pyvista as pv
+
+from style import cm
+
+
+def process(idx):
+    baseDir = Path(f"../data/{idx}DParameterStudy/7/")
+    vDir = baseDir / "vtkfiles/velocity/"
+    jsonFile = baseDir / "parameters.json"
+    f = open(jsonFile)
+    parameters = json.load(f)
+    f.close()
+
+    V0 = parameters["info"]["conversions"]["V0"]
+    L0 = parameters["info"]["conversions"]["L0"]
+    T0 = parameters["info"]["conversions"]["T0"]
+
+    vs = []
+
+    for i in range(101):
+        vFile = vDir / f"u_{50000*i}.vtk"
+
+        dataV = pv.read(vFile)
+        Lx, Ly, Lz = dataV.dimensions
+        vField = dataV.get_array("data") * V0
+        vField = np.reshape(vField, (Lx, Ly, Lz, 3), "F")
+
+        vs.append(vField[Lx // 2, Ly // 2, Lz // 2, 0])
+
+    plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+    plt.title("(b)", loc="left")
+    plt.plot(np.arange(101) * 50000 * T0 * 1e3, np.asarray(vs))
+    plt.xlabel(r"$t/\unit{\milli\second}$")
+    plt.ylabel(r"$u_\text{x}/\unit{\meter\per\second}$")
+    plt.savefig(f"../plots/{idx}DMC_timeEvolution.pdf", bbox_inches="tight", pad_inches=0)
+    plt.show()
+
+
+if __name__ == "__main__":
+    process(2)
+    process(3)

### 2024-02-22 NovelLBM.tex
workaround closes #7 closes #8

@@
 	\definecolor{secondaryBackground}{RGB}{195,195,195} % Because i can lol
+\fi
+
+% Workaround we have to use because some people cannot be expected to update their packages more often than once a decade
+% https://tex.stackexchange.com/a/612592
+% This is technically licenced under CC BY-SA 4.0
+\ifdefined\qty\else
+\ifdefined\NewCommandCopy
+\NewCommandCopy\qty\SI
+\else
+\NewDocumentCommand\qty{O{}mm}{\SI[#1]{#2}{#3}}
+\fi
+\fi
+\ifdefined\unit\else
+\ifdefined\NewCommandCopy
+\NewCommandCopy\unit\si
+\else
+\NewDocumentCommand\unit{O{}m}{\si[#1]{#2}}
+\fi
 \fi
@@
 	Alg 2e9 1.6455647956111251 ms (reveals the sim to be a scam)
-	MC 5e6 2.439024390243903 s
+	MC 5e6 10.065719379854297 ms
 }

### 2024-02-23 NovelLBM.tex
Removed many comments

@@
 \title{Novel lattice Boltzmann method for simulation of strongly shear thinning viscoelastic fluids}
-\author{Richard Kellnberger$^1$}
+\author{Richard Kellnberger$^1$, Tomasz Jüngst$^2$, Stephan Gekle$^1$}
 \date{January, 2024}
@@
 		$^1$ Biofluid Simulation and Modeling – Theoretische Physik VI, University of Bayreuth, Bayreuth, Germany
+		$^2$ FMZ
 	\end{center}
@@
 Our technique is based on the insight that stability issues in traditional viscoelastic LBMs arise due to an imbalance between the very large polymer stress and the much smaller viscous stress of the solvent.
-We overcome this issue by including ("shuffling") part of the polymer stress into the viscous part of the LBM algorithm.\RK{moving instead of including?}
+We overcome this issue by moving ("shuffling") part of the polymer stress into the viscous part of the LBM algorithm.
 
@@
 		\caption{Rheology data for alginate solution from 21 measurements of the viscosity (a) and normal stress (b).
-				Orange lines show a fit of the PTT rheological model. \SG{ larger font in figures }\RK{done}}
+				Orange lines show a fit of the PTT rheological model. }
 		\label{fig:fit_alginate}
@@
 		\caption{The viscosity (a) and normal stress (b) of a methyl cellulose solution from \cite{buyukurganci2023}.
-				Lines show a fit of the PTT rheological model. \SG{ include legend into figure. Maybe give color coding only in caption? }\RK{Done}\SG{ larger font in figures }\RK{done}}
+				Lines show a fit of the PTT rheological model. }
 		\label{fig:fit_mc}
@@
 %Although the FENE-P does reproduce shear-thinning, we were not able to obtain a satisfactory fit to our data for alginate and methyl cellulose with physically reasonable values of the model parameters.
-A good fit to our data was obtained with the so-called PTT model due to Phan-Thien and Tanner \cite{phan-thien1977,phan-thien1978} which has been developed explicitly for polymer networks in solution and thus appears to capture well the essential physics behind the alginate and methyl cellulose solutions.\RK{due to sounds bad}
+A good fit to our data was obtained with the so-called PTT model by Phan-Thien and Tanner \cite{phan-thien1977,phan-thien1978} which has been developed explicitly for polymer networks in solution and thus appears to capture well the essential physics behind the alginate and methyl cellulose solutions.
 
@@
 where $\ma{D}$ is the strain rate tensor.
-\SG{ check that PTT is given in this form in \cite{phan-thien1977,phan-thien1978} or cite other source }\RK{The given form is most similar to \cite{ferras2019}, which you removed?}
+We note that extended forms of the PTT model with a Mittag-Leffler instead of an exponential function have been studied as well \cite{ferras2019}.
 The polymer viscosity is denoted $\eta_\text{p}$ and $\lambda$ is the corresponding relaxation time.
@@
 In the fit, the solvent viscosity was fixed at $\eta_\text{s} = \SI{1}{\milli\pascal\second}$ as the viscosity of the PBS buffer. 
-\SG{ give ref }\RK{PBS is 99\% water.
-If you really want a citation tho we could use doi: 10.1063/1.4823586}
+%\SG{ give ref }\RK{PBS is 99\% water. If you really want a citation tho we could use doi: 10.1063/1.4823586} \SG{ ok, let's leave it out. }
 %At very high shear rates, the contained polymers are completely stretched and the viscosity asymptotically approaches the solvent value $ \eta _ \mathrm{s}$.
@@
 		\centering
-		\begin{tabular}{c|c|c|c}
-			Fluid & $\eta_\text{p}/\unit{\milli\pascal\second}$ & $\lambda/\unit{\milli\second}$ & $\epsilon$ \\
+		\begin{tabular}{c|c|c|c|c}
+			Fluid & $\eta_\text{p}/\unit{\milli\pascal\second}$ & $\lambda/\unit{\milli\second}$ & $\epsilon$ & $R_ \eta $\\
 			\hline
-			alginate \num{4} & \num{48.2\pm0.4e3} & \num{343 \pm 4} & \num{0.545 \pm 0.010} \\
-			methyl c. \num{0.49} & \num{18.7\pm0.4} & \num{0.344\pm0.003} & \num{0.270\pm0.003} \\
-			methyl c. \num{0.59} & \num{32.5\pm0.7} & \num{0.433\pm0.004} & \num{0.365\pm0.004} \\
-			methyl c. \num{0.83} & \num{81\pm2} & \num{0.714\pm0.009} & \num{0.496\pm0.006}
+			alginate \num{4}\% & \num{48.2\pm0.4e3} & \num{343 \pm 4} & \num{0.545 \pm 0.010} & $4.8 \times 10 ^{ 4 }$\\
+			methyl c. \num{0.49}\% & \num{18.7\pm0.4} & \num{0.344\pm0.003} & \num{0.270\pm0.003} & 18.7\\
+			methyl c. \num{0.59}\% & \num{32.5\pm0.7} & \num{0.433\pm0.004} & \num{0.365\pm0.004} & 32.5\\
+			methyl c. \num{0.83}\% & \num{81\pm2} & \num{0.714\pm0.009} & \num{0.496\pm0.006} & 81
 		\end{tabular}
 		\caption{Parameters of the PTT model obtained by fitting to the rheological measurements in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}.
-		\SG{ add a column with $R_ \eta $ }}\RK{would be identical to the content of the $\eta_p$ column, also would be used before introduced}\RK{names are not clear}
+		\SG{ add a column with $R_ \eta $ }}\RK{would be identical to the content of the $\eta_p$ column, also would be used before introduced} \SG{ Stimmt, aber ich will es auf einen Blick sichtbar machen }
 		\label{tab:PTTparameters}
@@
 
-We introduce the ratio between the zero-shear and the infinite-shear (i.e.\ solvent) viscosity as\RK{nope $\eta_p$ is not zero shear viscosity!}
+We introduce the ratio between the polymer and the solvent viscosity as
 \begin{align}
@@
 which will turn out to be an important parameter to determine numerical stability of LB simulations.
-\SG{ wo don't actually show that $R_ \eta  $ determines stability? }\RK{we do not. We could do a few simulations with $\alpha_s = 0$ and increasing $R_\eta$ until the sim breaks if you want}
+\SG{ wo don't actually show that $R_ \eta  $ determines stability?
+}\RK{we do not.
+We could do a few simulations with $\alpha_s = 0$ and increasing $R_\eta$ until the sim breaks if you want} \SG{ wie besprochen, bau einfach die Zitate ein, das reicht dann.
+}
 This ratio can similarly be defined for other models such as FENE-P or the inelastic, but shear-thinning Carreau-Yasuda model \cite{carreau1972, yasuda1979}.
@@
 \SG{ make sure that all papers cited in the introduction as ''3D'' are discussed here as well }\RK{dellar is missing}
-\SG{ and vice versa: make sure that all papers discussed here are also cited in the introduction }\RK{gupta2015\_2 not in intro}
+\SG{ and vice versa: make sure that all papers discussed here are also cited in the introduction }\RK{gupta2015\_2 not in intro} \SG{ dann setz einfach die Zitate so rein, wie du sie fuer passend haeltst.
+}
 Since the early days of LBM, variants for viscoelastic fluids have been developed.
 Keeping in mind our target geometries, we focus here on three-dimensional formulations.
-The first approaches avoided an explicit modeling of a viscoelastic constitutive equation and simply modified the LB collision operator to obtain a fluid obeying Jeffery's viscoelastic model \cite{lallemand2003}.
-\SG{ can we say more about Jeffery?
-Why is it bad?
-Is it shear-thinning?
-}\RK{not shear thinning in steady state as far as i know}
+The first approaches avoided an explicit modeling of a viscoelastic constitutive equation and simply modified the LB collision operator to obtain a basic viscoelastic fluid obeying Jeffery's model \cite{lallemand2003}.
 More advanced approaches include the work of Onishi \textit{et al.} \cite{onishi2005, onishi2006} who considered a non-shear-thinning Oldroyd-B model using a microscopic Fokker-Planck equation for the polymer dumbbells.
@@
 Coupling of the resulting polymer stress to the Navier-Stokes LBM can be achieved via the inclusion of point forces or via a modification of the equilibrium populations.
-A recent comparison in 2D found that the former in general leads to better stability \cite{dzanic2022}.\RK{No in fact, it uses the latter and found to be more accurate than a paper using the former, stability was entirely attributed to the decomposition and artificial diffusivity.}
+A recent comparison in 2D found that the former in general leads to better stability \cite{dzanic2022_2}.\RK{No in fact, it uses the latter and found to be more accurate than a paper using the former, stability was entirely attributed to the decomposition and artificial diffusivity.} \SG{ die Referenz war falsch, es war der andere Dzanic.
+Aber da steht eigentlich schon, dass forcing besser sei, oder?
+}
 
@@
 To model fixed inflow/outflow, bounce back boundaries using a Dirichlet boundary condition as described by Krüger \textit{et al.} \cite{Kruger_book} are used.
-\SG{ and inflow/outflow: give details }\RK{done}
 
@@
 We start by simulating the alginate and \SI{0.49}{\percent} methyl cellulose solutions with a viscosity ratio $R_\eta = \num{48.2e3}$ and $R_\eta = \num{18.7}$, respectively, in 2D planar Poiseuille flow.
-In physical units the channel has a height of \SI{20}{\micro\meter} which are discretized with 41 \SG{ XX }\RK{pipe is 41 box is 43} LBM nodes.
+In physical units the channel has a height of \SI{20}{\micro\meter} which are discretized with 41 LBM nodes.
 For the viscosity shuffling, we set $\alpha_\text{s} = 1$.
 Along the flow direction, the channel is periodic, and the flow is driven by a pressure gradient of \SI{-1e7}{\pascal\per\meter} for alginate and  approximately \SI{-1.2e7}{\pascal\per\meter} for methyl cellulose.
-\SG{ pressure for MC?
-}\RK{done}
-\RK{
-	2D Param (MC) -12459373.981063413
-	3D Param (MC) -24918747.962126825
-	2D Alg -1e7
-	3D Alg -2e7
-}
 The velocity field is initialized with zero.
 For methyl cellulose, we simulate the full temporal evolution with the polymers starting in the unstretched configuration.
-In the case of alginate, we speed up the convergence and start from a situation in which the polymers are pre-stretched \SG{ give details }\RK{initialized to the semianalytical solution}.
-After \num{2e9} LBM time steps for alginate and \num{5e6} LBM time steps for methyl cellulose \SG{ XX }\RK{done} corresponding to approximately \SI{1.6}{\milli\second} and \SI{2.4}{\second} \SG{ XX }\RK{done} of physical time respectively, the simulation is stopped and the flow field $u(y)$ is compared to the semi-analytical solution.
-\RK{
-	Alg 2e9 1.6455647956111251 ms (reveals the sim to be a scam)
-	MC 5e6 10.065719379854297 ms
-}
+In the case of alginate, we speed up the convergence and start from a situation in which the polymers are pre-stretched \SG{ give details }\RK{initialized to the semianalytical solution} \SG{ schreib am besten eine Referenz auf die Gleichung hin, muesste ja im Appendix stehen.
+}.
+After \num{2e9} LBM time steps for alginate and \num{5e6} LBM time steps for methyl cellulose corresponding to approximately \SI{1.6}{\milli\second} and \SI{2.4}{\second} of physical time, respectively, the simulation is stopped and the flow field $u(y)$ is compared to the semi-analytical solution.
+%\RK{
+%	Alg 2e9 1.6455647956111251 ms (reveals the sim to be a scam)
+%	MC 5e6 10.065719379854297 ms
+%}
 As shown in figure~\ref{fig:2Dvel}, very good agreement is found.
@@
 \end{equation}
-\SG{ give correct equn. }\RK{done}
 
 The spatially resolved errors are shown in figure~\ref{fig:2DvelErr} in the appendix.
-Averaging over the channel diameter, we obtain an L2 error of \num{9e-4} and \num{1e-3}\SG{ XX }\RK{done}\RK{we do not "average" over the diameter, we calculate the L2 error along the diameter} for alginate and methyl cellulose, respectively.
+Averaging over the channel diameter, we obtain an L2 error of \num{9e-4} and \num{1e-3}\RK{we do not "average" over the diameter, we calculate the L2 error along the diameter} for alginate and methyl cellulose, respectively.
 These conclusions remain robust even when varying the pressure gradient, and thus the flow velocity, over many orders of magnitude as shown in figure~\ref{fig:pressureErr}~(a) of the appendix.\RK{This is the worst case error for MC and it is tiny "remain robust" is too weak here}
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyUWorst.pdf}
-		\caption{(a) Velocity profile of alginate in planar channel flow. \SG{use $y$ instead of $r$ in 2D}\RK{done}.
+		\caption{(a) Velocity profile of alginate in planar channel flow. 
 		The time evolution of the center-line velocity is shown in the inset \SG{ to do }\RK{you really want this?}.
@@
 Numerically, the cylindrical situation is slightly more complex due to discretization errors ("staircase effect") when mapping the rounded channel walls onto the rectilinear LBM grid \cite{Lehmann.20229da}.
-We use the same material parameters as above, but double the pressure gradient to \SI{-2e7}{\pascal\per\meter} and approximately \SI{-2.5e7}{\pascal\per\meter} respectively\SG{ XX }\RK{done}.
+We use the same material parameters as above, but double the pressure gradient to \SI{-2e7}{\pascal\per\meter} and approximately \SI{-2.5e7}{\pascal\per\meter} respectively.
 \SG{ why?
@@
 See the velocities in our sims being the same with this scaling}
-The channel has a diameter of \SI{20}{\micro\meter}\SG{ XX }\RK{done} and is discretized with 41 lattice points.
+The channel has a diameter of \SI{20}{\micro\meter} and is discretized with 41 lattice points.
 Again, we initialize the polymers in the unstretched state for methyl cellulose and in the stretched state for alginate.
-The resulting velocity profile can be seen in figure~\ref{fig:3Dvel} and shows almost equally good agreement as for the planar case with an L2 error of \num{0.014} and \num{0.06}\SG{ XX }\RK{done}, respectively.
+The resulting velocity profile can be seen in figure~\ref{fig:3Dvel} and shows almost equally good agreement as for the planar case with an L2 error of \num{0.014} and \num{0.06}, respectively.
 The spatially resolved error in figure~\ref{fig:3DvelErr} of the appendix shows that this larger average is indeed mainly attributable to the staircase effect as the error near the walls increases significantly.
@@
 The authors studied an Oldroyd-B fluid in a planar Poiseuille flow and compared the error in the simulated velocity profile to an exact analytical solution.
-The Oldroyd-B model is a special case of the PTT model which is obtained by setting $\xi = \epsilon = 0$ in eq.~(\ref{eq:polymerStress}) and is thus easily tractable with our code.\RK{was simulated with a direct Oldroyd-B implementation, which I now see was unnecessary...}
-In figure~\ref{fig:malaspinas2010}, we show the L2 error as function of lattice resolution for different Weissenberg numbers $\mathrm{Wi}$ and \SG{ XX }\RK{It is a viscosity ratio, but I cannot name it like that for obvious reasons.} $R_ \nu $.
-To match with \cite{malaspinas2010}, we defined these as
+The Oldroyd-B model is a special case of the PTT model which is obtained by setting $\xi = \epsilon = 0$ in eq.~(\ref{eq:polymerStress}) and is thus easily tractable with our code.\RK{was simulated with a direct Oldroyd-B implementation, which I now see was unnecessary...} \SG{ hast du mal kurz geprueft, ob dasselbe rauskommt?
+}
+In figure~\ref{fig:malaspinas2010}, we show the L2 error as function of lattice resolution for different values of $\mathrm{Wi}$ and $R_ \nu $ which is defined as \cite{malaspinas2010}
 \begin{align}
@@
 \end{align}
-with the kinematic solvent and the polymer viscosity $\nu_\text{s}$ and $\nu_\text{p}$ \SG{ ...
-}\RK{done}.
+with the kinematic solvent and the polymer viscosity $\nu_\text{s}$ and $\nu_\text{p}$.
 \SG{ comment whether these definitions are identical or different than the definitions above.
 }\RK{different but can be transformed into each other $\frac{1}{R_\nu}-1=R_\eta$}
-Furthermore, in agreement with \cite{malaspinas2010}, also the L2 error is defined slightly differently than above, namely:\RK{slightly?}
+Furthermore, in agreement with \cite{malaspinas2010}, also the L2 error is defined differently than above, namely:
 	\begin{equation}\label{eq:l2error}
@@
 	\end{equation}
-\SG{ Beware equation 61 in the paper is wrong. It should have an 8 instead of the 4. Do you use equation 61? }\RK{was used for reproduction}
+At this point, we mention that there is a typographic mistake in eq.~(61) of \cite{malaspinas2010} where the prefactor should 8 instead of 4. \SG{ stimmt das so? }
 
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/Nozzle_sigma_vM.pdf}
-		\caption{Velocity profile (a) and von Mises stress (b) for methyl cellulose in a conical nozzle as used for bioprinting. \SG{ draw nozzle contour with black lines }}\RK{Done}
+		\caption{Velocity profile (a) and von Mises stress (b) for methyl cellulose in a conical nozzle as used for bioprinting.}
 		\label{fig:Nozzle_v}
@@
 For simplicity, we consider the viscoelastic fluid inside and outside the cell to be identical.
-The cell is initially spherical with a radius of \SI{6}{\micro\meter} and possesses a Youngs modulus of \SI{100}{\pascal} and a Poisson ratio of \num{0.48}\SG{ XX }\RK{done}.
+The cell is initially spherical with a radius of \SI{6}{\micro\meter} and possesses a Youngs modulus of \SI{100}{\pascal} and a Poisson ratio of \num{0.48}.
 It is placed into a shear flow with a shear rate of \SI{400}{\per\second} where the cell quickly reaches a steady state in which it deforms into a tank-treading ellipsoid.
 This is in qualitative agreement with simulations \cite{Mueller.2021} and classical theories \cite{Roscoe.1967}.
-For the discretization of the cell we use \num{5179}\SG{ xx }\RK{done} tetrahedrons and a radius of 6\SG{ xx }\RK{done} lattice units.
+For the discretization of the cell we use \num{5179} tetrahedrons and a radius of 6 lattice units.
 The lattice with a resolution of \num{100} lattice points is chosen significantly larger than the cell to assure negligible impact of the walls.
@@
 As additional quantitative validation, we simulate a pure shear flow driven by imposing a fixed velocity at the top and bottom of the computational box and using periodic boundary conditions in the other two directions.
-The box dimension is 2x43x2\SG{ xx }\RK{done}.
+The box dimension is 2x43x2.
 We use PTT with the methyl cellulose parameters and vary the shear rate to cover the full range starting from the zero-shear all the way to the infinite-shear plateau displayed in figure~\ref{fig:fit_mc} of the main text.

### 2024-02-26 NovelLBM.tex
upload log files

@@
 		\caption{Rheology data for alginate solution from 21 measurements of the viscosity (a) and normal stress (b).
-				Orange lines show a fit of the PTT rheological model. }
+				Orange lines show a fit of the PTT rheological model.}
 		\label{fig:fit_alginate}
@@
 		\caption{The viscosity (a) and normal stress (b) of a methyl cellulose solution from \cite{buyukurganci2023}.
-				Lines show a fit of the PTT rheological model. }
+				Lines show a fit of the PTT rheological model.}
 		\label{fig:fit_mc}
@@
 where $\ma{D}$ is the strain rate tensor.
-We note that extended forms of the PTT model with a Mittag-Leffler instead of an exponential function have been studied as well \cite{ferras2019}.
+We note that extended forms of the PTT model with a Mittag-Leffler instead of an exponential function have been studied as well \cite{ferras2019}\todo{not really what we want to say here.
+We took this formula mostly from there}.
 The polymer viscosity is denoted $\eta_\text{p}$ and $\lambda$ is the corresponding relaxation time.
@@
 		\begin{tabular}{c|c|c|c|c}
-			Fluid & $\eta_\text{p}/\unit{\milli\pascal\second}$ & $\lambda/\unit{\milli\second}$ & $\epsilon$ & $R_ \eta $\\
+			Fluid & $\eta_\text{p}/\unit{\milli\pascal\second}$ & $\lambda/\unit{\milli\second}$ & $\epsilon$ & $R_\eta$ \\
 			\hline
-			alginate \num{4}\% & \num{48.2\pm0.4e3} & \num{343 \pm 4} & \num{0.545 \pm 0.010} & $4.8 \times 10 ^{ 4 }$\\
-			methyl c. \num{0.49}\% & \num{18.7\pm0.4} & \num{0.344\pm0.003} & \num{0.270\pm0.003} & 18.7\\
-			methyl c. \num{0.59}\% & \num{32.5\pm0.7} & \num{0.433\pm0.004} & \num{0.365\pm0.004} & 32.5\\
-			methyl c. \num{0.83}\% & \num{81\pm2} & \num{0.714\pm0.009} & \num{0.496\pm0.006} & 81
+			alginate \SI{4}{\percent} & \num{48.2\pm0.4e3} & \num{343 \pm 4} & \num{0.545 \pm 0.010} & \num{4.8e4} \\
+			methyl c. \SI{0.49}{\percent} & \num{18.7\pm0.4} & \num{0.344\pm0.003} & \num{0.270\pm0.003} & \num{18.7} \\
+			methyl c. \SI{0.59}{\percent} & \num{32.5\pm0.7} & \num{0.433\pm0.004} & \num{0.365\pm0.004} & \num{32.5} \\
+			methyl c. \SI{0.83}{\percent} & \num{81\pm2} & \num{0.714\pm0.009} & \num{0.496\pm0.006} & \num{81}
 		\end{tabular}
 		\caption{Parameters of the PTT model obtained by fitting to the rheological measurements in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}.
-		\SG{ add a column with $R_ \eta $ }}\RK{would be identical to the content of the $\eta_p$ column, also would be used before introduced} \SG{ Stimmt, aber ich will es auf einen Blick sichtbar machen }
+		\SG{ add a column with $R_ \eta $ }}\RK{would be identical to the content of the $\eta_p$ column, also $R_\eta$ would be used before introduced} \SG{ Stimmt, aber ich will es auf einen Blick sichtbar machen }
 		\label{tab:PTTparameters}
@@
 \begin{align}
-	R_\eta = \frac{\eta_\text{p}}{\eta_\text{s}}		\label{eq:R_eta}
+	R_\eta = \frac{\eta_\text{p}}{\eta_\text{s}} = \frac{\eta_0-\eta_\infty}{\eta_\infty}		\label{eq:R_eta}
 \end{align}
@@
 We could do a few simulations with $\alpha_s = 0$ and increasing $R_\eta$ until the sim breaks if you want} \SG{ wie besprochen, bau einfach die Zitate ein, das reicht dann.
-}
-This ratio can similarly be defined for other models such as FENE-P or the inelastic, but shear-thinning Carreau-Yasuda model \cite{carreau1972, yasuda1979}.
+}\todo{do}
+This ratio can similarly be defined for other models such as FENE-P or the inelastic, but shear-thinning Carreau-Yasuda model \cite{carreau1972, yasuda1979} using the zero-shear viscosity $\eta_0$ and the infinite-shear viscosity $\eta_\infty$.
 For our alginate solution we obtain $R_\eta = \num{48.2\pm0.4e3}$, indicating that the solution viscosity at very low shear rates is more than four orders of magnitude larger than the solvent viscosity which represents a severe challenge to standard numerical algorithms.
@@
 	\centering
-		\begin{tabular}{l|p{3cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{2cm}}
+		\begin{tabular}{l|p{3cm}|p{1.6cm}|p{1.6cm}|p{1.6cm}|p{2cm}}
 			Author & Material & $\eta_0/\unit{\pascal\second}$ & $\eta_\infty/\unit{\pascal\second}$ & $R_\eta$ & extracted from \\
 			\hline
-			Amorim\cite{amorim2021} & pre-crosslinked alginate &  >1e4 & <3e-1 & >3e4 & Fig. 3b \\
+			Amorim\cite{amorim2021} & pre-crosslinked alginate &  $>\num{1e4}$ & $<\num{3e-1}$ & $>\num{3e4}$ & Fig. 3b \\
 			\rowcolor{secondaryBackground}
-			Pössl\cite{possl2021} & blend & 3e2 & 1e-4 & 3e6 & Table 4 \\
+			Pössl\cite{possl2021} & blend & \num{2e2} & \num{5e-1} & \num{4e2} & Figure 4 \\
 %			Paxton\cite{paxton2017} &Nivea Creme\n Alginate& 1e5\n5e4 & <1\n<5e1 & >1e5\n>1e3 & Fig. 4b \\
-			Paxton\cite{paxton2017} & Alginate& 5e4 & <5e1 & >1e3 & Fig. 4b \\
+			Paxton\cite{paxton2017} & Alginate& \num{5e4} & $<\num{5e1}$ & $>\num{1e3}$ & Fig. 4b \\
 			\rowcolor{secondaryBackground}
-			O'Connell\cite{oconnell2020} & pluronic F-127 & >1e6 & <8 & > 2e5 & Chapter 7 Fig. 13 \\
+			O'Connell\cite{oconnell2020} & pluronic F-127 & $>\num{1e6}$ & $<\num{8}$ & $>\num{2e5}$ & Chapter 7 Fig. 13 \\
 		\end{tabular}
 	\caption{Compilation of literature data on typical bioinks showing that a very viscosity ratio $ R_ \eta $ is a generic feature of these liquids.
-	\SG{ cross-check these values }\RK{as in with other literature?}
+	\SG{ cross-check these values }\RK{Done and formatted}
 	}
@@
 \end{table}
-\RK{While $\eta_0/\eta_\infty$ would have been sensible for $R_\eta$ definition, i used $(\eta_0-\eta_\infty)/\eta_\infty$ instead.
-This plays nicer with our models and does not make a difference, but the notation above is now inconsistent since del of CY}
 
@@
 \SG{ and vice versa: make sure that all papers discussed here are also cited in the introduction }\RK{gupta2015\_2 not in intro} \SG{ dann setz einfach die Zitate so rein, wie du sie fuer passend haeltst.
-}
+}\todo{do}
 Since the early days of LBM, variants for viscoelastic fluids have been developed.
@@
 Aber da steht eigentlich schon, dass forcing besser sei, oder?
-}
+}\todo{check/do not mention this}
 
@@
 In the case of alginate, we speed up the convergence and start from a situation in which the polymers are pre-stretched \SG{ give details }\RK{initialized to the semianalytical solution} \SG{ schreib am besten eine Referenz auf die Gleichung hin, muesste ja im Appendix stehen.
-}.
+}\todo{do}.
 After \num{2e9} LBM time steps for alginate and \num{5e6} LBM time steps for methyl cellulose corresponding to approximately \SI{1.6}{\milli\second} and \SI{2.4}{\second} of physical time, respectively, the simulation is stopped and the flow field $u(y)$ is compared to the semi-analytical solution.
@@
 The Oldroyd-B model is a special case of the PTT model which is obtained by setting $\xi = \epsilon = 0$ in eq.~(\ref{eq:polymerStress}) and is thus easily tractable with our code.\RK{was simulated with a direct Oldroyd-B implementation, which I now see was unnecessary...} \SG{ hast du mal kurz geprueft, ob dasselbe rauskommt?
-}
+}\RK{Nein}\todo{check}
 In figure~\ref{fig:malaspinas2010}, we show the L2 error as function of lattice resolution for different values of $\mathrm{Wi}$ and $R_ \nu $ which is defined as \cite{malaspinas2010}
@@
 	\end{equation}
-At this point, we mention that there is a typographic mistake in eq.~(61) of \cite{malaspinas2010} where the prefactor should 8 instead of 4. \SG{ stimmt das so? }
+At this point, we mention that there is a typographic mistake in eq.~(61) of \cite{malaspinas2010} where the prefactor should be 8 instead of 4. \SG{ stimmt das so? }\RK{Ja}
 

### 2024-02-26 assets/python/fig:ShuffleInPoiseuille.py

@@ -1,0 +1,128 @@
+# -*- coding: utf-8 -*-
+"""
+File to house the  class.
+
+Created on Mon Feb 26 12:32:31 2024
+
+@author: Richard Kellnberger
+"""
+
+import json
+from pathlib import Path
+from time import time
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pyvista as pv
+
+from fluidx3d.eval.models import PTT
+from fluidx3d.eval.style import cm, color
+
+
+def process(index):
+    baseDir = Path(f"../data/ShuffleInPoiseuille/{index}/")
+    cDir = baseDir / "vtkfiles/polymerConformationTensor/"
+    sDir = baseDir / "vtkfiles/strainRateTensor/"
+    vDir = baseDir / "vtkfiles/velocity/"
+    jsonFile = baseDir / "parameters.json"
+    f = open(jsonFile)
+    parameters = json.load(f)
+    f.close()
+
+    V0 = parameters["info"]["conversions"]["V0"]
+    L0 = parameters["info"]["conversions"]["L0"]
+    T0 = parameters["info"]["conversions"]["T0"]
+    rho0 = 1e3
+    p0 = rho0 * V0**2
+    G = parameters["info"]["px"] * p0 / L0
+    # print("###")
+    # print(parameters["info"]["px"])
+    # print(p0 / L0)
+    # print(G)
+
+    cFile = cDir / "CT_5000000.vtk"
+    sFile = sDir / "S_5000000.vtk"
+    vFile = vDir / "u_5000000.vtk"
+
+    if index == "2b":
+        cFile = cDir / "CT_50000000.vtk"
+        sFile = sDir / "S_50000000.vtk"
+        vFile = vDir / "u_50000000.vtk"
+
+    # print(uHP(0, G, eta_p_SI))
+    # print("---")
+    data = pv.read(cFile)
+    dataS = pv.read(sFile)
+    dataV = pv.read(vFile)
+    Lx, Ly, Lz = data.dimensions
+    # origin = data.origin
+    R = (Ly - 2) / 2 * L0
+
+    tauField = data.get_array("data") * PTT.mc0_49.eta_p / PTT.mc0_49.lambda_p
+    tauField = np.reshape(tauField, (Lx, Ly, Lz, 6), "F")
[…]

### 2024-02-26 assets/setups/ShuffleInPoiseuille/setup/defines.hpp

@@ -1,0 +1,181 @@
+#pragma once
+// ############################################ file paths #############################################
+
+//#define PATH_DEBUG "/data2/s1molehm/FluidX3D/Bead/interpolation/"
+//#define PATH_DEBUG "/tp6_gekle/data2/bt703473/debug/test2/"
+#define PATH_DEBUG "./bin/debug/" // path for debug files (PTX, LOG, VALIDATION)
+#define PATH_IBM   "./bin/ibm/"   // path for IBM extension
+
+
+// ############################################ LBM options ############################################
+
+// There hides a D2Q5 in the code
+//#define D2Q9
+//#define D3Q7 // very very inaccurate
+//#define D3Q13 // very inaccurate; Only works with MRT according to Krüger book p. 87; Does not reproduce VISCOELASTIC correctly.
+
+// Only use these:
+//#define D3Q15
+#define D3Q19 // Best value
+//#define D3Q27 // Better for high Reynolds numbers.
+
+#define SRT // singe relaxation time
+//#define TRT // two relaxiation time (as fast as SRT, but more accurate)
+//#define MRT // multi relaxiation time (as fast as SRT, but more accurate), (### not fully validated for for D3Q7 and D3Q13, incomplete relaxation times for D3Q7 and D3Q27 ###)
+
+//#define UPDATE_RHO // update density field after every step (not necessary for pure LBM)
+//#define UPDATE_U // update velocity field after every step (not necessary for pure LBM, makes tracer particle calculation faster)
+
+//#define MOVING_WALLS // moving bounce-back boundaries
+//#define BOUNDARY_EXPRESSION // combinable with MOVING_WALLS, !!!doesn't work on AMD for some reason!!!
+
+#define VISCOELASTIC
+// Only one of the following models may be defined
+//#define OLDROYD_B
+//#define FENEP
+#define PTT // From Ferras 2019 eq (3) and (2) original PTT
+//#define CARREAU_YASUDA
+
+//#define IBM // immersed boundary method (### under construction ###)
+//#define IBM_CELLS // simulate RBCs with the immersed-boundary method
+//#define IBM_NEW // IBM implementation by Stephan Gekle; Conflicts with IBM and IBM_CELLS
+//#define INOUT // activate volume tracking for RBCs
[…]

### 2024-02-26 assets/setups/ShuffleInPoiseuille/setup/setup.cpp

@@ -1,0 +1,196 @@
+#include "setup.hpp"
+#include "shapes.hpp"
+#include "opencl.hpp" // contains "options.hpp", "main.hpp"
+#include "ibm.hpp"
+#include <numeric>
+#include <sstream>
+
+#include <filesystem>
+using std::filesystem::path;
+#include <fstream>
+using std::ofstream;
+
+#include <fmt/core.h>
+// using fmt::format
+using fmt::print;
+#include <fmt/color.h>
+using fmt::color;
+
+#include <spdlog/spdlog.h>
+//using spdlog::info;
+
+#include "fieldWriter.hpp"
+using fluidx3d::io::fieldWriter::FieldWriter;
+#include "io.hpp"
+using fluidx3d::util::io::IO;
+#include "poiseuilleFlow.hpp"
+using fluidx3d::util::poiseuilleFlow::CircularPoiseuilleFlow;
+
+void example(SimulationOptions& options, Parameters& parameters) {
+	json raw = parameters.getRaw();
+	const int id = raw.at("id");
+	//const string path_files = "/tp6-gekle/nas/bt307867/cellsim/novel_2023-10-24/" + std::to_string(id) + "/";
+	const string path_files = fmt::format("ShuffleInPoiseuille/{}/", id);
+	const path filesPath(path_files);
+	const string path_vtk = path_files + "vtkfiles/";
+	const string path_vtk_velocity = path_vtk + "velocity/";
+	const string path_vtk_strainRateTensor = path_vtk + "strainRateTensor/";
+	const string path_vtk_viscousStressTensor = path_vtk + "viscousStressTensor/";
+	const string path_vtk_polymerConformationTensor = path_vtk + "polymerConformationTensor/";
+
+	/*
+	 * this parameter increases the time step
+	 * --> leads to larger relaxation time tau (not good, but acceptable)
+	 * --> leads to larger Ma (not good, but acceptable)
+	 * --> eventually may lead to inaccuracies
+	 */
+	const double dtScale = 1e0;  // decrease timestep
+
+	// Length of simulation box
+	uint Lx = 2;
+	uint Ly = 43;
+	uint Lz = 2;
+
+	/*
+	 * this parameter decreases the viscosity
[…]

### 2024-02-26 NovelLBM.tex
include Nozzle/RT-DC plots

@@
 		\caption{(a) Velocity profile of alginate in planar channel flow.
-		The time evolution of the center-line velocity is shown in the inset \SG{ to do }\RK{you really want this?}.
+		The time evolution of the center-line velocity is shown in the inset \ref{fig:2DTimeEvolution}\SG{ to do }\RK{Not an inset but plotted. Has to be inset?}.
 		(b) Velocity profile for methyl cellulose.
@@
 		\caption{(a) Velocity profile of alginate in cylindrical channel flow.
-		The time evolution of the center-line velocity when starting from a pre-stretched configuration (see main text) is shown in the inset.
+		The time evolution of the center-line velocity when starting from a pre-stretched configuration (see main text) is shown in the inset \ref{fig:3DTimeEvolution}.\RK{currently not an inset}
 		(b) Velocity profile for methyl cellulose.
@@
 The required values for velocity and polymer conformation are obtained from simulations of pipes of the respective radii and a fixed volume flow of $\approx\SI{3}{\micro\liter\per\second}$.
-The resulting flow field can be seen in figure \ref{fig:Nozzle_v}~(a).
+The resulting flow field can be seen in figure \ref{fig:Nozzle}~(a).
 To quantify the total stress as a single number, we use the von Mises stress which is defined as \cite{Mueller.2023}:
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/Nozzle_sigma_vM.pdf}
-		\caption{Velocity profile (a) and von Mises stress (b) for methyl cellulose in a conical nozzle as used for bioprinting.}
-		\label{fig:Nozzle_v}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/Nozzle_tau_12.pdf}
+		\caption{Velocity profile (a), von Mises stress (b) and shear stress (c) for methyl cellulose in a conical nozzle as used for bioprinting.
+For the calculated viscosity see figure~\ref{fig:Nozzle/RT-DC_eta}.}
+		\label{fig:Nozzle}
 	\end{figure}
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_v.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_sigma_vM.pdf}
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_tau.pdf}
-		\caption{Velocity profile (a) and shear stress (b) for methyl cellulose in a typical RT-DC geometry. \SG{ draw channel contour with black lines }\RK{done something else instead. Better?}
-		\SG{ change to von Mises instead of $ \tau _{ 12 }$? }}\RK{what plots do we want v, $\tau$, vM and $\eta$?; For nozzle as well?}
+		\caption{Velocity profile (a), von Mises stress (b) and shear stress (c) for methyl cellulose in a typical RT-DC geometry.
+For the calculated viscosity see figure~\ref{fig:Nozzle/RT-DC_eta}.\SG{ draw channel contour with black lines }\RK{done something else instead.
+Better?}
+		\SG{ change to von Mises instead of $ \tau _{ 12 }$? }\RK{done something}}
 		\label{fig:RT-DC}
@@
 This also shows why viscoelastic simulations cannot always be replaced by shear thinning models and should be considered despite the high computational cost.
-}\RK{plot would probably be better}
+}\RK{plot would probably be better}\todo{describe and reference plot as it looks terrible}
 
@@
 		\caption{Average error of the velocity for a planar (a) and a cylindrical (b) Poiseuille flow of methyl cellulose at different pressure gradients.
-		The peak in the error profile appears when the average shear rate across the channel corresponds to the maximum slope in the viscosity profile of figure~\ref{fig:wiParameterStudy}.
-}\RK{this is L2 error norm not "average"}
+		The peak in the error profile appears when the average shear rate across the channel corresponds to the maximum slope in the viscosity profile of figure~\ref{fig:wiParameterStudy}.}\RK{this is L2 error norm not "average"}
 		\label{fig:pressureErr}
@@
 
+	\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DAlginate_timeEvolution.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DMC_timeEvolution.pdf}
+		\caption{Time evolution of the center-line velocity of an alginate (a) and methyl cellulose (b) poiseuille flow in 2D as seen in figure~\ref{fig:2Dvel}.}
+		\label{fig:2DTimeEvolution}
+	\end{figure}
+
+	\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DAlginate_timeEvolution.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DMC_timeEvolution.pdf}
+		\caption{Time evolution of the center-line velocity of an alginate (a) and methyl cellulose (b) poiseuille flow in 3D as seen in figure~\ref{fig:3Dvel}.}
+		\label{fig:3DTimeEvolution}
+	\end{figure}
+
+	\begin{figure}[H]
+	\centering
+	\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/Nozzle_eta.pdf}
+	\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_eta.pdf}
+	\caption{"Viscosity" in a Nozzle (a) and RT-DC channel (b) calculated by dividing $\tau_{12}$ by the respective strain rate.
+This diverges along the center line, and thus it has been excluded.
+For the RT-DC channel this results in very large and unphysical values, which had to be clamped.
+The flow and stresses in these geometries can be seen in figures~\ref{fig:Nozzle} and \ref{fig:RT-DC}.}
+	\label{fig:Nozzle/RT-DC_eta}
+	\end{figure}
+
 \end{document}

### 2024-02-26 assets/python/fig:Nozzle.py

@@ -173,7 +173,7 @@ def process():
     plt.show()
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
-    # plt.title("(b)", loc="left", pad=45, x=-0.1)
+    plt.title("(c)", loc="left", pad=45, x=-0.1)
     plt.plot(x * L0 * 1e3, upper * L0 * 1e3, "k", linewidth=0.5)
     plt.plot(x * L0 * 1e3, lower * L0 * 1e3, "k", linewidth=0.5)
     plt.imshow(
@@ -205,7 +205,7 @@ def process():
     """
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
-    plt.title("(c)", loc="left", pad=45, x=-0.1)
+    plt.title("(a)", loc="left", pad=45, x=-0.1)
     plt.plot(x * L0 * 1e3, upper * L0 * 1e3, "k", linewidth=0.5)
     plt.plot(x * L0 * 1e3, lower * L0 * 1e3, "k", linewidth=0.5)
     plt.imshow(

### 2024-02-26 assets/python/fig:RT-DC.py

@@ -172,7 +172,7 @@ def process():
     plt.show()
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
-    # plt.title("(b)", loc="left", pad=45, x=-0.11)
+    plt.title("(c)", loc="left", pad=45, x=-0.11)
     plt.imshow(
         tau12.T,
         cmap="coolwarm",
@@ -197,7 +197,7 @@ def process():
     """
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
-    plt.title("(c)", loc="left", pad=45, x=-0.1)
+    plt.title("(b)", loc="left", pad=45, x=-0.1)
     plt.imshow(
         eta.T * 1e3,
         cmap="coolwarm",

### 2024-02-27 NovelLBM.tex
Updated comments

@@
 	\end{equation}
-where $\mathrm{Wi} = \lambda\dot{\gamma}$ is the Weissenberg number and $W_0$ is the Lambert $W$-function. \SG{ check that $ \eta _ \mathrm{s}$ is correct }\RK{what do you mean by correct?}
+where $\mathrm{Wi} = \lambda\dot{\gamma}$ is the Weissenberg number and $W_0$ is the Lambert $W$-function.
 Fitting these equations to the rheological data for alginate and methyl cellulose leads to satisfactory agreement as shown in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}.
@@
 Coupling of the resulting polymer stress to the Navier-Stokes LBM can be achieved via the inclusion of point forces or via a modification of the equilibrium populations.
-A recent comparison in 2D found that the former in general leads to better stability \cite{dzanic2022_2}.\RK{No in fact, it uses the latter and found to be more accurate than a paper using the former, stability was entirely attributed to the decomposition and artificial diffusivity.} \SG{ die Referenz war falsch, es war der andere Dzanic.
-Aber da steht eigentlich schon, dass forcing besser sei, oder?
-}\todo{check/do not mention this}
+Both methods have recently been compared in 2D \cite{dzanic2022_2}.
 
@@
 To include the polymer stress into the LBM, we use the stress coupling scheme according to Dzanic \textit{et al.} \cite{dzanic2022_2, gupta2015, onishi2006}.
-For this, ... \SG{ do we really do stress coupling? Above it said that force coupling is better? }\RK{yes, no idea why you said that}
-\SG{ give some more details, especially since we do SRT }.\RK{what does this have to do with SRT?}
-\SG{ also include inflow/outflow BCs }\RK{done}
-\SG{ do you advect polymer stress or polymer conformation? }\RK{A, which is most similar to polymer conformation}
+For this, ... \SG{ more details }
 To handle inflow/outflow boundaries, the polymer conformation tensor is specified on the boundary and advected using the corner transport upwind scheme.
@@
 containing an arbitrary parameter $\alpha_\text{s}$. 
-\SG{ is there an allowed range for $ \alpha _ \mathrm{s}$?
-}\RK{LBM viscosity should stay positive; While $\alpha_s > 1$ stops decreasing the polymer stress and increases it again it can still be sensible as the relation of the stresses will still drop (which is desirable)}
 Finally, this results in
@@
 \end{equation}
-
+which gives \num{9e-4} and \num{1e-3} for alginate and methyl cellulose, respectively.
 The spatially resolved errors are shown in figure~\ref{fig:2DvelErr} in the appendix.
-Averaging over the channel diameter, we obtain an L2 error of \num{9e-4} and \num{1e-3}\RK{we do not "average" over the diameter, we calculate the L2 error along the diameter} for alginate and methyl cellulose, respectively.
-These conclusions remain robust even when varying the pressure gradient, and thus the flow velocity, over many orders of magnitude as shown in figure~\ref{fig:pressureErr}~(a) of the appendix.\RK{This is the worst case error for MC and it is tiny "remain robust" is too weak here}
+These conclusions remain unchanged even when varying the pressure gradient, and thus the flow velocity, over many orders of magnitude as shown in figure~\ref{fig:pressureErr}~(a) of the appendix.
 
@@
 		(b) Velocity profile for methyl cellulose.
-		\SG{ make these plots for different $ \alpha _ \mathrm{s}$, either include here or put into appendix }\RK{Why? Is likely identical down to fp32 precision (see appendix C)}}
+}
 		\label{fig:2Dvel}
@@
 Numerically, the cylindrical situation is slightly more complex due to discretization errors ("staircase effect") when mapping the rounded channel walls onto the rectilinear LBM grid \cite{Lehmann.20229da}.
-We use the same material parameters as above, but double the pressure gradient to \SI{-2e7}{\pascal\per\meter} and approximately \SI{-2.5e7}{\pascal\per\meter} respectively.
-\SG{ why?
-} \RK{where analytical solutions exist in Poiseuille geometry the 3D solution differs from the 2D solution by a factor 2 (Due to the gradient of the stress in the derivation having a form in cylinder coordinates that can be solved by a factor 2).
-See the velocities in our sims being the same with this scaling}
+We use the same material parameters as above, but double the pressure gradient to \SI{-2e7}{\pascal\per\meter} and approximately \SI{-2.5e7}{\pascal\per\meter}, respectively, thereby mirroring the relation in Newtonian Poiseuille flow where twice the pressure is required to obtain the same flow rate in cylindrical compared to planar gemeotries.
 The channel has a diameter of \SI{20}{\micro\meter} and is discretized with 41 lattice points.
@@
 		(b) Velocity profile for methyl cellulose.
-				\SG{ make these plots for different $ \alpha _ \mathrm{s}$, either include or put into Si }\RK{Why? Is likely identical down to fp32 precision (see appendix C)}}
+				}
 		\label{fig:3Dvel}
@@
 with the kinematic solvent and the polymer viscosity $\nu_\text{s}$ and $\nu_\text{p}$. 
-\SG{ comment whether these definitions are identical or different than the definitions above.
-}\RK{different but can be transformed into each other $\frac{1}{R_\nu}-1=R_\eta$}
+We note that this can directly be transformed into the viscosity ratio used above as $\frac{1}{R_\nu}-1=R_\eta$.
 Furthermore, in agreement with \cite{malaspinas2010}, also the L2 error is defined differently than above, namely:
@@
 We note a certain dependence of the accuracy on $R_\nu$ which we consider nevertheless acceptable given the overall smallness of the error.
-Finally, we find that the error of our method decreases with lattice resolution to the power of \num{-2} \SG{ give number, show dashed line in plot }\RK{done}.\RK{They see diminishing returns we don't}
+Finally, we find that the error of our method decreases with lattice resolution to the power of \num{-2}. \RK{They see diminishing returns we don't} \SG{ explain }
 
@@
 Similarly, directly after the constriction, the high stress inside the observation channel persists over a certain distance that is needed for the polymer stress to decay.
-\RK{There are three, proceeds to name two}
+\RK{There are three, proceeds to name two} \SG{ ? }
 
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_tau.pdf}
-		\caption{Velocity profile (a), von Mises stress (b) and shear stress (c) for methyl cellulose in a typical RT-DC geometry.
-For the calculated viscosity see figure~\ref{fig:Nozzle/RT-DC_eta}.\SG{ draw channel contour with black lines }\RK{done something else instead.
-Better?}
+		\caption{Velocity profile (a), von Mises stress (b) and shear stress (c) for methyl cellulose in a typical RT-DC geometry. For the calculated viscosity see figure~\ref{fig:Nozzle/RT-DC_eta}.
 		\SG{ change to von Mises instead of $ \tau _{ 12 }$? }\RK{done something}}
@@
 These are particularly pronounced along the longest axis of the deformed cell.
-\SG{ connect to the ''viscoelastic wings'' paper \cite{Zhang.2020}}\RK{Our "wings" look very different}
 
@@
 \label{app:semianalyticalPoiseuille}
-\SG{ make a self-contained derivation which is understandable even without reading Oliveira \\}\RK{done}
-\SG{ use Gl.~(\ref{eq:polymerStress}) as starting point and end with Poiseuille solution, but also shear solution Gl.~(\ref{eq:shearN}, \ref{eq:shearEta}) \\}\RK{done}
-Our derivation is in principal similar to Oliveira \cite{oliveira1999}. For both Poiseuille flow and shear flow the following holds.
+Our derivation is to the one in Oliveira \cite{oliveira1999}. For both Poiseuille flow and shear flow, we assume that the velocity is unidirectional: 
 \begin{equation}
-	\vec{u} = \dot{\gamma}\left(y\right)\hat{e}_x
+	\vec{u} = \dot{\gamma}\left(y\right)\hat{e}_x.
 \end{equation}
-With this the constitutive equation~(\ref{eq:polymerStress}) for $\xi=0$ in steady state reduces to the following.
+\SG{ This equation does not work, $ \dot{ \gamma  }$ is a shear rate, it should read $ \partial u_x / \partial y = \dot{ \gamma  }$. }
+
+With this the constitutive equation~(\ref{eq:polymerStress}) for $\xi=0$ in steady state reduces to
 \begin{align}
@@
 \end{align}
-With $\Tr\ma{\tau} = \tau_{xy}$. In the three-dimensional case $y$ refers to the radial coordinate.
+for a planar flow.
+In axisymmetric flows $y$ in eqs.~(\ref{eq:PTTDerivation1}, \ref{eq:PTTDerivation2}) needs to be replaced by the radial coordinate $r$. \SG{ no factor 2? }
+With $\Tr\ma{\tau} = \tau_{xy}$. \SG{ should be $ \tau _{ xx }$? }
 Eliminating $\tau_{xy}$ yields the following.
@@
 		\caption{(a) The local viscosity determined by a shear flow simulation is in very good agreement with the semi-analytical theory.
-		(b) The error is negligibly small and independent of the shuffling parameter $\alpha_\text{s}$.
-		\SG{ plot over shear rate instead of $ \mathrm{Wi}$. Fix units of $ \eta $. }\RK{done, done}}
+		(b) The error is negligibly small and independent of the shuffling parameter $\alpha_\text{s}$.}
 		\label{fig:wiParameterStudy}
@@
 		\caption{L2 error of the velocity profile in figure~\ref{fig:2Dvel} with respect to the semi-analytical theory in a planar Poiseuille flow for alginate (a) and methyl cellulose (b).
-			The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall.}\RK{this is linear error}
+			The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall.}\RK{this is linear error} \SG{ define }
 		\label{fig:2DvelErr}
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr.pdf}
-		\caption{Average error of the velocity for a planar (a) and a cylindrical (b) Poiseuille flow of methyl cellulose at different pressure gradients.
-		The peak in the error profile appears when the average shear rate across the channel corresponds to the maximum slope in the viscosity profile of figure~\ref{fig:wiParameterStudy}.}\RK{this is L2 error norm not "average"}
+		\caption{L2 error of the velocity for a planar (a) and a cylindrical (b) Poiseuille flow of methyl cellulose at different pressure gradients.
+		The peak in the error profile appears when the average shear rate across the channel corresponds to the maximum slope in the viscosity profile of figure~\ref{fig:wiParameterStudy}.}
 		\label{fig:pressureErr}

### 2024-02-27 NovelLBM.tex
mark todos

@@
 	\centering
-		\begin{tabular}{l|p{3cm}|p{1.6cm}|p{1.6cm}|p{1.6cm}|p{2cm}}
+		\begin{tabular}{l|p{3cm}|p{1.8cm}|p{1.8cm}|p{1.8cm}|p{2cm}}
 			Author & Material & $\eta_0/\unit{\pascal\second}$ & $\eta_\infty/\unit{\pascal\second}$ & $R_\eta$ & extracted from \\
@@
 			\rowcolor{secondaryBackground}
-			O'Connell\cite{oconnell2020} & pluronic F-127 & $>\num{1e6}$ & $<\num{8}$ & $>\num{2e5}$ & Chapter 7 Fig. 13 \\
+			Jalaal\cite{jalaal2017} & pluronic F-127 & $>\num{1e3}$ & $<\num{1e-1}$ & $>\num{1e4}$ & FIG. 6. (e) \\
 		\end{tabular}
@@
 To include the polymer stress into the LBM, we use the stress coupling scheme according to Dzanic \textit{et al.} \cite{dzanic2022_2, gupta2015, onishi2006}.
-For this, ... \SG{ more details }
+For this, ... \SG{ more details }\todo{SRT collision operator as implemented, advection as implemented, the whole as implemented appendix that was deleted}
 To handle inflow/outflow boundaries, the polymer conformation tensor is specified on the boundary and advected using the corner transport upwind scheme.
@@
 		The time evolution of the center-line velocity is shown in the inset \ref{fig:2DTimeEvolution}\SG{ to do }\RK{Not an inset but plotted. Has to be inset?}.
-		(b) Velocity profile for methyl cellulose.
-}
+		(b) Velocity profile for methyl cellulose.}
 		\label{fig:2Dvel}
@@
 Numerically, the cylindrical situation is slightly more complex due to discretization errors ("staircase effect") when mapping the rounded channel walls onto the rectilinear LBM grid \cite{Lehmann.20229da}.
-We use the same material parameters as above, but double the pressure gradient to \SI{-2e7}{\pascal\per\meter} and approximately \SI{-2.5e7}{\pascal\per\meter}, respectively, thereby mirroring the relation in Newtonian Poiseuille flow where twice the pressure is required to obtain the same flow rate in cylindrical compared to planar gemeotries.
+We use the same material parameters as above, but double the pressure gradient to \SI{-2e7}{\pascal\per\meter} and approximately \SI{-2.5e7}{\pascal\per\meter}, respectively, thereby mirroring the relation in Newtonian Poiseuille flow where twice the pressure is required to obtain the same flow rate in cylindrical compared to planar geometries.
 The channel has a diameter of \SI{20}{\micro\meter} and is discretized with 41 lattice points.
@@
 		The time evolution of the center-line velocity when starting from a pre-stretched configuration (see main text) is shown in the inset \ref{fig:3DTimeEvolution}.\RK{currently not an inset}
-		(b) Velocity profile for methyl cellulose.
-				}
+		(b) Velocity profile for methyl cellulose.}
 		\label{fig:3Dvel}
@@
 We note a certain dependence of the accuracy on $R_\nu$ which we consider nevertheless acceptable given the overall smallness of the error.
-Finally, we find that the error of our method decreases with lattice resolution to the power of \num{-2}. \RK{They see diminishing returns we don't} \SG{ explain }
+Finally, we find that the error of our method decreases with lattice resolution to the power of \num{-2}.
+\RK{They see diminishing returns we don't} \SG{ explain }\RK{The topmost line starts from the first green dot and also is a power of -2 line, the second point is already a little of and the third and fourth deviate more and more.
+One could try to do a line with a smaller power, however that does not quite fit the data either.
+This is particularly evident for the red points.
+It looks like Malaspinas has about power of -2 for small N but the slope decreases for higher N.
+This can be explained through other error terms (for example their artificial viscosity) becoming more relevant as the lattice resolution caused error decreases.
+As we do not have those our error continues to decrease as expected}
 
@@
 		\caption{Velocity profile (a), von Mises stress (b) and shear stress (c) for methyl cellulose in a conical nozzle as used for bioprinting.
-For the calculated viscosity see figure~\ref{fig:Nozzle/RT-DC_eta}.}
+For the calculated viscosity see figure~\ref{fig:Nozzle/RT-DC_eta}.\RK{The black lines currently hide our resolution shall I remove them to be consistent with the RT-DC plots or do we prefer this?}}
 		\label{fig:Nozzle}
@@
 \label{app:semianalyticalPoiseuille}
-Our derivation is to the one in Oliveira \cite{oliveira1999}. For both Poiseuille flow and shear flow, we assume that the velocity is unidirectional: 
+Our derivation is \RK{hier könnte ein Adjektiv stehen} to the one in Oliveira \cite{oliveira1999}. For both Poiseuille flow and shear flow, we assume that the velocity is unidirectional:
 \begin{equation}
-	\vec{u} = \dot{\gamma}\left(y\right)\hat{e}_x.
+	\vec{u} = u_x\left(y\right)\hat{e}_x
 \end{equation}
-\SG{ This equation does not work, $ \dot{ \gamma  }$ is a shear rate, it should read $ \partial u_x / \partial y = \dot{ \gamma  }$. }
+\begin{equation}
+	\dot{\gamma}\left(y\right) = \frac{\partial u_x}{\partial y}
+\end{equation}
+\SG{ This equation does not work, $ \dot{ \gamma  }$ is a shear rate, it should read $ \partial u_x / \partial y = \dot{ \gamma  }$.
+}\RK{done, was supposed to read g(y) but could not read my own handwriting when copying...
+Made it a little more clear}
 
@@
 for a planar flow.
-In axisymmetric flows $y$ in eqs.~(\ref{eq:PTTDerivation1}, \ref{eq:PTTDerivation2}) needs to be replaced by the radial coordinate $r$. \SG{ no factor 2? }
-With $\Tr\ma{\tau} = \tau_{xy}$. \SG{ should be $ \tau _{ xx }$? }
+In axisymmetric flows $y$ in eqs.~(\ref{eq:PTTDerivation1}, \ref{eq:PTTDerivation2}) needs to be replaced by the radial coordinate $r$.
+\RK{2D case is also axisymmetric?}\SG{ no factor 2?
+}\RK{No, factor 2 comes from the NS eq.
+and thus is only relevant for Poiseuille solution.
+This replacement is also much more relevant there as here all ys disappear}
+With $\Tr\ma{\tau} = \tau_{xx}$. \SG{ should be $ \tau _{ xx }$? }\RK{yes}
 Eliminating $\tau_{xy}$ yields the following.
@@
 
+	\begin{figure}[H]
+		\centering
+		%\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/ShuffleInPoiseuille.pdf}
+		\caption{In Poiseuille flow, the result is near identical for different $\alpha_\text{s}$.
+The error reveals minor differences.
+Aside from the wall nodes, the largest error appears for small shuffle fractions.
+For large ones, the error appears to become independent of $\alpha_\text{s}$.
+This indicates, that the observed difference might be due to the Mach number changing for different $\alpha_\text{s}$ and not due to the shuffling itself.\RK{I could probably prove this by running sims at different $\alpha_s$ that consistently are at Ma << 1}}
+		\label{fig:ShuffleInPoiseuille}
+	\end{figure}\todo{include plot, reference in main text}
+
 \end{document}

### 2024-02-28 NovelLBM.tex
plot ShuffleInPoiseuille

@@
 A very popular simulation technique for Newtonian fluids is the Lattice Boltzmann method \cite{Kruger_book} due to its simplicity and high parallelizability.
-LBM has also been extended to viscoelastic situations, mainly in two \cite{ispolatov2002,wang2019,su2013,giraud1998,xie2018,dzanic2022,frank2006,zou2014,lee2017,dzanic2022_2,sedaghat2021,frantziskonis2011,qin2023,yoshino2008,papenkort2015,phillips2011,onishi2005} but occasionally also in three \cite{malaspinas2010,gupta2015,lallemand2003,ma2020,onishi2006,wang2020,dellar2014,su2013_2,wang2021,kuron2021,gupta2016} dimensions.
-To alleviate stability problems, some of these works include an artificial diffusivity of the polymer stress \cite{malaspinas2010,ma2020,wang2020,wang2021}.
-Other remedies include special decompositions of the stress tensor \cite{dzanic2022} or optimization of the solvent contribution \cite{gupta2015} \SG{ what is this?
-}\RK{Gupta is not specific in what he does but states to "optimize" $\eta_\text{s}$.
-I suspect an artificial increase but do not know}.
+LBM has also been extended to viscoelastic situations, mainly in two \cite{ispolatov2002,wang2019,su2013,giraud1998,xie2018,dzanic2022,frank2006,zou2014,lee2017,dzanic2022_2,sedaghat2021,frantziskonis2011,qin2023,yoshino2008,papenkort2015,phillips2011,onishi2005} but occasionally also in three \cite{malaspinas2010,gupta2015,gupta2015_2,lallemand2003,ma2020,onishi2006,wang2020,dellar2014,su2013_2,wang2021,kuron2021,gupta2016} dimensions.
+To alleviate stability problems, some of these works include an artificial diffusivity of the polymer stress \cite{malaspinas2010,ma2020,wang2020,wang2021}, or perform special decompositions of the stress tensor \cite{dzanic2022}.
 Despite these improvements, however, none of these methods has been applied to very high viscosity ratio fluids which are often used as cell carrier fluids in lab experiments or technological applications.
@@
 \end{align}
-which will turn out to be an important parameter to determine numerical stability of LB simulations.
+which we and others found to be an important parameter to determine numerical stability of LB simulations, especially if no artificial diffusivity is used \cite{malaspinas2010,dzanic2022_2}.
 \SG{ wo don't actually show that $R_ \eta  $ determines stability?
@@
 We could do a few simulations with $\alpha_s = 0$ and increasing $R_\eta$ until the sim breaks if you want} \SG{ wie besprochen, bau einfach die Zitate ein, das reicht dann.
-}\todo{do}
+}\RK{done}
 This ratio can similarly be defined for other models such as FENE-P or the inelastic, but shear-thinning Carreau-Yasuda model \cite{carreau1972, yasuda1979} using the zero-shear viscosity $\eta_0$ and the infinite-shear viscosity $\eta_\infty$.
@@
 \SG{ and vice versa: make sure that all papers discussed here are also cited in the introduction }\RK{gupta2015\_2 not in intro} \SG{ dann setz einfach die Zitate so rein, wie du sie fuer passend haeltst.
-}\todo{do}
+}\RK{done}
 Since the early days of LBM, variants for viscoelastic fluids have been developed.
@@
 The first approaches avoided an explicit modeling of a viscoelastic constitutive equation and simply modified the LB collision operator to obtain a basic viscoelastic fluid obeying Jeffery's model \cite{lallemand2003}.
+This can also be archived by the introduction of a second local stress tensor \cite{dellar2014}.
 More advanced approaches include the work of Onishi \textit{et al.} \cite{onishi2005, onishi2006} who considered a non-shear-thinning Oldroyd-B model using a microscopic Fokker-Planck equation for the polymer dumbbells.
@@
 To improve numerical stability, some authors propose the inclusion of an artificial diffusivity \cite{malaspinas2010,ma2020,wang2020,wang2021}, which introduces a small error compared to the analytical solution of the constitutive equation.
-Other remedies include special decompositions of the stress tensor\cite{dzanic2022} or optimization of the solvent contribution\cite{gupta2015} \SG{ rephrase and give some more details }\RK{I have not the slightest clue what gupta is doing.
-I assume optimize is code for increase until stable but I do not know.}.
+Others perform special decompositions of the stress tensor\cite{dzanic2022}.
 Coupling of the resulting polymer stress to the Navier-Stokes LBM can be achieved via the inclusion of point forces or via a modification of the equilibrium populations.
@@
 However, another stability criterion, which is often overlooked is the viscosity ratio $R_\eta$ as defined in eq.~(\ref{eq:R_eta}).
-Existing methods often stay at or below $R_\eta = \num{1}$ \cite{gupta2015,onishi2006,wang2020,su2013_2,gupta2015_2}, while others report being limited below $R_\eta = \num{10}$ \cite{malaspinas2010,ma2020,kuron2021} due to stability issues.
+Existing methods often stay at or below $R_\eta = \num{1}$ \cite{gupta2015,onishi2006,wang2020,su2013_2,gupta2015_2}, while others report being limited below $R_\eta = \num{10}$ \cite{malaspinas2010,ma2020,kuron2021} according to Malaspinas \textit{et al.} due to stability issues.
 The details are listed in table~\ref{tab:viscRatio}.
@@
 Similarly, directly after the constriction, the high stress inside the observation channel persists over a certain distance that is needed for the polymer stress to decay.
-\RK{There are three, proceeds to name two} \SG{ ? }
+\RK{There are three, proceeds to name two} \SG{ ? }\todo{do}
 
@@
 		\label{fig:2DvelErr}
-	\end{figure}
+	\end{figure}\todo{do}
 
@@
 		\centering
-		%\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/ShuffleInPoiseuille.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/ShuffleInPoiseuille.pdf}
 		\caption{In Poiseuille flow, the result is near identical for different $\alpha_\text{s}$.
@@
 		\label{fig:ShuffleInPoiseuille}
-	\end{figure}\todo{include plot, reference in main text}
+	\end{figure}\todo{reference in main text}
 

### 2024-02-28 assets/python/fig:ShuffleInPoiseuille.py

@@ -125,4 +125,5 @@ if __name__ == "__main__":
     plt.xlabel(r"$y/\unit{\micro\meter}$")
     plt.ylabel(r"$error$")
     plt.legend()
+    plt.savefig("../plots/ShuffleInPoiseuille.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()

### 2024-02-29 NovelLBM.tex
remove lines

@@
 	\begin{center}
-		$^1$ Biofluid Simulation and Modeling – Theoretische Physik VI, University of Bayreuth, Bayreuth, Germany
+		$^1$ Biofluid Simulation and Modeling – Theoretische Physik VI, University of Bayreuth, Bayreuth, Germany\\
 		$^2$ FMZ
@@
 		\end{tabular}
-		\caption{Parameters of the PTT model obtained by fitting to the rheological measurements in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}.
-		\SG{ add a column with $R_ \eta $ }}\RK{would be identical to the content of the $\eta_p$ column, also $R_\eta$ would be used before introduced} \SG{ Stimmt, aber ich will es auf einen Blick sichtbar machen }
+		\caption{Parameters of the PTT model obtained by fitting to the rheological measurements in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}}.
 		\label{tab:PTTparameters}
@@
 	\caption{Compilation of literature data on typical bioinks showing that a very viscosity ratio $ R_ \eta $ is a generic feature of these liquids.
-	\SG{ cross-check these values }\RK{Done and formatted}
 	}
@@
 \section{Existing LBM methods}
-
-\SG{ make sure that all papers cited in the introduction as ''3D'' are discussed here as well }\RK{dellar is missing}
-\SG{ and vice versa: make sure that all papers discussed here are also cited in the introduction }\RK{gupta2015\_2 not in intro} \SG{ dann setz einfach die Zitate so rein, wie du sie fuer passend haeltst.
-}\RK{done}
 Since the early days of LBM, variants for viscoelastic fluids have been developed.
@@
 To include the polymer stress into the LBM, we use the stress coupling scheme according to Dzanic \textit{et al.} \cite{dzanic2022_2, gupta2015, onishi2006}.
-For this, ... \SG{ more details }\todo{SRT collision operator as implemented, advection as implemented, the whole as implemented appendix that was deleted}
+Specifically, we implement the LBM collision as follows.
+\begin{equation}
+	f_i\left(\vec{x}+\vec{c_i}\Delta t, t+\Delta t\right) - f_i\left(\vec{x}, t\right) = -\frac{\Delta t}{\tau_\text{r}}\left[f_i\left(\vec{x}, t\right) - f_i^\text{eq}\left(\vec{x}, t\right) + B_i\right]
+\end{equation}
+Where $f_i$ are the populations, $f_i^\text{eq}$ are the equilibrium populations, $\vec{c_i}$ are the lattice velocities, $\Delta t$ is the time step, $\tau_\text{r}$ is the relaxation time and $B_i$ are the stress contributions defined as follows.
+\begin{equation}
+	B_i = w_i\left(\frac{\vec{c_i}\vec{c_i}}{2c_\text{s}^4}-\frac{\uT}{2c_\text{s}^2}\right):\ma{\tau}
+\end{equation}
+Where $w_i$ are the lattice weights, $c_\text{s}$ is the lattice speed of sound and $\ma{\tau}$ is the polymer stress tensor. The colon denotes the Frobenius inner product.
+\SG{ more details }\RK{done}
 To handle inflow/outflow boundaries, the polymer conformation tensor is specified on the boundary and advected using the corner transport upwind scheme.
@@
 The LBM solver is run with $\eta_\text{s} + \alpha_\text{s}\eta_\text{p}$ as its viscosity.
-The polymer stress determined by equation~\ref{eq:polymerStress} is reduced by the amount $\alpha_\text{s}\eta_\text{p}\ma{D}$ at every time step before it is coupled into the LBM.
+The polymer stress determined by equation~\ref{eq:polymerStress} is reduced by the amount $2\alpha_\text{s}\eta_\text{p}\ma{D}$ at every time step before it is coupled into the LBM.
 
@@
 In physical units the channel has a height of \SI{20}{\micro\meter} which are discretized with 41 LBM nodes.
-For the viscosity shuffling, we set $\alpha_\text{s} = 1$.
+For the viscosity shuffling, we set $\alpha_\text{s} = 1$. The exact value of $\alpha_\text{s}$ does not matter as can be seen in figure~\ref{fig:ShuffleInPoiseuille}.
 Along the flow direction, the channel is periodic, and the flow is driven by a pressure gradient of \SI{-1e7}{\pascal\per\meter} for alginate and  approximately \SI{-1.2e7}{\pascal\per\meter} for methyl cellulose.
@@
 For methyl cellulose, we simulate the full temporal evolution with the polymers starting in the unstretched configuration.
-In the case of alginate, we speed up the convergence and start from a situation in which the polymers are pre-stretched \SG{ give details }\RK{initialized to the semianalytical solution} \SG{ schreib am besten eine Referenz auf die Gleichung hin, muesste ja im Appendix stehen.
-}\todo{do}.
+In the case of alginate, we speed up the convergence and start from a situation in which the polymers are pre-stretched.
+For this we calculate $\tau_{xx}$ and $\tau_{xy}$ using equations~(\ref{eq:tau_xx}) and (\ref{eq:PTTDerivation2}) using the $\dot{\gamma}$ calculated from equation~(\ref{eq:semiAnalyticGD}).
+The polymer stress is then initialized using these values.
+\SG{ give details }\RK{initialized to the semianalytical solution} \SG{ schreib am besten eine Referenz auf die Gleichung hin, muesste ja im Appendix stehen.
+}\RK{done}.
 After \num{2e9} LBM time steps for alginate and \num{5e6} LBM time steps for methyl cellulose corresponding to approximately \SI{1.6}{\milli\second} and \SI{2.4}{\second} of physical time, respectively, the simulation is stopped and the flow field $u(y)$ is compared to the semi-analytical solution.
@@
 	\end{equation}
-At this point, we mention that there is a typographic mistake in eq.~(61) of \cite{malaspinas2010} where the prefactor should be 8 instead of 4. \SG{ stimmt das so? }\RK{Ja}
+At this point, we mention that there is a typographic mistake in eq.~(61) of \cite{malaspinas2010} where the prefactor should be 8 instead of 4.
 
@@
 Finally, we find that the error of our method decreases with lattice resolution to the power of \num{-2}.
-\RK{They see diminishing returns we don't} \SG{ explain }\RK{The topmost line starts from the first green dot and also is a power of -2 line, the second point is already a little of and the third and fourth deviate more and more.
-One could try to do a line with a smaller power, however that does not quite fit the data either.
-This is particularly evident for the red points.
-It looks like Malaspinas has about power of -2 for small N but the slope decreases for higher N.
-This can be explained through other error terms (for example their artificial viscosity) becoming more relevant as the lattice resolution caused error decreases.
-As we do not have those our error continues to decrease as expected}
+The error found by Malaspinas \textit{et al.} has a similar decrease for small $N$, but sees less reduction at higher $N$.
 
@@
 \end{align}
-It can be seen that the highest stresses arise at the nozzle exit in direct vicinity to the wall.
+It can be seen in figure~\ref{fig:Nozzle}~(b) that the highest stresses arise at the nozzle exit in direct vicinity to the wall.
 This means that even for fast flows, cells flowing close to the center experience less stress than cells flowing near the walls in agreement with earlier results in Newtonian fluids \cite{Mueller.2023}.
@@
 		\caption{Velocity profile (a), von Mises stress (b) and shear stress (c) for methyl cellulose in a conical nozzle as used for bioprinting.
-For the calculated viscosity see figure~\ref{fig:Nozzle/RT-DC_eta}.\RK{The black lines currently hide our resolution shall I remove them to be consistent with the RT-DC plots or do we prefer this?}}
+For the calculated viscosity see figure~\ref{fig:Nozzle/RT-DC_eta}.}
 		\label{fig:Nozzle}
@@
 For this simulation we use periodic boundary conditions and a constant body force corresponding to a pressure gradient of \SI{1e7}{\pascal}.
-In figure~\ref{fig:RT-DC}, we show the velocity profile and the shear component of the stress which is the relevant component if a local shear viscosity is to be defined.
+In figure~\ref{fig:RT-DC}, we show the velocity profile, the von Mises stress and the shear component of the stress which is the relevant component if a local shear viscosity is to be defined.
 There are three qualitative differences compared to a purely viscous fluid.
@@
 Similarly, directly after the constriction, the high stress inside the observation channel persists over a certain distance that is needed for the polymer stress to decay.
-\RK{There are three, proceeds to name two} \SG{ ? }\todo{do}
+If one would divide the stress in these two regions by the strain rate in an attempt to obtain a viscosity one would find a very low and a very high viscosity respectively.
+These can be outside the range of viscosities, that can be obtained through rheological measurements with the fluid.
+This effect is even more pronounced along the walls directly after the outlet.
+Here the viscosities obtained in this manner become negative.
+Due to the strain rate approaching $0$ at several locations within the simulation volume, this calculation often diverges.
+The clamped result can be seen in figure~\ref{fig:Nozzle/RT-DC_eta}.
+These discrepancies, especially the ones at the walls, show the breakdown of the viscosity interpretation in viscoelastic cases and signify the regions of interesting behavior.
+This also shows why viscoelastic simulations cannot always be replaced by purely viscous models and should be considered despite the high computational cost.
+\SG{ decide whether we want to show a viscosity plot and remove or leave this part}\RK{done}
 
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_tau.pdf}
-		\caption{Velocity profile (a), von Mises stress (b) and shear stress (c) for methyl cellulose in a typical RT-DC geometry. For the calculated viscosity see figure~\ref{fig:Nozzle/RT-DC_eta}.
-		\SG{ change to von Mises instead of $ \tau _{ 12 }$? }\RK{done something}}
+		\caption{Velocity profile (a), von Mises stress (b) and shear stress (c) for methyl cellulose in a typical RT-DC geometry. For the calculated viscosity see figure~\ref{fig:Nozzle/RT-DC_eta}.}
 		\label{fig:RT-DC}
 	\end{figure}
-
-\SG{ decide whether we want to show a viscosity plot and remove or leave this part:
-If one would divide the stress in these two regions by the strain rate in an attempt to obtain a viscosity one would find an extremely low and an extremely high viscosity respectively.
-Depending on the exact parameters "viscosities" can be reached that cannot be obtained through rheological measurements with the fluid.
-Meaning these viscosities are not valid.
-This is even clearer along the walls directly after the outlet.
-Here the viscosites obtained in this manner become negative.
-This shows the breakdown of the viscosity interpretation in viscoelastic cases and signifies the regions of interesting behavior.
-This also shows why viscoelastic simulations cannot always be replaced by shear thinning models and should be considered despite the high computational cost.
-}\RK{plot would probably be better}\todo{describe and reference plot as it looks terrible}
 
@@
 \end{equation}
-\SG{ This equation does not work, $ \dot{ \gamma  }$ is a shear rate, it should read $ \partial u_x / \partial y = \dot{ \gamma  }$.
-}\RK{done, was supposed to read g(y) but could not read my own handwriting when copying...
-Made it a little more clear}
 
@@
 This replacement is also much more relevant there as here all ys disappear}
-With $\Tr\ma{\tau} = \tau_{xx}$. \SG{ should be $ \tau _{ xx }$? }\RK{yes}
+With $\Tr\ma{\tau} = \tau_{xx}$.
 Eliminating $\tau_{xy}$ yields the following.
@@
 \end{equation}
-This is solved by the Lambert $W$ function as follows.
+This is solved by the Lambert $W$ function as follows.\todo{split 2D and 3D derivation}
 \begin{equation}
-	\tau_{xx} = \frac{\eta_\text{p}}{2\epsilon\lambda}W_0\left(4\epsilon\lambda^2\dot{\gamma}^2\right)
+	\tau_{xx} = \frac{\eta_\text{p}}{2\epsilon\lambda}W_0\left(4\epsilon\lambda^2\dot{\gamma}^2\right)\label{eq:tau_xx}
 \end{equation}
-With $\tau_{yy} = 0$ this yields the following.
+With $\tau_{yy} = 0$ this yields the first normal stress difference $N_1$ as follows. The second normal stress difference is proportional to $\xi$ and therefore $0$.
 \begin{equation}
@@
 	\begin{equation}
-		r = c\dot{\gamma} - R_\eta\frac{c}{d}\sqrt{W_0\left(d^2\dot{\gamma}^2\right)}
+		r = c\dot{\gamma} - R_\eta\frac{c}{d}\sqrt{W_0\left(d^2\dot{\gamma}^2\right)}\label{eq:semiAnalyticGD}
 	\end{equation}
@@
 For large ones, the error appears to become independent of $\alpha_\text{s}$.
-This indicates, that the observed difference might be due to the Mach number changing for different $\alpha_\text{s}$ and not due to the shuffling itself.\RK{I could probably prove this by running sims at different $\alpha_s$ that consistently are at Ma << 1}}
+This indicates, that the observed difference might be due to the Mach number changing for different $\alpha_\text{s}$ and not due to the shuffling itself.
+This is due lower $\alpha_\text{s}$ leading to lower LBM viscosities and such to higher Mach numbers.}
 		\label{fig:ShuffleInPoiseuille}
-	\end{figure}\todo{reference in main text}
+	\end{figure}
 

### 2024-02-29 assets/python/fig:Nozzle.py

@@ -129,8 +129,8 @@ def process():
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
     plt.title("(a)", loc="left", pad=45, x=-0.1)
-    plt.plot(x * L0 * 1e3, upper * L0 * 1e3, "k", linewidth=0.5)
-    plt.plot(x * L0 * 1e3, lower * L0 * 1e3, "k", linewidth=0.5)
+    # plt.plot(x * L0 * 1e3, upper * L0 * 1e3, "k", linewidth=0.5)
+    # plt.plot(x * L0 * 1e3, lower * L0 * 1e3, "k", linewidth=0.5)
     plt.imshow(
         vSlice.T,
         cmap="coolwarm",
@@ -151,8 +151,8 @@ def process():
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
     plt.title("(b)", loc="left", pad=45, x=-0.1)
-    plt.plot(x * L0 * 1e3, upper * L0 * 1e3, "k", linewidth=0.5)
-    plt.plot(x * L0 * 1e3, lower * L0 * 1e3, "k", linewidth=0.5)
+    # plt.plot(x * L0 * 1e3, upper * L0 * 1e3, "k", linewidth=0.5)
+    # plt.plot(x * L0 * 1e3, lower * L0 * 1e3, "k", linewidth=0.5)
     plt.imshow(
         vonMiesesSlice.T,
         cmap="coolwarm",
@@ -174,8 +174,8 @@ def process():
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
     plt.title("(c)", loc="left", pad=45, x=-0.1)
-    plt.plot(x * L0 * 1e3, upper * L0 * 1e3, "k", linewidth=0.5)
-    plt.plot(x * L0 * 1e3, lower * L0 * 1e3, "k", linewidth=0.5)
+    # plt.plot(x * L0 * 1e3, upper * L0 * 1e3, "k", linewidth=0.5)
+    # plt.plot(x * L0 * 1e3, lower * L0 * 1e3, "k", linewidth=0.5)
     plt.imshow(
         tau12.T,
         cmap="coolwarm",
@@ -206,8 +206,8 @@ def process():
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
     plt.title("(a)", loc="left", pad=45, x=-0.1)
[…]

### 2024-03-01 NovelLBM.tex
3D shear

@@
 \usepackage{colortbl} %colored table rows and columns
+
+\usepackage{mleftright}
+\mleftright
 
@@
 \DeclareMathOperator{\Dif}{D}
+\DeclareMathOperator{\sgn}{sgn}
 
@@
 \begin{equation}
-	f_i\left(\vec{x}+\vec{c_i}\Delta t, t+\Delta t\right) - f_i\left(\vec{x}, t\right) = -\frac{\Delta t}{\tau_\text{r}}\left[f_i\left(\vec{x}, t\right) - f_i^\text{eq}\left(\vec{x}, t\right) + B_i\right]
+	f_i\left(\vec{x}+\vec{c}_i\Delta t, t+\Delta t\right) - f_i\left(\vec{x}, t\right) = -\frac{\Delta t}{\tau_\text{r}}\left[f_i\left(\vec{x}, t\right) - f_i^\text{eq}\left(\vec{x}, t\right) + B_i\right]
 \end{equation}
@@
 \begin{equation}
-	B_i = w_i\left(\frac{\vec{c_i}\vec{c_i}}{2c_\text{s}^4}-\frac{\uT}{2c_\text{s}^2}\right):\ma{\tau}
+	B_i = w_i\left(\frac{\vec{c}_i\vec{c}_i}{2c_\text{s}^4}-\frac{\uT}{2c_\text{s}^2}\right):\ma{\tau}
 \end{equation}
@@
 \label{app:semianalyticalPoiseuille}
-Our derivation is \RK{hier könnte ein Adjektiv stehen} to the one in Oliveira \cite{oliveira1999}. For both Poiseuille flow and shear flow, we assume that the velocity is unidirectional:
+Our derivation is similar to the one in Oliveira \cite{oliveira1999}.
+The origin is placed in the center of the channel.
+The $x$-axis points in flow direction.
+For the two-dimensional case the $y$-axis points along the velocity gradient.
+We separate the derivation for two and three dimensions for mathematical clarity. They are however similar. We start with shear flow in the two-dimensional case.\todo{maybe}
+\subsection{Shear flow}
+For both Poiseuille flow and shear flow, symmetry dictates that the velocity is unidirectional:
 \begin{equation}
-	\vec{u} = u_x\left(y\right)\hat{e}_x
+	\vec{u} = u_x\left(r\right)\hat{e}_x
 \end{equation}
 \begin{equation}
-	\dot{\gamma}\left(y\right) = \frac{\partial u_x}{\partial y}
+	\dot{\gamma}\left(r\right) = \frac{\partial u_x}{\partial r} = \sgn\left(y\right)\frac{\partial u_x}{\partial y} \leq 0
 \end{equation}
+With $r = \abs{y}$.
+For pure shear flow, $\dot{\gamma}$ is a constant.
 
-With this the constitutive equation~(\ref{eq:polymerStress}) for $\xi=0$ in steady state reduces to
+With this the constitutive equation~(\ref{eq:polymerStress}) for $\xi=0$ in steady state reduces to the following. Note, that $\ma{\tau}$ is symmetric.\RK{Am I allowed to assume this is trivial?}
 \begin{align}
-	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xx} &= 2\lambda\dot{\gamma}\tau_{xy} \label{eq:PTTDerivation1}\\
-	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xy} &= \eta_\text{p}\dot{\gamma} \label{eq:PTTDerivation2}
+	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xx} &= 2\lambda\sgn\left(y\right)\dot{\gamma}\tau_{xy}\\
+	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xy} &= \eta_\text{p}\sgn\left(y\right)\dot{\gamma}
 \end{align}
-for a planar flow.
-In axisymmetric flows $y$ in eqs.~(\ref{eq:PTTDerivation1}, \ref{eq:PTTDerivation2}) needs to be replaced by the radial coordinate $r$.
-\RK{2D case is also axisymmetric?}\SG{ no factor 2?
-}\RK{No, factor 2 comes from the NS eq.
-and thus is only relevant for Poiseuille solution.
-This replacement is also much more relevant there as here all ys disappear}
-With $\Tr\ma{\tau} = \tau_{xx}$.
-Eliminating $\tau_{xy}$ yields the following.
+With $\Tr\ma{\tau} = \tau_{xx}$. Note that all other components aside from $\tau_{xx}$ and $\tau_{xy}$/$\tau_{yx}$ are zero.
+We define $\tau_{xr} = \tau_{xy}\sgn\left(y\right) < 0$ to get the following.
+\begin{align}
+	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xx} &= 2\lambda\dot{\gamma}\tau_{xr} \label{eq:PTTDerivation1}\\
+	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xr} &= \eta_\text{p}\dot{\gamma} \label{eq:PTTDerivation2}
+\end{align}
+Eliminating $\tau_{xr}$ yields the following.
 \begin{equation}
@@
 \end{equation}
-This is solved by the Lambert $W$ function as follows.\todo{split 2D and 3D derivation}
+This is solved by the Lambert $W$ function as follows.
 \begin{equation}
@@
 \begin{equation}
-	N_1 = \sigma_{xx} - \sigma_{yy} = \tau_{xx} = \frac{\eta_\text{p}}{2\epsilon\lambda}W_0\left(4\epsilon \mathrm{Wi}^2\right) %\label{eq:shearN}
+	N_1 = \sigma_{xx} - \sigma_{yy} = \tau_{xx} = \frac{\eta_\text{p}}{2\epsilon\lambda}W_0\left(4\epsilon\mathrm{Wi}^2\right) %\label{eq:shearN}
 \end{equation}
@@
 \begin{align}
-	\eta &= \frac{\sigma_{xy}}{\dot{\gamma}} \\
-	&= \frac{\tau_{xy} + \eta_\text{s}\dot{\gamma}}{\dot{\gamma}} \\
+	\eta &= \frac{\sigma_{xr}}{\dot{\gamma}} \\
+	&= \frac{\tau_{xr} + \eta_\text{s}\dot{\gamma}}{\dot{\gamma}} \\
 	&= \eta\left(\dot{\gamma}\right) = \frac{\eta_\text{p}}{\exp\left[0.5W_0\left(4\epsilon \mathrm{Wi}^2\right)\right]} + \eta_\text{s} %\label{eq:shearEta}
 \end{align}
-This gives the relevant solutions for the shear flow. For Poiseuille flow, we start with the Cauchy momentum equation (neglecting gravity), which reads as follows.
+With $\sigma_{xr} = \sigma_{xy}\sgn\left(y\right) < 0$.
+This gives the relevant solutions for shear flow. However, these equations also hold for Poiseuille flow.
+
+In three dimensions we pick cylindrical coordinates as follows.
+\begin{align}
+	x &= x\\
+	y &= r\cos\varphi\\
+	z &= r\sin\varphi
+\end{align}
+Limiting $\varphi$ to $\varphi\in\left\{0, \pi\right\}$ reproduces the above definition of $r$ in two dimensions.
+Other than this expansion of the definitions, the equations from above are the same in three dimension as they are in two.
+\RK{The definitions of $r$ above are entirely valid in 2D and picked in a way to make the signs consistent with 3D.
+In my opinion this means, that we do not need to show the calculation here.
+But I could if you want multiple pages of boring math.
+See:}
+
+\RK{
+
+\begin{equation}
+	\nabla\vec{u} = \frac{\partial u_x}{\partial r}\hat{e}_r\otimes\hat{e}_x
+\end{equation}
+\begin{equation}
+	\ma{\tau} = \tau_{ij}\hat{e}_i\otimes\hat{e}_j
+\end{equation}
+\begin{equation}
+\begin{split}
+	\left(\nabla\vec{u}\right)^\mathrm{T}\cdot\ma{\tau} = \frac{\partial u_x}{\partial r}\hat{e}_x\otimes\hat{e}_r&\left(\tau_{xx}\hat{e}_x\otimes\hat{e}_x+\tau_{xr}\hat{e}_x\otimes\hat{e}_r+\tau_{x\varphi}\hat{e}_x\otimes\hat{e}_\varphi\right.\\
+	&+\tau_{rx}\hat{e}_r\otimes\hat{e}_x+\tau_{rr}\hat{e}_r\otimes\hat{e}_r+\tau_{r\varphi}\hat{e}_r\otimes\hat{e}_\varphi\\
+	&\left.{ }+\tau_{\varphi x}\hat{e}_\varphi\otimes\hat{e}_x+\tau_{\varphi r}\hat{e}_\varphi\otimes\hat{e}_r+\tau_{\varphi\varphi}\hat{e}_\varphi\otimes\hat{e}_\varphi\right)
+\end{split}
+\end{equation}
+\begin{equation}
+	\left(\nabla\vec{u}\right)^\mathrm{T}\cdot\ma{\tau} = \frac{\partial u_x}{\partial r}\left(\tau_{rx}\hat{e}_x\otimes\hat{e}_x+\tau_{rr}\hat{e}_x\otimes\hat{e}_r+\tau_{r\varphi}\hat{e}_x\otimes\hat{e}_\varphi\right)
+\end{equation}
+Make other term via transpose.
+\begin{equation}
+	\begin{split}
+		0 &= \frac{\partial u_x}{\partial r}\left[2\tau_{rx}\hat{e}_x\otimes\hat{e}_x+\tau_{rr}\left(\hat{e}_x\otimes\hat{e}_r+\hat{e}_r\otimes\hat{e}_x\right)+\tau_{r\varphi}\hat{e}_x\otimes\hat{e}_\varphi + \tau_{r\varphi}\hat{e}_\varphi\otimes\hat{e}_x\right]\\
+		&- \exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\frac{\ma{\tau}}{\lambda} + \frac{\eta_\text{p}}{\lambda}\frac{\partial u_x}{\partial r}\left(\hat{e}_r\otimes\hat{e}_x + \hat{e}_x\otimes\hat{e}_r\right)
+	\end{split}
+\end{equation}
+If $\hat{e}_i\otimes\hat{e}_j$ does not appear in this equation $\tau_{ij} = 0$.
+\begin{equation}
+	0 = \frac{\partial u_x}{\partial r}\left[2\tau_{rx}\hat{e}_x\otimes\hat{e}_x\right]- \exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\frac{\ma{\tau}}{\lambda} + \frac{\eta_\text{p}}{\lambda}\frac{\partial u_x}{\partial r}\left(\hat{e}_r\otimes\hat{e}_x + \hat{e}_x\otimes\hat{e}_r\right)
+\end{equation}
+If $\ma{\tau}$ is symmetric $\tau_{rx} = \tau_{xr}$.
+\begin{equation}
+	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\frac{\ma{\tau}}{\lambda} = \dot{\gamma}\left[2\tau_{xr}\hat{e}_x\otimes\hat{e}_x\right] + \frac{\eta_\text{p}}{\lambda}\dot{\gamma}\left(\hat{e}_r\otimes\hat{e}_x + \hat{e}_x\otimes\hat{e}_r\right)
+\end{equation}
+Separate by components.
+\begin{align}
+	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xx} &= 2\lambda\dot{\gamma}\tau_{xr} \\
+	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xr} &= \eta_\text{p}\dot{\gamma}
+\end{align}
+The trace works out to:
+\begin{equation}
+	\Tr\ma{\tau} = \tau_{xx} + \tau_{rr} + \tau_{\varphi\varphi} = \tau_{xx}
+\end{equation}
+TODO: $N_1$? Defined along shear axis or always yy? ends up as $\tau_{xx}$ either way
+
+}
+
+\subsection{Channel flow}
+For Poiseuille flow, we start with the Cauchy momentum equation (neglecting gravity), which reads as follows.
+\begin{equation}
+	\rho\frac{\Dif\vec{u}}{\Dif t} = -\nabla p + \nabla\cdot\sigma
+\end{equation}
+In steady state for this geometry, once integrated along $y$, this reduces to the following.
+\begin{equation}
+	\sigma_{xy} = \frac{\partial p}{\partial x}y
+\end{equation}
+The total stress experienced by the fluid is the one described by the constitutive equation plus the solvent contribution and thus the following holds.
+\begin{equation}
+	\tau_{xy} = \partial_xpy - \eta_\text{s}\dot{\gamma}
+\end{equation}
+Dividing equation~(\ref{eq:PTTDerivation1_2D}) by equation~(\ref{eq:PTTDerivation2_2D}) leads to the following relation.
+\begin{equation}
+	\tau_{xx} = \frac{2\lambda}{\eta_\text{p}}\tau_{xy}^2 =  \frac{2\lambda}{\eta_\text{p}}\left(\partial_xpy - \eta_\text{s}\dot{\gamma}\right)^2
+\end{equation}
+Inserting this back into equation~(\ref{eq:PTTDerivation2_2D}) yields the following.
+\begin{align}
+	\dot{\gamma} &= \exp\left(\frac{2\epsilon\lambda^2}{\eta_\text{p}^2}\left[\partial_xpy - \eta_\text{s}\dot{\gamma}\right]^2\right)\frac{1}{\eta_\text{p}}\left(\partial_xpy-\eta_\text{s}\dot{\gamma}\right)
+	\intertext{This cannot be integrated as easily as without $\eta_\text{s}$, and is only solvable semi-analytically.}
+	1 &= \exp\left(\frac{2\epsilon\lambda^2}{\eta_\text{p}^2}\left[\partial_xpy - \eta_\text{s}\dot{\gamma}\right]^2\right)\frac{1}{\eta_\text{p}}\left(\partial_xp\frac{y}{\dot{\gamma}}-\eta_\text{s}\right) \\
+	0 &= \frac{2\epsilon\lambda^2}{\eta_\text{p}^2}\left[\partial_xpy - \eta_\text{s}\dot{\gamma}\right]^2 - \ln\eta_\text{p} + \ln\left(\partial_xp\frac{y}{\dot{\gamma}}-\eta_\text{s}\right) \\
+	0 &= 2\epsilon\lambda^2\dot{\gamma}^2\left[\partial_xp\frac{y}{\dot{\gamma}\eta_\text{p}} - \frac{\eta_\text{s}}{\eta_\text{p}}\right]^2 + \ln\left(\partial_xp\frac{y}{\dot{\gamma}\eta_\text{p}}-\frac{\eta_\text{s}}{\eta_\text{p}}\right) \\
+	0 &= 2\epsilon\lambda^2\dot{\gamma}^2\left[\partial_xp\frac{y}{\dot{\gamma}\eta_\text{p}} - \frac{\eta_\text{s}}{\eta_\text{p}}\right]^2 + \ln\left(\partial_xp\frac{y}{\dot{\gamma}\eta_\text{p}}-\frac{\eta_\text{s}}{\eta_\text{p}}\right)
+	\intertext{This has the following form}
+	0 &= ab^2 + \ln b
+\end{align}
+This can be solved using the Lambert $W$ function as follows.
+\begin{align}
+	b &= \sqrt{\frac{W_0\left(2a\right)}{2a}}
+	\intertext{Resolving for $y$ yields the following.}
+	y &= \frac{\eta_\text{s}}{\partial_xp}\dot{\gamma} + \sgn\left(\dot{\gamma}\right)\frac{\eta_\text{p}}{2\lambda\sqrt{\epsilon}\partial_xp}\sqrt{W_0\left(4\epsilon\lambda^2\dot{\gamma}^2\right)}
+\end{align}
+We notice, that this is the solution for a poiseuille flow with viscosity $\eta_\text{s}$ expanded by a term that applies a nonuniform scaling of the profile  along the $y$-axis towards higher absolute values.
+We simplify again using $c < 0$ and $d > 0$.
+\begin{equation}
+	y = c\dot{\gamma} - R_\eta\frac{c}{d}\sqrt{W_0\left(d^2\dot{\gamma}^2\right)}\label{eq:semiAnalyticGD_2D}
+\end{equation}\todo{sign and rest of explainer at the end?}
+Finally this function needs to be inverted.
+This needs to be done numerically.
+We calculate a range of $\dot{\gamma}$ from $0$ to $\frac{R}{c}$ with a small step interval.
+Here $R$ is the radius of the channel or pipe.
+This is guaranteed to contain all relevant radii.
+We flip the axis and integrate numerically using \pyth{scipy.integrate.cumulative_trapezoid} \cite{scipy}.
+This is very accurate as we conveniently picked the spacing of our now $x$-axis in a way, that the $y$-axis ($\dot{\gamma}$) varies little for each step.
+From the recovered curve $u$ is calculated at each required $r$ through linear interpolation.
+
+\subsection{Pipe flow}
+
+For Poiseuille flow, we start with the Cauchy momentum equation (neglecting gravity), which reads as follows.
 \begin{equation}
@@
 	\begin{equation}
-		r = c\dot{\gamma} - R_\eta\frac{c}{d}\sqrt{W_0\left(d^2\dot{\gamma}^2\right)}\label{eq:semiAnalyticGD}
+		r = c\dot{\gamma} - R_\eta\frac{c}{d}\sqrt{W_0\left(d^2\dot{\gamma}^2\right)}\label{eq:semiAnalyticGD_3D}
 	\end{equation}

### 2024-03-04 NovelLBM.tex
note
derivation expanded

--- 2024-02-29 NovelLBM.tex
@@
 \label{app:semianalyticalPoiseuille}
-Our derivation is \RK{hier könnte ein Adjektiv stehen} to the one in Oliveira \cite{oliveira1999}. For both Poiseuille flow and shear flow, we assume that the velocity is unidirectional:
+Our derivation is similar to the one in Oliveira \cite{oliveira1999}. The origin is placed in the center of the channel. The $x$-axis points in flow direction.
+We solve both the three-dimensional and the two-dimensional case. In three dimensions we pick cylindrical coordinates as follows.
+\begin{align}
+	x &= x\\
+	y &= r\cos\varphi\\
+	z &= r\sin\varphi
+\end{align}
+This unusual choice is to keep the coordinate systems consistent between the two- and three-dimensional cases.
+For two dimensions the $y$-axis points along the velocity gradient.
+This follows from the 3D case limiting $\varphi$ to $\varphi\in\left\{0, \pi\right\}$.
+Consequently, we define $r = \abs{y}$ in the 2D case.
+Note, that in 2D this leads to the sign being tracked explicitly as follows.
 \begin{equation}
-	\vec{u} = u_x\left(y\right)\hat{e}_x
-\end{equation}
-\begin{equation}
-	\dot{\gamma}\left(y\right) = \frac{\partial u_x}{\partial y}
+	\frac{\partial}{\partial r} =  \sgn\left(y\right)\frac{\partial}{\partial y}
 \end{equation}
 
-With this the constitutive equation~(\ref{eq:polymerStress}) for $\xi=0$ in steady state reduces to
+For both Poiseuille flow and shear flow, symmetry dictates, that the velocity is unidirectional:
+\begin{equation}
+	\vec{u} = u_x\left(r\right)\hat{e}_x
+\end{equation}
+We also define the shear rate as follows.
+\begin{equation}
+\dot{\gamma}\left(r\right) = \frac{\partial u_x}{\partial r} \leq 0
+\end{equation}
+Note, that with this the shear rate is always negative. Also, $\dot{\gamma}$ is a constant for pure shear flow.
+
+We start with the solutions of the constitutive equation.
+\subsection{Shear solutions}
+In two dimensions, the constitutive equation~(\ref{eq:polymerStress}) for $\xi=0$ in steady state easily reduces to the following. Note, that $\ma{\tau}$ is symmetric.
 \begin{align}
-	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xx} &= 2\lambda\dot{\gamma}\tau_{xy} \label{eq:PTTDerivation1}\\
-	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xy} &= \eta_\text{p}\dot{\gamma} \label{eq:PTTDerivation2}
+	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xx} &= 2\lambda\sgn\left(y\right)\dot{\gamma}\tau_{xy}\\
+	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xy} &= \eta_\text{p}\sgn\left(y\right)\dot{\gamma}
 \end{align}
-for a planar flow.
-In axisymmetric flows $y$ in eqs.~(\ref{eq:PTTDerivation1}, \ref{eq:PTTDerivation2}) needs to be replaced by the radial coordinate $r$.
-\RK{2D case is also axisymmetric?}\SG{ no factor 2?
-}\RK{No, factor 2 comes from the NS eq.
-and thus is only relevant for Poiseuille solution.
-This replacement is also much more relevant there as here all ys disappear}
-With $\Tr\ma{\tau} = \tau_{xx}$.
-Eliminating $\tau_{xy}$ yields the following.
+With $\Tr\ma{\tau} = \tau_{xx}$. Note that all other components aside from $\tau_{xx}$ and $\tau_{xy}$/$\tau_{yx}$ are zero.
+We define $\tau_{xr} = \tau_{xy}\sgn\left(y\right) \leq 0$ to get the following.
+\begin{align}
+	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xx} &= 2\lambda\dot{\gamma}\tau_{xr} \label{eq:PTTDerivation1}\\
+	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xr} &= \eta_\text{p}\dot{\gamma} \label{eq:PTTDerivation2}
+\end{align}
+
+The three-dimensional case yields the same formula using significantly more math.
+We set $\xi=0$ and start from the velocity gradient.
+\begin{equation}
+	\nabla\vec{u} = \frac{\partial u_x}{\partial r}\hat{e}_r\otimes\hat{e}_x
+\end{equation}
+This, together with the general formula for $\ma{\tau}$,
+\begin{equation}
+	\ma{\tau} = \tau_{ij}\hat{e}_i\otimes\hat{e}_j
+\end{equation}
+is used to find the non-zero terms of the upper convected derivative in steady state as follows.
+\begin{equation}
+	\begin{split}
+		\left(\nabla\vec{u}\right)^\mathrm{T}\cdot\ma{\tau} = \frac{\partial u_x}{\partial r}\hat{e}_x\otimes\hat{e}_r&\left(\tau_{xx}\hat{e}_x\otimes\hat{e}_x+\tau_{xr}\hat{e}_x\otimes\hat{e}_r+\tau_{x\varphi}\hat{e}_x\otimes\hat{e}_\varphi\right.\\
+		&+\tau_{rx}\hat{e}_r\otimes\hat{e}_x+\tau_{rr}\hat{e}_r\otimes\hat{e}_r+\tau_{r\varphi}\hat{e}_r\otimes\hat{e}_\varphi\\
+		&\left.{ }+\tau_{\varphi x}\hat{e}_\varphi\otimes\hat{e}_x+\tau_{\varphi r}\hat{e}_\varphi\otimes\hat{e}_r+\tau_{\varphi\varphi}\hat{e}_\varphi\otimes\hat{e}_\varphi\right)
+	\end{split}
+\end{equation}
+With the orthonormality
+\begin{equation}
+	\hat{e}_a\otimes\hat{e}_b\hat{e}_c\otimes\hat{e}_d = \hat{e}_a\hat{e}_b^\mathrm{T}\hat{e}_c\hat{e}_d^\mathrm{T} = \hat{e}_a\left(\hat{e}_b\cdot\hat{e}_c\right)\hat{e}_d^\mathrm{T} = \hat{e}_a\left(\delta_{bc}\right)\hat{e}_d^\mathrm{T} = \delta_{bc}\hat{e}_a\otimes\hat{e}_d
+\end{equation}
+we can reduce this to the following.
+\begin{equation}
+	\left(\nabla\vec{u}\right)^\mathrm{T}\cdot\ma{\tau} = \frac{\partial u_x}{\partial r}\left(\tau_{rx}\hat{e}_x\otimes\hat{e}_x+\tau_{rr}\hat{e}_x\otimes\hat{e}_r+\tau_{r\varphi}\hat{e}_x\otimes\hat{e}_\varphi\right)
+\end{equation}
+The second non-zero term in the upper convected derivative due to the symmetry of $\ma{\tau}$ is the transpose of this.
+Together with the strain rate tensor, which is calculated using the velocity gradient from above, the complete constitutive equation reads:
+\begin{equation}
+	\begin{split}
+		0 &= \frac{\partial u_x}{\partial r}\left[2\tau_{rx}\hat{e}_x\otimes\hat{e}_x+\tau_{rr}\left(\hat{e}_x\otimes\hat{e}_r+\hat{e}_r\otimes\hat{e}_x\right)+\tau_{r\varphi}\left(\hat{e}_x\otimes\hat{e}_\varphi + \hat{e}_\varphi\otimes\hat{e}_x\right)\right]\\
+		&- \exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\frac{\ma{\tau}}{\lambda} + \frac{\eta_\text{p}}{\lambda}\frac{\partial u_x}{\partial r}\left(\hat{e}_r\otimes\hat{e}_x + \hat{e}_x\otimes\hat{e}_r\right)
+	\end{split}
+\end{equation}
+We separate this equation by components, meaning if $\hat{e}_i\otimes\hat{e}_j$ does not appear in this equation $\tau_{ij} = 0$.
+\begin{equation}
+	0 = \frac{\partial u_x}{\partial r}\left[2\tau_{rx}\hat{e}_x\otimes\hat{e}_x\right]- \exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\frac{\ma{\tau}}{\lambda} + \frac{\eta_\text{p}}{\lambda}\frac{\partial u_x}{\partial r}\left(\hat{e}_r\otimes\hat{e}_x + \hat{e}_x\otimes\hat{e}_r\right)
+\end{equation}
+The symmetry of $\ma{\tau}$ also holds in cylindrical coordinates, meaning $\tau_{rx} = \tau_{xr}$. We reorder accordingly.
+\begin{equation}
+	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\frac{\ma{\tau}}{\lambda} = \dot{\gamma}\left[2\tau_{xr}\hat{e}_x\otimes\hat{e}_x\right] + \frac{\eta_\text{p}}{\lambda}\dot{\gamma}\left(\hat{e}_r\otimes\hat{e}_x + \hat{e}_x\otimes\hat{e}_r\right)
+\end{equation}
+We separate the components once more. Yielding two unique equations.
+\begin{align}
+	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xx} &= 2\lambda\dot{\gamma}\tau_{xr} \\
+	\exp\left(\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}\right)\tau_{xr} &= \eta_\text{p}\dot{\gamma}
+\end{align}
+The trace con be found to be:
+\begin{equation}
+	\Tr\ma{\tau} = \tau_{xx} + \tau_{rr} + \tau_{\varphi\varphi} = \tau_{xx}
+\end{equation}
+As stated above this solution has the same form as for the two-dimensional case. Therefore, the following holds for both cases.
+We eliminate $\tau_{xr}$ yielding the following.
 \begin{equation}
@@
 \end{equation}
-With $\tau_{yy} = 0$ this yields the first normal stress difference $N_1$ as follows. The second normal stress difference is proportional to $\xi$ and therefore $0$.
+As already mentioned above most components of $\ma{\tau}$ are zero, using specifically
 \begin{equation}
-	N_1 = \sigma_{xx} - \sigma_{yy} = \tau_{xx} = \frac{\eta_\text{p}}{2\epsilon\lambda}W_0\left(4\epsilon \mathrm{Wi}^2\right) %\label{eq:shearN}
+	0 = \begin{cases}
+		\tau_{yy} = \sigma_{yy},\quad\text{in 2D} \\
+		\tau_{rr} = \sigma_{rr},\quad\text{in 3D}
+	\end{cases}
+\end{equation}
+yields the first normal stress difference $N_1$ as follows. The second normal stress difference is proportional to $\xi$ and therefore $0$.
+\begin{equation}
+	N_1 = \sigma_{xx} - \begin{cases}
+		\sigma_{yy},\quad\text{in 2D} \\
+		\sigma_{rr},\quad\text{in 3D}
+	\end{cases} = \tau_{xx} = \frac{\eta_\text{p}}{2\epsilon\lambda}W_0\left(4\epsilon\mathrm{Wi}^2\right) %\label{eq:shearN}
 \end{equation}
@@
 \begin{align}
-	\eta &= \frac{\sigma_{xy}}{\dot{\gamma}} \\
-	&= \frac{\tau_{xy} + \eta_\text{s}\dot{\gamma}}{\dot{\gamma}} \\
+	\eta &= \frac{\sigma_{xr}}{\dot{\gamma}} \\
+	&= \frac{\tau_{xr} + \eta_\text{s}\dot{\gamma}}{\dot{\gamma}} \\
 	&= \eta\left(\dot{\gamma}\right) = \frac{\eta_\text{p}}{\exp\left[0.5W_0\left(4\epsilon \mathrm{Wi}^2\right)\right]} + \eta_\text{s} %\label{eq:shearEta}
 \end{align}
-This gives the relevant solutions for the shear flow. For Poiseuille flow, we start with the Cauchy momentum equation (neglecting gravity), which reads as follows.
+With $\sigma_{xr} = \sigma_{xy}\sgn\left(y\right) \leq 0$ in the 2D case analogous to $\tau_{xr}$.
+This concludes the relevant solutions for shear flow. However, these equations also hold for Poiseuille flow. Next we calculate the velocity profile for Poiseuille flow.
+\subsection{Velocity profile}
+We start with the Cauchy momentum equation (neglecting gravity), which reads as follows.
 \begin{equation}
-	\rho\frac{\Dif\vec{u}}{\Dif t} = -\nabla p + \nabla\cdot\sigma
+	\rho\frac{\Dif\vec{u}}{\Dif t} = -\nabla p + \nabla\cdot\ma{\sigma}
 \end{equation}
-In steady state for this geometry, once integrated along $y$, this reduces to the following.
+In steady state for this geometry in two dimensions, this reduces to the following.
 \begin{equation}
-	\sigma_{xy} = \frac{\partial p}{\partial x}\frac{y}{2^j}
+	\frac{\partial \sigma_{xr}}{\partial r} = \frac{\partial p}{\partial x}
 \end{equation}
-Here $j$ is $0$ for the two-dimensional case and $1$ in the three-dimensional flow.
-The total stress experienced by the fluid is the one described by the constitutive equation plus the solvent contribution and thus the following holds.
+In three dimensions there is a slight difference. We start from the stress.
 \begin{equation}
-	\tau_{xy} = \partial_xp\frac{r}{2^j} - \eta_\text{s}\dot{\gamma}
+	\ma{\sigma} =  \ma{\tau} + 2\eta_\text{s}\ma{D} = \ma{\tau} + \eta_\text{s}\left(\hat{e}_{x}\otimes\hat{e}_{r} + \hat{e}_{r}\otimes\hat{e}_{x}\right)
 \end{equation}
-Here we switched from y to writing $y$ to $r$ in order to clarify, that this is a radial coordinate being $0$ in the center of the channel for both cases.
+Therefor as seen for $\ma{\tau}$ above, $\ma{\sigma}$ also only has $\sigma_{xx}$, $\sigma_{xr}$, $\sigma_{rx}$ components.
+Furthermore, from symmetry $x$ and $\varphi$ derivatives of $\ma{\sigma}$ are zero.
+This reduces the divergence to the following.
+\begin{equation}
+	\nabla\cdot\sigma = \frac{\partial \sigma_{xr}}{\partial r}\hat{e}_x + \frac{\sigma_{xr}}{r}\hat{e}_x
+\end{equation}
+Notably this leads to a different reduced Cauchy momentum equation than for the 2D case.
+\begin{equation}
+	\frac{\partial \sigma_{xr}}{\partial r} + \frac{\sigma_{xr}}{r} = \frac{\partial p}{\partial x}
+\end{equation}
+However, due to the convenient form of the additional term both cases are solved by the following.
+\begin{equation}
+	\sigma_{xr} = \frac{\partial p}{\partial x}\frac{r}{2^j}
+\end{equation}
+Here $j$ is $0$ for the two-dimensional case and $1$ in the three-dimensional flow. From here the solution is independent of the dimensionality again.
+The total stress experienced by the fluid is the one described by the constitutive equation plus the solvent contribution, which can also be written as follows.
+\begin{equation}
+	\tau_{xr} = \partial_xp\frac{r}{2^j} - \eta_\text{s}\dot{\gamma}
+\end{equation}
 Dividing equation~(\ref{eq:PTTDerivation1}) by equation~(\ref{eq:PTTDerivation2}) leads to the following relation.
 \begin{equation}
-	\tau_{xx} = \frac{2\lambda}{\eta_\text{p}}\tau_{xy}^2 =  \frac{2\lambda}{\eta_\text{p}}\left(\partial_xp\frac{r}{2^j} - \eta_\text{s}\dot{\gamma}\right)^2
+	\tau_{xx} = \frac{2\lambda}{\eta_\text{p}}\tau_{xr}^2 =  \frac{2\lambda}{\eta_\text{p}}\left(\partial_xp\frac{r}{2^j} - \eta_\text{s}\dot{\gamma}\right)^2
 \end{equation}
@@
 	\begin{align}
-		b &= -\sqrt{\frac{W_0\left(2a\right)}{2a}}
+		b &= \sqrt{\frac{W_0\left(2a\right)}{2a}}
 		\intertext{Resolving for $r$ yields the following.}

### 2024-03-05 NovelLBM.tex
L1 error definition

@@
 \end{equation}
-which gives \num{9e-4} and \num{1e-3} for alginate and methyl cellulose, respectively.
-The spatially resolved errors are shown in figure~\ref{fig:2DvelErr} in the appendix.
+Using the simulated velocities $\vec{u_i}$ and the semi-analytical results $\vec{u}$. This gives \num{9e-4} and \num{1e-3} for alginate and methyl cellulose, respectively.
+The spatially resolved L1 error defined as follows is shown in figure~\ref{fig:2DvelErr} in the appendix.
+\begin{equation}
+	e_\text{L1} = \frac{\vec{u_i} - \vec{u}\left(y_i\right)}{\vec{u}\left(y_i\right)}
+\end{equation}
+\RK{This error definition is new}
 These conclusions remain unchanged even when varying the pressure gradient, and thus the flow velocity, over many orders of magnitude as shown in figure~\ref{fig:pressureErr}~(a) of the appendix.
@@
 The resulting velocity profile can be seen in figure~\ref{fig:3Dvel} and shows almost equally good agreement as for the planar case with an L2 error of \num{0.014} and \num{0.06}, respectively.
-The spatially resolved error in figure~\ref{fig:3DvelErr} of the appendix shows that this larger average is indeed mainly attributable to the staircase effect as the error near the walls increases significantly.
+The spatially resolved L1 error in figure~\ref{fig:3DvelErr} of the appendix shows that this larger average is indeed mainly attributable to the staircase effect as the error near the walls increases significantly.
 The robustness against pressure gradient changes is shown in figure~\ref{fig:pressureErr}~(b) of the appendix.
@@
 The Oldroyd-B model is a special case of the PTT model which is obtained by setting $\xi = \epsilon = 0$ in eq.~(\ref{eq:polymerStress}) and is thus easily tractable with our code.\RK{was simulated with a direct Oldroyd-B implementation, which I now see was unnecessary...} \SG{ hast du mal kurz geprueft, ob dasselbe rauskommt?
-}\RK{Nein}\todo{check}
+}\RK{Ja, ist aber auch von code offensichtlich, der unterschied wird zur OpenCL compile time entfernt}
 In figure~\ref{fig:malaspinas2010}, we show the L2 error as function of lattice resolution for different values of $\mathrm{Wi}$ and $R_ \nu $ which is defined as \cite{malaspinas2010}
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErrWorst.pdf}
-		\caption{L2 error of the velocity profile in figure~\ref{fig:2Dvel} with respect to the semi-analytical theory in a planar Poiseuille flow for alginate (a) and methyl cellulose (b).
-			The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall.}\RK{this is linear error} \SG{ define }
+		\caption{L1 error of the velocity profile in figure~\ref{fig:2Dvel} with respect to the semi-analytical theory in a planar Poiseuille flow for alginate (a) and methyl cellulose (b).
+			The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall.}\RK{this is linear error} \SG{ define }\RK{done}
 		\label{fig:2DvelErr}
-	\end{figure}\todo{do}
+	\end{figure}
 
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErrWorst.pdf}
-		\caption{L2 error of the velocity profile in \ref{fig:3Dvel} with respect to the semi-analytical theory in a cylindrical Poiseuille flow for alginate (a) and methyl cellulose (b).
-			The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall.}\RK{this is linear error}
+		\caption{L1 error of the velocity profile in \ref{fig:3Dvel} with respect to the semi-analytical theory in a cylindrical Poiseuille flow for alginate (a) and methyl cellulose (b).
+			The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall.}
 		\label{fig:3DvelErr}

### 2024-03-05 assets/python/fig:2DAlginate.py

@@ -77,7 +77,7 @@ def process(i):
         # label=f"{i}",
     )
     plt.xlabel(r"$y/\unit{\micro\meter}$")
-    plt.ylabel(r"$error$")
+    plt.ylabel(r"$e_\text{L1}$")
     # plt.legend()
     plt.savefig("../plots/2DAlginateErr.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()

### 2024-03-05 assets/python/fig:2DParameterStudy.py

@@ -91,7 +91,7 @@ def process(index):
         label=f"{i}",
     )
     plt.xlabel(r"$r/\unit{\micro\meter}$")
-    plt.ylabel(r"$error$")
+    plt.ylabel(r"$e_\text{L1}$")
     plt.legend()
     plt.savefig(f"../plots/2DParameterStudyErr{i}.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()
@@ -175,7 +175,7 @@ def plotWorst(index=7):
         # label=f"{i}",
     )
     plt.xlabel(r"$y/\unit{\micro\meter}$")
-    plt.ylabel(r"$error$")
+    plt.ylabel(r"$e_\text{L1}$")
     # plt.legend()
     plt.savefig("../plots/2DParameterStudyErrWorst.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()
@@ -215,7 +215,7 @@ if __name__ == "__main__":
     plt.plot(Gs, errs, "rx")
     plt.xscale("log")
     plt.xlabel(r"$-\frac{\partial p}{\partial x}/\unit{\pascal\per\meter}$")
-    plt.ylabel(r"$error$")
+    plt.ylabel(r"$e_\text{L2}$")
     plt.savefig("../plots/2DParameterStudyErr.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()
 

### 2024-03-05 assets/python/fig:3DAlginate.py

@@ -77,7 +77,7 @@ def process(i):
         # label=f"{i}",
     )
     plt.xlabel(r"$r/\unit{\micro\meter}$")
-    plt.ylabel(r"$error$")
+    plt.ylabel(r"$e_\text{L1}$")
     # plt.legend()
     plt.savefig("../plots/3DAlginateErr.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()

### 2024-03-05 assets/python/fig:3DParameterStudy.py

@@ -91,7 +91,7 @@ def process(index):
         label=f"{i}",
     )
     plt.xlabel(r"$r/\unit{\micro\meter}$")
-    plt.ylabel(r"$error$")
+    plt.ylabel(r"$e_\text{L1}$")
     plt.legend()
     plt.savefig(f"../plots/3DParameterStudyErr{i}.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()
@@ -175,7 +175,7 @@ def plotWorst(index=7):
         # label=f"{i}",
     )
     plt.xlabel(r"$r/\unit{\micro\meter}$")
-    plt.ylabel(r"$error$")
+    plt.ylabel(r"$e_\text{L1}$")
     # plt.legend()
     plt.savefig("../plots/3DParameterStudyErrWorst.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()
@@ -215,7 +215,7 @@ if __name__ == "__main__":
     plt.plot(Gs, errs, "rx")
     plt.xscale("log")
     plt.xlabel(r"$-\frac{\partial p}{\partial x}/\unit{\pascal\per\meter}$")
-    plt.ylabel(r"$error$")
+    plt.ylabel(r"$e_\text{L2}$")
     plt.savefig("../plots/3DParameterStudyErr.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()
 

### 2024-03-05 assets/python/fig:ShuffleInPoiseuille.py

@@ -99,7 +99,7 @@ def process(index):
         # label=f"{i}",
     )
     plt.xlabel(r"$y/\unit{\micro\meter}$")
-    plt.ylabel(r"$error$")
+    plt.ylabel(r"$e_\text{L1}$")
     # plt.legend()
     # plt.savefig("../plots/2DParameterStudyErrWorst.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()
@@ -123,7 +123,7 @@ if __name__ == "__main__":
     plt.plot(r * 1e6, errs[1], "x", color=color(3), label=r"$\alpha_\text{s}=\num{1}$")
     plt.plot(r * 1e6, errs[2], "x", color=color(4), label=r"$\alpha_\text{s}=\num{10}$")
     plt.xlabel(r"$y/\unit{\micro\meter}$")
-    plt.ylabel(r"$error$")
+    plt.ylabel(r"$e_\text{L1}$")
     plt.legend()
     plt.savefig("../plots/ShuffleInPoiseuille.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()

### 2024-03-05 NovelLBM.tex
note

@@
 where $\ma{D}$ is the strain rate tensor.
-We note that extended forms of the PTT model with a Mittag-Leffler instead of an exponential function have been studied as well \cite{ferras2019}\todo{not really what we want to say here.
+We note that extended forms of the PTT model with a Mittag-Leffler instead of an exponential function have been studied as well \cite{ferras2019}\RK{not really what we want to say here.
 We took this formula mostly from there}.

### 2024-03-06 NovelLBM.tex
Consistent stresses

@@
 To quantify the total stress as a single number, we use the von Mises stress which is defined as \cite{Mueller.2023}:
-\begin{align}
-	\sigma_\text{vM} = \sqrt{\frac{1}{2}\left[\left(\sigma_1 - \sigma_2\right)^2 + \left(\sigma_2 - \sigma_3\right)^2 + \left(\sigma_3 - \sigma_1\right)^2\right]}.
-\end{align}
+\begin{equation}
+	\tau_\text{vM} = \sqrt{\frac{3}{2}\tau_{ij}^\text{dev}\tau_{ij}^\text{dev}}.
+\end{equation}
+With the deviator of the stress tensor defined as follows.
+\begin{equation}
+	\tau_{ij}^\text{dev} = \tau_{ij} - \frac{1}{3}\tau_{kk}
+\end{equation}
 It can be seen in figure~\ref{fig:Nozzle}~(b) that the highest stresses arise at the nozzle exit in direct vicinity to the wall.
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/Nozzle_v.pdf}
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/Nozzle_sigma_vM.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/Nozzle_tau_vM.pdf}
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/Nozzle_tau_12.pdf}
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_v.pdf}
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_sigma_vM.pdf}
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_tau.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_tau_vM.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_tau_12.pdf}
 		\caption{Velocity profile (a), von Mises stress (b) and shear stress (c) for methyl cellulose in a typical RT-DC geometry. For the calculated viscosity see figure~\ref{fig:Nozzle/RT-DC_eta}.}
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_eta.pdf}
-		\caption{"Viscosity" in a Nozzle (a) and RT-DC channel (b) calculated by dividing $\tau_{12}$ by the respective strain rate.
+		\caption{"Viscosity" in a Nozzle (a) and RT-DC channel (b) calculated by dividing $\tau_{12}$ by the respective strain rate and adding the solvent viscosity.
 This diverges along the center line, and thus it has been excluded.

### 2024-03-06 assets/python/fig:Nozzle.py

@@ -166,10 +166,10 @@ def process():
     )
     plt.xlabel(r"$x/\unit{\milli\meter}$")
     plt.ylabel(r"$y/\unit{\milli\meter}$")
-    plt.colorbar(location="top", label=r"$\sigma_\text{vM}/\unit{\pascal}$")
+    plt.colorbar(location="top", label=r"$\tau_\text{vM}/\unit{\pascal}$")
     plt.gca().spines["top"].set_visible(False)
     plt.gca().spines["right"].set_visible(False)
-    plt.savefig("../plots/Nozzle_sigma_vM.pdf", dpi=1200, bbox_inches="tight", pad_inches=0)
+    plt.savefig("../plots/Nozzle_tau_vM.pdf", dpi=1200, bbox_inches="tight", pad_inches=0)
     plt.show()
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))

### 2024-03-06 assets/python/fig:RT-DC.py

@@ -165,10 +165,10 @@ def process():
     )
     plt.xlabel(r"$x/\unit{\micro\meter}$")
     plt.ylabel(r"$y/\unit{\micro\meter}$")
-    plt.colorbar(location="top", label=r"$\sigma_\text{vM}/\unit{\pascal}$")
+    plt.colorbar(location="top", label=r"$\tau_\text{vM}/\unit{\pascal}$")
     plt.gca().spines["top"].set_visible(False)
     plt.gca().spines["right"].set_visible(False)
-    plt.savefig("../plots/RT-DC_sigma_vM.pdf", dpi=1200, bbox_inches="tight", pad_inches=0)
+    plt.savefig("../plots/RT-DC_tau_vM.pdf", dpi=1200, bbox_inches="tight", pad_inches=0)
     plt.show()
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
@@ -183,7 +183,7 @@ def process():
     plt.colorbar(location="top", label=r"$\tau_{12}/\unit{\pascal}$")
     plt.gca().spines["top"].set_visible(False)
     plt.gca().spines["right"].set_visible(False)
-    plt.savefig("../plots/RT-DC_tau.pdf", dpi=1200, bbox_inches="tight", pad_inches=0)
+    plt.savefig("../plots/RT-DC_tau_12.pdf", dpi=1200, bbox_inches="tight", pad_inches=0)
     plt.show()
 
     r"""

### 2024-03-08 NovelLBM.tex
small corrections

@@
 \end{equation}
-yields the first normal stress difference $N_1$ as follows. The second normal stress difference is proportional to $\xi$ and therefore $0$.
+yields the first normal stress difference $N_1$ as follows.
 \begin{equation}
@@
 \end{equation}
+The second normal stress difference, which is defined as follows, is zero on account of the components in the equation being zero.
+\begin{equation}
+	N_2 = \begin{cases}
+		\sigma_{yy} - \sigma_{zz} = \tau_{yy} - \tau_{zz},\quad\text{in 2D} \\
+		\sigma_{rr} - \sigma_{\varphi\varphi} = \tau_{rr} - \tau_{\varphi\varphi},\quad\text{in 3D}
+	\end{cases} = 0
+\end{equation}
+\RK{zz Komponente in 2D ist ein bischen fragwürdig...
+Da beißt mich jetzt, dass ich mit 2D eigentlich channel flow meine.
+Sollte man bei der geometrie oben evtl.
+erwähnen.
+$N_2$ proportional zu $\xi$ stimmt übrigens.
+Aufgrund von $\sigma_{ii} = \tau_{ii}$ kann man für $N_1$ und $N_2$ nämlich die Lösungen für $\eta_\text{s} = 0$ verwenden (siehe ferras\cite{ferras2019})}
 For the viscosity, we insert this into equation~(\ref{eq:PTTDerivation2}) and retrieve the following.
@@
 \subsection{Velocity profile}
-We start with the Cauchy momentum equation (neglecting gravity), which reads as follows.
+We start with the Navier-Stokes equation (neglecting gravity), which reads as follows.
 \begin{equation}
@@
 		0 &= \frac{2\epsilon\lambda^2}{\eta_\text{p}^2}\left[\partial_xp\frac{r}{2^j} - \eta_\text{s}\dot{\gamma}\right]^2 - \ln\eta_\text{p} + \ln\left(\partial_xp\frac{r}{2^j\dot{\gamma}}-\eta_\text{s}\right) \\
-		0 &= 2\epsilon\lambda^2\dot{\gamma}^2\left[\partial_xp\frac{r}{2^j\dot{\gamma}\eta_\text{p}} - \frac{\eta_\text{s}}{\eta_\text{p}}\right]^2 + \ln\left(\partial_xp\frac{r}{2^j\dot{\gamma}\eta_\text{p}}-\frac{\eta_\text{s}}{\eta_\text{p}}\right) \\
 		0 &= 2\epsilon\lambda^2\dot{\gamma}^2\left[\partial_xp\frac{r}{2^j\dot{\gamma}\eta_\text{p}} - \frac{\eta_\text{s}}{\eta_\text{p}}\right]^2 + \ln\left(\partial_xp\frac{r}{2^j\dot{\gamma}\eta_\text{p}}-\frac{\eta_\text{s}}{\eta_\text{p}}\right)

### 2024-03-11 assets/setups/RT-DC/1/setup/setup.cpp
typo

@@ -100,7 +100,7 @@ void example(SimulationOptions& options, Parameters& parameters) {
 	units.set_m_kg_s(1.0f, 1, rho, grid_SI, V0, rho_SI);
 
 
-	const double lambda_polymer_SI = 0.321-3;
+	const double lambda_polymer_SI = 0.321e-3;
 	const double lambda_polymer = lambda_polymer_SI/T0;
 	spdlog::info("lp: {}", lambda_polymer);
 	const double eta_polymer = eta_polymer_SI/mu0;

### 2024-03-19 NovelLBM.tex
use public package
RT-DC size as simulated

@@
 
-\usepackage{pythonhighlightRK} % provides python environment
+\usepackage{pythonhighlight} % provides python environment
 
@@
 
-Our next example is the RT-DC geometry in which cells from a reservoir are squeezed through a narrow observation channel \cite{Toepfner.2018, Fregin:2019gx} with a square cross-section of 20x20 \unit{\micro\meter}.
+Our next example is the RT-DC geometry in which cells from a reservoir are squeezed through a narrow observation channel \cite{Toepfner.2018, Fregin:2019gx} with a square cross-section of \qtyproduct{40x40}{\micro\meter}.
 For this simulation we use periodic boundary conditions and a constant body force corresponding to a pressure gradient of \SI{1e7}{\pascal}.

### 2024-03-23 NovelLBM.tex
Final small changes

@@
 \usepackage{hyperref} %link support
+\hypersetup{colorlinks,breaklinks,
+            allcolors=blue}
+
 \usepackage{pdflscape} %pages can be landscape
@@
 \author{Richard Kellnberger$^1$, Tomasz Jüngst$^2$, Stephan Gekle$^1$}
-\date{January, 2024}
+\date{\today}
 \begin{document}
@@
 	\begin{center}
-		$^1$ Biofluid Simulation and Modeling – Theoretische Physik VI, University of Bayreuth, Bayreuth, Germany\\
-		$^2$ FMZ
+		$^1$ Biofluid Simulation and Modeling – Theoretische Physik VI, Universität Bayreuth, Bayreuth, Germany\\
+		$^2$ Department of Functional Materials in Medicine and Dentistry Institute of Functional Materials and Biofabrication (IFB) and KeyLab Polymers for Medicine of the Bavarian Polymer Institute (BPI) Universität Würzburg, Würzburg, Germany
 	\end{center}
@@
 
-	\tableofcontents
+%	\tableofcontents
 
@@
 In particular the simulation of strongly shear-thinning fluids, where the ratio between the high-shear and low-shear viscosities is large, is often prevented by stability problems.
-Here we present a novel approach to overcome these issues.
+Here we present a novel approach to overcome this issue.
 The central idea is to artificially increase the solvent viscosity which allows the method to benefit from the very good stability properties of the LBM.
-To compensate for this additional viscous stress, we reduce the polymer stress by the same amount.
+To compensate for this additional viscous stress, the polymer stress is reduced by the same amount.
 We apply this novel method to simulate two realistic cell carrier fluids, methyl cellulose and alginate solutions, of which the latter exhibits a viscosity ratio exceeding \num{10000}.
@@
 To understand the rheology of such complex liquids in non-trivial geometries, computer simulations are an invaluable tool.
-While a number of numerical techniques have been developed, the simulation of viscoelastic liquids remain an involved subject \cite{Alves.2020}, in particular for high viscosity ratios.
-A very popular simulation technique for Newtonian fluids is the Lattice Boltzmann method \cite{Kruger_book} due to its simplicity and high parallelizability.
+While a number of numerical techniques have been developed, the simulation of viscoelastic liquids remains an involved subject \cite{Alves.2020}, in particular for high viscosity ratios.
+A very popular simulation technique for Newtonian fluids is the Lattice Boltzmann method (LBM) \cite{Kruger_book} due to its simplicity and high parallelizability.
 LBM has also been extended to viscoelastic situations, mainly in two \cite{ispolatov2002,wang2019,su2013,giraud1998,xie2018,dzanic2022,frank2006,zou2014,lee2017,dzanic2022_2,sedaghat2021,frantziskonis2011,qin2023,yoshino2008,papenkort2015,phillips2011,onishi2005} but occasionally also in three \cite{malaspinas2010,gupta2015,gupta2015_2,lallemand2003,ma2020,onishi2006,wang2020,dellar2014,su2013_2,wang2021,kuron2021,gupta2016} dimensions.
@@
 Three concentrations of \SI{0.49}{\percent}, \SI{0.59}{\percent} and \SI{0.83}{\percent} methyl cellulose in PBS were investigated, and their rheology is shown in figure~\ref{fig:fit_mc}.
-Even at the highest concentration the zero-shear viscosity is two orders of magnitude lower than for the considered alginate solution.
+%Even at the highest concentration the zero-shear viscosity is two orders of magnitude lower than for the considered alginate solution.
 	\begin{figure}[H]
@@
 
-The PTT model is specified by a differential equation for the polymer stress $\ma{\tau}$:
+The PTT model can be written in the form of a differential equation for the polymer stress $\ma{\tau}$ \cite{ferras2019}:
 	\begin{equation}
@@
 where $\ma{D}$ is the strain rate tensor.
-We note that extended forms of the PTT model with a Mittag-Leffler instead of an exponential function have been studied as well \cite{ferras2019}\RK{not really what we want to say here.
-We took this formula mostly from there}.
+We note that \cite{ferras2019} have also studied extended forms of the PTT model with a Mittag-Leffler instead of an exponential function, whereas here we restrict ourselves to the exponential version.
 The polymer viscosity is denoted $\eta_\text{p}$ and $\lambda$ is the corresponding relaxation time.
-$\epsilon$ is the so-called extensibility parameter which controls at what shear rates thinning takes place and $\xi$ describes the slip in the polymer network which we will set to zero in the following.
+$\epsilon$ is the so-called extensibility parameter which controls at which shear rates thinning takes place and $\xi$ describes the slip in the polymer network which we will set to zero in the following.
 The upper convected derivative of an arbitrary tensor $\ma{A}$ is defined as follows:
@@
 	\end{equation}
+\SG{ Kannst du der Vollständigkeit halber nochmal die Definition von $ \nabla \ma{ A }$ hinschreiben? }	
 Finally, the total fluid stress $\ma{\sigma}$ is the sum of the polymer stress $\ma{\tau}$ and a solvent stress due to the Newtonian solvent with viscosity $\eta_\text{s}$:
@@
 		\end{tabular}
-		\caption{Parameters of the PTT model obtained by fitting to the rheological measurements in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc}}.
+		\caption{Parameters of the PTT model obtained by fitting to the rheological measurements in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc} and corresponding viscosity ratios from eq.~(\ref{eq:R_eta}).}
 		\label{tab:PTTparameters}
@@
 which we and others found to be an important parameter to determine numerical stability of LB simulations, especially if no artificial diffusivity is used \cite{malaspinas2010,dzanic2022_2}.
-\SG{ wo don't actually show that $R_ \eta  $ determines stability?
-}\RK{we do not.
-We could do a few simulations with $\alpha_s = 0$ and increasing $R_\eta$ until the sim breaks if you want} \SG{ wie besprochen, bau einfach die Zitate ein, das reicht dann.
-}\RK{done}
 This ratio can similarly be defined for other models such as FENE-P or the inelastic, but shear-thinning Carreau-Yasuda model \cite{carreau1972, yasuda1979} using the zero-shear viscosity $\eta_0$ and the infinite-shear viscosity $\eta_\infty$.
@@
 			\rowcolor{secondaryBackground}
-			Jalaal\cite{jalaal2017} & pluronic F-127 & $>\num{1e3}$ & $<\num{1e-1}$ & $>\num{1e4}$ & FIG. 6. (e) \\
+			Jalaal \cite{jalaal2017} & pluronic F-127 & $>\num{1e3}$ & $<\num{1e-1}$ & $>\num{1e4}$ & FIG. 6. (e) \\
 		\end{tabular}
@@
 The first approaches avoided an explicit modeling of a viscoelastic constitutive equation and simply modified the LB collision operator to obtain a basic viscoelastic fluid obeying Jeffery's model \cite{lallemand2003}.
-This can also be archived by the introduction of a second local stress tensor \cite{dellar2014}.
+This can also be achieved by the introduction of a second local stress tensor \cite{dellar2014}.
 More advanced approaches include the work of Onishi \textit{et al.} \cite{onishi2005, onishi2006} who considered a non-shear-thinning Oldroyd-B model using a microscopic Fokker-Planck equation for the polymer dumbbells.
@@
 \begin{equation}
-	f_i\left(\vec{x}+\vec{c}_i\Delta t, t+\Delta t\right) - f_i\left(\vec{x}, t\right) = -\frac{\Delta t}{\tau_\text{r}}\left[f_i\left(\vec{x}, t\right) - f_i^\text{eq}\left(\vec{x}, t\right) + B_i\right]
+	f_i\left(\vec{x}+\vec{c}_i\Delta t, t+\Delta t\right) - f_i\left(\vec{x}, t\right) = -\frac{\Delta t}{\tau_\text{r}}\left[f_i\left(\vec{x}, t\right) - f_i^\text{eq}\left(\vec{x}, t\right) + B_i\right].
 \end{equation}
-Where $f_i$ are the populations, $f_i^\text{eq}$ are the equilibrium populations, $\vec{c_i}$ are the lattice velocities, $\Delta t$ is the time step, $\tau_\text{r}$ is the relaxation time and $B_i$ are the stress contributions defined as follows.
+Here, $f_i$ are the populations, $f_i^\text{eq}$ are the equilibrium populations, $\vec{c_i}$ are the lattice velocities, $\Delta t$ is the time step, $\tau_\text{r}$ is the relaxation time and $B_i$ are the stress contributions defined as follows.
 \begin{equation}
-	B_i = w_i\left(\frac{\vec{c}_i\vec{c}_i}{2c_\text{s}^4}-\frac{\uT}{2c_\text{s}^2}\right):\ma{\tau}
+	B_i = w_i\left(\frac{\vec{c}_i\vec{c}_i}{2c_\text{s}^4}-\frac{\uT}{2c_\text{s}^2}\right):\ma{\tau}.
 \end{equation}
-Where $w_i$ are the lattice weights, $c_\text{s}$ is the lattice speed of sound and $\ma{\tau}$ is the polymer stress tensor. The colon denotes the Frobenius inner product.
-\SG{ more details }\RK{done}
+Here, $w_i$ are the lattice weights, $c_\text{s}$ is the lattice speed of sound and $\ma{\tau}$ is the polymer stress tensor. The colon denotes the Frobenius inner product.
 To handle inflow/outflow boundaries, the polymer conformation tensor is specified on the boundary and advected using the corner transport upwind scheme.
@@
 In physical units the channel has a height of \SI{20}{\micro\meter} which are discretized with 41 LBM nodes.
-For the viscosity shuffling, we set $\alpha_\text{s} = 1$. The exact value of $\alpha_\text{s}$ does not matter as can be seen in figure~\ref{fig:ShuffleInPoiseuille}.
+For the viscosity shuffling, we set $\alpha_\text{s} = 1$ here and check different values further below. 
 Along the flow direction, the channel is periodic, and the flow is driven by a pressure gradient of \SI{-1e7}{\pascal\per\meter} for alginate and  approximately \SI{-1.2e7}{\pascal\per\meter} for methyl cellulose.
@@
 In the case of alginate, we speed up the convergence and start from a situation in which the polymers are pre-stretched.
-For this we calculate $\tau_{xx}$ and $\tau_{xy}$ using equations~(\ref{eq:tau_xx}) and (\ref{eq:PTTDerivation2}) using the $\dot{\gamma}$ calculated from equation~(\ref{eq:semiAnalyticGD}).
+For this we calculate $\tau_{xx}$ and $\tau_{xy}$ using equations~(\ref{eq:tau_xx}) and (\ref{eq:PTTDerivation2}) using the $\dot{\gamma}$ calculated from equation~(\ref{eq:semiAnalyticGD_3D}).
 The polymer stress is then initialized using these values.
-\SG{ give details }\RK{initialized to the semianalytical solution} \SG{ schreib am besten eine Referenz auf die Gleichung hin, muesste ja im Appendix stehen.
-}\RK{done}.
+%\SG{ give details }\RK{initialized to the semianalytical solution} \SG{ schreib am besten eine Referenz auf die Gleichung hin, muesste ja im Appendix stehen. }\RK{done}.
 After \num{2e9} LBM time steps for alginate and \num{5e6} LBM time steps for methyl cellulose corresponding to approximately \SI{1.6}{\milli\second} and \SI{2.4}{\second} of physical time, respectively, the simulation is stopped and the flow field $u(y)$ is compared to the semi-analytical solution.
@@
 As shown in figure~\ref{fig:2Dvel}, very good agreement is found.
+The time evolution of the center-line velocity is shown in figure~\ref{fig:2DTimeEvolution} of the appendix.
 For a quantitative assessment, we compute the L2 error as follows.
@@
 \end{equation}
-\RK{This error definition is new}
 These conclusions remain unchanged even when varying the pressure gradient, and thus the flow velocity, over many orders of magnitude as shown in figure~\ref{fig:pressureErr}~(a) of the appendix.
+Similarly, the exact value of $\alpha_\text{s}$ does not matter as can be seen in figure~\ref{fig:ShuffleInPoiseuille}.
 
@@
 		\caption{(a) Velocity profile of alginate in planar channel flow.
-		The time evolution of the center-line velocity is shown in the inset \ref{fig:2DTimeEvolution}\SG{ to do }\RK{Not an inset but plotted. Has to be inset?}.
 		(b) Velocity profile for methyl cellulose.}
@@
 We use the same material parameters as above, but double the pressure gradient to \SI{-2e7}{\pascal\per\meter} and approximately \SI{-2.5e7}{\pascal\per\meter}, respectively, thereby mirroring the relation in Newtonian Poiseuille flow where twice the pressure is required to obtain the same flow rate in cylindrical compared to planar geometries.
-The channel has a diameter of \SI{20}{\micro\meter} and is discretized with 41 lattice points.
+The channel has a diameter of \SI{20}{\micro\meter} and is discretized with 41 lattice points in $y$ and $z$ direction.
 Again, we initialize the polymers in the unstretched state for methyl cellulose and in the stretched state for alginate.
@@
 The spatially resolved L1 error in figure~\ref{fig:3DvelErr} of the appendix shows that this larger average is indeed mainly attributable to the staircase effect as the error near the walls increases significantly.
+The time evolution of the center-line velocity is shown in figure~\ref{fig:3DTimeEvolution} of the appendix.
 The robustness against pressure gradient changes is shown in figure~\ref{fig:pressureErr}~(b) of the appendix.
@@
 		\caption{(a) Velocity profile of alginate in cylindrical channel flow.
-		The time evolution of the center-line velocity when starting from a pre-stretched configuration (see main text) is shown in the inset \ref{fig:3DTimeEvolution}.\RK{currently not an inset}
+		The time evolution of the center-line velocity when starting from a pre-stretched configuration (see main text) is shown in figure~\ref{fig:3DTimeEvolution}.
 		(b) Velocity profile for methyl cellulose.}
@@
 The authors studied an Oldroyd-B fluid in a planar Poiseuille flow and compared the error in the simulated velocity profile to an exact analytical solution.
-The Oldroyd-B model is a special case of the PTT model which is obtained by setting $\xi = \epsilon = 0$ in eq.~(\ref{eq:polymerStress}) and is thus easily tractable with our code.\RK{was simulated with a direct Oldroyd-B implementation, which I now see was unnecessary...} \SG{ hast du mal kurz geprueft, ob dasselbe rauskommt?
-}\RK{Ja, ist aber auch von code offensichtlich, der unterschied wird zur OpenCL compile time entfernt}
+The Oldroyd-B model is a special case of the PTT model which is obtained by setting $\xi = \epsilon = 0$ in eq.~(\ref{eq:polymerStress}) and is thus easily tractable with our code.
 In figure~\ref{fig:malaspinas2010}, we show the L2 error as function of lattice resolution for different values of $\mathrm{Wi}$ and $R_ \nu $ which is defined as \cite{malaspinas2010}
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/malaspinas2010.pdf}
-		\caption{L2 error as defined in equation \ref{eq:l2error} from Malaspinas \textit{et al.}\cite{malaspinas2010} (dots) compared to our algorithm (x) as a function of grid resolution.
+		\caption{L2 error as defined in equation (\ref{eq:l2error}) from Malaspinas \textit{et al.}\cite{malaspinas2010} (dots) compared to our algorithm (x) as a function of grid resolution.
 		Blue and green crosses are not visible as they overlap exactly with the orange and red crosses, respectively, showing that the accuracy of our method is independent of $\mathrm{Wi}$ in the studied parameter range.}
@@
 The nozzle has a length of \SI{18}{\milli\meter}.
-Due to the difference in inlet/outlet radii, the system cannot be modeled with periodic boundary conditions, and we use inflow/outflow boundary conditions as described in section~\ref{sec:Methods} instead.
+Due to the difference in inlet/outlet radii, the system cannot be modeled with periodic boundary conditions, and we use inflow/outflow boundary conditions as described in section~\ref{sec:Methods}.
 The required values for velocity and polymer conformation are obtained from simulations of pipes of the respective radii and a fixed volume flow of $\approx\SI{3}{\micro\liter\per\second}$.
@@
 \end{equation}
-With the deviator of the stress tensor defined as follows.
+with the deviator of the stress tensor defined as follows
 \begin{equation}
-	\tau_{ij}^\text{dev} = \tau_{ij} - \frac{1}{3}\tau_{kk}
+	\tau_{ij}^\text{dev} = \tau_{ij} - \frac{1}{3}\tau_{kk}.
 \end{equation}
@@
 		\caption{Velocity profile (a), von Mises stress (b) and shear stress (c) for methyl cellulose in a conical nozzle as used for bioprinting.
-For the calculated viscosity see figure~\ref{fig:Nozzle/RT-DC_eta}.}
+For the calculated viscosity see figure~\ref{fig:Nozzle/RT-DC_eta} of the appendix.}
 		\label{fig:Nozzle}
@@
 
-Our next example is the RT-DC geometry in which cells from a reservoir are squeezed through a narrow observation channel \cite{Toepfner.2018, Fregin:2019gx} with a square cross-section of \qtyproduct{40x40}{\micro\meter}.
+Our next example is the RT-DC geometry in which cells from a reservoir are squeezed through a narrow observation channel \cite{Toepfner.2018, Fregin:2019gx} with a square cross-section of $40 \times 40 \mu$m.
+%\qtyproduct{40x40}{\micro\meter}.
 For this simulation we use periodic boundary conditions and a constant body force corresponding to a pressure gradient of \SI{1e7}{\pascal}.
+\SG{ units.
+Is this Pa/m or is this the pressure difference between inlet and outlet?
+}
 In figure~\ref{fig:RT-DC}, we show the velocity profile, the von Mises stress and the shear component of the stress which is the relevant component if a local shear viscosity is to be defined.
@@
 This also shows why viscoelastic simulations cannot always be replaced by purely viscous models and should be considered despite the high computational cost.
-\SG{ decide whether we want to show a viscosity plot and remove or leave this part}\RK{done}
 
@@
 
+\section{Acknowledgements}
+
+The authors would like to thank the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Project number 326998133, TRR 225 Biofabrication (subprojects B07 and B09) and the Federal Ministry of Education and Research (BMBF) under Project SOP\_Bioprint under Contract Number 13XP5071B for enabling data collection.
+
 	\newpage
@@
 
-\SG{ Tomasz should extend this paragraph }
-The solutions used here are \SI{4}{\percent} by weight of DuPont VIVAPHARM Alginate PH176 in PBS.
-The measurements were done using a plate-plate rheometer.
+The solutions were prepared by dissolving alginate (DuPont VIVAPHARM Alginate PH176) in ultrapure water at a ratio of 4 \% w/v. 
+To ensure homogeneous dissolution, the material was stored at 37$^\circ$C for 24 h and regularly mixed to ensure complete dissolution. 
+The measurements were conducted with a 25 mm plate-plate geometry at a 500 $\mu$m gap on a rheometer (Anton paar MCR 702). 
+A solvent trap was used to limit evaporation. 
+All measurements were done at a set temperature of 25$^\circ$C as shear rate sweep. 
 Data is agglomerated from 21 independent measurements.
-The first normal stress difference $N_1$ is calculated from the measured normal force using the following equation \cite{kulicke1977}.
+The first normal stress difference $N_1$ is calculated from the measured normal force using the following equation \cite{kulicke1977}:
 	\begin{equation}
@@
 	\end{equation}
-	Where $F$ is the measured normal force, $R$ is the radius of the rheometer, $\rho$ is the density of the fluid and $\omega$ is the angular velocity of the rheometer.
+	where $F$ is the measured normal force, $R$ is the radius of the rheometer, $\rho$ is the density of the fluid and $\omega$ is the angular velocity of the rheometer.
 The second term is usually omitted and as we found it to matter little, and as the quality of the data we have available is too limited to warrant such detailed corrections, we also choose to omit it.
@@
 \end{equation}
-\RK{zz Komponente in 2D ist ein bischen fragwürdig...
+%\RK{zz Komponente in 2D ist ein bischen fragwürdig...
 Da beißt mich jetzt, dass ich mit 2D eigentlich channel flow meine.
@@
 		\caption{(a) The local viscosity determined by a shear flow simulation is in very good agreement with the semi-analytical theory.
-		(b) The error is negligibly small and independent of the shuffling parameter $\alpha_\text{s}$.}
+		(b) The error is negligibly small and independent of the shuffling parameter $\alpha_\text{s}$. \SG{ at which $ \dot{ \gamma  }$? }}
 		\label{fig:wiParameterStudy}
@@
 		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DAlginate_timeEvolution.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DMC_timeEvolution.pdf}
+		\caption{Time evolution of the center-line velocity of an alginate (a) and methyl cellulose (b) solution in planar Poiseuille flow as seen in figure~\ref{fig:2Dvel}.}
+		\label{fig:2DTimeEvolution}
+	\end{figure}
+
+	\begin{figure}[H]
+		\centering
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DAlginateErr.pdf}
@@
 		\caption{L1 error of the velocity profile in figure~\ref{fig:2Dvel} with respect to the semi-analytical theory in a planar Poiseuille flow for alginate (a) and methyl cellulose (b).
-			The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall.}\RK{this is linear error} \SG{ define }\RK{done}
+			The relative error is highest near the wall as the velocity is lowest there, but also because the simple half way bounce back boundaries used here allow some slip along the wall.}
 		\label{fig:2DvelErr}
+	\end{figure}
+
+	\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr.pdf}
+		\caption{L2 error of the velocity for a planar (a) and a cylindrical (b) Poiseuille flow of methyl cellulose at different pressure gradients.
+		The peak in the error profile appears when the average shear rate across the channel corresponds to the maximum slope in the viscosity profile of figure~\ref{fig:wiParameterStudy}.}
+		\label{fig:pressureErr}
+	\end{figure}
+
+	\begin{figure}[H]
+		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DAlginate_timeEvolution.pdf}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DMC_timeEvolution.pdf}
+		\caption{Time evolution of the center-line velocity of an alginate (a) and methyl cellulose (b) cylindrical Poiseuille flow as seen in figure~\ref{fig:3Dvel}.}
+		\label{fig:3DTimeEvolution}
 	\end{figure}
@@
 		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DParameterStudyErr.pdf}
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DParameterStudyErr.pdf}
-		\caption{L2 error of the velocity for a planar (a) and a cylindrical (b) Poiseuille flow of methyl cellulose at different pressure gradients.
-		The peak in the error profile appears when the average shear rate across the channel corresponds to the maximum slope in the viscosity profile of figure~\ref{fig:wiParameterStudy}.}
-		\label{fig:pressureErr}
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/ShuffleInPoiseuille.pdf}
+		\caption{In Poiseuille flow, the result is near identical for different $\alpha_\text{s}$.
+The error reveals minor differences.
+Aside from the wall nodes, the largest error appears for small shuffle fractions.
+For large ones, the error appears to become independent of $\alpha_\text{s}$.
+This indicates, that the observed difference might be due to the Mach number changing for different $\alpha_\text{s}$ and not due to the shuffling itself.
+This is due lower $\alpha_\text{s}$ leading to lower LBM viscosities and such to higher Mach numbers.
+\SG{ is this planar or cylindrical?
+}}
+		\label{fig:ShuffleInPoiseuille}
 	\end{figure}
 
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DAlginate_timeEvolution.pdf}
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/2DMC_timeEvolution.pdf}
-		\caption{Time evolution of the center-line velocity of an alginate (a) and methyl cellulose (b) poiseuille flow in 2D as seen in figure~\ref{fig:2Dvel}.}
-		\label{fig:2DTimeEvolution}
-	\end{figure}
-
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DAlginate_timeEvolution.pdf}
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/3DMC_timeEvolution.pdf}
-		\caption{Time evolution of the center-line velocity of an alginate (a) and methyl cellulose (b) poiseuille flow in 3D as seen in figure~\ref{fig:3Dvel}.}
-		\label{fig:3DTimeEvolution}
-	\end{figure}
+	%%%%%%
 
@@
 
-	\begin{figure}[H]
-		\centering
-		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/ShuffleInPoiseuille.pdf}
-		\caption{In Poiseuille flow, the result is near identical for different $\alpha_\text{s}$.
-The error reveals minor differences.
-Aside from the wall nodes, the largest error appears for small shuffle fractions.
-For large ones, the error appears to become independent of $\alpha_\text{s}$.
-This indicates, that the observed difference might be due to the Mach number changing for different $\alpha_\text{s}$ and not due to the shuffling itself.
-This is due lower $\alpha_\text{s}$ leading to lower LBM viscosities and such to higher Mach numbers.}
-		\label{fig:ShuffleInPoiseuille}
-	\end{figure}
-
 \end{document}

### 2024-03-23 NovelLBM.tex
units

@@
 \usepackage{hyperref} %link support
-\hypersetup{colorlinks,breaklinks,
-            allcolors=blue}
+\hypersetup{colorlinks,breaklinks,allcolors=blue}
 
@@
 	\vspace{\fill}
-	\begin{center}
-		%TODO abstact
-	\end{center}
 	%TODO keywords
@@
 	\begin{equation}
-		\frac{\Dif\ma{A}}{\Dif t} = \frac{\partial\ma{A}}{\partial t} + \vec{u}\cdot\nabla\ma{A}.
+		\frac{\Dif\ma{A}}{\Dif t} = \frac{\partial\ma{A}}{\partial t} + \left(\vec{u}\cdot\nabla\right)\ma{A}.
 	\end{equation}
-\SG{ Kannst du der Vollständigkeit halber nochmal die Definition von $ \nabla \ma{ A }$ hinschreiben? }	
+\SG{ Kannst du der Vollständigkeit halber nochmal die Definition von $ \nabla \ma{ A }$ hinschreiben? }\RK{Nein}
 Finally, the total fluid stress $\ma{\sigma}$ is the sum of the polymer stress $\ma{\tau}$ and a solvent stress due to the Newtonian solvent with viscosity $\eta_\text{s}$:
@@
 			\hline
-			alginate \SI{4}{\percent} & \num{48.2\pm0.4e3} & \num{343 \pm 4} & \num{0.545 \pm 0.010} & \num{4.8e4} \\
+			alginate \SI{4}{\percent} & \num{48.2\pm0.4e3} & \num{343 \pm 4} & \num{0.545 \pm 0.010} & \num{4.82e4} \\
+			\rowcolor{secondaryBackground}
 			methyl c. \SI{0.49}{\percent} & \num{18.7\pm0.4} & \num{0.344\pm0.003} & \num{0.270\pm0.003} & \num{18.7} \\
 			methyl c. \SI{0.59}{\percent} & \num{32.5\pm0.7} & \num{0.433\pm0.004} & \num{0.365\pm0.004} & \num{32.5} \\
+			\rowcolor{secondaryBackground}
 			methyl c. \SI{0.83}{\percent} & \num{81\pm2} & \num{0.714\pm0.009} & \num{0.496\pm0.006} & \num{81}
 		\end{tabular}
-		\caption{Parameters of the PTT model obtained by fitting to the rheological measurements in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc} and corresponding viscosity ratios from eq.~(\ref{eq:R_eta}).}
+		\caption{Parameters of the PTT model obtained by fitting to the rheological measurements in figures~\ref{fig:fit_alginate} and \ref{fig:fit_mc} along with corresponding viscosity ratios from eq.~(\ref{eq:R_eta}).}
 		\label{tab:PTTparameters}
@@
 				Onishi\cite{onishi2006} & ? & 1 & In 3.1: $\beta = \frac{\mu_\text{p}}{\mu_\text{s} + \mu_\text{p}}$ \& Table 1: $\beta=\num{0.5}$ \\
-				Wang\cite{wang2020} & \glqq up to O(1)\grqq & 5 & In II: $\eta_\text{p} = c\eta_\text{s}$ \& FIG. 9: $c = \num{5}$\\
+				Wang\cite{wang2020} & "up to O(1)" & 5 & In II: $\eta_\text{p} = c\eta_\text{s}$ \& FIG. 9: $c = \num{5}$\\
 				\rowcolor{secondaryBackground}
@@
 The polymer stress is then initialized using these values.
-%\SG{ give details }\RK{initialized to the semianalytical solution} \SG{ schreib am besten eine Referenz auf die Gleichung hin, muesste ja im Appendix stehen. }\RK{done}.
 After \num{2e9} LBM time steps for alginate and \num{5e6} LBM time steps for methyl cellulose corresponding to approximately \SI{1.6}{\milli\second} and \SI{2.4}{\second} of physical time, respectively, the simulation is stopped and the flow field $u(y)$ is compared to the semi-analytical solution.
-%\RK{
-%	Alg 2e9 1.6455647956111251 ms (reveals the sim to be a scam)
-%	MC 5e6 10.065719379854297 ms
-%}
 As shown in figure~\ref{fig:2Dvel}, very good agreement is found.
@@
 
-Our next example is the RT-DC geometry in which cells from a reservoir are squeezed through a narrow observation channel \cite{Toepfner.2018, Fregin:2019gx} with a square cross-section of $40 \times 40 \mu$m.
-%\qtyproduct{40x40}{\micro\meter}.
-For this simulation we use periodic boundary conditions and a constant body force corresponding to a pressure gradient of \SI{1e7}{\pascal}.
+Our next example is the RT-DC geometry in which cells from a reservoir are squeezed through a narrow observation channel \cite{Toepfner.2018, Fregin:2019gx} with a square cross-section of \qtyproduct{40x40}{\micro\meter}.
+%$\SI{40}{\micro\meter} \times \SI{40}{\micro\meter}$.%Correctly typeset version, that compiles for Stephan.
+For this simulation we use periodic boundary conditions and a constant body force corresponding to a pressure gradient of \SI{1e7}{\pascal\per\meter}.
 \SG{ units.
 Is this Pa/m or is this the pressure difference between inlet and outlet?
-}
+}\RK{done}
 In figure~\ref{fig:RT-DC}, we show the velocity profile, the von Mises stress and the shear component of the stress which is the relevant component if a local shear viscosity is to be defined.
@@
 
-The solutions were prepared by dissolving alginate (DuPont VIVAPHARM Alginate PH176) in ultrapure water at a ratio of 4 \% w/v. 
-To ensure homogeneous dissolution, the material was stored at 37$^\circ$C for 24 h and regularly mixed to ensure complete dissolution. 
-The measurements were conducted with a 25 mm plate-plate geometry at a 500 $\mu$m gap on a rheometer (Anton paar MCR 702). 
+The solutions were prepared by dissolving alginate (DuPont VIVAPHARM Alginate PH176) in ultrapure water at a ratio of \SI{40}{\milli\gram\per\milli\liter}, which here is refereed to as \SI{4}{\percent}.
+To ensure homogeneous dissolution, the material was stored at \SI{37}{\celsius} for \SI{24}{\hour} and regularly mixed to ensure complete dissolution.
+The measurements were conducted with a \SI{25}{\milli\meter} plate-plate geometry at a \SI{500}{\micro\meter} gap on a rheometer (Anton paar MCR 702).
 A solvent trap was used to limit evaporation.
-All measurements were done at a set temperature of 25$^\circ$C as shear rate sweep. 
+All measurements were done at a set temperature of \SI{25}{\celsius} as shear rate sweep.
 Data is agglomerated from 21 independent measurements.
@@
 		\caption{(a) The local viscosity determined by a shear flow simulation is in very good agreement with the semi-analytical theory.
-		(b) The error is negligibly small and independent of the shuffling parameter $\alpha_\text{s}$. \SG{ at which $ \dot{ \gamma  }$? }}
+		(b) The error is negligibly small and independent of the shuffling parameter $\alpha_\text{s}$. \SG{ at which $ \dot{ \gamma  }$? }\RK{\SI{1}{\per\second}}}
 		\label{fig:wiParameterStudy}
@@
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/ShuffleInPoiseuille.pdf}
-		\caption{In Poiseuille flow, the result is near identical for different $\alpha_\text{s}$.
+		\caption{In planar Poiseuille flow, the result is near identical for different $\alpha_\text{s}$.
 The error reveals minor differences.
@@
 \SG{ is this planar or cylindrical?
-}}
+}\RK{done}}
 		\label{fig:ShuffleInPoiseuille}

### 2024-03-27 NovelLBM.tex
Update NovelLBM.tex

@@
 The first is an alginate solution which is often used in biofabrication but can also serve as a common food additive.
-Our solution contains \SI{4}{\percent} alginate dissolved in PBS and was measured in a commercial plate-plate rheometer (see appendix~\ref{app:experiment} for experimental details).
+Our solution contains \SI{4}{\percent} w/v alginate dissolved in ultrapure water and was measured in a commercial plate-plate rheometer (see appendix~\ref{app:experiment} for experimental details).
 The shear-dependent viscosity $\eta$ and the first normal stress difference $N_1$ are shown as function of shear rate in figure~\ref{fig:fit_alginate}.
@@
 	\end{equation}
-\SG{ Kannst du der Vollständigkeit halber nochmal die Definition von $ \nabla \ma{ A }$ hinschreiben? }\RK{Nein}
 Finally, the total fluid stress $\ma{\sigma}$ is the sum of the polymer stress $\ma{\tau}$ and a solvent stress due to the Newtonian solvent with viscosity $\eta_\text{s}$:
@@
 			\hline
-			alginate \SI{4}{\percent} & \num{48.2\pm0.4e3} & \num{343 \pm 4} & \num{0.545 \pm 0.010} & \num{4.82e4} \\
+			alginate \SI{4}{\percent} w/v & \num{48.2\pm0.4e3} & \num{343 \pm 4} & \num{0.545 \pm 0.010} & \num{4.82e4} \\
 			\rowcolor{secondaryBackground}
@@
 For this simulation we use periodic boundary conditions and a constant body force corresponding to a pressure gradient of \SI{1e7}{\pascal\per\meter}.
-\SG{ units.
-Is this Pa/m or is this the pressure difference between inlet and outlet?
-}\RK{done}
 In figure~\ref{fig:RT-DC}, we show the velocity profile, the von Mises stress and the shear component of the stress which is the relevant component if a local shear viscosity is to be defined.
@@
 
-The authors would like to thank the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Project number 326998133, TRR 225 Biofabrication (subprojects B07 and B09) and the Federal Ministry of Education and Research (BMBF) under Project SOP\_Bioprint under Contract Number 13XP5071B for enabling data collection.
+The authors would like to thank the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Project number 326998133, TRR 225 Biofabrication (subprojects B07, B09 and Z01) and the Federal Ministry of Education and Research (BMBF) under Project SOP\_Bioprint (Contract Number 13XP5071B) for enabling data collection.
 
@@
 
-The solutions were prepared by dissolving alginate (DuPont VIVAPHARM Alginate PH176) in ultrapure water at a ratio of \SI{40}{\milli\gram\per\milli\liter}, which here is refereed to as \SI{4}{\percent}.
+The solutions were prepared by dissolving alginate (DuPont VIVAPHARM Alginate PH176) in ultrapure water at a ratio of \SI{40}{\milli\gram\per\milli\liter}, which here is refereed to as \SI{4}{\percent} w/v.
 To ensure homogeneous dissolution, the material was stored at \SI{37}{\celsius} for \SI{24}{\hour} and regularly mixed to ensure complete dissolution.
@@
 		\caption{(a) The local viscosity determined by a shear flow simulation is in very good agreement with the semi-analytical theory.
-		(b) The error is negligibly small and independent of the shuffling parameter $\alpha_\text{s}$. \SG{ at which $ \dot{ \gamma  }$? }\RK{\SI{1}{\per\second}}}
+		(b) The error is negligibly small and independent of the shuffling parameter $\alpha_\text{s}$. Shown at \SI{1}{\per\second} and .}
 		\label{fig:wiParameterStudy}
-	\end{figure}
+	\end{figure}\todo{1e5; maybe write this in legend}
 

### 2024-03-27 assets/python/fig:shuffleParameterStudy.py
shuffle error for different gamma dot

@@ -50,23 +50,98 @@ def process(index):
     return eta, D12
 
 
+def processNew(index):
+    baseDir = Path(f"../data/SuffleParameterStudy/{index}/")
+    cDir = baseDir / "vtkfiles/polymerConformationTensor/"
+    sDir = baseDir / "vtkfiles/strainRateTensor/"
+    jsonFile = baseDir / "parameters.json"
+    f = open(jsonFile)
+    parameters = json.load(f)
+    f.close()
+
+    V0 = parameters["info"]["conversions"]["V0"]
+    L0 = parameters["info"]["conversions"]["L0"]
+    T0 = parameters["info"]["conversions"]["T0"]
+    rho0 = 1e3
+
+    cFile = cDir / "A_10000000.vtk"
+    sFile = sDir / "D_10000000.vtk"
+    data = pv.read(cFile)
+    dataS = pv.read(sFile)
+    Lx, Ly, Lz = data.dimensions
+    tauField = data.get_array("data") * PTT.mc0_49.eta_p / PTT.mc0_49.lambda_p
+    tauField = np.reshape(tauField, (Lx, Ly, Lz, 6), "F")
+    sField = dataS.get_array("data") / T0
+    sField = np.reshape(sField, (Lx, Ly, Lz, 6), "F")
+
+    tau12 = tauField[Lx // 2, Ly // 2, Lz // 2, 3]
+    D12 = sField[Lx // 2, Ly // 2, Lz // 2, 3]
+    shearRateSI = parameters["shearRateSI"]
+    eta = tau12 / shearRateSI + 1e-3
+    return eta, D12
+
+
 etas = []
 ds = []
+
+etas2 = []
+ds2 = []
 for i in range(11):
     eta, D12 = process(i)
     etas.append(eta)
     ds.append(D12)
 
+for i in range(20, 31):
+    eta, D12 = processNew(i)
+    etas2.append(eta)
+    ds2.append(D12)
+
 alpha_s = np.arange(1, 2.1, 0.1)
 etas = np.asarray(etas) * 1e3
+etas2 = np.asarray(etas2) * 1e3
 
 plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
 plt.title("(b)", loc="left")
-plt.plot(alpha_s, etas, "rx")
[…]

### 2024-03-27 assets/setups/SuffleParameterStudy/setup2/defines.hpp

@@ -1,0 +1,182 @@
+#pragma once
+// ############################################ file paths #############################################
+
+//#define PATH_DEBUG "/data2/s1molehm/FluidX3D/Bead/interpolation/"
+//#define PATH_DEBUG "/tp6_gekle/data2/bt703473/debug/test2/"
+#define PATH_DEBUG "./bin/debug/" // path for debug files (PTX, LOG, VALIDATION)
+#define PATH_IBM   "./bin/ibm/"   // path for IBM extension
+
+
+// ############################################ LBM options ############################################
+
+// There hides a D2Q5 in the code
+//#define D2Q9
+//#define D3Q7 // very very inaccurate
+//#define D3Q13 // very inaccurate; Only works with MRT according to Krüger book p. 87; Does not reproduce VISCOELASTIC correctly.
+
+// Only use these:
+//#define D3Q15
+#define D3Q19 // Best value
+//#define D3Q27 // Better for high Reynolds numbers.
+
+#define SRT // singe relaxation time
+//#define TRT // two relaxiation time (as fast as SRT, but more accurate)
+//#define MRT // multi relaxiation time (as fast as SRT, but more accurate), (### not fully validated for for D3Q7 and D3Q13, incomplete relaxation times for D3Q7 and D3Q27 ###)
+
+//#define UPDATE_RHO // update density field after every step (not necessary for pure LBM)
+//#define UPDATE_U // update velocity field after every step (not necessary for pure LBM, makes tracer particle calculation faster)
+
+#define MOVING_WALLS // moving bounce-back boundaries
+//#define PRESSURE_WALLS // pressure boundaries
+//#define BOUNDARY_EXPRESSION // combinable with MOVING_WALLS, !!!doesn't work on AMD for some reason!!!
+
+#define VISCOELASTIC
+// Only one of the following models may be defined
+//#define OLDROYD_B
+//#define FENEP
+#define PTT // From Ferras 2019 eq (3) and (2) original PTT
+//#define CARREAU_YASUDA
+
+//#define IBM // immersed boundary method (### under construction ###)
+//#define IBM_CELLS // simulate RBCs with the immersed-boundary method
+//#define IBM_NEW // IBM implementation by Stephan Gekle; Conflicts with IBM and IBM_CELLS
+//#define INOUT // activate volume tracking for RBCs
[…]

### 2024-03-27 assets/setups/SuffleParameterStudy/setup2/setup.cpp

@@ -1,0 +1,196 @@
+#include "setup.hpp"
+#include "shapes.hpp"
+#include "opencl.hpp" // contains "options.hpp", "main.hpp"
+#include "ibm.hpp"
+#include <numeric>
+#include <sstream>
+
+#include <filesystem>
+using std::filesystem::path;
+#include <fstream>
+using std::ofstream;
+#include <iostream>
+using std::endl;
+
+#include <fmt/format.h>
+// using fmt::format
+using fmt::print;
+#include <fmt/color.h>
+using fmt::color;
+
+#include <spdlog/spdlog.h>
+//using spdlog::info;
+
+#include "cellWriter.hpp"
+using fluidx3d::io::cellWriter::CellWriter;
+#include "fieldWriter.hpp"
+using fluidx3d::io::fieldWriter::FieldWriter;
+#include "io.hpp"
+using fluidx3d::util::io::IO;
+#include "poiseuilleFlow.hpp"
+using fluidx3d::util::poiseuilleFlow::CircularPoiseuilleFlow;
+
+void example(SimulationOptions& options, Parameters& parameters) {
+	json raw = parameters.getRaw();
+	const int id = raw.at("id");
+	//const string path_files = "/tp6-gekle/nas/bt307867/cellsim/novel_2023-10-24/" + std::to_string(id) + "/";
+	const string path_files = fmt::format("SuffleParameterStudy/{}/", id);
+	const path filesPath(path_files);
+	const path vtkPath = filesPath/"vtkfiles";
+	const path path_vtk_velocity = vtkPath/"velocity";
+	const path path_vtk_strainRateTensor = vtkPath/"strainRateTensor";
+	const path path_vtk_viscousStressTensor = vtkPath/"viscousStressTensor";
+	const path path_vtk_polymerConformationTensor = vtkPath/"polymerConformationTensor";
+
+	/*
+	 * this parameter increases the time step
+	 * --> leads to larger relaxation time tau (not good, but acceptable)
+	 * --> leads to larger Ma (not good, but acceptable)
+	 * --> eventually may lead to inaccuracies
+	 */
+	const double dtScale = 1e0;  // decrease timestep
+
+	// Length of simulation box
+	uint Lx = 2;
+	uint Ly = 43;
+	uint Lz = 2;
+
+	/*
[…]

### 2024-03-28 assets/python/fig:Nozzle.py
update nozzle

@@ -21,7 +21,7 @@ from fluidx3d.eval.style import cm
 
 
 def process():
-    baseDir = Path("../data/novel_2024-01-22/0/")
+    baseDir = Path("../data/novel_2024-03-26/2/")
     cDir = baseDir / "vtkfiles/polymerConformationTensor/"
     sDir = baseDir / "vtkfiles/strainRateTensor/"
     vDir = baseDir / "vtkfiles/velocity/"
@@ -37,7 +37,7 @@ def process():
     p0 = rho0 * V0**2
 
     cFile = cDir / "CT_5000000.vtk"
-    sFile = sDir / "S_500000.vtk"
+    sFile = sDir / "S_5000000.vtk"
     vFile = vDir / "u_5000000.vtk"
 
     data = pv.read(cFile)

### 2024-03-28 assets/setups/Nozzle/2/setup/defines.hpp

@@ -12,7 +12,7 @@
 // There hides a D2Q5 in the code
 //#define D2Q9
 //#define D3Q7 // very very inaccurate
-//#define D3Q13 // very inaccurate; Only works with MRT according to Krüger book p. 87; Does not reproduce EQUILIBRIUM_STRESS correctly.
+//#define D3Q13 // very inaccurate; Only works with MRT according to Krüger book p. 87; Does not reproduce VISCOELASTIC correctly.
 
 // Only use these:
 //#define D3Q15
@@ -26,20 +26,20 @@
 //#define UPDATE_RHO // update density field after every step (not necessary for pure LBM)
 //#define UPDATE_U // update velocity field after every step (not necessary for pure LBM, makes tracer particle calculation faster)
 
-#define MOVING_WALLS // moving bounce-back boundaries (incompatible with EQUILIBRIUM_BOUNDARIES due to unnecessary flag recycling)
-//#define EQUILIBRIUM_BOUNDARIES // non-reflecting velocity boundaries, generally more stable, but less accurate (incompatible with MOVING_WALLS due to unnecessary flag recycling)
-//#define BOUNDARY_EXPRESSION // combinable with EQUILIBRIUM_BOUNDARIES xor MOVING_WALLS, !!!doesn't work on AMD for some reason!!!
+#define MOVING_WALLS // moving bounce-back boundaries
+//#define PRESSURE_WALLS // pressure boundaries
+//#define BOUNDARY_EXPRESSION // combinable with MOVING_WALLS, !!!doesn't work on AMD for some reason!!!
 
 #define VISCOELASTIC
-#define EQUILIBRIUM_STRESS // Include viscoelastic forces by shifting the equilibrium populations (Onishi 2005) instead of via force
-#define STRAIN_RATE_TENSOR_FROM_POP // If set, the strain rate tensor used for shuffling is calculated from the populations otherwise the one from the velocity gradient is used
 // Only one of the following models may be defined
 //#define OLDROYD_B
 //#define FENEP
 #define PTT // From Ferras 2019 eq (3) and (2) original PTT
+//#define CARREAU_YASUDA
 
 //#define IBM // immersed boundary method (### under construction ###)
[…]

### 2024-03-28 assets/setups/Nozzle/2/setup/setup.cpp

@@ -14,7 +14,7 @@ using std::regex, std::regex_match, std::smatch;
 #include <string>
 using std::stof, std::stoi, std::string;
 
-#include <fmt/core.h>
+#include <fmt/format.h>
 // using fmt::format
 using fmt::print;
 #include <fmt/color.h>
@@ -35,7 +35,7 @@ using fluidx3d::util::poiseuilleFlow::CircularPoiseuilleFlow;
 void example(SimulationOptions& options, Parameters& parameters) {
 	json raw = parameters.getRaw();
 	const int id = raw.at("id");
-	const string path_files = fmt::format("/tp6-gekle/nas/bt307867/cellsim/novel_2024-01-22/{}/", id);
+	const string path_files = fmt::format("/tp6-gekle/nas/bt307867/cellsim/novel_2024-03-26/{}/", id);
 	//const string path_files = fmt::format("Nozzle/{}/", id);
 	const path filesPath(path_files);
 	const string path_vtk = path_files + "vtkfiles/";
@@ -156,7 +156,7 @@ void example(SimulationOptions& options, Parameters& parameters) {
 		if(std::hypot(y - (Ly/2.) + 0.5, z - (Lz/2.) + 0.5) >= localR + 0.5) {
 			lattice.flags[n] = TYPE_W;
 		}else if(x == 0 || x == Lx-1) {
-			lattice.flags[n] = TYPE_W;
+			lattice.flags[n] = TYPE_VW;
 		} else {
 			lattice.flags[n] = TYPE_F; //TODO should be globally set  //TODO does not seem to be an issue??? Or is this messing with my sims?
 		}

### 2024-03-28 assets/python/fig:RT-DC.py
additional requirements

@@ -221,6 +221,23 @@ def process():
     plt.savefig("../plots/RT-DC_eta_cut.pdf", bbox_inches="tight", pad_inches=0)
     plt.show()
 
+    plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+    # plt.title("(c)", loc="left", pad=45, x=-0.11)
+    plt.imshow(
+        tau12.T,
+        cmap="coolwarm",
+        extent=[0, (Lx - 1) * L0 * 1e6, -Ly / 2 * L0 * 1e6, Ly / 2 * L0 * 1e6],
+    )
+    plt.xlabel(r"$x/\unit{\micro\meter}$")
+    plt.ylabel(r"$y/\unit{\micro\meter}$")
+    # plt.colorbar(location="top", label=r"$\tau_{12}/\unit{\pascal}$")
+    plt.gca().spines["top"].set_visible(False)
+    plt.gca().spines["right"].set_visible(False)
+    plt.savefig(
+        "../plots/RT-DC_tau_12_graphical_abstract.pdf", dpi=1200, bbox_inches="tight", pad_inches=0
+    )
+    plt.show()
+
 
 if __name__ == "__main__":
     t1 = time()

### 2024-03-28 NovelLBM.tex
shuffle error for different gamma dot
remove comment

@@
 		\caption{(a) The local viscosity determined by a shear flow simulation is in very good agreement with the semi-analytical theory.
-		(b) The error is negligibly small and independent of the shuffling parameter $\alpha_\text{s}$. Shown at \SI{1}{\per\second} and .}
+		(b) The error is negligibly small and independent of the shuffling parameter $\alpha_\text{s}$.}
 		\label{fig:wiParameterStudy}
-	\end{figure}\todo{1e5; maybe write this in legend}
+	\end{figure}
 
@@
 This indicates, that the observed difference might be due to the Mach number changing for different $\alpha_\text{s}$ and not due to the shuffling itself.
-This is due lower $\alpha_\text{s}$ leading to lower LBM viscosities and such to higher Mach numbers.
-\SG{ is this planar or cylindrical?
-}\RK{done}}
+This is due lower $\alpha_\text{s}$ leading to lower LBM viscosities and such to higher Mach numbers.}
 		\label{fig:ShuffleInPoiseuille}

### 2024-04-09 NovelLBM.tex
add corresponding author and smuggle in orcid

@@
 \addbibresource{assets/bib/bib.bib}
+
+\usepackage{orcidlink}
 
@@
 \title{Novel lattice Boltzmann method for simulation of strongly shear thinning viscoelastic fluids}
-\author{Richard Kellnberger$^1$, Tomasz Jüngst$^2$, Stephan Gekle$^1$}
+\author{Richard Kellnberger$^{1\dagger}$\orcidlink{0009-0003-1782-4735}, Tomasz Jüngst$^2$, Stephan Gekle$^1$\orcidlink{0000-0001-5597-1160}}
 \date{\today}
@@
 		$^2$ Department of Functional Materials in Medicine and Dentistry Institute of Functional Materials and Biofabrication (IFB) and KeyLab Polymers for Medicine of the Bavarian Polymer Institute (BPI) Universität Würzburg, Würzburg, Germany
+	\end{center}
+	\begin{center}
+		$^\dagger$ Corresponding author. Email: \href{mailto:Richard.Kellnberger@uni-bayreuth.de}{Richard.Kellnberger@uni-bayreuth.de}
 	\end{center}

### 2024-06-11 assets/responseToReview.txt
prepare answers to reviewers

Note: equation numbers refer to old numbering (numbers have shifted due to expanded description of LBM and FV)

Reviewer 1:

-What are the parameters η_0 and η_∞ appeared in Eq. (7)?

Zero-shear viscosity and infinite-shear viscosity as stated in the sentence following eq. (7).

-Please provide more details on the elements of the lattice Boltzmann method, for instance, lattice model considered in this work, the discrete velocities and the equilibrium populations.

Assuming "latticel model" refers to the velocity set: We use D3Q19 (see 4.1), otherwiese please elaborate.
# TODO the velocities and eqilibrium populations can be found on wikipedia

-The authors should provide the relation between the relaxation time and viscosity appeared in first term on the right-hand side of Eq. (12). In addition, if Eq. (12) is considered, should the term B_i given by Eq. (9) be modified?

# TODO The only reason you ask this is because you know the answer, so why write it down?
Eq (12) described that \tau is modified, this has implications for eq (9), to reduce ambiguity we intrudced a \prime into the notation and qonsequently Eq (9) has been (slightly) modified and the text below has been expanded for clarity. A reference to \tau^\prime has been introduced below eq (12) as well

-Is the relaxation time τ_r=1 adopted in numerical simulations?

Yes, see 4.1

-Why is the finite-volume method adopted for polymer stress? Please give some details on the finite-volume method. In addition, it is known that in the lattice Boltzmann method, the square or cubic lattice is adopted, and thus the finite-difference method seems a better choice?

# TODO Why not?
# TODO What details on the finite volume method are you missing?
Finite difference is a lot harder to implement, requires more compute, has a lot more loose ends to tie and is a lot less stable. Why would I ever do this?

-As seen from Fig. 4, there is an apparent difference between the numerical results and semi-analytical solution, especially in the center part of the channel. Please give some explanations on this point.

As can be seen from Fig. 3 this descrapency is only present in 3D. As the 2D case was simulated using the same algorithm technically also in 3D (periodic on the extra axis), the only difference between the simulations is the geometry. The error is actually largest on the walls (see figure 14). As stated between figure 3 and 4, the approximation of a round channel using a cubic lattice introduces a staircase-effect resulting in significant error near the walls. These errors of course propagate to the center.

-In the framework of lattice Boltzmann method, the multiple-relaxation-time (MRT) model can be considered to improve the numerical stability. Can MRT model be adopted in this work to overcome the numerical instability problem?

MRT gets a lot more credit than it deserves. If tuned for a specific problem it can marginally improve stability. The stability issues discussed in the present work arise at R_\eta between 1 and 10, for realistic fluids we need to reach nearly 50k (alignate). MRT might be able to help if the algorithm is nearly stable anyway. For the issue presented here the classical approach is no where near stable. We do have MRT implemented and can switch it on with a single flag. We practically never do, because it is generally not worth the overhead.

Reviewer 2:

(1)The introduction is too simple. The development of LBM for simulating viscoelastic fluids is not reviewed thoroughly.

# TODO this is physics and not a history lecture -> Delegated to Stephan

(2) The numerical method should be given in detail and in a logical way. Section 4.1 does not given in detail of the LBM. Section 4.2 tries to show the finite-volume method for polymer stress but only presents the LBM for the flow field, which is incorrect. The finite volume method for the polymer stress is actually missing.

# TODO The present work describes an extension to the LBM and as such only describes the part relevant to these extensions. Otherwise we refer to the literature.
You seem to suggest, that the stated LBM equation is incorrect please elaborate.
# TODO The finite volume method is actually fully described (without the use of a single equation)

(3) In the validation part, the computational steps needs 2×10^9 for the simple 1D flow. The efficiency of the proposed method is really low. This is not acceptable for 3D simulations.

There is no 1D flow in the present work. In the section you are referring to alginate was simulated for 2e9 steps in 2D and 3D. The "not acceptable" 3D simulation took 1d 8h on a gaming GPU from 2019.

Runtime being inversly proportional to Re is an issue of LBM and not related to our method in particular. It can be addressed using Re scaling if one wishes to.

(4) Validations and applications in 3D cases should be presented since authors claim to fill the gap in the abstract.

Aside from figures 3 and 5, which are specifically stated to be planer, the whole paper is 3D.
Technically even those two where calculated in 3D with an periodic axis with translational symmetry in order to be able to use the same velocity set for all simulations as stated in 4.1:
"We use a D3Q19 lattice in full three dimensions together with a single relaxation time collision operator."

### 2024-06-11 NovelLBM.tex
prepare answers to reviewers

@@
 \newcommand{\SG}[1]{{\color{red}SG: #1}}
+\newcommand{\RR}[1]{{\color{orange}#1}} % review revision
 
@@
 \begin{equation}
-	B_i = w_i\left(\frac{\vec{c}_i\vec{c}_i}{2c_\text{s}^4}-\frac{\uT}{2c_\text{s}^2}\right):\ma{\tau}.
+	B_i = w_i\left(\frac{\vec{c}_i\vec{c}_i}{2c_\text{s}^4}-\frac{\uT}{2c_\text{s}^2}\right):\ma{\tau\RR{^\prime}}.
 \end{equation}
-Here, $w_i$ are the lattice weights, $c_\text{s}$ is the lattice speed of sound and $\ma{\tau}$ is the polymer stress tensor. The colon denotes the Frobenius inner product.
+Here, $w_i$ are the lattice weights, $c_\text{s}$ is the lattice speed of sound and $\ma{\tau\RR{^\prime}}$ is the \RR{stress tensor to be coupled into the LBM.
+In the case of viscoelastic fluids this typically is the} polymer stress tensor.
+\RR{For our method this tensor is modified as described in the following section.
+}The colon denotes the Frobenius inner product.
 To handle inflow/outflow boundaries, the polymer conformation tensor is specified on the boundary and advected using the corner transport upwind scheme.
@@
 The LBM solver is run with $\eta_\text{s} + \alpha_\text{s}\eta_\text{p}$ as its viscosity.
-The polymer stress determined by equation~\ref{eq:polymerStress} is reduced by the amount $2\alpha_\text{s}\eta_\text{p}\ma{D}$ at every time step before it is coupled into the LBM.
+The polymer stress determined by equation~\ref{eq:polymerStress} is reduced by the amount $2\alpha_\text{s}\eta_\text{p}\ma{D}$ at every time step before \RR{$\ma{\tau^\prime} = \ma{\tau} - 2\alpha_\text{s}\eta_\text{p}\ma{D}$} is coupled into the LBM.
 

### 2024-06-17 assets/responseToReview.txt
LBM basics appendix

@@
 Assuming "latticel model" refers to the velocity set: We use D3Q19 (see 4.1), otherwiese please elaborate.
-# TODO the velocities and eqilibrium populations can be found on wikipedia
+Discrete velocities and equilibrium populations have been added to a new appendix linked from 4.1
 
@@
 
-# TODO The only reason you ask this is because you know the answer, so why write it down?
+As mentioned below eq (12) this viscosity is used for the LBM solver, therefore the standard LBM relation (see new appendix) applies to this viscosity.
 Eq (12) described that \tau is modified, this has implications for eq (9), to reduce ambiguity we intrudced a \prime into the notation and qonsequently Eq (9) has been (slightly) modified and the text below has been expanded for clarity.

### 2024-06-17 NovelLBM.tex
LBM basics appendix

@@
 \usepackage{amsmath}
+\setcounter{MaxMatrixCols}{20} % Allow bigger matrices
 \usepackage{amssymb}
@@
 
-The Lattice-Boltzmann method (LBM) has become a standard tool in numerical fluid mechanics \cite{Kruger_book}, and we therefore describe it here only very briefly.
+The Lattice-Boltzmann method (LBM) has become a standard tool in numerical fluid mechanics \cite{Kruger_book}, and we therefore \RR{only mention the key choices here.
+Further details can be found in the appendix~\ref{app:LBM} or in literature.}
 We use a D3Q19 lattice in full three dimensions together with a single relaxation time collision operator.
@@
 
+	\RR{
+	\section{Basics of Lattice-Boltzmann}\label{app:LBM}
+	An excellent overview on Lattice-Boltzmann methods (LBM) can be found in the book by Krüger et al.
+on the subject \cite{Kruger_book}.
+Our implementation of the base algorithm mostly follows the book, though some implementation details differ.
+We mention the most important basics of LBM here and recommend the book for further reading.
+	Instead of solving the Navier-Stokes equation LBM solves the Boltzmann equation which is a generalization.
+The Boltzmann equation is discretized both in space $\vec{x}$ and time $t$.
+Also, the velocity is limited to discrete values $\vec{c}_i$, the so-called velocity sets.
+The velocity sets are usually denoted as D$d$Q$q$, with $d$ being the number of dimensions and $q$ being the number of discrete velocities.
+The density is split into the so-called populations $f_i\left(\vec{x}, t\right)$, which are parts of the density moving along a certain discrete velocity at a certain discrete point in time at a certain discrete point in space.
+With these discretizations the equation reads as follows.
+	\begin{equation}
+		f_i\left(\vec{x}+\vec{c}_i\Delta t, t+\Delta t\right) = f_i\left(\vec{x}, t\right) + \Omega_i\left(\vec{x}, t\right)
+	\end{equation}
+	Here $\Delta t$ is the duration of a time step (distance between the discrete points in time) and $\Omega_i\left(\vec{x}, t\right)$ is the collision operator.
+The equation describes the populations moving along the discrete velocities to a neighboring point (streaming) while exchanging momentum modeled by the collision operator (collision).
+The collision operator redistributes the populations, that meet at any given lattice point.
+This is highly complex and is therefore usually approximated using the Bhatnagar-Gross-Krook (BGK) operator, which reads as follows.
+	\begin{equation}
+		\Omega_i = - \frac{f_i - f_i^\text{eq}}{\tau_\text{r}}\Delta t
+	\end{equation}
+	Here $\tau_\text{r}$ is the relaxation time and $f_i^\text{eq}$ are the equilibrium populations defined as follows.
+	\begin{equation}
+		f_i^\text{eq} = w_i\rho\left[1 + \frac{\vec{u}\cdot\vec{c_i}}{c_\text{s}^2} + \frac{\left(\vec{u}\cdot\vec{c_i}\right)^2}{2c_\text{s}^4} + \frac{\vec{u}\cdot\vec{u}}{2c_\text{s}^2}\right]
+	\end{equation}
+	Here $\vec{u}$ is the local fluid velocity, $\rho$ is the local density, $w_i$ are the lattice weights associated to the chosen velocity set and $c_\text{s}$ is the lattice speed of sound defined as follows.
+	\begin{equation}
+		c_\text{s}^2 = \frac{1}{3}\frac{\Delta x^2}{\Delta t^2}
+	\end{equation}
+	Here $\Delta x$ is the distance between two discrete lattice points.
+	The LBM equation with BGK therefore takes the shape of a relaxation towards equilibrium:
+	\begin{equation}
+		f_i\left(\vec{x}+\vec{c}_i\Delta t, t+\Delta t\right) - f_i\left(\vec{x}, t\right) = -\frac{\Delta t}{\tau_\text{r}}\left[f_i\left(\vec{x}, t\right) - f_i^\text{eq}\left(\vec{x}, t\right)\right].
+	\end{equation}
+	It should be noted, that this is the simple case for a Newtonian fluid.
+If additional (extern) forces are to be considered, additional terms are added on the right-hand side to account for these.
+For simple forces we use the algorithm presented by Guo et al.
+\cite{guo2002}.
+The following equations relate the discrete quantities back to the physical quantities.
+	\begin{align}
+		\rho &= \sum_if_i^\text{eq} = \sum_if_i \\
+		\rho\vec{u} &= \sum_i\vec{c}_if_i^\text{eq} = \sum_i\vec{c}_if_i \\
+		\frac{\eta}{\rho} &= c_\text{s}^2\left(\tau_\text{r} - \frac{\Delta t}{2}\right)
+	\end{align}
+	Here $\eta$ is the viscosity.
+These equations are typically solved in lattice units (LU).
+These result from fixing three values in LU and calculating conversion factors for all other units accordingly from these.
+The physical values are then divided by these scaling factors.
+This is mathematically identical to scaling the whole equation and can be used to simplify the calculations and to keep the values in a range optimal for computation.
+Typically, one picks $\rho_\text{LU} = 1$ and $\eta_\text{LU} = \frac{1}{6}$.
+Naturally $\Delta x_\text{LU} = 1$ and $\Delta t_\text{LU} = 1$.
+A convenient third scale is the resolution, meaning the relation of $\Delta x$ to the size of the system.
+The relaxation time can be freely chosen, but is ideal at unity in LU.
+	The LBM scheme with the BGK operator is called single relaxation time (SRT).
+There are generalizations for two relaxation times (TRT) and for one relaxation time per $i$ (multi relaxation time, MRT).
+We found the more complex schemes to rarely yield worthwhile improvement and stick to SRT.
+While there are multiple valid options we use D3Q19 as the velocity set.
+The 19 velocities and their weights are noted in the following.
+
+	\begin{equation}
+		\begin{split}
+			&\frac{\Delta t}{\Delta x}\vec{c}_i = \\
+			&\begin{Bmatrix}
+				0 & 1 & -1 & 0 & 0 & 0 & 0 & 1 & -1 & 1 & -1 & 0 & 0 & 1 & -1 & 1 & -1 & 0 & 0 \\
+				0 & 0 & 0 & 1 & -1 & 0 & 0 & 1 & -1 & 0 & 0 & 1 & -1 & -1 & 1 & 0 & 0 & 1 & -1 \\
+				0 & 0 & 0 & 0 & 0 & 1 & -1 & 0 & 0 & 1 & -1 & 1 & -1 & 0 & 0 & -1 & 1 & -1 & 1
+			\end{Bmatrix}
+		\end{split}
+	\end{equation}
+	Where each column is a vector.
+	\begin{equation}
+		w_i = \begin{cases}
+			\frac{1}{3},\quad i=0\\
+			\frac{1}{18},\quad 1 \leq i \leq 6\\
+			\frac{1}{36},\quad \text{otherwise}
+		\end{cases}
+	\end{equation}
+	}
+
 \end{document}

### 2024-06-18 assets/responseToReview.txt
FV wording

@@
-Note: equation numbers refer to old numbering (numbers have shifted due to expanded description of LBM and FV)
-
 Reviewer 1:
@@
 
-# TODO Why not?
-# TODO What details on the finite volume method are you missing?
-Finite difference is a lot harder to implement, requires more compute, has a lot more loose ends to tie and is a lot less stable. Why would I ever do this?
+Makes boundary conditions trivial (flux = 0); CTU (which is a FV scheme) has been reported to increase stability [Kuron]
+Added some more details to 4.2 how we use FV here.
+Finite difference is a lot harder to implement (boundary conditions), has a lot more loose ends to tie (to assure conservation for example) and is less stable.
 
@@
 
-# TODO The present work describes an extension to the LBM and as such only describes the part relevant to these extensions. Otherwise we refer to the literature.
-You seem to suggest, that the stated LBM equation is incorrect please elaborate.
-# TODO The finite volume method is actually fully described (without the use of a single equation)
+Added additional LBM section
+You seem to suggest, that the stated LBM equation is incorrect. Please elaborate.
+Added some more details to 4.2 how we use FV here.
 

### 2024-06-18 NovelLBM.tex
FV wording

@@
 We use a D3Q19 lattice in full three dimensions together with a single relaxation time collision operator.
-Our implementation is based on FluidX3D which has been extensively used and validated in earlier publications \cite{Lehmann.20229da}.
+Our implementation is based on FluidX3D which has been extensively used and validated in earlier publications \cite{lehmann2021, Lehmann.20229da}.
 The core of the algorithm is implemented in OpenCL and thus capable of running on GPUs from different vendors.
@@
 The spatio-temporal dynamics of the polymer stress $\ma{\tau}$ is given by equation~(\ref{eq:polymerStress}) in the form of an advection-reaction equation.
-We solve this equation by a finite-volume scheme running in parallel (with identical time step) to the LBM solver.
-Advection is handled using the corner transport upwind scheme \cite{kuron2021}.
-At the walls, a zero-flux boundary condition for the stress is used.
+We solve this equation by a finite-volume scheme running in parallel (with identical time step) to the LBM solver.\RR{ For this, the simulation volume is subdivided in $1\times1\times1$ (in LU) cubes centered around each lattice node.
+The average value of $\ma{\tau}$ within these volumes is takes as the value at the lattice node.}
+Advection is handled using the corner transport upwind scheme \cite{kuron2021}.\RR{ The remaining derivatives are calculated using finite differences.}
+At the walls\RR{, which coincide with the surfaces of the finite volumes}, a zero-flux boundary condition for the stress is used.
 The source terms are integrated using the Euler method.

### 2024-06-22 NovelLBM.tex
Updates to revision

@@
 LBM has also been extended to viscoelastic situations, mainly in two \cite{ispolatov2002,wang2019,su2013,giraud1998,xie2018,dzanic2022,frank2006,zou2014,lee2017,dzanic2022_2,sedaghat2021,frantziskonis2011,qin2023,yoshino2008,papenkort2015,phillips2011,onishi2005} but occasionally also in three \cite{malaspinas2010,gupta2015,gupta2015_2,lallemand2003,ma2020,onishi2006,wang2020,dellar2014,su2013_2,wang2021,kuron2021,gupta2016} dimensions.
+\RR{We will discuss these approaches in detail in section~\ref{sec:existingLBM} below.}
 To alleviate stability problems, some of these works include an artificial diffusivity of the polymer stress \cite{malaspinas2010,ma2020,wang2020,wang2021}, or perform special decompositions of the stress tensor \cite{dzanic2022}.
@@
 
-We introduce the ratio between the polymer and the solvent viscosity as
+We introduce the ratio between the polymer and the solvent viscosity \RR{and express it as a ratio between the viscosity at zero shear rate, $ \eta _0$, and the viscosity at infinite shear rate $ \eta _ \infty $}:
 \begin{align}
@@
 \section{Existing LBM methods}
+\label{sec:existingLBM}
 Since the early days of LBM, variants for viscoelastic fluids have been developed.
@@
 The average value of $\ma{\tau}$ within these volumes is takes as the value at the lattice node.}
-Advection is handled using the corner transport upwind scheme \cite{kuron2021}.\RR{ The remaining derivatives are calculated using finite differences.}
+Advection is handled using the corner transport upwind scheme \cite{kuron2021}. \SG{ add two phrases about CTU which somewhat non-standard }
+\RR{ The remaining derivatives are calculated using finite differences.} 
 At the walls\RR{, which coincide with the surfaces of the finite volumes}, a zero-flux boundary condition for the stress is used.
@@
 After \num{2e9} LBM time steps for alginate and \num{5e6} LBM time steps for methyl cellulose corresponding to approximately \SI{1.6}{\milli\second} and \SI{2.4}{\second} of physical time, respectively, the simulation is stopped and the flow field $u(y)$ is compared to the semi-analytical solution.
+\RR{An artificial increase of the Reynolds number to reduce computational time is possible in principle, but is not employed here to bring out clearly the characteristics of our method.}
 As shown in figure~\ref{fig:2Dvel}, very good agreement is found.
@@
 
-Our next example is the RT-DC geometry in which cells from a reservoir are squeezed through a narrow observation channel \cite{Toepfner.2018, Fregin:2019gx} with a square cross-section of \qtyproduct{40x40}{\micro\meter}.
+Our next example is the RT-DC geometry in which cells from a reservoir are squeezed through a narrow observation channel \cite{Toepfner.2018, Fregin:2019gx} with a square cross-section of %\qtyproduct{40x40}{\micro\meter}.
 %$\SI{40}{\micro\meter} \times \SI{40}{\micro\meter}$.%Correctly typeset version, that compiles for Stephan.
@@
 	\RR{
-	\section{Basics of Lattice-Boltzmann}\label{app:LBM}
-	An excellent overview on Lattice-Boltzmann methods (LBM) can be found in the book by Krüger et al.
-on the subject \cite{Kruger_book}.
-Our implementation of the base algorithm mostly follows the book, though some implementation details differ.
+	\section{Lattice-Boltzmann Implementation}\label{app:LBM}
+	An excellent overview on Lattice-Boltzmann methods (LBM) can be found in the book by Krüger et al. on the subject \cite{Kruger_book}. 
+	Our implementation mostly follows the book, though some implementation details differ. 
 	We mention the most important basics of LBM here and recommend the book for further reading.
-	Instead of solving the Navier-Stokes equation LBM solves the Boltzmann equation which is a generalization.
+	Instead of solving the Navier-Stokes equation LBM solves the Boltzmann equation for fluid particle distributions. 
 	The Boltzmann equation is discretized both in space $\vec{x}$ and time $t$. 
@@
 	The density is split into the so-called populations $f_i\left(\vec{x}, t\right)$, which are parts of the density moving along a certain discrete velocity at a certain discrete point in time at a certain discrete point in space.
-With these discretizations the equation reads as follows.
+	With these discretizations the Boltzmann equation reads as follows.
 	\begin{equation}
@@
 	It should be noted, that this is the simple case for a Newtonian fluid. 
-If additional (extern) forces are to be considered, additional terms are added on the right-hand side to account for these.
-For simple forces we use the algorithm presented by Guo et al.
-\cite{guo2002}.
+	If additional (external) forces are to be considered, additional terms are added on the right-hand side to account for these. 
+	For simple forces we use the algorithm presented by Guo et al. \cite{guo2002}.  \SG{ what are ''simple forces''? }
 	The following equations relate the discrete quantities back to the physical quantities.

### 2024-06-22 responses/Response1.tex
Updates to revision

\documentclass[12pt,a4paper, onesided]{article}
% !TeX program=pdflatex
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[ngerman,american]{babel}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{xcolor}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{Submission ID \SG{ to fill }}
\rfoot{\thepage}
\setlength\parindent{0pt}

\newcommand{\SG}[1]{{\color{red}SG:~#1}}
\newcommand{\SJM}[1]{{\color{orange}SM:~#1}}
\newcommand{\SW}[1]{{\color{purple}SW:~#1}}

\newcommand*{\referee}[1]{%
    \small
    \begin{quote} 
        \textsf{#1}
    \end{quote}
    \normalsize
}

\begin{document}
\section*{Response to Referee 1}

\referee{What are the parameters $\eta_0$ and $\eta_ \infty $ appeared in Eq. (7)?}

The parameters $ \eta _0$ and $ \eta _ \infty $ are the viscosities predicted by the model for zero and  and infinite shear rates, respectively.
We now mention this just before Eq. (7).

\referee{Please provide more details on the elements of the lattice Boltzmann method, for instance, lattice model considered in this work, the discrete velocities and the equilibrium populations.}

We have added a new appendix E where we discuss the LB method in general as well as our specific implementation details. 
\SG{der Appendix ist an sich ok, aber sollte noch frueher und deutlicher auf unsere Implementierung eingehen, z.B. D3Q19 bereits dort erwähnen, wo du auf velocity sets eingehst. Beim Guo forcing konkret sagen, wofuer wir es verwenden (''simple forces'' ist hier zu vage). Bei der Dichte und der Viskositaet ist es nicht so wichtig, was man ''typically'' nimmt, sondern was du konkret in deinen Simulationen genommen hast. }

\referee{The authors should provide the relation between the relaxation time and viscosity appeared in first term on the right-hand side of Eq. (12). In addition, if Eq. (12) is considered, should the term $B_i$ given by Eq. (9) be modified?}

As mentioned below eq (12) this viscosity is used for the LBM solver, therefore the standard LBM relation (see new appendix) applies to this viscosity.
To reduce ambiguity between equations (9) and (12), we introduced a prime into the notation and consequently Eq (9) has been (slightly) modified and the text below has been expanded for clarity. 
A reference to $\tau^\prime$ has been introduced below eq (12) as well.

\referee{Is the relaxation time $\tau_r=1$ adopted in numerical simulations?}

Yes, as we now mention in the new appendix E.

\referee{Why is the finite-volume method adopted for polymer stress? Please give some details on the finite-volume method. In addition, it is known that in the lattice Boltzmann method, the square or cubic lattice is adopted, and thus the finite-difference method seems a better choice?}

Our choice of the finite-volume method is motivated primarily by its clarity and simplicity when implementing complex boundary conditions.
Furthermore, the finite-volume method matches well with the so-called corner-transport-upwind (CTU) scheme which we use for advection and for which earlier works \SG{ give ref of Kuron } reported increased stability.
To make these points clearer to the reader, we added many corresponding details to section 4.2 of the revised manuscript.
%Finite difference is a lot harder to implement (boundary conditions), has a lot more loose ends to tie (to assure conservation for example) and is less stable.

\referee{As seen from Fig. 4, there is an apparent difference between the numerical results and semi-analytical solution, especially in the center part of the channel. Please give some explanations on this point.}

As in most LBM simulations, an important source of error is the discretisation of the boundary.
When discretising a physically round boundary such as the cylinder in figure 4 on a cubic lattice, the boundary shape necessarily becomes imprecise - the so-called ''staircase'' effect.
As can be seen in figure 14, the relative error is indeed largest near the wall.
We therefore explain the - apparently - large error in the center in figure 4 by a propagation of discretisation errors into the fluid.

%As can be seen from Fig. 3 this discrepancy is only present in 3D. 
%As the 2D case was simulated using the same algorithm technically also in 3D (periodic on the extra axis), the only difference between the simulations is the geometry. 
%The error is actually largest on the walls (see figure 14). 
%As stated between figure 3 and 4, the approximation of a round channel using a cubic lattice introduces a staircase-effect resulting in significant error near the walls. 
%These errors of course propagate to the center.

\referee{In the framework of lattice Boltzmann method, the multiple-relaxation-time (MRT) model can be considered to improve the numerical stability. Can MRT model be adopted in this work to overcome the numerical instability problem?}

\SG{ Die Antwort geht so nicht, es geht hier nicht um eine Grundsatzdikussion zu MRT sondern um eine konkrete Frage zu unserem System.
Es gibt drei Moeglichkeiten zur Antwort:

(i) Wir bedanken uns artig für den Vorschlag und sagen, dass wir es in Zukunft ausprobieren werden, aber dass es für diese Arbeit zu weit fuehrt.

(ii) Wir sagen, dass MRT hier nichts nuetzt. Dann brauchen wir aber konkrete Belege dafuer. Fuer welche Systeme wurde MRT ausprobiert? Was war der Effekt? Konnte die Stabilitaet fuer den klassischen Ansatz ohne viscosity shuffling durch MRT verbessert werden?

(iii) Wir argumentieren, dass andere in der Literatur MRT benutzt haben und dass es dort auch nichts gebracht hat. Deswegen machen wir uns nicht die Muehe, es auszuprobieren.

Man kann die Varianten auch kombinieren. Kannst du zu (ii) und (iii) mal raussuchen, was da der Stand ist?}

%MRT gets a lot more credit than it deserves.
%If tuned for a specific problem it can marginally improve stability. 
%The stability issues discussed in the present work arise at $R_\eta$ between 1 and 10, for realistic fluids we need to reach nearly 50k (alignate). 
%MRT might be able to help if the algorithm is nearly stable anyway. 
%For the issue presented here the classical approach is no where near stable. 
%We do have MRT implemented and can switch it on with a single flag. 
%We practically never do, because it is generally not worth the overhead.

\end{document}

### 2024-06-22 responses/Response2.tex
Updates to revision

\documentclass[12pt,a4paper, onesided]{article}
% !TeX program=pdflatex
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[ngerman,american]{babel}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{xcolor}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{Submission ID \SG{ to fill }}
\rfoot{\thepage}
\setlength\parindent{0pt}

\newcommand{\SG}[1]{{\color{red}SG:~#1}}
\newcommand{\SJM}[1]{{\color{orange}SM:~#1}}
\newcommand{\SW}[1]{{\color{purple}SW:~#1}}

\newcommand*{\referee}[1]{%
    \small
    \begin{quote} 
        \textsf{#1}
    \end{quote}
    \normalsize
}

\begin{document}
\section*{Response to Referee 2}

\referee{The introduction is too simple. The development of LBM for simulating viscoelastic fluids is not reviewed thoroughly.}

Indeed, the introduction gives only a very brief summary of existing LBM schemes for viscoelastic fluids.
A detailed discussion of these approaches is given in section~3. 
Our motivation for shifting the discussion from the introduction (which, we agree with the referee, would be the canonical place) to the main text is that we want to give the reader the necessary background on viscoelastic models in section 2 before.
Having done so allows us a more thorough and more comprehensible discussion of the ensuing LBM schemes.

We have added a reference to section 3 in the introduction to avoid misunderstandings in the revised version.

\referee{The numerical method should be given in detail and in a logical way. Section 4.1 does not given in detail of the LBM. Section 4.2 tries to show the finite-volume method for polymer stress but only presents the LBM for the flow field, which is incorrect. The finite volume method for the polymer stress is actually missing.}

Following the comment of the referee, we have added an entire new section (appendix E) where we give details about the LB method in general as well as our implementation in particular.
In addition, we have extended section 4.2. where we present the finite-volume method that we use for the polymer stress.

\referee{In the validation part, the computational steps needs $2 \cdot 10^9$ for the simple 1D flow. The efficiency of the proposed method is really low. This is not acceptable for 3D simulations.}

We agree with the referee that the number of $2 \cdot 10^9$ time steps may appear rather large in the first place.
However, LBM schemes can be implemented in an extremely efficient manner, especially using GPUs (note that our code, both the LBM and the finite-volume part, is entirely GPU-based).
The longest simulation presented in the manuscript which is for a fully 3D cylindrical flow took 1 day and 8 hours on a five-year old gaming GPU.

That said, the referee is right that highly viscous fluids such as, in particular, the alginate solution considered in this work, are a challenge to all LBM schemes.
We hypothesize that this is one of the reasons why such highly viscous complex fluids have been simulated with LBM before.
A possible remedy which may be considered in future work is the so-called Reynolds scaling.
Herein, the Reynolds number of the flow is artificially increased which decreases the LBM runtime without modifying the physical flow field as long as Re remains (much) smaller than 1.
We now mention this possibility above Eq. (13) in the manuscript.

\referee{Validations and applications in 3D cases should be presented since authors claim to fill the gap in the abstract.}

Aside from figures 3 and 5, which are planar geometries, all our systems are fully 3D.
This includes the cylindrical flow in figure 4. 
Even more important, it includes the RT-DC geometry shown in figure 7 and the fully three-dimensional cell in figure 8.
To bring out more clearly the latter aspect, we have added to figure 8 an illustration of our simulated system \SG{ denote current figure as 8b, and add a standard 3D Paraview picture as 8a. }

\end{document}

### 2024-06-22 NovelLBM.tex
fix whitespace

@@
 
-Our next example is the RT-DC geometry in which cells from a reservoir are squeezed through a narrow observation channel \cite{Toepfner.2018, Fregin:2019gx} with a square cross-section of %\qtyproduct{40x40}{\micro\meter}.
+Our next example is the RT-DC geometry in which cells from a reservoir are squeezed through a narrow observation channel \cite{Toepfner.2018, Fregin:2019gx} with a square cross-section of \qtyproduct{40x40}{\micro\meter}.
 %$\SI{40}{\micro\meter} \times \SI{40}{\micro\meter}$.%Correctly typeset version, that compiles for Stephan.

### 2024-06-22 NovelLBM.tex
comments in main doc

@@
 The average value of $\ma{\tau}$ within these volumes is takes as the value at the lattice node.}
-Advection is handled using the corner transport upwind scheme \cite{kuron2021}. \SG{ add two phrases about CTU which somewhat non-standard }
+Advection is handled using the corner transport upwind scheme\RR{ (CTU)} \cite{kuron2021}.\RR{ CTU considers the finite volume cell to be virtually displaced by $\vec{u}\Delta t$, where $\vec{u}$ is the local velocity and $\Delta t$ is the size of a time step.
+The resulting overlap with the neighboring cells (as a fraction of the cell volume) dictates what percentage of the polymer stress currently located at the cell is advected to the respective neighbor.
+This scheme prevents checkerboard instabilities.} \SG{ add two phrases about CTU which somewhat non-standard }\RK{done}
 \RR{ The remaining derivatives are calculated using finite differences.}
@@
 	If additional (external) forces are to be considered, additional terms are added on the right-hand side to account for these.
-	For simple forces we use the algorithm presented by Guo et al. \cite{guo2002}.  \SG{ what are ''simple forces''? }
+	For forces we use the algorithm presented by Guo et al. \cite{guo2002}.  \SG{ what are ''simple forces''? }\RK{as opposed to stresses which are generalized forces. -> removed the "simple"}
 	The following equations relate the discrete quantities back to the physical quantities.

### 2024-06-22 NovelLBM.tex
review1

@@
 	The velocity sets are usually denoted as D$d$Q$q$, with $d$ being the number of dimensions and $q$ being the number of discrete velocities.
+	We use D3Q19. Its 19 velocities can be found in equation~(\ref{eq:D3Q19c}).
 	The density is split into the so-called populations $f_i\left(\vec{x}, t\right)$, which are parts of the density moving along a certain discrete velocity at a certain discrete point in time at a certain discrete point in space.
@@
 	\end{equation}
-	Here $\vec{u}$ is the local fluid velocity, $\rho$ is the local density, $w_i$ are the lattice weights associated to the chosen velocity set and $c_\text{s}$ is the lattice speed of sound defined as follows.
+	Here $\vec{u}$ is the local fluid velocity, $\rho$ is the local density, $w_i$ are the lattice weights associated to the chosen velocity set (given in equation~(\ref{eq:D3Q19w}) for D3Q19) and $c_\text{s}$ is the lattice speed of sound defined as follows.
 	\begin{equation}
@@
 	If additional (external) forces are to be considered, additional terms are added on the right-hand side to account for these.
-	For forces we use the algorithm presented by Guo et al. \cite{guo2002}.  \SG{ what are ''simple forces''? }\RK{as opposed to stresses which are generalized forces. -> removed the "simple"}
+	For the forces used to drive the simple periodic flows and the forces from the IBM used to simulate cells, we use the algorithm presented by Guo et al.
+\cite{guo2002}.
+\SG{ what are ''simple forces''?
+}\RK{as opposed to stresses which are generalized forces.
+-> removed the "simple"}
 	The following equations relate the discrete quantities back to the physical quantities.
@@
 	This is mathematically identical to scaling the whole equation and can be used to simplify the calculations and to keep the values in a range optimal for computation.
-	Typically, one picks $\rho_\text{LU} = 1$ and $\eta_\text{LU} = \frac{1}{6}$.
+	We pick $\rho_\text{LU} = 1$ and $\eta_\text{LU} = \frac{1}{6}$ as is typically done.
 	Naturally $\Delta x_\text{LU} = 1$ and $\Delta t_\text{LU} = 1$.
-	A convenient third scale is the resolution, meaning the relation of $\Delta x$ to the size of the system.
+	A convenient third scale is the resolution, meaning the relation of $\Delta x$ to the size of the system, which we pick depending on the geometry.
 	The relaxation time can be freely chosen, but is ideal at unity in LU.
@@
 
-	\begin{equation}
+	\begin{equation}\label{eq:D3Q19c}
 		\begin{split}
@@
 	Where each column is a vector.
-	\begin{equation}
+	\begin{equation}\label{eq:D3Q19w}
 		w_i = \begin{cases}

### 2024-06-22 responses/Response1.tex
review1

@@
 \usepackage{lmodern}
-\usepackage[ngerman,american]{babel}
+\usepackage[american]{babel}
 
@@
 \newcommand{\SW}[1]{{\color{purple}SW:~#1}}
+\newcommand{\RK}[1]{{\color{cyan}RK: #1}}
+
+\usepackage[
+backend=bibtex,
+citestyle=numeric-comp,
+maxbibnames=10,
+sorting=none
+]{biblatex}
+\addbibresource{../assets/bib/bib.bib}
 
@@
 
-The parameters $ \eta _0$ and $ \eta _ \infty $ are the viscosities predicted by the model for zero and  and infinite shear rates, respectively.
-We now mention this just before Eq. (7).
+The parameters $\eta_0$ and $\eta_\infty$ are the viscosities predicted by the model for zero and infinite shear rates, respectively.
+We now mention this just before Eq. (7).\RK{Eigentlich beziehen sich die auf CY bzw. auf experimentelle Daten.}
 
@@
 Bei der Dichte und der Viskositaet ist es nicht so wichtig, was man ''typically'' nimmt, sondern was du konkret in deinen Simulationen genommen hast.
-}
+}\RK{Habe deine Beispiele übernommen}
 
@@
 Our choice of the finite-volume method is motivated primarily by its clarity and simplicity when implementing complex boundary conditions.
-Furthermore, the finite-volume method matches well with the so-called corner-transport-upwind (CTU) scheme which we use for advection and for which earlier works \SG{ give ref of Kuron } reported increased stability.
+Furthermore, the finite-volume method matches well with the so-called corner-transport-upwind (CTU) scheme which we use for advection and for which earlier works \cite{kuron2021}\SG{ give ref of Kuron }\RK{done} reported increased stability.
 To make these points clearer to the reader, we added many corresponding details to section 4.2 of the revised manuscript.
@@
 Man kann die Varianten auch kombinieren. Kannst du zu (ii) und (iii) mal raussuchen, was da der Stand ist?}
+\RK{
+(i) Der Vorschlag ist in etwa so sinnvoll wie vorzuschlagen unsere GPUs pink anzumalen und zu schauen ob das hilft.
+Da wir MRT ohnehin schon implementiert haben wäre das auch deutlich einfacher gewesen als das Zeug hier zu erfinden.
+Das führt also mit Nichten zu weit.
+Mir ist ein Rätsel wie du diese Antwort für eine echte Möglichkeit halten kannst.
+
+(ii) Wir haben es ausprobiert.
+Es hatte schon für die simpelsten Systeme keinerlei Effekt.
+Was auch wenig überraschend ist, denn wenn wir die Literatur mal eben nach Leuten durchsuchen die nicht nur nachplappern MRT würde die Stabilität verbessern sondern die raussuchen die dazu was konkretes zeigen (z.B.
+https://doi.org/10.1016/j.jnnfm.2011.01.002 https://ntrs.nasa.gov/api/citations/20020075050/downloads/20020075050.pdf), so stellen wir fest, dass die von Re = 100 und aufwärts reden.
+Bei MRT geht es um die Verbesserung der Stabilität zeigabhängiger bis turbulenter Strömungen.
+Das hat mit unserem Problem schlichtweg nichts zu tun, deshalb haben wir nie für irgendwas einen relevanten Effekt durch MRT gesehen.
+
+(iii) Die Literatur die wir zitieren (Dzanic) gibt sogar an, dass MRT für ihren klassischen Ansatz nicht angemessen ist weil nicht turbulent "Although the current LB solver
+uses the SRT model, which is appropriate for the
+current investigation [i.e., Re $\tilde{}$ O (1)], exten-
+sions to two-relaxation-time (TRT) and multiple-
+relaxation-time (MRT) models are easily applica-
+ble for the scheme in scenarios involving inertialess
+(Re << 1) or turbulent (Re >> 1e3 ) conditions."
+oder ganz allgemein zu MRT von Krüger:
+"However, the simplicity and efficiency of the lattice Boltzmann
+BGK collision operator comes at the cost of reduced accuracy (in particular for large
+viscosities) and stability (especially for small viscosities). Multiple-relaxation-time
+(MRT) collision operators offer a larger number of free parameters that can be tuned
+to overcome these problems."
+Die Literatur die wir zitieren (mit Ausnahme von Gupta) benutzt kein MRT (Kuron TRT rest SRT), weil MRT hier nichts verloren hat.
+Und Gupta rechtfertigt seine Verwendung auch nur mit "Ist besser, siehe paper das von hohen Re spricht" ohne das selbst für seinen Fall zu belegen.
+In unserem Literaturvergleich ist er der Schlechteste.
+
+Wenn du möchtest, können wir gerne schreiben "haben wir ausprobiert, bringt nichts" (ich wüsste aber nicht welche Belege wir hierfür liefern sollten/müssten, die Simulation ergibt so und so nan), aber ich halte diesen "Vorschlag" für nicht angemessen und will nicht riskieren, dass dem auch noch einfällt wir könnten die ganzen Parameter ja mal durchtunen.
+}
 
@@
 
+\printbibliography[heading=bibintoc]
+
 \end{document}

### 2024-06-23 responses/Response2.tex
review2

@@
 \newcommand{\SW}[1]{{\color{purple}SW:~#1}}
+\newcommand{\RK}[1]{{\color{cyan}RK: #1}}
 
@@
 However, LBM schemes can be implemented in an extremely efficient manner, especially using GPUs (note that our code, both the LBM and the finite-volume part, is entirely GPU-based).
-The longest simulation presented in the manuscript which is for a fully 3D cylindrical flow took 1 day and 8 hours on a five-year old gaming GPU.
+The longest simulation presented in the manuscript which is for a fully 3D cylindrical flow took 1 day and 8 hours on a five-year old gaming GPU.\RK{Wohlgemerkt war das der 3D Poisueille fürs Alginat (was das eigentliche Problem ist, das RT-DC mesh ist viel größer, haben wir aber mit MC gerechnet, hat 40 Minuten gedauert).
+Für die MC hat der 3D Poiseuille nicht ganz 5 Minuten gedauert.}
 
 That said, the referee is right that highly viscous fluids such as, in particular, the alginate solution considered in this work, are a challenge to all LBM schemes.
-We hypothesize that this is one of the reasons why such highly viscous complex fluids have been simulated with LBM before.
+We hypothesize that this is one of the reasons why such highly viscous complex fluids have been simulated with LBM before.\RK{Fehlt da ein not?
+Ist dann inhaltlich aber auch falsch, weil Re scaling.
+Es wurde nicht simuliert weil nicht stabil}
 A possible remedy which may be considered in future work is the so-called Reynolds scaling.
@@
 Even more important, it includes the RT-DC geometry shown in figure 7 and the fully three-dimensional cell in figure 8.
-To bring out more clearly the latter aspect, we have added to figure 8 an illustration of our simulated system \SG{ denote current figure as 8b, and add a standard 3D Paraview picture as 8a. }
+To bring out more clearly the latter aspect, we have added to figure 8 an illustration of our simulated system \SG{ denote current figure as 8b, and add a standard 3D Paraview picture as 8a.
+}\RK{Im Sinne von Bild von der deformierten Zelle?
+Oder meinst du ein anderes System wo man mehr sieht als einen unförmigen blob im nichts?}
 

### 2024-06-24 assets/python/fig:CellInShear.py
include cell render

@@ -95,6 +95,7 @@ def process():
     plt.show()
 
     plt.figure(figsize=(15.5 * cm, 15.5 / 2 * cm))
+    plt.title("(b)", loc="left")
     plt.imshow(
         vonMiesesSlice.T,
         cmap="coolwarm",

### 2024-06-26 NovelLBM.tex
include cell render
update responses

@@
 LBM has also been extended to viscoelastic situations, mainly in two \cite{ispolatov2002,wang2019,su2013,giraud1998,xie2018,dzanic2022,frank2006,zou2014,lee2017,dzanic2022_2,sedaghat2021,frantziskonis2011,qin2023,yoshino2008,papenkort2015,phillips2011,onishi2005} but occasionally also in three \cite{malaspinas2010,gupta2015,gupta2015_2,lallemand2003,ma2020,onishi2006,wang2020,dellar2014,su2013_2,wang2021,kuron2021,gupta2016} dimensions.
-\RR{We will discuss these approaches in detail in section~\ref{sec:existingLBM} below.}
+We will discuss these approaches in detail in section~\ref{sec:existingLBM} below.
 To alleviate stability problems, some of these works include an artificial diffusivity of the polymer stress \cite{malaspinas2010,ma2020,wang2020,wang2021}, or perform special decompositions of the stress tensor \cite{dzanic2022}.
@@
 
-We introduce the ratio between the polymer and the solvent viscosity \RR{and express it as a ratio between the viscosity at zero shear rate, $ \eta _0$, and the viscosity at infinite shear rate $ \eta _ \infty $}:
+We introduce the ratio between the polymer and the solvent viscosity and express it as a ratio between the viscosity at zero shear rate, $\eta_0$, and the viscosity at infinite shear rate $\eta_\infty$:
 \begin{align}
@@
 
-The Lattice-Boltzmann method (LBM) has become a standard tool in numerical fluid mechanics \cite{Kruger_book}, and we therefore \RR{only mention the key choices here.
-Further details can be found in the appendix~\ref{app:LBM} or in literature.}
+The Lattice-Boltzmann method (LBM) has become a standard tool in numerical fluid mechanics \cite{Kruger_book}, and we therefore only mention the key choices here.
+Further details can be found in the appendix~\ref{app:LBM} or in literature.
 We use a D3Q19 lattice in full three dimensions together with a single relaxation time collision operator.
@@
 The spatio-temporal dynamics of the polymer stress $\ma{\tau}$ is given by equation~(\ref{eq:polymerStress}) in the form of an advection-reaction equation.
-We solve this equation by a finite-volume scheme running in parallel (with identical time step) to the LBM solver.\RR{ For this, the simulation volume is subdivided in $1\times1\times1$ (in LU) cubes centered around each lattice node.
-The average value of $\ma{\tau}$ within these volumes is takes as the value at the lattice node.}
-Advection is handled using the corner transport upwind scheme\RR{ (CTU)} \cite{kuron2021}.\RR{ CTU considers the finite volume cell to be virtually displaced by $\vec{u}\Delta t$, where $\vec{u}$ is the local velocity and $\Delta t$ is the size of a time step.
+We solve this equation by a finite-volume scheme running in parallel (with identical time step) to the LBM solver.
+For this, the simulation volume is subdivided in $1\times1\times1$ (in LU) cubes centered around each lattice node.
+The average value of $\ma{\tau}$ within these volumes is takes as the value at the lattice node.
+Advection is handled using the corner transport upwind scheme (CTU) \cite{kuron2021}.
+CTU considers the finite volume cell to be virtually displaced by $\vec{u}\Delta t$, where $\vec{u}$ is the local velocity and $\Delta t$ is the size of a time step.
 The resulting overlap with the neighboring cells (as a fraction of the cell volume) dictates what percentage of the polymer stress currently located at the cell is advected to the respective neighbor.
-This scheme prevents checkerboard instabilities.} \SG{ add two phrases about CTU which somewhat non-standard }\RK{done}
-\RR{ The remaining derivatives are calculated using finite differences.}
-At the walls\RR{, which coincide with the surfaces of the finite volumes}, a zero-flux boundary condition for the stress is used.
+This scheme prevents checkerboard instabilities.
+The remaining derivatives are calculated using finite differences.
+At the walls, which coincide with the surfaces of the finite volumes, a zero-flux boundary condition for the stress is used.
 The source terms are integrated using the Euler method.
@@
 \begin{equation}
-	B_i = w_i\left(\frac{\vec{c}_i\vec{c}_i}{2c_\text{s}^4}-\frac{\uT}{2c_\text{s}^2}\right):\ma{\tau\RR{^\prime}}.
-\end{equation}
-Here, $w_i$ are the lattice weights, $c_\text{s}$ is the lattice speed of sound and $\ma{\tau\RR{^\prime}}$ is the \RR{stress tensor to be coupled into the LBM.
-In the case of viscoelastic fluids this typically is the} polymer stress tensor.
-\RR{For our method this tensor is modified as described in the following section.
-}The colon denotes the Frobenius inner product.
+	B_i = w_i\left(\frac{\vec{c}_i\vec{c}_i}{2c_\text{s}^4}-\frac{\uT}{2c_\text{s}^2}\right):\ma{\tau^\prime}.
+\end{equation}
+Here, $w_i$ are the lattice weights, $c_\text{s}$ is the lattice speed of sound and $\ma{\tau^\prime}$ is the stress tensor to be coupled into the LBM.
+In the case of viscoelastic fluids this typically is the polymer stress tensor.
+For our method this tensor is modified as described in the following section.
+The colon denotes the Frobenius inner product.
 To handle inflow/outflow boundaries, the polymer conformation tensor is specified on the boundary and advected using the corner transport upwind scheme.
@@
 The LBM solver is run with $\eta_\text{s} + \alpha_\text{s}\eta_\text{p}$ as its viscosity.
-The polymer stress determined by equation~\ref{eq:polymerStress} is reduced by the amount $2\alpha_\text{s}\eta_\text{p}\ma{D}$ at every time step before \RR{$\ma{\tau^\prime} = \ma{\tau} - 2\alpha_\text{s}\eta_\text{p}\ma{D}$} is coupled into the LBM.
+The polymer stress determined by equation~\ref{eq:polymerStress} is reduced by the amount $2\alpha_\text{s}\eta_\text{p}\ma{D}$ at every time step before $\ma{\tau^\prime} = \ma{\tau} - 2\alpha_\text{s}\eta_\text{p}\ma{D}$ is coupled into the LBM.
 
@@
 After \num{2e9} LBM time steps for alginate and \num{5e6} LBM time steps for methyl cellulose corresponding to approximately \SI{1.6}{\milli\second} and \SI{2.4}{\second} of physical time, respectively, the simulation is stopped and the flow field $u(y)$ is compared to the semi-analytical solution.
-\RR{An artificial increase of the Reynolds number to reduce computational time is possible in principle, but is not employed here to bring out clearly the characteristics of our method.}
+An artificial increase of the Reynolds number to reduce computational time is possible in principle, but is not employed here to bring out clearly the characteristics of our method.
 As shown in figure~\ref{fig:2Dvel}, very good agreement is found.
@@
 		\centering
+		\adjincludegraphics[trim=0 0 0 0, clip, scale=0.15]{assets/images/cellInShear.png}
 		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/cellInShear_sigma_vM.pdf}
-		\caption{The von Mises stress around a cell in viscoelastic shear flow.}
+		\caption{Cell in viscoelastic shear flow. (a) The 3D shape of the deformed cell and (b) a 2D cross-section of the von Mises stress.}
 		\label{fig:cellInShear_vM}
@@
 
-	\RR{
 	\section{Lattice-Boltzmann Implementation}\label{app:LBM}
@@
 	If additional (external) forces are to be considered, additional terms are added on the right-hand side to account for these.
-	For the forces used to drive the simple periodic flows and the forces from the IBM used to simulate cells, we use the algorithm presented by Guo et al.
-\cite{guo2002}.
-\SG{ what are ''simple forces''?
-}\RK{as opposed to stresses which are generalized forces.
--> removed the "simple"}
+	For the forces used to drive the simple periodic flows and the forces from the IBM used to simulate cells, we use the algorithm presented by Guo et al. \cite{guo2002}.
 	The following equations relate the discrete quantities back to the physical quantities.
@@
 	\end{equation}
-	}
 

### 2024-06-26 responses/Response1.tex
update responses

--- 2024-06-22 responses/Response1.tex
@@
 \fancyhf{}
-\rhead{Submission ID \SG{ to fill }}
+\rhead{Submission ID FLD-24-0080}
 \rfoot{\thepage}
@@
 \newcommand{\SW}[1]{{\color{purple}SW:~#1}}
+\newcommand{\RK}[1]{{\color{cyan}RK: #1}}
+
+\usepackage[
+backend=bibtex,
+citestyle=numeric-comp,
+maxbibnames=10,
+sorting=none
+]{biblatex}
+\addbibresource{../assets/bib/bib.bib}
+
+\usepackage[locale=US]{siunitx}
+\sisetup{per-mode=fraction}
+\sisetup{separate-uncertainty=true}
 
@@
 We have added a new appendix E where we discuss the LB method in general as well as our specific implementation details.
-\SG{der Appendix ist an sich ok, aber sollte noch frueher und deutlicher auf unsere Implementierung eingehen, z.B.
-D3Q19 bereits dort erwähnen, wo du auf velocity sets eingehst.
-Beim Guo forcing konkret sagen, wofuer wir es verwenden (''simple forces'' ist hier zu vage).
-Bei der Dichte und der Viskositaet ist es nicht so wichtig, was man ''typically'' nimmt, sondern was du konkret in deinen Simulationen genommen hast.
-}
 
@@
 Our choice of the finite-volume method is motivated primarily by its clarity and simplicity when implementing complex boundary conditions.
-Furthermore, the finite-volume method matches well with the so-called corner-transport-upwind (CTU) scheme which we use for advection and for which earlier works \SG{ give ref of Kuron } reported increased stability.
+Furthermore, the finite-volume method matches well with the so-called corner-transport-upwind (CTU) scheme which we use for advection and for which earlier works \cite{kuron2021} reported increased stability.
 To make these points clearer to the reader, we added many corresponding details to section 4.2 of the revised manuscript.
@@
 
-\SG{ Die Antwort geht so nicht, es geht hier nicht um eine Grundsatzdikussion zu MRT sondern um eine konkrete Frage zu unserem System.
-Es gibt drei Moeglichkeiten zur Antwort:
-
-(i) Wir bedanken uns artig für den Vorschlag und sagen, dass wir es in Zukunft ausprobieren werden, aber dass es für diese Arbeit zu weit fuehrt.
-
-(ii) Wir sagen, dass MRT hier nichts nuetzt.
-Dann brauchen wir aber konkrete Belege dafuer.
-Fuer welche Systeme wurde MRT ausprobiert?
-Was war der Effekt?
-Konnte die Stabilitaet fuer den klassischen Ansatz ohne viscosity shuffling durch MRT verbessert werden?
-
-(iii) Wir argumentieren, dass andere in der Literatur MRT benutzt haben und dass es dort auch nichts gebracht hat. Deswegen machen wir uns nicht die Muehe, es auszuprobieren.
-
-Man kann die Varianten auch kombinieren. Kannst du zu (ii) und (iii) mal raussuchen, was da der Stand ist?}
+MRT is considered to improve numerical stability of time dependent or turbulent flow in high $Re$ cases \cite{dzanic2022, Kruger_book}, it is used for $Re = \num{100}$ \cite{chai2011} and above \cite{dhumieres2002}.
+As the problem discussed in the present work has very low $Re$, it would not be expected to improve stability here.
+Consequently, SRT is used by all authors we list in our literature overview except for Kuron et al.
+(TRT) \cite{kuron2021} and Gupta et al.
+(MRT) \cite{gupta2015}.
+Notably, while Gupta et al.
+use MRT their method achieves the lowest $max\left(R_\eta\right)$ in our overview.
+We do not want to imply, that MRT might be counterproductive here (Gupta et al.
+did not compare to SRT), but it is also clearly no remedy.
+That being said, given, that we have MRT implemented anyway, we of course tried it before coming up with the present algorithm and were not able to observe any improvement.
 

### 2024-06-26 responses/Response2.tex
update responses

@@
 Even more important, it includes the RT-DC geometry shown in figure 7 and the fully three-dimensional cell in figure 8.
-To bring out more clearly the latter aspect, we have added to figure 8 an illustration of our simulated system \SG{ denote current figure as 8b, and add a standard 3D Paraview picture as 8a.
-}\RK{Im Sinne von Bild von der deformierten Zelle?
-Oder meinst du ein anderes System wo man mehr sieht als einen unförmigen blob im nichts?}
+To bring out more clearly the latter aspect, we have added to figure 8 an illustration of our simulated system.
 

### 2024-06-27 NovelLBM.tex
Updates

@@
 Further details can be found in the appendix~\ref{app:LBM} or in literature.
-We use a D3Q19 lattice in full three dimensions together with a single relaxation time collision operator.
+We use a D3Q19 lattice in full three dimensions together with a single relaxation time (SRT) collision operator.
+\RR{Various tests with a multiple relaxation time (MRT) collision operator did not show significant differences.}
 Our implementation is based on FluidX3D which has been extensively used and validated in earlier publications \cite{lehmann2021, Lehmann.20229da}.

### 2024-06-27 responses/Response1.tex
Updates

@@
 
-The parameters $\eta_0$ and $\eta_\infty$ are the viscosities predicted by the model for zero and infinite shear rates, respectively.
-We now mention this just before Eq. (7).\RK{Eigentlich beziehen sich die auf CY bzw. auf experimentelle Daten.}
+The parameters $\eta_0$ and $\eta_\infty$ are the viscosities for zero and infinite shear rates, respectively.
+We now mention this just before Eq. (7).
 
@@
 As the problem discussed in the present work has very low $Re$, it would not be expected to improve stability here. 
-Consequently, SRT is used by all authors we list in our literature overview except for Kuron et al.
-(TRT) \cite{kuron2021} and Gupta et al.
-(MRT) \cite{gupta2015}.
+Consequently, SRT is used by all authors we list in our literature overview except for Kuron et al. (TRT) \cite{kuron2021} and Gupta et al. (MRT) \cite{gupta2015}. 
 Notably, while Gupta et al.
-use MRT their method achieves the lowest $max\left(R_\eta\right)$ in our overview.
-We do not want to imply, that MRT might be counterproductive here (Gupta et al.
-did not compare to SRT), but it is also clearly no remedy.
-That being said, given, that we have MRT implemented anyway, we of course tried it before coming up with the present algorithm and were not able to observe any improvement.
+use MRT their method achieves the lowest $max\left(R_\eta\right)$ in our overview, which leads us to believe that MRT does not lead to stability improvement for low Reynolds viscoelastic situations such as ours.
+
+To confirm the above hints from the literature, we have done ourselves some tests with MRT (which is implemented in our code) but could not find any stability improvement. 
+We now mention this in the revised manuscript in section 4.1.
 

### 2024-06-27 responses/Response2.tex
Updates

--- 2024-06-22 responses/Response2.tex
@@
 The longest simulation presented in the manuscript which is for a fully 3D cylindrical flow took 1 day and 8 hours on a five-year old gaming GPU.
+%\RK{Wohlgemerkt war das der 3D Poisueille fürs Alginat (was das eigentliche Problem ist, das RT-DC mesh ist viel größer, haben wir aber mit MC gerechnet, hat 40 Minuten gedauert).
+Für die MC hat der 3D Poiseuille nicht ganz 5 Minuten gedauert.}
 
 That said, the referee is right that highly viscous fluids such as, in particular, the alginate solution considered in this work, are a challenge to all LBM schemes.
-We hypothesize that this is one of the reasons why such highly viscous complex fluids have been simulated with LBM before.
+%We hypothesize that this is one of the reasons why such highly viscous complex fluids have not been simulated with LBM before.\RK{Fehlt da ein not?
+Ist dann inhaltlich aber auch falsch, weil Re scaling.
+Es wurde nicht simuliert weil nicht stabil}
 A possible remedy which may be considered in future work is the so-called Reynolds scaling.
@@
 Even more important, it includes the RT-DC geometry shown in figure 7 and the fully three-dimensional cell in figure 8.
-To bring out more clearly the latter aspect, we have added to figure 8 an illustration of our simulated system \SG{ denote current figure as 8b, and add a standard 3D Paraview picture as 8a. }
+To bring out more clearly the latter aspect, we have added to figure 8 an illustration of our simulated system.
 

### 2024-06-27 NovelLBM.tex
final coloring

--- 2024-06-26 NovelLBM.tex
@@
 Further details can be found in the appendix~\ref{app:LBM} or in literature.
-We use a D3Q19 lattice in full three dimensions together with a single relaxation time collision operator.
+We use a D3Q19 lattice in full three dimensions together with a single relaxation time (SRT) collision operator.
+Various tests with a multiple relaxation time (MRT) collision operator did not show significant differences.
 Our implementation is based on FluidX3D which has been extensively used and validated in earlier publications \cite{lehmann2021, Lehmann.20229da}.
